### 2014-01-25 ECCV/paper.tex
Initial commit

% last updated in April 2002 by Antje Endemann
% Based on CVPR 07 and LNCS, with modifications by DAF, AZ and elle, 2008 and AA, 2010, and CC, 2011

\documentclass[runningheads]{llncs}
\usepackage{graphicx}
\usepackage{amsmath,amssymb} % define this before the line numbering.
\usepackage{ruler}
\usepackage{color}
\usepackage[width=122mm,left=12mm,paperwidth=146mm,height=193mm,top=12mm,paperheight=217mm]{geometry}
\begin{document}
% \renewcommand\thelinenumber{\color[rgb]{0.2,0.5,0.8}\normalfont\sffamily\scriptsize\arabic{linenumber}\color[rgb]{0,0,0}}
% \renewcommand\makeLineNumber {\hss\thelinenumber\ \hspace{6mm} \rlap{\hskip\textwidth\ \hspace{6.5mm}\thelinenumber}}
% \linenumbers
\pagestyle{headings}
\mainmatter
\def\ECCV12SubNumber{***}  % Insert your submission number here

\title{Design of Blur Invariant Fiducial for Low Cost Quadcopter} % Replace
% with your title

\titlerunning{ECCV-12 submission ID \ECCV12SubNumber}

\authorrunning{ECCV-12 submission ID \ECCV12SubNumber}

\author{Anonymous ECCV submission}
\institute{Paper ID \ECCV12SubNumber}

\maketitle

\begin{abstract}

\end{abstract}

\section{Introduction}
\subsection{Motivation}
\section{Related Work}

\section{Our Contribution}

\section{Results}

\section{Conclusion}

\section{Future Work}

\subsection{Citations}

The list of references is headed ``References" and is not assigned a
number
in the decimal system of headings. The list should be set in small print
and placed at the end of your contribution, in front of the appendix,
if one exists.
Please do not insert a pagebreak before the list of references if the
page is not completely filled.
An example is given at the
end of this information sheet. For citations in the text please use
square brackets and consecutive numbers: \cite{Alpher02},
\cite{Alpher03}, \cite{Alpher04} \dots

\bibliographystyle{splncs}
\bibliography{egbib}

\clearpage\mbox{}Page \thepage\ of the manuscript.
\clearpage\mbox{}Page \thepage\ of the manuscript.
\clearpage\mbox{}Page \thepage\ of the manuscript.
\clearpage\mbox{}Page \thepage\ of the manuscript.
\clearpage\mbox{}Page \thepage\ of the manuscript.
\clearpage\mbox{}Page \thepage\ of the manuscript.
This is the last page of the manuscript.
\par\vfill\par
Now we have reached the maximum size of the ECCV 2012 submission.
\end{document}

### 2014-01-27 ECCV/paper.tex
added
added motivation
initial commit

@@
 \usepackage{color}
+\usepackage{url}
 \usepackage[width=122mm,left=12mm,paperwidth=146mm,height=193mm,top=12mm,paperheight=217mm]{geometry}
@@
 \section{Related Work}
+ARToolkit \cite{ARToolkit02} /ARTag \cite{Fiala05} \\
+Pi-Tag \cite{Pitag13} \\
+Blut \cite{Wu:2011}
+\section{Our Contribution}
+\subsection{Fiducial Detection}
 
-\section{Our Contribution}
-
-\section{Results}
+\section{Experimental Results}
 
@@
 \section{Future Work}
-
-\subsection{Citations}
-
-The list of references is headed ``References" and is not assigned a
-number
-in the decimal system of headings. The list should be set in small print
-and placed at the end of your contribution, in front of the appendix,
-if one exists.
-Please do not insert a pagebreak before the list of references if the
-page is not completely filled.
-An example is given at the
-end of this information sheet. For citations in the text please use
-square brackets and consecutive numbers: \cite{Alpher02},
-\cite{Alpher03}, \cite{Alpher04} \dots
 

### 2014-01-27 DetectFiducial/src/GaborFilter.cpp

@@ -1,0 +1,60 @@
+/*
+ * GaborFilter.cpp
+ *
+ *  Created on: Jan 23, 2014
+ *      Author: meghshyam
+ */
+
+#include "GaborFilter.h"
+#include <opencv2/imgproc/imgproc.hpp>
+#include <opencv/highgui.h>
+#include <math.h>
+GaborFilter::GaborFilter() {
+	// TODO Auto-generated constructor stub
+
+}
+
+GaborFilter::~GaborFilter() {
+	// TODO Auto-generated destructor stub
+}
+
+Mat& GaborFilter::filter(Mat &input){
+	Size ksize(16,16);
+	double sigma, theta, lambd, gamma, psi1, psi2;
+	int ktype = CV_64F;
+	sigma = 8;
+	lambd  = 8; theta   = 0;
+	psi1     = 0; psi2 =  M_PI/2;
+	gamma   = 0.5;
+	Mat output[8];
+	Mat final_output;
+	imshow("input", input);
+	for(int i=0; i<8; i++)
+	{
+		Mat kernel1 = getGaborKernel(ksize,sigma,theta,lambd,gamma,psi2);
+		Mat output1, output_color;
+		filter2D(input, output1, CV_32F, kernel1);
+		theta += 45*M_PI/180;
+		pow(output1, 2, output_color);
+		cvtColor(output_color, output[i], CV_RGB2GRAY );
+		if(i > 0)
+		{
+			add(final_output, output[i], final_output);
+		}else{
+			final_output = output[i];
+		}
+	}
+	final_output = final_output * (1.0/8.0);
+	pow(final_output, 0.5, final_output);
+	double minVal;
+	double maxVal;
+	Point minLoc;
+	Point maxLoc;
+
+	minMaxLoc( final_output, &minVal, &maxVal, &minLoc, &maxLoc );
+	final_output = final_output * (1.0/maxVal);
+	threshold(final_output, final_output, 0.3, 1, THRESH_BINARY);
+	imshow("gabor", final_output);
+	waitKey();
+	return final_output;
+}

### 2014-01-27 DetectFiducial/src/GaborFilter.h

@@ -1,0 +1,21 @@
+/*
+ * GaborFilter.h
+ *
+ *  Created on: Jan 23, 2014
+ *      Author: meghshyam
+ */
+
+#ifndef GABORFILTER_H_
+#define GABORFILTER_H_
+
+#include<opencv/cv.h>
+
+using namespace cv;
+class GaborFilter {
+public:
+	GaborFilter();
+	virtual ~GaborFilter();
+	Mat& filter(Mat &);
+};
+
+#endif /* GABORFILTER_H_ */

### 2014-01-27 DetectFiducial/src/main.cpp

@@ -1,0 +1,42 @@
+/*
+ * main.cpp
+ *
+ *  Created on: Jan 24, 2014
+ *      Author: meghshyam
+ */
+#include <opencv2/imgproc/imgproc.hpp>
+#include <opencv2/highgui/highgui.hpp>
+#include <opencv/cv.h>
+#include "GaborFilter.h"
+#include <iostream>
+
+using namespace cv;
+using namespace std;
+
+std::vector<Mat>& findConnectedComponents(Mat &);
+int main(int argc, char *argv[])
+{
+	if(argc < 2){
+		cout<<"Usage:detectFiducial <filename>\n";
+		exit(-1);
+	}
+
+	//Read image
+
+	Mat input;
+	input = imread(argv[1], 1);
+
+	//Apply Gabor Filter on input image
+
+	GaborFilter gbFilter;
+	Mat gaborOutput;
+	gaborOutput = gbFilter.filter(input);
+
+	//Find Connected components in Gabor output
+	//std::vector<Mat> connectedComponents = findConnectedComponents(gaborOutput);
+}
+
+std::vector<Mat> & findConnectedComponents(Mat &binaryImage){
+	std::vector<Mat> out;
+	return out;
+}

### 2014-01-28 DetectFiducial/src/GaborFilter.cpp
written flow of code

@@ -22,7 +22,7 @@ Mat& GaborFilter::filter(Mat &input){
 	Size ksize(16,16);
 	double sigma, theta, lambd, gamma, psi1, psi2;
 	int ktype = CV_64F;
-	sigma = 8;
+	sigma = 4.49;
 	lambd  = 8; theta   = 0;
 	psi1     = 0; psi2 =  M_PI/2;
 	gamma   = 0.5;
@@ -31,7 +31,7 @@ Mat& GaborFilter::filter(Mat &input){
 	imshow("input", input);
 	for(int i=0; i<8; i++)
 	{
-		Mat kernel1 = getGaborKernel(ksize,sigma,theta,lambd,gamma,psi2);
+		Mat kernel1 = getGaborKernel(ksize,sigma,theta,lambd,gamma,psi1/2);
 		Mat output1, output_color;
 		filter2D(input, output1, CV_32F, kernel1);
 		theta += 45*M_PI/180;

### 2014-01-28 DetectFiducial/src/main.cpp

@@ -13,7 +13,7 @@
 using namespace cv;
 using namespace std;
 
-std::vector<Mat>& findConnectedComponents(Mat &);
+std::vector<std::vector<Point>> & findConnectedComponents(Mat &);
 int main(int argc, char *argv[])
 {
 	if(argc < 2){
@@ -33,10 +33,18 @@ int main(int argc, char *argv[])
 	gaborOutput = gbFilter.filter(input);
 
 	//Find Connected components in Gabor output
-	//std::vector<Mat> connectedComponents = findConnectedComponents(gaborOutput);
+	//std::vector<Point> connectedComponents = findConnectedComponents(gaborOutput);
+
+	//Cluster the connected components
+
+	//Merge the clusters
+
+	//Detect code in the bounding box
+
+	//Classify the detected code
 }
 
-std::vector<Mat> & findConnectedComponents(Mat &binaryImage){
-	std::vector<Mat> out;
+std::vector<std::vector<Point>> & findConnectedComponents(Mat &binaryImage){
+	std::vector<Point> out;
 	return out;
 }

### 2014-01-28 ECCV/paper.tex
1. Added connected components 2. workaround for complex kernel in Gabor filter

@@
 \section{Introduction}
+
 \subsection{Motivation}
+Tracking vehicle by an autonomous vehicle. \\
+Fiducials for tracking under motion blur.
+
 \section{Related Work}
@@
 Blut \cite{Wu:2011}
+
 \section{Our Contribution}
-\subsection{Fiducial Detection}
+
+\subsection{Design of Fiducial}
+
+\subsection{Fiducial Detection Algorithm}
+Apply Gabor Filter on input image \\
+Find Connected components in Gabor output \\
+Cluster the connected components \\
+Merge the clusters \\
+Detect code in the bounding box \\
+Classify the detected code
 
@@
 
-\clearpage\mbox{}Page \thepage\ of the manuscript.
-\clearpage\mbox{}Page \thepage\ of the manuscript.
-\clearpage\mbox{}Page \thepage\ of the manuscript.
-\clearpage\mbox{}Page \thepage\ of the manuscript.
-\clearpage\mbox{}Page \thepage\ of the manuscript.
-\clearpage\mbox{}Page \thepage\ of the manuscript.
-This is the last page of the manuscript.
-\par\vfill\par
-Now we have reached the maximum size of the ECCV 2012 submission.
 \end{document}

### 2014-01-28 DetectFiducial/src/ConnectedComponents.cpp

@@ -1,0 +1,322 @@
+///////////////////////////////////////////////////////////////////////////////////////
+//
+//  IMPORTANT: READ BEFORE DOWNLOADING, COPYING, INSTALLING OR USING.
+
+//
+//  By downloading, copying, installing or using the software you agree to this license.
+//  If you do not agree to this license, do not download, install,
+//  copy or use the software.
+//
+//
+//                        Intel License Agreement
+//                For Open Source Computer Vision Library
+//
+// Copyright (C) 2000, Intel Corporation, all rights reserved.
+// Third party copyrights are property of their respective owners.
+//
+// Redistribution and use in source and binary forms, with or without modification,
+// are permitted provided that the following conditions are met:
+//
+//   * Redistribution's of source code must retain the above copyright notice,
+//     this list of conditions and the following disclaimer.
+//
+//   * Redistribution's in binary form must reproduce the above copyright notice,
+//     this list of conditions and the following disclaimer in the documentation
+//     and/or other materials provided with the distribution.
+//
+//   * The name of Intel Corporation may not be used to endorse or promote products
+//     derived from this software without specific prior written permission.
+//
+// This software is provided by the copyright holders and contributors "as is" and
+// any express or implied warranties, including, but not limited to, the implied
+// warranties of merchantability and fitness for a particular purpose are disclaimed.
+// In no event shall the Intel Corporation or contributors be liable for any direct,
+// indirect, incidental, special, exemplary, or consequential damages
+// (including, but not limited to, procurement of substitute goods or services;
+// loss of use, data, or profits; or business interruption) however caused
[…]

### 2014-01-28 DetectFiducial/src/ConnectedComponents.h

@@ -1,0 +1,16 @@
+/*
+ * ConnectedComponents.h
+ *
+ *  Created on: Jan 28, 2014
+ *      Author: meghshyam
+ */
+
+#ifndef CONNECTEDCOMPONENTS_H_
+#define CONNECTEDCOMPONENTS_H_
+
+#include <opencv/cv.h>
+
+int connectedComponents(cv::Mat img, cv::Mat labels, int connectivity, int ltype);
+
+
+#endif /* CONNECTEDCOMPONENTS_H_ */

### 2014-01-28 DetectFiducial/src/GaborFilter.cpp

@@ -18,33 +18,36 @@ GaborFilter::~GaborFilter() {
 	// TODO Auto-generated destructor stub
 }
 
-Mat& GaborFilter::filter(Mat &input){
-	Size ksize(16,16);
+void GaborFilter::filter(Mat &input, Mat &gaborOutput){
+	Size ksize(64,64);
 	double sigma, theta, lambd, gamma, psi1, psi2;
 	int ktype = CV_64F;
-	sigma = 4.49;
+	int bw =1;
 	lambd  = 8; theta   = 0;
 	psi1     = 0; psi2 =  M_PI/2;
 	gamma   = 0.5;
-	Mat output[8];
+	sigma = lambd/M_PI*sqrt(log(2)/2)*(pow(2,bw)+1)/(pow(2,bw)-1);
 	Mat final_output;
+	Mat inputGray, output[8];
 	imshow("input", input);
+	cvtColor(input, inputGray, CV_RGB2GRAY);
 	for(int i=0; i<8; i++)
 	{
-		Mat kernel1 = getGaborKernel(ksize,sigma,theta,lambd,gamma,psi1/2);
-		Mat output1, output_color;
-		filter2D(input, output1, CV_32F, kernel1);
-		theta += 45*M_PI/180;
-		pow(output1, 2, output_color);
-		cvtColor(output_color, output[i], CV_RGB2GRAY );
+		Mat output1, output2, magOutput;
+		Mat kernel1 = getGaborKernel(ksize,sigma,theta,lambd,gamma,psi1);
+		filter2D(inputGray, output1, CV_32F, kernel1);
+		Mat kernel2 = getGaborKernel(ksize,sigma,theta,lambd,gamma,psi2);
+		filter2D(inputGray, output2, CV_32F, kernel2);
+		magnitude(output1, output2, magOutput);
+		pow(magOutput, 2, output[i]);
 		if(i > 0)
 		{
 			add(final_output, output[i], final_output);
 		}else{
 			final_output = output[i];
 		}
+		theta += 45*M_PI/180;
 	}
-	final_output = final_output * (1.0/8.0);
 	pow(final_output, 0.5, final_output);
 	double minVal;
 	double maxVal;
@@ -53,8 +56,5 @@ Mat& GaborFilter::filter(Mat &input){
 
 	minMaxLoc( final_output, &minVal, &maxVal, &minLoc, &maxLoc );
 	final_output = final_output * (1.0/maxVal);
[…]

### 2014-01-28 DetectFiducial/src/GaborFilter.h

@@ -15,7 +15,7 @@ class GaborFilter {
 public:
 	GaborFilter();
 	virtual ~GaborFilter();
-	Mat& filter(Mat &);
+	void filter(Mat &, Mat&);
 };
 
 #endif /* GABORFILTER_H_ */

### 2014-01-28 DetectFiducial/src/main.cpp

@@ -8,13 +8,14 @@
 #include <opencv2/highgui/highgui.hpp>
 #include <opencv/cv.h>
 #include "GaborFilter.h"
+#include "ConnectedComponents.h"
 #include <iostream>
 
 using namespace cv;
 using namespace std;
 
-std::vector<std::vector<Point>> & findConnectedComponents(Mat &);
-int main(int argc, char *argv[])
+void findConnectedComponents(Mat &, vector<vector<Point> > & );
+int main(int argc, char* argv[])
 {
 	if(argc < 2){
 		cout<<"Usage:detectFiducial <filename>\n";
@@ -29,11 +30,13 @@ int main(int argc, char *argv[])
 	//Apply Gabor Filter on input image
 
 	GaborFilter gbFilter;
-	Mat gaborOutput;
-	gaborOutput = gbFilter.filter(input);
-
+	Mat gaborOutput(input.size(), CV_8UC1);
+	gbFilter.filter(input, gaborOutput);
+	imshow("gabour output", gaborOutput);
+	waitKey();
 	//Find Connected components in Gabor output
-	//std::vector<Point> connectedComponents = findConnectedComponents(gaborOutput);
+	vector<vector<Point> > connectedComponents;
+	findConnectedComponents(gaborOutput, connectedComponents);
 
 	//Cluster the connected components
 
@@ -44,7 +47,26 @@ int main(int argc, char *argv[])
 	//Classify the detected code
 }
 
-std::vector<std::vector<Point>> & findConnectedComponents(Mat &binaryImage){
-	std::vector<Point> out;
-	return out;
+void findConnectedComponents(Mat &binaryImage, vector< vector<Point> > &out){
+//	vector<Vec4i> hierarchy;
+//	findContours( binaryImage, out, hierarchy, CV_RETR_CCOMP, CV_CHAIN_APPROX_SIMPLE );
+//	Mat dst = Mat::zeros(binaryImage.size(), CV_8UC3);
+//
+//	if( !out.empty() && !hierarchy.empty() )
+//	{
+//		// iterate through all the top-level contours,
+//		// draw each connected component with its own random color
+//		int idx = 0;
+//		for( ; idx >= 0; idx = hierarchy[idx][0] )
+//		{
+//			Scalar color( (rand()&255), (rand()&255), (rand()&255) );
+//			drawContours( dst, out, idx, color, CV_FILLED, 8, hierarchy );
+//		}
+//	}
+//
[…]

### 2014-01-29 DetectFiducial/src/ConnectedComponents.cpp
1. added connectedComponentsWithStats 2. added clustering code

@@ -43,6 +43,7 @@
 //
 #include <opencv/cv.h>>
 #include <vector>
+#include "ConnectedComponents.h"
 
 struct NoOp{
 	NoOp(){
@@ -308,7 +309,7 @@ int connectedComponents_sub1(const cv::Mat &I, cv::Mat &L, int connectivity, Sta
 	return -1;
 }
 
-extern int connectedComponents(cv::Mat img, cv::Mat labels, int connectivity, int ltype){
+extern int connectedComponents(cv::Mat &img, cv::Mat &labels, int connectivity, int ltype){
 	NoOp sop;
 	if(ltype == CV_16U){
 		return connectedComponents_sub1(img, labels, connectivity, sop);
@@ -320,3 +321,65 @@ extern int connectedComponents(cv::Mat img, cv::Mat labels, int connectivity, in
 	}
 }
 
+struct CCStatsOp{
+        cv::Mat *statsv;
+        cv::Mat *centroidsv;
+        std::vector<Point2ui64> integrals;
+
+        CCStatsOp(cv::Mat *_statsv, cv::Mat *_centroidsv): statsv(_statsv), centroidsv(_centroidsv){
+        }
+        inline
+        void init(int nlabels){
+            (*statsv).create(cv::Size(CC_STAT_MAX, nlabels), cv::DataType<int>::type);
+            (*centroidsv).create(cv::Size(2, nlabels), cv::DataType<double>::type);
+
+            for(int l = 0; l < (int) nlabels; ++l){
+                int *row = (int *) &(*statsv).at<int>(l, 0);
+                row[CC_STAT_LEFT] = INT_MAX;
+                row[CC_STAT_TOP] = INT_MAX;
+                row[CC_STAT_WIDTH] = INT_MIN;
+                row[CC_STAT_HEIGHT] = INT_MIN;
+                row[CC_STAT_AREA] = 0;
+            }
+            integrals.resize(nlabels, Point2ui64(0, 0));
+        }
+        void operator()(int r, int c, int l){
+            int *row = &(*statsv).at<int>(l, 0);
+            row[CC_STAT_LEFT] = MIN(row[CC_STAT_LEFT], c);
+            row[CC_STAT_WIDTH] = MAX(row[CC_STAT_WIDTH], c);
+            row[CC_STAT_TOP] = MIN(row[CC_STAT_TOP], r);
+            row[CC_STAT_HEIGHT] = MAX(row[CC_STAT_HEIGHT], r);
+            row[CC_STAT_AREA]++;
[…]

### 2014-01-29 DetectFiducial/src/ConnectedComponents.h

@@ -10,7 +10,23 @@
 
 #include <opencv/cv.h>
 
-int connectedComponents(cv::Mat img, cv::Mat labels, int connectivity, int ltype);
+int connectedComponents(cv::Mat &img, cv::Mat &labels, int connectivity, int ltype);
+int connectedComponentsWithStats(cv::Mat &img, cv::Mat &labels, cv::Mat &statsv, cv::Mat &centroids, int connectivity, int ltype);
+//! connected components algorithm output formats
+
+enum { CC_STAT_LEFT   = 0,
+
+       CC_STAT_TOP    = 1,
+
+       CC_STAT_WIDTH  = 2,
+
+       CC_STAT_HEIGHT = 3,
+
+       CC_STAT_AREA   = 4,
+
+       CC_STAT_MAX    = 5
+
+     };
 
 
 #endif /* CONNECTEDCOMPONENTS_H_ */

### 2014-01-29 DetectFiducial/src/main.cpp

@@ -6,6 +6,7 @@
  */
 #include <opencv2/imgproc/imgproc.hpp>
 #include <opencv2/highgui/highgui.hpp>
+#include <opencv2/flann/flann.hpp>
 #include <opencv/cv.h>
 #include "GaborFilter.h"
 #include "ConnectedComponents.h"
@@ -14,7 +15,8 @@
 using namespace cv;
 using namespace std;
 
-void findConnectedComponents(Mat &, vector<vector<Point> > & );
+void findConnectedComponents(Mat &, Mat & );
+void doCluster(Mat&, Mat&);
 int main(int argc, char* argv[])
 {
 	if(argc < 2){
@@ -33,12 +35,12 @@ int main(int argc, char* argv[])
 	Mat gaborOutput(input.size(), CV_8UC1);
 	gbFilter.filter(input, gaborOutput);
 	imshow("gabour output", gaborOutput);
-	waitKey();
 	//Find Connected components in Gabor output
-	vector<vector<Point> > connectedComponents;
+	Mat connectedComponents, clusters;
 	findConnectedComponents(gaborOutput, connectedComponents);
 
 	//Cluster the connected components
+	doCluster(connectedComponents, clusters);
 
 	//Merge the clusters
 
@@ -47,26 +49,41 @@ int main(int argc, char* argv[])
 	//Classify the detected code
 }
 
-void findConnectedComponents(Mat &binaryImage, vector< vector<Point> > &out){
-//	vector<Vec4i> hierarchy;
-//	findContours( binaryImage, out, hierarchy, CV_RETR_CCOMP, CV_CHAIN_APPROX_SIMPLE );
-//	Mat dst = Mat::zeros(binaryImage.size(), CV_8UC3);
-//
-//	if( !out.empty() && !hierarchy.empty() )
-//	{
-//		// iterate through all the top-level contours,
-//		// draw each connected component with its own random color
-//		int idx = 0;
-//		for( ; idx >= 0; idx = hierarchy[idx][0] )
-//		{
-//			Scalar color( (rand()&255), (rand()&255), (rand()&255) );
-//			drawContours( dst, out, idx, color, CV_FILLED, 8, hierarchy );
-//		}
-//	}
-//
-//	imshow( "Connected Components", dst );
+void findConnectedComponents(Mat &binaryImage, Mat &out){
+	Mat stats, centroids;
[…]

### 2014-01-30 DetectFiducial/src/main.cpp
changed clustering code

@@ -17,6 +17,7 @@ using namespace std;
 
 void findConnectedComponents(Mat &, Mat & );
 void doCluster(Mat&, Mat&);
+float distL2(int * a, float *b, int dim);
 int main(int argc, char* argv[])
 {
 	if(argc < 2){
@@ -34,16 +35,27 @@ int main(int argc, char* argv[])
 	GaborFilter gbFilter;
 	Mat gaborOutput(input.size(), CV_8UC1);
 	gbFilter.filter(input, gaborOutput);
-	imshow("gabour output", gaborOutput);
+
 	//Find Connected components in Gabor output
 	Mat connectedComponents, clusters;
 	findConnectedComponents(gaborOutput, connectedComponents);
 
 	//Cluster the connected components
 	doCluster(connectedComponents, clusters);
+	int numClusters = clusters.rows;
+	for(int i=0; i<numClusters; i++)
+	{
+		int * row = (int *)&clusters.at<int>(i,0);
+		int x1 = row[0];
+		int y1 = row[1];
+		int x2 = row[2];
+		int y2 = row[3];
+		Point pt1(x1,y1), pt2(x2,y2);
+		rectangle(input, pt1, pt2, Scalar(0,255,0) );
+	}
 
-	//Merge the clusters
-
+	imshow("cluster output", input);
+	waitKey();
 	//Detect code in the bounding box
 
 	//Classify the detected code
@@ -67,14 +79,12 @@ void findConnectedComponents(Mat &binaryImage, Mat &out){
 			int y1 = stats.at<int>(i, CC_STAT_TOP);
 			int x2 = x1 + stats.at<int>(i, CC_STAT_WIDTH);
 			int y2 = y1 + stats.at<int>(i, CC_STAT_HEIGHT);
-			Point pt1(x1,y1), pt2(x2,y2);
+			//Point pt1(x1,y1), pt2(x2,y2);
 			int * row = (int *)&out.at<int>(i-1,0);
 			row[0] = x1; row[1] = y1; row[2] = x2; row[3] = y2;
-			rectangle(binaryImage, pt1, pt2, Scalar(255,0,0) );
+			//rectangle(binaryImage, pt1, pt2, Scalar(255,0,0) );
 		}
 	}
-	imshow( "Connected Components", binaryImage);
-	waitKey();
 }
 
 void doCluster(Mat &connectedComponents, Mat& clusters)
@@ -86,4 +96,57 @@ void doCluster(Mat &connectedComponents, Mat& clusters)
[…]

### 2014-02-03 ECCV/paper.tex
dummy change.

@@
 Detect code in the bounding box \\
-Classify the detected code
+Classify the detected code by the classifer trained on standards.
 

### 2014-02-03 ECCV/paper.tex
Few more related work.

@@
 ARToolkit \cite{ARToolkit02} /ARTag \cite{Fiala05} \\
+Circular Data Matrix Fiducial System \cite{NaimarkF02}
+Reliable Fiducial Detection in Natural Scenes \cite{ClausF04}
+RUNE-Tag \cite{runetag11}
 Pi-Tag \cite{Pitag13} \\

### 2014-02-03 DetectFiducial/src/GaborFilter.cpp
Corrected memory bugs.

@@ -29,7 +29,6 @@ void GaborFilter::filter(Mat &input, Mat &gaborOutput){
 	sigma = lambd/M_PI*sqrt(log(2)/2)*(pow(2,bw)+1)/(pow(2,bw)-1);
 	Mat final_output;
 	Mat inputGray, output[8];
-	imshow("input", input);
 	cvtColor(input, inputGray, CV_RGB2GRAY);
 	for(int i=0; i<8; i++)
 	{

### 2014-02-03 DetectFiducial/src/main.cpp

@@ -16,8 +16,8 @@ using namespace cv;
 using namespace std;
 
 void findConnectedComponents(Mat &, Mat & );
-void doCluster(Mat&, Mat&);
-float distL2(int * a, float *b, int dim);
+void doCluster(const Mat&, Mat&);
+float distL2(const float* a, const float *b, int dim);
 int main(int argc, char* argv[])
 {
 	if(argc < 2){
@@ -29,7 +29,6 @@ int main(int argc, char* argv[])
 
 	Mat input;
 	input = imread(argv[1], 1);
-
 	//Apply Gabor Filter on input image
 
 	GaborFilter gbFilter;
@@ -45,11 +44,12 @@ int main(int argc, char* argv[])
 	int numClusters = clusters.rows;
 	for(int i=0; i<numClusters; i++)
 	{
-		int * row = (int *)&clusters.at<int>(i,0);
+		float * row = (float *)&clusters.at<float>(i,0);
 		int x1 = row[0];
 		int y1 = row[1];
 		int x2 = row[2];
 		int y2 = row[3];
+		//cout<<x1<<","<<y1<<","<<x2<<","<<y2<<"\n";
 		Point pt1(x1,y1), pt2(x2,y2);
 		rectangle(input, pt1, pt2, Scalar(0,255,0) );
 	}
@@ -66,8 +66,8 @@ void findConnectedComponents(Mat &binaryImage, Mat &out){
 	Mat components(binaryImage.size(), CV_8UC1);
 	//connectedComponents(binaryImage, components, 4, CV_16U);
 	int numLabels = connectedComponentsWithStats(binaryImage, components, stats, centroids, 4, CV_16U);
-	cout<<"Number of components:"<<numLabels-1<<"\n";
-	out.create(numLabels-1, 4, DataType<int>::type);
+	out.create(numLabels-1, 4, DataType<float>::type);
+	int k=0;
 	for(int i=1; i<numLabels; i++)
 	{
 		//cout<<"area = "<<stats.at<int>(i, CC_STAT_AREA)<<"\n";
@@ -79,39 +79,41 @@ void findConnectedComponents(Mat &binaryImage, Mat &out){
 			int y1 = stats.at<int>(i, CC_STAT_TOP);
 			int x2 = x1 + stats.at<int>(i, CC_STAT_WIDTH);
 			int y2 = y1 + stats.at<int>(i, CC_STAT_HEIGHT);
[…]

### 2014-02-05 AlgLib/clst_ahc.cpp
Initial commit

@@ -1,0 +1,174 @@
+#include "stdafx.h"
+#include <stdlib.h>
+#include <stdio.h>
+#include <math.h>
+#include "dataanalysis.h"
+#include "ap.h"
+using namespace alglib;
+
+void processEntry(int index, int numObs, int clusterIndex, integer_2d_array Z, int * clusterid, int *done)
+{
+	for(int j=0; j<2; j++){
+		int a = Z(index,j);
+		if (a >= numObs){
+			a-= numObs;
+			done[a] = 1;
+			processEntry(a, numObs, clusterIndex, Z, clusterid, done);
+		}else{
+			clusterid[a] = clusterIndex;
+		}
+	}
+}
+
+int main(int argc, char **argv)
+{
+    //
+    // The very simple clusterization example
+    //
+    // We have a set of points in 2D space:
+    //     (P0,P1,P2,P3,P4) = ((1,1),(1,2),(4,1),(2,3),(4,1.5))
+    //
+    //  |
+    //  |     P3
+    //  |
+    //  | P1          
+    //  |             P4
+    //  | P0          P2
+    //  |-------------------------
+    //
+    // We want to perform Agglomerative Hierarchic Clusterization (AHC),
+    // using complete linkage (default algorithm) and Euclidean distance
+    // (default metric).
+    //
+    // In order to do that, we:
+    // * create clusterizer with clusterizercreate()
+    // * set points XY and metric (2=Euclidean) with clusterizersetpoints()
+    // * run AHC algorithm with clusterizerrunahc
+    //
+    // You may see that clusterization itself is a minor part of the example,
+    // most of which is dominated by comments :)
+    //
+    clusterizerstate s;
+    ahcreport rep;
+    real_2d_array xy = "[[1,1],[1,2],[4,1],[2,3],[4,1.5]]";
+
+    clusterizercreate(s);
+    clusterizersetpoints(s, xy, 2);
+    clusterizerrunahc(s, rep);
+	integer_2d_array Z(rep.z);
+	real_1d_array dist(rep.mergedist);
+	int numRows = Z.rows();
+	int numCols = Z.cols();
+	int numObs = 5;
+	for(int i=0; i<numRows; i++)
+	{
+		int a = Z(i,0);
+		int b = Z(i,1);
+		printf("%d\t%d\t%.4f\n", a,b,dist[i]);
+	}
+
+	int *clusterid = new int[numRows];
[…]

### 2014-02-05 ECCV/paper.tex
Details about algorithm

--- 2014-01-28 ECCV/paper.tex
@@
 \section{Related Work}
-ARToolkit \cite{ARToolkit02} /ARTag \cite{Fiala05} \\
+ARToolkit \cite{ARToolkit02} \cite{kato-artoolkit} /ARTag \cite{Fiala05} \\
+Circular Data Matrix Fiducial System \cite{NaimarkF02} \\
+Reliable Fiducial Detection in Natural Scenes \cite{ClausF04}\\
+RUNE-Tag \cite{runetag11} \\
 Pi-Tag \cite{Pitag13} \\
@@
 \subsection{Fiducial Detection Algorithm}
-Apply Gabor Filter on input image \\
-Find Connected components in Gabor output \\
-Cluster the connected components \\
-Merge the clusters \\
-Detect code in the bounding box \\
-Classify the detected code
+\begin{itemize}
+  \item Apply Gabor Filter on input image
+  \item Find Connected components in Gabor output
+  \item Cluster the connected components in bounding box
+  \item Detect code in the bounding box
+  \begin{itemize}
+    \item Run PCA on Gabor output in bounding box
+    \item Find intensity profile along first principal component passing through
+    centroid
+    \item If there are less than four black to white transitions in the
+    intensity profile, ignore the bouding box
+    \item Otherwise, classify the detected code by the classifer trained on
+    standards.
+  \end{itemize}
+\end{itemize}
 
 \section{Experimental Results}
+\subsection{Comparison}
+We will compare our results with standard fiducials such as ARTag. Also, we will
+compare our results with Blur driven tracker.
+\subsubsection{Comparison with ARTag}
+\subsubsection{Comparison with Blut}
 
@@
 \section{Future Work}
-
+Pose Estimation
 \bibliographystyle{splncs}

### 2014-02-06 DetectFiducial/src/ConnectedComponents.cpp
1. Changed Clustering code (Used AlgLib) 2. Added PCA code 3. Minor changes in function signature

@@ -370,7 +370,7 @@ struct CCStatsOp{
     };
 
 
-extern int connectedComponentsWithStats(cv::Mat &img, cv::Mat &labels, cv::Mat &statsv,
+extern int connectedComponentsWithStats(const cv::Mat &img, cv::Mat &labels, cv::Mat &statsv,
 		cv::Mat &centroids, int connectivity, int ltype)
 {
     CCStatsOp sop(&statsv, &centroids);

### 2014-02-06 DetectFiducial/src/ConnectedComponents.h

@@ -11,7 +11,7 @@
 #include <opencv/cv.h>
 
 int connectedComponents(cv::Mat &img, cv::Mat &labels, int connectivity, int ltype);
-int connectedComponentsWithStats(cv::Mat &img, cv::Mat &labels, cv::Mat &statsv, cv::Mat &centroids, int connectivity, int ltype);
+int connectedComponentsWithStats(const cv::Mat &img, cv::Mat &labels, cv::Mat &statsv, cv::Mat &centroids, int connectivity, int ltype);
 //! connected components algorithm output formats
 
 enum { CC_STAT_LEFT   = 0,

### 2014-02-06 DetectFiducial/src/main.cpp

@@ -10,14 +10,33 @@
 #include <opencv/cv.h>
 #include "GaborFilter.h"
 #include "ConnectedComponents.h"
+#include <dataanalysis.h>
+#include <ap.h>
 #include <iostream>
 
 using namespace cv;
 using namespace std;
+using namespace alglib;
 
-void findConnectedComponents(Mat &, Mat & );
+void findConnectedComponents(const Mat &, Mat & );
 void doCluster(const Mat&, Mat&);
-float distL2(const float* a, const float *b, int dim);
+void getPoints(const Mat &binOutput, int left, int top, int right, int bottom, Mat &outPts);
+bool detectCode(const Mat &pts, int left, int top, int right, int bottom, Mat &input, vector<float>& intensity_profile );
+
+void processEntry(int index, int numObs, int clusterIndex, integer_2d_array Z, int * clusterid, int *done)
+{
+	for(int j=0; j<2; j++){
+		int a = Z(index,j);
+		if (a >= numObs){
+			a-= numObs;
+			done[a] = 1;
+			processEntry(a, numObs, clusterIndex, Z, clusterid, done);
+		}else{
+			clusterid[a] = clusterIndex;
+		}
+	}
+}
+
 int main(int argc, char* argv[])
 {
 	if(argc < 2){
@@ -26,11 +45,10 @@ int main(int argc, char* argv[])
 	}
 
 	//Read image
-
 	Mat input;
 	input = imread(argv[1], 1);
-	//Apply Gabor Filter on input image
 
+	//Apply Gabor Filter on input image
 	GaborFilter gbFilter;
 	Mat gaborOutput(input.size(), CV_8UC1);
 	gbFilter.filter(input, gaborOutput);
@@ -54,14 +72,169 @@ int main(int argc, char* argv[])
 		rectangle(input, pt1, pt2, Scalar(0,255,0) );
 	}
 
-	imshow("cluster output", input);
-	waitKey();
-	//Detect code in the bounding box
+	//imshow("cluster output", input);
 
-	//Classify the detected code
+
+	//Detect code in the bounding box
+	vector<float> intensity_profile;
+	bool found = false;
+	for(int i=0; i<numClusters; i++)
+	{
+		float * row = (float *)&clusters.at<float>(i,0);
+		int x1 = row[0];
+		int y1 = row[1];
+		int x2 = row[2];
+		int y2 = row[3];
+		Mat pts;
[…]

### 2014-02-07 DetectFiducial/src/main.cpp
Added code to get intensity profile

@@ -67,13 +67,9 @@ int main(int argc, char* argv[])
 		int y1 = row[1];
 		int x2 = row[2];
 		int y2 = row[3];
-		//cout<<x1<<","<<y1<<","<<x2<<","<<y2<<"\n";
 		Point pt1(x1,y1), pt2(x2,y2);
 		rectangle(input, pt1, pt2, Scalar(0,255,0) );
 	}
-
-	//imshow("cluster output", input);
-
 
 	//Detect code in the bounding box
 	vector<float> intensity_profile;
@@ -87,9 +83,11 @@ int main(int argc, char* argv[])
 		int y2 = row[3];
 		Mat pts;
 		Point pt1(x1,y1), pt2(x2,y2);
-		rectangle(gaborOutput, pt1, pt2, Scalar(255,0,0) );
-		imshow("gabor", gaborOutput);
-		waitKey();
+
+		  rectangle(gaborOutput, pt1, pt2, Scalar(255,0,0) );
+		  imshow("gabor", gaborOutput);
+		  waitKey();
+
 		getPoints(gaborOutput, x1, y1, x2, y2, pts);
 		found = detectCode(pts, x1, y1, x2, y2, input, intensity_profile);
 		if(found)
@@ -98,6 +96,7 @@ int main(int argc, char* argv[])
 	if(!found){
 		cout<<"Code not detected\n";
 	}else{
+		cout<<"Code detected\n";
 		//Classify the detected code
 	}
 	waitKey();
@@ -108,7 +107,6 @@ bool detectCode(const Mat &pts, int left, int top, int right, int bottom, Mat &i
 	int dim = pts.cols;
 	PCA pca(pts, Mat(), CV_PCA_DATA_AS_ROW, 2);
 	float * ptr = pca.eigenvectors.ptr<float>(0);
-	//vector<double> prin_comp(ptr, ptr + dim);
 	double slope = ptr[1]/ptr[0];
 	int centroid[2] = {0,0};
 	for(int i=0; i<numPts; i++){
@@ -118,101 +116,187 @@ bool detectCode(const Mat &pts, int left, int top, int right, int bottom, Mat &i
 	centroid[0] /= numPts;
 	centroid[1] /= numPts;
 
-	vector<Point> upward_pts;
-	vector<Point> downward_pts;
+	int centroid_pos[2] = {0, 0};
+	int centroid_neg[2] = {0, 0};
[…]

### 2014-02-08 DetectFiducial/src/GaborFilter.cpp
Fixed bugs

@@ -9,6 +9,8 @@
 #include <opencv2/imgproc/imgproc.hpp>
 #include <opencv/highgui.h>
 #include <math.h>
+#include <iostream>
+using namespace std;
 GaborFilter::GaborFilter() {
 	// TODO Auto-generated constructor stub
 
@@ -29,7 +31,12 @@ void GaborFilter::filter(Mat &input, Mat &gaborOutput){
 	sigma = lambd/M_PI*sqrt(log(2)/2)*(pow(2,bw)+1)/(pow(2,bw)-1);
 	Mat final_output;
 	Mat inputGray, output[8];
-	cvtColor(input, inputGray, CV_RGB2GRAY);
+	if(input.channels() >=3 )
+		cvtColor(input, inputGray, CV_BGR2GRAY);
+	else
+		inputGray = input.clone();
+	//cout<<"Type of imageo:"<<inputGray.type()<<"\n";
+
 	for(int i=0; i<8; i++)
 	{
 		Mat output1, output2, magOutput;

### 2014-02-08 DetectFiducial/src/main.cpp

@@ -70,6 +70,8 @@ int main(int argc, char* argv[])
 		Point pt1(x1,y1), pt2(x2,y2);
 		rectangle(input, pt1, pt2, Scalar(0,255,0) );
 	}
+//	imshow("box",input);
+//	waitKey();
 
 	//Detect code in the bounding box
 	vector<float> intensity_profile;
@@ -83,11 +85,13 @@ int main(int argc, char* argv[])
 		int y2 = row[3];
 		Mat pts;
 		Point pt1(x1,y1), pt2(x2,y2);
+/*
 
 		  rectangle(gaborOutput, pt1, pt2, Scalar(255,0,0) );
 		  imshow("gabor", gaborOutput);
 		  waitKey();
 
+*/
 		getPoints(gaborOutput, x1, y1, x2, y2, pts);
 		found = detectCode(pts, x1, y1, x2, y2, input, intensity_profile);
 		if(found)
@@ -99,7 +103,6 @@ int main(int argc, char* argv[])
 		cout<<"Code detected\n";
 		//Classify the detected code
 	}
-	waitKey();
 }
 
 bool detectCode(const Mat &pts, int left, int top, int right, int bottom, Mat &input, vector<float>& intensity_profile ){
@@ -136,11 +139,16 @@ bool detectCode(const Mat &pts, int left, int top, int right, int bottom, Mat &i
 	centroids[1][0] = centroid[0]; centroids[1][1] = centroid[1];
 	centroids[2][0] = centroid_pos[0]; centroids[2][1] = centroid_pos[1];
 
-	Mat grayInput(input.size(), CV_32FC1);
-	cvtColor(input, grayInput, CV_BGR2GRAY);
+	Mat grayInput;//(input.size(), DataType<float>::type);
+	//cout<<"Type of image1:"<<grayInput.type()<<"\n";
+	if(input.channels() >=3 )
+		cvtColor(input, grayInput, CV_RGB2GRAY);
+	else
+		grayInput = input.clone();
+	//cout<<"Type of image1:"<<grayInput.type()<<"\n";
 
 	int numPtsPerLine[3];
-	float * intensities[3];
+	uchar * intensities[3];
 	vector<Point> line_pts[3];
 
 	for(int index=0; index<3; index++)
@@ -235,21 +243,23 @@ bool detectCode(const Mat &pts, int left, int top, int right, int bottom, Mat &i
 			}
 		}
 
-		if(upward_pts.size() > 0 && downward_pts.size() > 0){
[…]

### 2014-02-20 DetectFiducial/src/main.cpp
Cascaded classifier

@@ -1,4 +1,4 @@
-/*
+ /*
  * main.cpp
  *
  *  Created on: Jan 24, 2014
@@ -28,7 +28,7 @@ using namespace alglib;
 void findConnectedComponents(const Mat &, Mat & );
 void doCluster(const Mat&, Mat&);
 void getPoints(const Mat &binOutput, int left, int top, int right, int bottom, Mat &outPts);
-bool detectCode(const Mat &pts, int left, int top, int right, int bottom, const Mat &input, vector<float>& intensity_profile );
+bool detectCode(const Mat &pts, int left, int top, int right, int bottom, const Mat &input, vector<float>& intensity_profile, int& num_rings );
 void createTrainingData(const string &orig_dirname, Mat & trainingData, Mat & response);
 
 int findDiffMinMax(vector<int> ring_widths[], int dim, int first, int second){
@@ -120,6 +120,11 @@ int main(int argc, char* argv[])
 	//Detect code in the bounding box
 	vector<float> intensity_profile;
 	bool found = false;
+	Mat trainingData,response;
+	string dirname = "/home/meghshyam/git/fiducial/DetectFiducial/trainingData/";
+	createTrainingData(dirname, trainingData, response);
+	const int K =11;
+	CvKNearest knn(trainingData, response, Mat(), false, K);
 	for(int i=0; i<numClusters; i++)
 	{
 		float * row = (float *)&clusters.at<float>(i,0);
@@ -142,37 +147,44 @@ int main(int argc, char* argv[])
 		x2 = x2 > width ? width : x2;
 		y2 = y2 > height ? height : y2;
 		*/
-		found = detectCode(pts, x1, y1, x2, y2, input, intensity_profile);
+		intensity_profile.clear();
+		int num_rings = -1;
+		found = detectCode(pts, x1, y1, x2, y2, input, intensity_profile, num_rings);
 		if(found)
+		{
+			if(num_rings ==1 ){
+			Mat sample(1, 100, DataType<float>::type);
+			Mat profile_mat(intensity_profile);
+			transpose(profile_mat, profile_mat);
+			resize(profile_mat, sample, sample.size());
+/*
+		FileStorage file("test2.xml", FileStorage::WRITE);
+		file<<"Orig_sample"<<profile_mat;
+		file<<"Sample"<<sample;
+		file.release();
+*/
+			Mat responses(K,1,DataType<float>::type);
[…]

### 2014-02-21 DetectFiducial/src/main.cpp
added code to output tag on image

@@ -125,6 +125,8 @@ int main(int argc, char* argv[])
 	createTrainingData(dirname, trainingData, response);
 	const int K =11;
 	CvKNearest knn(trainingData, response, Mat(), false, K);
+
+	Mat output = input.clone();
 	for(int i=0; i<numClusters; i++)
 	{
 		float * row = (float *)&clusters.at<float>(i,0);
@@ -134,6 +136,7 @@ int main(int argc, char* argv[])
 		int y2 = row[3];
 		Mat pts;
 		Point pt1(x1,y1), pt2(x2,y2);
+
 #ifdef DEBUG2
 	  rectangle(clonedgaborOutput, pt1, pt2, Scalar(255,0,0) );
 	  imshow("gabor", clonedgaborOutput);
@@ -150,36 +153,49 @@ int main(int argc, char* argv[])
 		intensity_profile.clear();
 		int num_rings = -1;
 		found = detectCode(pts, x1, y1, x2, y2, input, intensity_profile, num_rings);
+		char classid[2];
+		string str = "Class:";
 		if(found)
 		{
+			rectangle(output, pt1, pt2, Scalar(0,255,0));
 			if(num_rings ==1 ){
-			Mat sample(1, 100, DataType<float>::type);
-			Mat profile_mat(intensity_profile);
-			transpose(profile_mat, profile_mat);
-			resize(profile_mat, sample, sample.size());
-/*
+				Mat sample(1, 100, DataType<float>::type);
+				Mat profile_mat(intensity_profile);
+				transpose(profile_mat, profile_mat);
+				resize(profile_mat, sample, sample.size());
+				/*
 		FileStorage file("test2.xml", FileStorage::WRITE);
 		file<<"Orig_sample"<<profile_mat;
 		file<<"Sample"<<sample;
 		file.release();
-*/
-			Mat responses(K,1,DataType<float>::type);
-			const float ** neighbours;
+				 */
+				Mat responses(K,1,DataType<float>::type);
+				const float ** neighbours;
 
-			Mat results(sample.rows, 1, DataType<float>::type);
-			Mat dist(K, 1, DataType<float>::type);
-			knn.find_nearest (sample, K, results, responses, dist);
-			cout<<"Class:"<<results.at<float>(0)<<"\n";
+				Mat results(sample.rows, 1, DataType<float>::type);
+				Mat dist(K, 1, DataType<float>::type);
[…]

### 2014-02-23 ECCV/paper.tex
1. Added abstract, introduction and some more related work

@@
 % \renewcommand\makeLineNumber {\hss\thelinenumber\ \hspace{6mm} \rlap{\hskip\textwidth\ \hspace{6.5mm}\thelinenumber}}
-% \linenumbers
+% \linenumbers \
 \pagestyle{headings}
@@
 \begin{abstract}
+Fiducial markers are commonly used to track an object in an unknown environment
+and finds use in various applications in Virtual Reality, Medical imaging,
+Surveys, etc. The performance of popular fiducials is satisfactory when there is
+little motion or no motion in the device obtaining the imagery. But when there
+is continuous and swift motion, as in the case of low cost quadcopters,
+performance of these fiducials degrade significantly due to motion blur.
+Inspired from Circular Data Matrix\cite{NaimarkF02} we have designed a fiducial
+that may be thought of as a binary code.  It contains concentric white rings of
+equal widths on a black background with a blurred border. Our
+algorithm is based on the fact that there is no blur in the direction
+perpendicular to the direction of the motion.
 
@@
 \section{Introduction}
+A fiducial marker or simply a fiducial is an synthetic object placed in the
+scene, which can provide additional information about the environment.
 
-\subsection{Motivation}
-Tracking vehicle by an autonomous vehicle. \\
-Fiducials for tracking under motion blur.
+Low cost quadcopters such as AR Drone are very unstable which causes non-uniform
+motion resulting lot of motion blur in captured images. Also, as image transfer
+is done through wireless media using UDP, there is possibility of missing 
+intermediate frames . It results in lower frame rate (maximum 20-25 frames per
+second (FPS)) instead of normal rate of 30 FPS. This dropping of frames may
+cause drastic change in position of object in successive frames. Thus,
+performance of traditional tracking methods is not satisfactory for tracking
+through quadcopters. Our aim is to design a fiducial which we will be able to track under significant
+amount of motion blur and is robust in terms of drastic change in its position
+in successive frames.
+
+We observed that blur in a single frame captured through quadcopter is linear.
+There is no blur in the direction perpendicular to the direction of motion. We
+tried to design a fiducial whose ``signature'' remains intact in any direction.
 
 \section{Related Work}
-ARToolkit \cite{ARToolkit02} \cite{kato-artoolkit} /ARTag \cite{Fiala05} \\
+The ARToolkit \cite{ARToolkit02} \cite{kato-artoolkit} is well known toolkit in
+AR system, widely used to find pose of the object on which it is placed.
+Fiala et.al \cite{Fiala05} developed fiducial named, ARTag, bi-tonal system
+containing 2002 planar markers, each consisting of a square border and an
+interior region filled with a 6x6 grid of black or white cells. It proved to be
+more efficient than \cite{ARToolkit02} in terms of detection rate as well as the
+number of different patterns which can be created.
+
+Concentric Rings\cite{concentric} \\
+Multicolor rings \cite{Cho:2001} \cite{Cho97fastcolor} \\
 Circular Data Matrix Fiducial System \cite{NaimarkF02} \\
-Reliable Fiducial Detection in Natural Scenes \cite{ClausF04}\\
+
+Zhang el. al.\cite{Zhang:2002} and Claus et. al. \cite{ClausF04} have done
+quite comprehensive comparative study of various fiducial marker systems with
+respect to processing time, recognition rate and accuracy with
+respect to viewing angle and distance.
+
 RUNE-Tag \cite{runetag11} \\
@@
 
-\section{Our Contribution}
+\section{Design of Fiducial}
 
-\subsection{Design of Fiducial}
-
-\subsection{Fiducial Detection Algorithm}
+\section{Fiducial Detection Algorithm}
 \begin{itemize}
@@
 
-\section{Conclusion}
+\section{Discussion}
 
-\section{Future Work}
+\section{Conclusion and Future Work}
+
 Pose Estimation
+
 \bibliographystyle{splncs}

### 2014-02-24 ECCV/paper.tex
Added Design, Algorithm.

@@
 \section{Design of Fiducial}
+Inspired from Circular Data Matrix\cite{NaimarkF02} we have designed a fiducial
+that may be thought of as a binary code.  It contains concentric white rings of
+equal widths on a black background with a blurred border. The outermost and
+innermost rings represent the start and end of the code and is embedded in the
+fiducial; these are not considered part of the code itself. The binary code is
+represented by the presence (or absence) of rings between ``marker'' rings.
+Depending on which ring is present or absent, the resulting binary code will
+change. The number of different patterns depends on the number of bits in the
+binary code. For example, if the binary code has three bits, there will be a
+maximum of three rings between``marker'' rings and we end up with eight
+different patterns.
+
+\begin{figure}
+\centering
+  \includegraphics[width=.2\linewidth]{newconcentric_00.pdf}  
+  \includegraphics[width=.2\linewidth]{newconcentric_01.pdf}
+  \includegraphics[width=.2\linewidth]{newconcentric_10.pdf}
+  \includegraphics[width=.2\linewidth]{newconcentric_11.pdf}
+  \caption{Two bit binary coded Fiducials (from left to right: Binary Code 00,
+  Binary Code 01, Binary Code 10, Binary Code 11)}
+  \label{fig:fiducials}
+\end{figure}
 
 \section{Fiducial Detection Algorithm}
+Overall flow of fiducial detection algorithm can be summarised as follows:
 \begin{itemize}
@@
 
-\section{Experimental Results}
+\textbf{Gabor Filter}: A 2D Gabor filter is a Gaussian kernel function modulated
+by a sinusoidal plane wave\cite{GaborFilter}. It is used to find high gradient
+patches from the image. In our case, it will detect blur invariant sections of the fiducials We
+have applied Gabor filter for eight different orientations and then calculated
+L2 norm of all outputs.
+
+\textbf{Clustering}: Connected components are found from the Gabor output. 
+These connected components are then clustered in hierarchical fashion, to find
+the group of closely positioned patches.
+
+\textbf{PCA}: Principal Component Analysis is done on the clustered Gabor
+output. Along 1st principal component, intensity profile in the original image is found.
+Number of transitions in the intensity profile will give us the number of rings.
+
+\textbf{Classification}: Each synthetic fiducial pattern is blurred along 36
+orientations (0, 10, 20, \ldots , 350) and intensity profile along first
+principal component from every output is taken as training data for that fiducial pattern.
+Training data for patterns having same number of rings is grouped together;
+e.g., in two bit binary coded fiducial, training data for pattern “01” and “10”
+will be grouped together. Now, depending on the number of detected rings, test
+pattern is matched against corresponding training data using K-Nearest Neighbor
+Classifier (K=5).
+
+\section{Experimental Validation}
 \subsection{Comparison}

### 2014-02-24 ECCV/paper.tex
Changed template to ECCV 2014

@@
 
-Concentric Rings\cite{concentric} \\
+Concentric Rings\cite{NaimarkF02} \\
 Multicolor rings \cite{Cho:2001} \cite{Cho97fastcolor} \\

### 2014-02-24 ECCV/paper.tex
Added results.

@@
 \mainmatter
-\def\ECCV12SubNumber{***}  % Insert your submission number here
+\def\ECCV14SubNumber{150}  % Insert your submission number here
 
@@
 
-\titlerunning{ECCV-12 submission ID \ECCV12SubNumber}
+\titlerunning{ECCV-14 submission ID \ECCV14SubNumber}
 
-\authorrunning{ECCV-12 submission ID \ECCV12SubNumber}
+\authorrunning{ECCV-14 submission ID \ECCV14SubNumber}
 
 \author{Anonymous ECCV submission}
-\institute{Paper ID \ECCV12SubNumber}
+\institute{Paper ID \ECCV14SubNumber}
 
@@
 perpendicular to the direction of the motion.
-
+\dots
+\keywords{Fiducials, Blur Invariant Tracking,}
 \end{abstract}
@@
 performance of traditional tracking methods is not satisfactory for tracking
-through quadcopters. Our aim is to design a fiducial which we will be able to track under significant
-amount of motion blur and is robust in terms of drastic change in its position
-in successive frames.
+through quadcopters. Our aim is to design a fiducial which we will be able to
+track under significant amount of motion blur and is robust in terms of drastic
+change in its position in successive frames.
 
@@
 \textbf{Gabor Filter}: A 2D Gabor filter is a Gaussian kernel function modulated
-by a sinusoidal plane wave\cite{GaborFilter}. It is used to find high gradient
-patches from the image. In our case, it will detect blur invariant sections of the fiducials We
+by a sinusoidal plane wave. It is used to find high gradient patches from the
+image. In our case, it will detect blur invariant sections of the fiducials. We
 have applied Gabor filter for eight different orientations and then calculated
@@
 Training data for patterns having same number of rings is grouped together;
-e.g., in two bit binary coded fiducial, training data for pattern “01” and “10”
-will be grouped together. Now, depending on the number of detected rings, test
-pattern is matched against corresponding training data using K-Nearest Neighbor
-Classifier (K=5).
+e.g., in two bit binary coded fiducial, training data for pattern ``01'' and
+``10'' will be grouped together. Now, depending on the number of detected
+rings, test pattern is matched against corresponding training data using
+K-Nearest Neighbor Classifier (K=5).
+
+\begin{figure}
+\centering
+  \includegraphics[width=.3\linewidth]{concentric_01_5_blurred_180.jpg}  
+  \includegraphics[width=.3\linewidth]{concentric_01_5_blurred_45.jpg}
+  \includegraphics[width=.3\linewidth]{concentric_01_5_blurred_90.jpg}  
+  \caption{Sample images used to create training data for the fiducial pattern
+  with binary code ``01''}
+\end{figure}
 
 \section{Experimental Validation}
+Our system has been tested on the image sequences captured from AR Drone
+quadcopter. Each image sequence contains frames containing different fiducial
+pattern. Sample output for each fiducial pattern is shown in Fig.
+\ref{fig:output0} -- Fig. \ref{fig:output3}.
+
+\begin{figure}
+\centering
+  \includegraphics[width=.8\linewidth]{output_00.jpg}
+  \caption{Sample output for the fiducial pattern with binary code ``00''}
+  \label{fig:output0}
+\end{figure}
+
+\begin{figure}
+\centering
+  \includegraphics[width=.8\linewidth]{output_01.jpg}
+  \caption{Sample output for the fiducial pattern with binary code ``01''}
+  \label{fig:output1}
+\end{figure}
+
+\begin{figure}
+\centering
+  \includegraphics[width=.8\linewidth]{output_10.jpg}
+  \caption{Sample output for the fiducial pattern with binary code ``10''}
+  \label{fig:output2}
+\end{figure}
+
+\begin{figure}
+\centering
+  \includegraphics[width=.8\linewidth]{output_11.jpg}
+  \caption{Sample output for the fiducial pattern with binary code ``11''}
+  \label{fig:output3}
+\end{figure}
+
+Our system has also been tested on images containing multiple fiducial patterns
+in the same frame. Our algorithm successfully detected all fiducial patterns as
+well as correctly classified them as shown in Fig. \ref{fig:output_all}
+\begin{figure}
+\centering
+  \includegraphics[width=.8\linewidth]{output_all_2.jpg}
+  \caption{Sample output containing all two bit binary coded fiducial patterns}
+  \label{fig:output_all}
+\end{figure}
+
 \subsection{Comparison}

### 2014-02-25 ECCV/paper.tex
Expanded Related Work

@@
 performance of these fiducials degrade significantly due to motion blur.
-Inspired from Circular Data Matrix\cite{NaimarkF02} we have designed a fiducial
+Inspired from Circular Data Matrix\cite{NaimarkF02}, we have designed a fiducial
 that may be thought of as a binary code. It contains concentric white rings of
-equal widths on a black background with a blurred border. Our
+equal widths on a black background with a blurred border. Our fiducial detection
 algorithm is based on the fact that there is no blur in the direction
-perpendicular to the direction of the motion.
-\dots
-\keywords{Fiducials, Blur Invariant Tracking,}
+perpendicular to the direction of the motion. We will show through experimental
+validation that our fiducial works better than popular fiducials such as
+ARTag under signifacant motion blur.
+
+\keywords{Fiducials, Tracking, Blur Invariant}
 \end{abstract}
@@
 motion resulting lot of motion blur in captured images. Also, as image transfer
-is done through wireless media using UDP, there is possibility of missing 
-intermediate frames . It results in lower frame rate (maximum 20-25 frames per
-second (FPS)) instead of normal rate of 30 FPS. This dropping of frames may
-cause drastic change in position of object in successive frames. Thus,
-performance of traditional tracking methods is not satisfactory for tracking
-through quadcopters. Our aim is to design a fiducial which we will be able to
-track under significant amount of motion blur and is robust in terms of drastic
-change in its position in successive frames.
+is done through wireless media using User Datagram Protocol (UDP), there is
+possibility of missing intermediate frames . It results in lower frame rate
+(around 15 frames per second (FPS)) instead of normal rate of 30 FPS. This
+frequent dropping of frames may cause drastic change in position of object in
+successive frames. Thus, performance of traditional tracking methods is not
+satisfactory for tracking through quadcopters. Our aim is to design a fiducial
+which we will be able to track under significant amount of motion blur and is
+robust in terms of drastic change in its position in successive frames.
 
@@
 The ARToolkit \cite{ARToolkit02} \cite{kato-artoolkit} is well known toolkit in
-AR system, widely used to find pose of the object on which it is placed.
-Fiala et.al \cite{Fiala05} developed fiducial named, ARTag, bi-tonal system
-containing 2002 planar markers, each consisting of a square border and an
-interior region filled with a 6x6 grid of black or white cells. It proved to be
-more efficient than \cite{ARToolkit02} in terms of detection rate as well as the
-number of different patterns which can be created.
+Augmented Reality system, widely used to find pose of the object on which it is
+placed.  Fiala et al. \cite{Fiala05} developed fiducial named, ARTag, bi-tonal
+system containing 2002 planar markers, each consisting of a square border and
+an interior region filled with a 6x6 grid of black or white cells. It proved to
+be more efficient than \cite{ARToolkit02} in terms of marker recognition rate
+as well as the number of different patterns which can be created.
 
-Concentric Rings\cite{NaimarkF02} \\
-Multicolor rings \cite{Cho:2001} \cite{Cho97fastcolor} \\
-Circular Data Matrix Fiducial System \cite{NaimarkF02} \\
+Concentric Rings are reported used first by Gatrell et al.\cite{concentric} for
+monocular pose estimation as well as object identification in space. Cho et al.
+\cite{Cho:2001}\cite{Cho97fastcolor} have used multi color rings in wide area
+tracking in large scale applications. In \cite{NaimarkF02}, Naimark et al.
+have developed ``Circular Data Matrix Fiducial System'', for wide area tracking.
 
-Zhang el. al.\cite{Zhang:2002} and Claus et. al. \cite{ClausF04} have done
+Zhang el. al.\cite{Zhang:2002} and Claus et al. \cite{ClausF04} have done
 quite comprehensive comparative study of various fiducial marker systems with
@@
 
-RUNE-Tag \cite{runetag11} \\
-Pi-Tag \cite{Pitag13} \\
-Blut \cite{Wu:2011}
+Bergamasco et al. \cite{runetag11} developed RUNE-Tag, fiducial marker
+system which works under large amount of occlusion. Bergamasco et al. also 
+designed Pi-Tag \cite{Pitag13}, marker design based on projective
+invariants.
+Wu et al.\cite{Wu:2011} have developed BLUr-driven Tracker (BLUT) framework for
+tracking motion-blurred targets.
 
@@
 \centering
-  \includegraphics[width=.2\linewidth]{newconcentric_00.pdf}  
-  \includegraphics[width=.2\linewidth]{newconcentric_01.pdf}
-  \includegraphics[width=.2\linewidth]{newconcentric_10.pdf}
-  \includegraphics[width=.2\linewidth]{newconcentric_11.pdf}
+  \includegraphics[width=.22\linewidth]{newconcentric_00.pdf}  
+  \includegraphics[width=.22\linewidth]{newconcentric_01.pdf}
+  \includegraphics[width=.22\linewidth]{newconcentric_10.pdf}
+  \includegraphics[width=.22\linewidth]{newconcentric_11.pdf}
   \caption{Two bit binary coded Fiducials (from left to right: Binary Code 00,
@@
 \section{Fiducial Detection Algorithm}
+Our fiducial detection strategy is different from \cite{NaimarkF02} and works
+under significant amount of blur. Our algorithm is based on the fact that there
+is no blur in the direction perpendicular to the direction of the motion.
 Overall flow of fiducial detection algorithm can be summarised as follows:
@@
 image. In our case, it will detect blur invariant sections of the fiducials. We
-have applied Gabor filter for eight different orientations and then calculated
-L2 norm of all outputs.
+have applied Gabor filter for eight different orientations ($\theta = 0, 45,
+90, 135, 180, 225, 270, 315$) and then calculated L2 norm of all outputs.
 
@@
 \textbf{PCA}: Principal Component Analysis is done on the clustered Gabor
-output. Along 1st principal component, intensity profile in the original image is found.
-Number of transitions in the intensity profile will give us the number of rings.
+output. Along first principal component, intensity profile in the original image
+is found. Number of transitions in the intensity profile will give us the
+number of rings.
 
@@
 \section{Discussion}
-
+\begin{itemize}
+\item Processing Time
+\item False Positives and False Negatives
+\item Pose Estimation
+\end{itemize}
 \section{Conclusion and Future Work}
-
-Pose Estimation
 

### 2014-02-25 ECCV/paper.tex
Added other fiducial images

@@
 \usepackage{graphicx}
+\usepackage{caption}
+\usepackage{subcaption}
+\captionsetup{compatibility=false}
 \usepackage{amsmath,amssymb} % define this before the line numbering.
@@
 \usepackage[width=122mm,left=12mm,paperwidth=146mm,height=193mm,top=12mm,paperheight=217mm]{geometry}
+
 \begin{document}
@@
 % \linenumbers \
+
 \pagestyle{headings}
@@
 \section{Related Work}
+
+\begin{figure}
+
+ \begin{subfigure}[b]{0.19\textwidth}  
+ \centering 
+  \includegraphics[width=\linewidth]{pattKanji.pdf}
+  \caption{ARToolkit}  
+ \end{subfigure}
+ \begin{subfigure}[b]{0.19\textwidth}
+  \centering
+  \includegraphics[width=\linewidth]{ARtag.jpg}
+  \caption{ARTag}
+ \end{subfigure}
+ \begin{subfigure}[b]{0.19\textwidth}
+  \centering
+  \includegraphics[width=\linewidth]{intersense.jpg}
+  \caption{Intersense}  
+ \end{subfigure}
+ \begin{subfigure}[b]{0.19\textwidth}
+  \centering
+  \includegraphics[width=\linewidth]{pifiducial.png}
+  \caption{Pi-Tag}  
+ \end{subfigure}
+ \begin{subfigure}[b]{0.19\textwidth}
+  \centering
+  \includegraphics[width=\linewidth]{newconcentric_01.pdf}
+  %\includegraphics[width=0.5\linewidth]{newconcentric_10.pdf}
+  \caption{Our Fiducial}  
+ \end{subfigure}
+ \caption{Various Fiducial Marker Designs}
+ \label{fig:previous_work}  
+\end{figure}
+
 The ARToolkit \cite{ARToolkit02} \cite{kato-artoolkit} is well known toolkit in
@@
 
-Concentric Rings are reported used first by Gatrell et al.\cite{concentric} for
-monocular pose estimation as well as object identification in space. Cho et al.
+Concentric Rings are reportedly used first by Gatrell et al.\cite{concentric}
+for monocular pose estimation as well as object identification in space. Cho et al.
 \cite{Cho:2001}\cite{Cho97fastcolor} have used multi color rings in wide area
@@
 invariants.
+
+\subsection{Limitations}
+The main hurdle in detection of current fiducials is, the detecton of features;
+lines in \cite{ARToolkit02}, corners in \cite{Fiala05} while ellipses in
+\cite{Cho:2001}, \cite{Cho97fastcolor}, \cite{runetag11} and \cite{Pitag13}.
+Such features are very difficult to correctly detect under significant motion
+blur. So, under blur, recognition rate of these fiducials is very low.
+
 Wu et al.\cite{Wu:2011} have developed BLUr-driven Tracker (BLUT) framework for
-tracking motion-blurred targets.
+tracking motion-blurred targets. BLUT framework works well when there is
+uniform motion and the position of tracked object does not change drastically in
+successive frames. But in our case, due to frequntly dropping of intermediate
+frame, this criterion may not be satisfied.
 
@@
 represented by the presence (or absence) of rings between ``marker'' rings.
+
 Depending on which ring is present or absent, the resulting binary code will
@@
 maximum of three rings between``marker'' rings and we end up with eight
-different patterns.
+different patterns. Fig. \ref{fig:fiducials} shows two bit binary coded
+fiducials.
 
@@
 \centering
-  \includegraphics[width=.3\linewidth]{concentric_01_5_blurred_180.jpg}  
-  \includegraphics[width=.3\linewidth]{concentric_01_5_blurred_45.jpg}
-  \includegraphics[width=.3\linewidth]{concentric_01_5_blurred_90.jpg}  
+  \includegraphics[width=.22\linewidth]{concentric_01_5_blurred_180.jpg}  
+  \includegraphics[width=.22\linewidth]{concentric_01_5_blurred_45.jpg}
+  \includegraphics[width=.22\linewidth]{concentric_01_5_blurred_90.jpg}  
+  \includegraphics[width=.22\linewidth]{concentric_01_5_blurred_135.jpg}
   \caption{Sample images used to create training data for the fiducial pattern

### 2014-02-26 ECCV/paper.tex
1. Added related work about tracking 2. Added simulation details

@@
 \usepackage{graphicx}
-\usepackage{caption}
+\usepackage[font=small]{caption}
 \usepackage{subcaption}
@@
 
+Our problem may be classified broadly in two areas; fiducial markers and
+tracking. So, we will briefly discuss work done in both areas.
 \begin{figure}
-
+ \begin{subfigure}[b]{0.19\textwidth}
+  \centering
+  \includegraphics[width=\linewidth]{intersense.jpg}
+  Intersense\cite{NaimarkF02}  
+ \end{subfigure}
  \begin{subfigure}[b]{0.19\textwidth}  
@@
   \includegraphics[width=\linewidth]{pattKanji.pdf}
-  \caption{ARToolkit}  
+  ARToolkit\cite{ARToolkit02}  
  \end{subfigure}
@@
   \includegraphics[width=\linewidth]{ARtag.jpg}
-  \caption{ARTag}
- \end{subfigure}
- \begin{subfigure}[b]{0.19\textwidth}
-  \centering
-  \includegraphics[width=\linewidth]{intersense.jpg}
-  \caption{Intersense}  
+  ARTag\cite{Fiala05}
  \end{subfigure} 
@@
   \includegraphics[width=\linewidth]{pifiducial.png}
-  \caption{Pi-Tag}  
+  Pi-Tag\cite{Pitag13}  
  \end{subfigure}
@@
   \includegraphics[width=\linewidth]{newconcentric_01.pdf}  
-  %\includegraphics[width=0.5\linewidth]{newconcentric_10.pdf}
-  \caption{Our Fiducial}  
+  Our Fiducial  
  \end{subfigure}
@@
 
-\subsection{Limitations}
 The main hurdle in detection of current fiducials is, the detecton of features;
@@
 \cite{Cho:2001}, \cite{Cho97fastcolor}, \cite{runetag11} and \cite{Pitag13}.
-Such features are very difficult to correctly detect under significant motion
+Such features are very difficult to detect accurately under significant motion
 blur. So, under blur, recognition rate of these fiducials is very low.
 
-Wu et al.\cite{Wu:2011} have developed BLUr-driven Tracker (BLUT) framework for
-tracking motion-blurred targets. BLUT framework works well when there is
-uniform motion and the position of tracked object does not change drastically in
-successive frames. But in our case, due to frequntly dropping of intermediate
-frame, this criterion may not be satisfied.
+Fiducial detection in video may be considered as tracking problem where tracked
+object is fiducial itself. Visual tracking plays an important role in
+surveillance, robotics, human computer interaction, and medical
+imaging\cite{Yilmaz:2006}. Yilmaz et al.\cite{Yilmaz:2006} have done survey of
+various tracking methods. Most tracking methods
+( \cite{Ross:2008} \cite{Wu:2009} \cite{Perez02} \cite{Mei:2009} ) assume image
+sequence to be blur free. But in reality, motion blur is inherent part of most
+of the videos. Wu et al.\cite{Wu:2011} have developed BLUr-driven Tracker (BLUT)
+framework for tracking motion-blurred targets. BLUT is based on the observation
+that although motion blurs degrade the visual features of the target, they, at
+thde same time, provide useful cues about the movements to help tracking.
+
+BLUT framework successfully tracks blurred target when there is uniform motion
+and the position of tracked object does not change drastically in successive
+frames. But in our case, due to frequntly dropping of intermediate frame, this
+criterion may not be satisfied.
 
@@
 \section{Experimental Validation}
+First, we have used synthetic images to test resilience to blur. We have scaled
+down ARTag fiducial and our fiducial to size 150x150.  Then, we blurred both
+fiducials along all orientations using different scales. Finally, we tried to
+detect ARTag in these blurred images using ALVAR library\cite{alvar} and our fiducial
+using algorithm given in previous section.
+
 Our system has been tested on the image sequences captured from AR Drone

### 2014-02-26 DetectFiducial/src/main.cpp
Added code to put bigger text on background in output image.

@@ -17,7 +17,7 @@
 
 
 //#define TRAIN_MODE
-//#define DEBUG
+//define DEBUG
 //#define DEBUG2
 //#define DEBUG3
 
@@ -86,7 +86,9 @@ int main(int argc, char* argv[])
 	Mat gaborOutput(input.size(), CV_8UC1);
 	gbFilter.filter(input, gaborOutput);
 #ifdef DEBUG
-	Mat clonedgaborOutput = gaborOutput.clone();
+	//Mat clonedgaborOutput = gaborOutput.clone();
+	Mat clonedgaborOutput(gaborOutput.size(), CV_8UC3);
+	cvtColor(gaborOutput, clonedgaborOutput, CV_GRAY2BGR, 3);
 #endif
 
 #ifndef TRAIN_MODE
@@ -109,12 +111,13 @@ int main(int argc, char* argv[])
 		int y2 = row[3];
 		Point pt1(x1,y1), pt2(x2,y2);
 #ifdef DEBUG
-		rectangle(cloned_input, pt1, pt2, Scalar(0,255,0) );
+		rectangle(clonedgaborOutput, pt1, pt2, Scalar(0,255,0), 3);
 #endif
 	}
 #ifdef DEBUG
-	imshow("box",cloned_input);
-	waitKey();
+	imshow("box",clonedgaborOutput);
+	imwrite("cluster.jpg", clonedgaborOutput);
+	//waitKey();
 #endif
 
 	//Detect code in the bounding box
@@ -157,7 +160,7 @@ int main(int argc, char* argv[])
 		string str = "Class:";
 		if(found)
 		{
-			rectangle(output, pt1, pt2, Scalar(0,255,0));
+			rectangle(output, pt1, pt2, Scalar(0,255,0), 3);
 			if(num_rings ==1 ){
 				Mat sample(1, 100, DataType<float>::type);
 				Mat profile_mat(intensity_profile);
@@ -191,10 +194,15 @@ int main(int argc, char* argv[])
 					str.append("3");
 				}
 			}
-			putText(output, str, pt2, FONT_HERSHEY_PLAIN, 1, Scalar(255,0,0));
+			Point pt_text_start = pt2 - Point(0,23);
+			Point pt_text_end = pt2 + Point(82,0);
+			rectangle(output,pt_text_start, pt_text_end, Scalar(0,255,255),-1);
[…]

### 2014-02-26 ECCV/paper.tex
1. Changed output images 2. Added workflow, teaser

@@
 
+\begin{figure}
+\includegraphics[width=\linewidth]{teaser.pdf}
+\caption{Figure showing experimental setup and comparison of
+output of ALVAR\cite{alvar} (for detecting ARTag) versus output of our
+algorithm, in normal and blurred scene}
+\end{figure}
+
 \section{Related Work}
-
 Our problem may be classified broadly in two areas; fiducial markers and
@@
 \section{Design of Fiducial}
+
+\begin{figure}
+\centering
+  \includegraphics[width=.22\linewidth]{newconcentric_00.pdf}  
+  \includegraphics[width=.22\linewidth]{newconcentric_01.pdf}
+  \includegraphics[width=.22\linewidth]{newconcentric_10.pdf}
+  \includegraphics[width=.22\linewidth]{newconcentric_11.pdf}
+  \caption{Two bit binary coded Fiducials (from left to right: Binary Code 00,
+  Binary Code 01, Binary Code 10, Binary Code 11)}
+  \label{fig:fiducials}
+\end{figure}
+
 Inspired from Circular Data Matrix\cite{NaimarkF02} we have designed a fiducial
@@
 
+\section{Fiducial Detection Algorithm}
 \begin{figure}
-\centering
-  \includegraphics[width=.22\linewidth]{newconcentric_00.pdf}  
-  \includegraphics[width=.22\linewidth]{newconcentric_01.pdf}
-  \includegraphics[width=.22\linewidth]{newconcentric_10.pdf}
-  \includegraphics[width=.22\linewidth]{newconcentric_11.pdf}
-  \caption{Two bit binary coded Fiducials (from left to right: Binary Code 00,
-  Binary Code 01, Binary Code 10, Binary Code 11)}
-  \label{fig:fiducials}
+\includegraphics[width=\linewidth]{overall_flow.pdf}
+\caption{Overall Workflow}
 \end{figure}
-
-\section{Fiducial Detection Algorithm}
 Our fiducial detection strategy is different from \cite{NaimarkF02} and works

### 2014-02-27 ECCV/paper.tex
Added introduction about fiducials and relevant references.

@@
 \usepackage[width=122mm,left=12mm,paperwidth=146mm,height=193mm,top=12mm,paperheight=217mm]{geometry}
+\usepackage{multirow}
 
@@
 algorithm is based on the fact that there is no blur in the direction
-perpendicular to the direction of the motion. We will show through experimental
-validation that our fiducial works better than popular fiducials such as
-ARTag under signifacant motion blur.
+perpendicular to the direction of the motion. The algorithm finds this
+direction in a simple but accurate way. Then, we find ``signature'' of our
+fiducial along this direction and further classify it to find the actual code
+embedded in the fiducial. We will show through experimental validation that our
+fiducial works better than popular fiducials such as ARTag under signifacant motion blur.
 
@@
 A fiducial marker or simply a fiducial is an synthetic object placed in the
-scene, which can provide additional information about the environment.
+scene, which can provide additional information about the environment. Sometimes
+naturally available features in a scene may be used as replacement to fiducials.
+But, natural features may not be available always and quality cannot be
+guranteed in every scene. So, results are not satisfactory in uncontrolled
+environment and hence use of such features is limited. Artificial fiducials are
+widely used in Augmented Reality(AR)\cite{Zhang:2002}\cite{Dorfmuller99}
+applications, vision based navigation of robots\cite{Davison:2007} etc.
 
-Low cost quadcopters such as AR Drone are very unstable which causes non-uniform
-motion resulting lot of motion blur in captured images. Also, as image transfer
-is done through wireless media using User Datagram Protocol (UDP), there is
-possibility of missing intermediate frames . It results in lower frame rate
-(around 15 frames per second (FPS)) instead of normal rate of 30 FPS. This
-frequent dropping of frames may cause drastic change in position of object in
-successive frames. Thus, performance of traditional tracking methods is not
-satisfactory for tracking through quadcopters. Our aim is to design a fiducial
-which we will be able to track under significant amount of motion blur and is
-robust in terms of drastic change in its position in successive frames.
+Recently, use of Unmanned Aerial Vehicles(UAV) such as quadcopters is increased
+in various tracking activities (e.g. aerial surveillance, search and rescue
+operations etc.).Low cost quadcopters such as AR Drone are very unstable which
+causes non-uniform motion resulting lot of motion blur in captured images.
+Also, as image transfer is done through wireless media using User Datagram
+Protocol (UDP), there is possibility of missing intermediate frames . It
+results in lower frame rate (around 15 frames per second (FPS)) instead of
+normal rate of 30 FPS. This frequent dropping of frames may cause drastic
+change in position of object in successive frames. Thus, performance of
+traditional tracking methods is not satisfactory for tracking through
+quadcopters. Our aim is to design a fiducial which we will be able to track
+under significant amount of motion blur and is robust in terms of drastic
+change in its position in successive frames.
 
@@
 
+%\begin{tabular}
+
+%\end{tabular}
 Our system has been tested on the image sequences captured from AR Drone

### 2014-02-28 ECCV/paper.tex
Cropped output files, removed space between figures and text
Cleaned up bibliography, added table related to blur angle range

@@
 \usepackage{multirow}
+\usepackage{tabularx}
+\newcolumntype{Y}{>{\centering\arraybackslash}X}
+\captionsetup[table]{belowskip=12pt,aboveskip=4pt}
+\setlength{\floatsep}{5pt plus 2pt minus 2pt}
+\setlength{\textfloatsep}{5pt plus 2pt minus 2pt}
+\setlength{\intextsep}{5pt plus 2pt minus 2pt}
 
@@
   \centering
-  \includegraphics[width=\linewidth]{newconcentric_01.pdf}  
+  \includegraphics[width=\linewidth]{our_fiducial}  
   Our Fiducial  
@@
 \section{Design of Fiducial}
+
+We conducted a small experiment to test ARTag's resilience towards blur.
+We scaled down ARTag fiducial to size 150x150.  Then, we blurred ARTag 
+at various orientations using different scales. Finally, we tried to detect
+ARTag in these blurred images using ALVAR library\cite{alvar}.
+
+\begin{table}
+\caption{Recognition rate of AR Tag at various blur scales}
+\centering
+\begin{tabularx}{0.75\textwidth}{c *{6}{|Y}|}
+\cline{2-6}
+& \multicolumn{5}{ c |}{Recognition Rate (in percent)} \\
+\cline{2-6} & \multicolumn{5}{ c |}{Blur Scale} \\ \cline{2-6}
+& 30 & 35 & 40 & 45 & 50 \\ \cline{1-6}
+\multicolumn{1}{ | c | }{ARTAg} & 100 & 19 & 9 & 5 & 0 \\ \cline{1-6}
+\cline{1-6}
+\end{tabularx}
+\label{tab:ARTag_blur}
+\end{table}
+
+From Table \ref{tab:ARTag_blur}, it can be clearly seen that performance of
+ARTag drastically with increase in blur scale.
+
+We have also analysed the recognition rate along different blur orientations at
+different blur scales. We found that per blur scale, at certain blur
+orientations, recognition of ARTag fails. Table shows the range of blur angles
+for which we are able to recognise the ARTag at different blur scales.
+
+\begin{table}
+\caption{Blur angle range}
+\centering
+\begin{tabularx}{0.75\textwidth}{|Y|Y|}
+\cline{1-2}
+Blur Scale & Blur Angle Range \\ \cline{1-2}
+35 & 32--58 \\ \cline{1-2}
+40 & 41--48 \\ \cline{1-2}
+45 & 41--48 \\ \cline{1-2}
+50 & 44--46 \\ \cline{1-2}
+\end{tabularx}
+\end{table}
 
@@
 \section{Experimental Validation}
-First, we have used synthetic images to test resilience to blur. We have scaled
-down ARTag fiducial and our fiducial to size 150x150.  Then, we blurred both
-fiducials along all orientations using different scales. Finally, we tried to
-detect ARTag in these blurred images using ALVAR library\cite{alvar} and our fiducial
-using algorithm given in previous section.
 
-%\begin{tabular}
-
-%\end{tabular}
 Our system has been tested on the image sequences captured from AR Drone

### 2014-02-28 ECCV/paper.tex
Added Introduction about quadcopter navigation. Added missing figure.

@@
 \section{Introduction}
-A fiducial marker or simply a fiducial is an synthetic object placed in the
-scene, which can provide additional information about the environment. Sometimes
-naturally available features in a scene may be used as replacement to fiducials.
-But, natural features may not be available always and quality cannot be
-guranteed in every scene. So, results are not satisfactory in uncontrolled
-environment and hence use of such features is limited. Artificial fiducials are
-widely used in Augmented Reality(AR)\cite{Zhang:2002}\cite{Dorfmuller99}
+Recently, use of Unmanned Aerial Vehicles(UAV) such as quadcopters is increased
+in various tracking activities e.g. aerial surveillance, search and rescue
+operations etc. Navigation of these vehicles is mainly based on the
+onboard inertial sensors. But sensor based measurments are prone to errors. So,
+visual cues captured through onboard camera can be used along with the sensor
+based measurments.  But, natural features may not be available always and
+quality cannot be guranteed in every scene. So, results are not satisfactory in
+uncontrolled environment and hence use of such features is limited specifically
+when we need very high precision.
+
+Artificial markers are used when we need high precision. A fiducial marker or
+simply a fiducial is an synthetic object placed in the scene, which can provide
+additional information about the environment. Artificial fiducials are widely 
+used in Augmented Reality(AR) \cite{Zhang:2002}\cite{Dorfmuller99}
 applications, vision based navigation of robots\cite{Davison:2007} etc.
 
-Recently, use of Unmanned Aerial Vehicles(UAV) such as quadcopters is increased
-in various tracking activities (e.g. aerial surveillance, search and rescue
-operations etc.).Low cost quadcopters such as AR Drone are very unstable which
+Low cost quadcopters such as AR Drone are very unstable which
 causes non-uniform motion resulting lot of motion blur in captured images.
@@
 From Table \ref{tab:ARTag_blur}, it can be clearly seen that performance of
-ARTag drastically with increase in blur scale.
+ARTag drastically degrade with increase in blur scale.
 
-We have also analysed the recognition rate along different blur orientations at
-different blur scales. We found that per blur scale, at certain blur
-orientations, recognition of ARTag fails. Table shows the range of blur angles
-for which we are able to recognise the ARTag at different blur scales.
+We have also analysed the recognition rate along different blur orientations
+(from 0 to 90 degrees) at different blur scales. We found that per blur scale,
+at certain blur orientations, recognition of ARTag fails. Table shows the range
+of blur angles for which we are able to recognise the ARTag at different blur
+scales. From Table \ref{tab:artag_blurangle}, it can be seen that, when blur
+scale is greater than 30, ARTag is not recognisable with horizontal blur
+orientation(blur angle near zero degrees) as well as vertial blur
+orientation(blur angle near 90 degrees).
 
@@
 Blur Scale & Blur Angle Range \\ \cline{1-2}
-35 & 32--58 \\ \cline{1-2}
-40 & 41--48 \\ \cline{1-2}
-45 & 41--48 \\ \cline{1-2}
-50 & 44--46 \\ \cline{1-2}
+30 & 0 -- 90\\ \cline{1-2}
+35 & 32 -- 58 \\ \cline{1-2}
+40 & 41 -- 48 \\ \cline{1-2}
+45 & 41 -- 48 \\ \cline{1-2}
+50 & 44 -- 46 \\ \cline{1-2}
 \end{tabularx}
+\label{tab:artag_blurangle}
 \end{table}

### 2014-03-01 ECCV/paper.tex
Added comparison with BLUT as well as with PiTag

@@
 \section{Fiducial Detection Algorithm}
+
+We have performed blur simulation experiment on Pi-tag \cite{Pitag13} to find
+how blur effects circular patterns. We tried to detect blurred Pi-tag using
+\cite{ros_pitag}.
+
+\begin{figure}
+\begin{subfigure}[b]{0.3\textwidth}
+  \centering
+  \includegraphics[width=\linewidth]{detect_noblur.jpg}
+  No Blur  
+ \end{subfigure}
+ \begin{subfigure}[b]{0.3\textwidth}
+  \centering
+  \includegraphics[width=\linewidth]{detect_blur15.jpg}
+  Blur Scale = 15  
+ \end{subfigure}
+ \begin{subfigure}[b]{0.3\textwidth}
+  \centering
+  \includegraphics[width=\linewidth]{nodetect_blur20.jpg}
+  Blur Scale = 20  
+ \end{subfigure}
+ \caption{Effect of blur on detection of Pi-Tag}
+ \label{fig:pitag_blur}
+\end{figure}
+
+From Fig. \ref{fig:pitag_blur}, it can be seen that, Pi-tag detection
+fails when blur scale is more than 15. The reason behind this is, Pi-tag
+detection is based on Ellipse detection which will fail in the presence of
+significant amount of blur. So, ellipse detection may not be the efficient way
+to detect circular patterns under blur.
+
 \begin{figure}
@@
 \end{figure}
-Our fiducial detection strategy is different from \cite{NaimarkF02} and works
-under significant amount of blur. Our algorithm is based on the fact that there
+
+Our fiducial detection strategy is different from \cite{NaimarkF02}\cite{Pitag13} and
+works under significant amount of blur. Our algorithm is based on the fact that there
 is no blur in the direction perpendicular to the direction of the motion.
 Overall flow of fiducial detection algorithm can be summarised as follows:
+
 \begin{itemize}
@@
 We will compare our results with standard fiducials such as ARTag. Also, we will
-compare our results with Blur driven tracker.
+compare our results with Blur driven tracker(BLUT)\cite{Wu:2011}.
 \subsubsection{Comparison with ARTag}
-\subsubsection{Comparison with Blut}
+
+\subsubsection{Comparison with BLUT} 
+We have used sample image sequence to test the performance of BLUT\cite{Wu:2011}
+and compare it with out result on the same image sequence. From Fig. \ref{fig:BLUT_output},
+it can be inferred that BLUT is able to track the fiducial when the position of
+fiducial doesnot change too much in successive frames. Also, it can be seen
+that, once BLUT looses the track of the fiducial, it is not able to recover from
+that. But, our algorithm is able to track the fiducial irrespecive of the change
+in the position of the fiducial in the image as shown in Fig.
+\ref{fig:our_output}.
+
+\begin{figure}
+\begin{subfigure}[b]{.19\textwidth}
+\includegraphics[width=\linewidth]{11.jpg}
+\end{subfigure}
+\begin{subfigure}[b]{.19\textwidth}
+\includegraphics[width=\linewidth]{12.jpg}
+\end{subfigure}
+\begin{subfigure}[b]{.19\textwidth}
+\includegraphics[width=\linewidth]{13.jpg}
+\end{subfigure}
+\begin{subfigure}[b]{.19\textwidth}
+\includegraphics[width=\linewidth]{14.jpg}
+\end{subfigure}
+\begin{subfigure}[b]{.19\textwidth}
+\includegraphics[width=\linewidth]{15.jpg}
+\end{subfigure}
+\caption{Output of BlUT on sample image sequence}
+\label{fig:BLUT_output}
+\end{figure}
+
+\begin{figure}
+\begin{subfigure}[b]{.19\textwidth}
+\includegraphics[width=\linewidth]{output11.jpg}
+\end{subfigure}
+\begin{subfigure}[b]{.19\textwidth}
+\includegraphics[width=\linewidth]{output12.jpg}
+\end{subfigure}
+\begin{subfigure}[b]{.19\textwidth}
+\includegraphics[width=\linewidth]{output13.jpg}
+\end{subfigure}
+\begin{subfigure}[b]{.19\textwidth}
+\includegraphics[width=\linewidth]{output14.jpg}
+\end{subfigure}
+\begin{subfigure}[b]{.19\textwidth}
+\includegraphics[width=\linewidth]{output15.jpg}
+\end{subfigure}
+\caption{Output of our algorithm on image sequence used in
+Fig. \ref{fig:BLUT_output}}
+\label{fig:our_output}
+\end{figure}
 

### 2014-03-01 ECCV/paper.tex
1. Synced with Michael's version 2. Added training data figure, recognition rate chart, tables and more ...

@@
 \usepackage{tabularx}
+\setlength{\extrarowheight}{2pt}
 \newcolumntype{Y}{>{\centering\arraybackslash}X}
 \captionsetup[table]{belowskip=12pt,aboveskip=4pt}
-\setlength{\floatsep}{5pt plus 2pt minus 2pt}
-\setlength{\textfloatsep}{5pt plus 2pt minus 2pt}
-\setlength{\intextsep}{5pt plus 2pt minus 2pt}
+\setlength{\floatsep}{7pt plus 2pt minus 2pt}
+\setlength{\textfloatsep}{7pt plus 2pt minus 2pt}
+\setlength{\intextsep}{7pt plus 2pt minus 2pt}
 
@@
 
-\title{Design of Blur Invariant Fiducial for Low Cost Quadcopter} % Replace
+\title{A Motion Blur Resilient Fiducial Marker For Quadcopter Imaging} % Replace
 % with your title
@@
 \begin{abstract}
-Fiducial markers are commonly used to track an object in an unknown environment
-and finds use in various applications in Virtual Reality, Medical imaging,
-Surveys, etc. The performance of popular fiducials is satisfactory when there is
-little motion or no motion in the device obtaining the imagery. But when there
-is continuous and swift motion, as in the case of low cost quadcopters,
-performance of these fiducials degrade significantly due to motion blur.
-Inspired from Circular Data Matrix\cite{NaimarkF02}, we have designed a fiducial
-that may be thought of as a binary code. It contains concentric white rings of
-equal widths on a black background with a blurred border. Our fiducial detection
-algorithm is based on the fact that there is no blur in the direction
-perpendicular to the direction of the motion. The algorithm finds this
-direction in a simple but accurate way. Then, we find ``signature'' of our
-fiducial along this direction and further classify it to find the actual code
-embedded in the fiducial. We will show through experimental validation that our
-fiducial works better than popular fiducials such as ARTag under signifacant motion blur.
-
-\keywords{Fiducials, Tracking, Blur Invariant}
+This paper describes the design and evaluation of a binary fiducial marker
+design for use with low-cost quadcopters.  Fiducial markers are commonly placed
+into environments to provide a reliable and unique scene marker conducive for
+tracking and recognition.   For quadcopter applications, fiducials are
+typically used for evaluating planning algorithms by allowing ground truth
+positions in the scene to be detected from the quadcopter's camera. Quadcopters,
+however, are subject to quick and unstable motions that causes notable motion
+blur that severely affects the detection rate of existing fiducial markers. 
+This motivated us to design a fiducial that is robust to motion blur. Our design
+uses a series of concentric circles with the observation is that the direction
+perpendicular to the motion blur direction will be unaffected by the blur and
+therefore still be recognized as a binary code.  We detail the design and
+detection algorithm for our fiducial and show that our marker can significantly
+outperform existing fiducials on scenes captured with a quadcopter.
+\keywords{Fiducials, Tracking, Detection using Blur}
 \end{abstract}
@@
 based measurments.  But, natural features may not be available always and
-quality cannot be guranteed in every scene. So, results are not satisfactory in
+quality cannot be guaranteed in every scene. So, results are not satisfactory in
 uncontrolled environment and hence use of such features is limited specifically
@@
 \section{Related Work}
-Our problem may be classified broadly in two areas; fiducial markers and
-tracking. So, we will briefly discuss work done in both areas.
+Our work is related to two areas: fiducial markers and
+object tracking. We will briefly discuss work done in both areas.
 \begin{figure}
@@
 Augmented Reality system, widely used to find pose of the object on which it is
-placed.  Fiala et al. \cite{Fiala05} developed fiducial named, ARTag, bi-tonal
-system containing 2002 planar markers, each consisting of a square border and
+placed.  Fiala et al. \cite{Fiala05} developed a fiducial termed, ARTag, which is a
+bi-tonal system consisting of a square border and
 an interior region filled with a 6x6 grid of black or white cells. It proved to
@@
 
-Concentric Rings are reportedly used first by Gatrell et al.\cite{concentric}
+Concentric rings are reportedly used first by Gatrell et al.\cite{concentric}
 for monocular pose estimation as well as object identification in space. Cho et al.
@@
 
-The main hurdle in detection of current fiducials is, the detecton of features;
+The main hurdle in detection of current fiducials is, the detecton of features:
 lines in \cite{ARToolkit02}, corners in \cite{Fiala05} while ellipses in
@@
 
+Before we detail the design of our fiducial, we examine the performance of two
+popular fidicuals, ARTags and PiTags, in the face of motion blur.
+
 We conducted a small experiment to test ARTag's resilience towards blur.
@@
 
-\begin{table}
-\caption{Recognition rate of AR Tag at various blur scales}
+\begin{minipage}{\textwidth}
+  \begin{minipage}[b]{0.49\textwidth}
+\captionof{table}{Recognition rate of AR Tag at various blur scales}
 \centering
-\begin{tabularx}{0.75\textwidth}{c *{6}{|Y}|}
-\cline{2-6}
-& \multicolumn{5}{ c |}{Recognition Rate (in percent)} \\
-\cline{2-6} & \multicolumn{5}{ c |}{Blur Scale} \\ \cline{2-6}
-& 30 & 35 & 40 & 45 & 50 \\ \cline{1-6}
-\multicolumn{1}{ | c | }{ARTAg} & 100 & 19 & 9 & 5 & 0 \\ \cline{1-6}
-\cline{1-6}
+ \begin{tabularx}{0.75\textwidth}{|Y|Y|}
+\cline{1-2}
+Blur Scale & Recognition Rate(\%) \\ \cline{1-2}
+30 & 100\\ \cline{1-2}
+35 & 19 \\ \cline{1-2}
+40 & 9 \\ \cline{1-2}
+45 & 5 \\ \cline{1-2}
+50 & 0 \\ \cline{1-2}
 \end{tabularx}
 \label{tab:ARTag_blur}
-\end{table}
+ \end{minipage}	
+ \begin{minipage}[b]{0.49\textwidth} 	
+\captionof{table}{Blur angle range}
+\centering
+\begin{tabularx}{0.75\textwidth}{|Y|Y|}
+\cline{1-2}
+Blur Scale & Blur Angle Range \\ \cline{1-2}
+30 & 0 -- 90\\ \cline{1-2}
+35 & 32 -- 58 \\ \cline{1-2}
+40 & 41 -- 48 \\ \cline{1-2}
+45 & 41 -- 48 \\ \cline{1-2}
+50 & 44 -- 46 \\ \cline{1-2}
+\end{tabularx}
+\label{tab:artag_blurangle}
+ \end{minipage}
+\end{minipage}
 
@@
 orientation(blur angle near 90 degrees).
-
-\begin{table}
-\caption{Blur angle range}
-\centering
-\begin{tabularx}{0.75\textwidth}{|Y|Y|}
-\cline{1-2}
-Blur Scale & Blur Angle Range \\ \cline{1-2}
-30 & 0 -- 90\\ \cline{1-2}
-35 & 32 -- 58 \\ \cline{1-2}
-40 & 41 -- 48 \\ \cline{1-2}
-45 & 41 -- 48 \\ \cline{1-2}
-50 & 44 -- 46 \\ \cline{1-2}
-\end{tabularx}
-\label{tab:artag_blurangle}
-\end{table}
 
@@
 \end{figure}
+Our fiducial detection strategy is different from \cite{NaimarkF02,Pitag13} and works
+under significant amount of blur.   In particular, we assume that scene motion 
+blur be modelled locally as a linear motion blur~\cite{}.  Under this assumption,
+scene content perpendicular to the blur direction is unaffected by the blur.  Because
+of our circular design, this means the perpendicular direction can be observed as a 
+unblurred linear pattern.  Figure X shows an example with various motion directions.
 
-Our fiducial detection strategy is different from \cite{NaimarkF02}\cite{Pitag13} and
-works under significant amount of blur. Our algorithm is based on the fact that there
-is no blur in the direction perpendicular to the direction of the motion.
 Overall flow of fiducial detection algorithm can be summarised as follows:
@@
   \item Apply Gabor Filter on input image
-  \item Find Connected components in Gabor output
-  \item Cluster the connected components in bounding box
+  \item Find connected components in Gabor output
+  \item Cluster the connected components into bounding boxes
   \item Detect code in the bounding box
@@
     centroid
-    \item If there are less than four black to white transitions in the
-    intensity profile, ignore the bouding box
-    \item Otherwise, classify the detected code by the classifer trained on
+    \item Classify the detected code by training examples
     standards.
@@
 have applied Gabor filter for eight different orientations ($\theta = 0, 45,
-90, 135, 180, 225, 270, 315$) and then calculated L2 norm of all outputs.
+90, 135, 180, 225, 270, 315$). We have used following parameters for
+creating each Gabor kernel: $\lambda = 8$, $\gamma = 0.5$, $\sigma =
+0.56\lambda$, $\psi = 0 \text(for real) = \pi/2 (for imaginary part)$. 
+Then L2 norm of outputs along all orientations is calculated and finally, L2
+normed image is binarized.
+
+\begin{figure}
+\centering
+  \includegraphics[width=\linewidth]{training_data.pdf}  
+  \caption{Training data for the fiducial pattern with binary code ``01''}
+\end{figure}
 
@@
 orientations (0, 10, 20, \ldots , 350) and intensity profile along first
-principal component from every output is taken as training data for that fiducial pattern.
-Training data for patterns having same number of rings is grouped together;
-e.g., in two bit binary coded fiducial, training data for pattern ``01'' and
-``10'' will be grouped together. Now, depending on the number of detected
-rings, test pattern is matched against corresponding training data using
-K-Nearest Neighbor Classifier (K=5).
+principal component from every output is taken as training data for that
+fiducial pattern. Test pattern is matched against training data using 
+K-Nearest Neighbor Classifier (K=5) to output class label.
 
-\begin{figure}
-\centering
-  \includegraphics[width=.22\linewidth]{concentric_01_5_blurred_180.jpg}  
-  \includegraphics[width=.22\linewidth]{concentric_01_5_blurred_45.jpg}
-  \includegraphics[width=.22\linewidth]{concentric_01_5_blurred_90.jpg}  
-  \includegraphics[width=.22\linewidth]{concentric_01_5_blurred_135.jpg}
-  \caption{Sample images used to create training data for the fiducial pattern
-  with binary code ``01''}
-\end{figure}
+To increase classification accuracy, training data for patterns having same
+number of rings is grouped together; e.g., in two bit binary coded fiducial,
+training data for pattern ``01'' and ``10'' will be grouped together, In three
+bit binary coded fiducial, training data for pattern “001”, “010” and “100” will
+form one group while training data for pattern “110”, “011” and “101” will be
+in other group, etc. Now, Depending on the number of detected rings in test
+pattern, it is matched against corresponding group of training data, again
+using  K-Nearest Neighbor Classifier. In this way, if we detect either zero
+rings or maximum possible rings in the test pattern, there will be no need to do
+further classification.
 
@@
 \begin{figure}
+\begin{subfigure}{0.5\textwidth}
 \centering
-  \includegraphics[width=.8\linewidth]{output_00.jpg}
-  \caption{Sample output for the fiducial pattern with binary code ``00''}
+  \includegraphics[width=\linewidth]{output_00.jpg}
+  \caption{Binary code ``00''}
   \label{fig:output0}
-\end{figure}
-
-\begin{figure}
+\end{subfigure}
+\begin{subfigure}{0.5\textwidth}
 \centering
-  \includegraphics[width=.8\linewidth]{output_01.jpg}
-  \caption{Sample output for the fiducial pattern with binary code ``01''}
+  \includegraphics[width=\linewidth]{output_01.jpg}
+  \caption{Binary code ``01''}
   \label{fig:output1}
-\end{figure}
-
-\begin{figure}
+\end{subfigure}
+\begin{subfigure}{0.5\textwidth}
 \centering
-  \includegraphics[width=.8\linewidth]{output_10.jpg}
-  \caption{Sample output for the fiducial pattern with binary code ``10''}
+  \includegraphics[width=\linewidth]{output_10.jpg}
+  \caption{Binary code ``10''}
   \label{fig:output2}
-\end{figure}
-
-\begin{figure}
+\end{subfigure}
+\begin{subfigure}{0.5\textwidth}
 \centering
-  \includegraphics[width=.8\linewidth]{output_11.jpg}
-  \caption{Sample output for the fiducial pattern with binary code ``11''}
+  \includegraphics[width=\linewidth]{output_11.jpg}
+  \caption{Binary code ``11''}
   \label{fig:output3}
+  \end{subfigure}
+  \caption{Sample Outputs for two bit binary coded fiducials}
 \end{figure}
@@
 \subsubsection{Comparison with ARTag}
+First, we have repeated blur simulation experiment on our fiducials too, i.e.,
+we have downsized our fiducial to size 150x150 and blurred it along various
+orientations with different blur scales. Then, we tried to detect the patterns
+using algorithm presented in earlier section. The comparison of recongition
+rate is shown in Fig. \label{fig:recognition_rate}.
+
+\begin{figure}
+\centering
+\includegraphics[width=\linewidth]{recognition_rate.png}
+\caption{Comparison of recognition rate of AR Tag and our fiducials on
+blur simulated data at various blur scales}
+\label{fig:recognition_rate}
+\end{figure}
+
+Later, we recorded the real data using AR Drone quadcopter. In our experimental
+setup, we have kept our fiducial alog with two AR Tags, to compare the
+resilience of blur by each fiducial type. We have used ar\_track\_alvar, ROS
+Wrapper for ALVAR libray \cite{ros_alvar}, to detect AR Tags from the stream
+captured through quadcopter. The comparison of recognition rate shown in Table
+\ref{tab:recongition_accuracy}. Classification accuracy of all fiducials(ARTag
+as well as ours) is almost 100\%.
+
+\begin{table}
+\caption{Comparison of Recognition Rate of AR Tag and our fiducials on real
+data captured through AR Drone}
+\centering
+\begin{tabularx}{0.8\textwidth}{|Y|Y|Y|Y|Y|}
+\cline{1-5}
+\multirow{2}{*}{AR Tag} & \multicolumn{4}{ c |}{Our Fiducial} \\ \cline{2-5}
+& 00 & 01 & 10 & 11 \\  \cline{1-5}
+65.6\% & 86.5\% & 94.1\% & 92.74\% & 93.54\% \\ \cline{1-5}
+\end{tabularx}
+\label{tab:recongition_accuracy}
+\end{table}
 
@@
 \end{subfigure}
-\caption{Output of BlUT on sample image sequence}
+\caption{Output of BLUT on sample image sequence}
 \label{fig:BLUT_output}

### 2014-03-01 ECCV/paper.tex
Added blur direction image and done other corrections

@@
 of our circular design, this means the perpendicular direction can be observed as a 
-unblurred linear pattern.  Figure X shows an example with various motion directions.
+unblurred linear pattern.  Figure \ref{fig:blur_direction} shows an example with
+various motion directions.
+
+\begin{figure}
+\centering
+\includegraphics[width=\linewidth]{blur_direction.pdf}
+\caption{Relation of blur direction and unblurred linear pattern}
+\label{fig:blur_direction}
+\end{figure}
 
@@
 creating each Gabor kernel: $\lambda = 8$, $\gamma = 0.5$, $\sigma =
-0.56\lambda$, $\psi = 0 \text(for real) = \pi/2 (for imaginary part)$. 
+0.56\lambda$, $\psi = 0 \text{(for real part)}, \pi/2 \text{(for imaginary
+part)}$.
 Then L2 norm of outputs along all orientations is calculated and finally, L2

### 2014-03-02 ECCV/paper.tex
Changed figures, added discussion, incorporated Michael's changes.

@@
 \usepackage{url}
+\usepackage{comment}
 \usepackage[width=122mm,left=12mm,paperwidth=146mm,height=193mm,top=12mm,paperheight=217mm]{geometry}
@@
 \usepackage{tabularx}
-\setlength{\extrarowheight}{2pt}
 \newcolumntype{Y}{>{\centering\arraybackslash}X}
@@
 This paper describes the design and evaluation of a binary fiducial marker
-design for use with low-cost quadcopters.  Fiducial markers are commonly placed
-into environments to provide a reliable and unique scene marker conducive for
+for use with low-cost quadcopters.  Fiducial markers are commonly placed
+in environments to provide a reliable and unique marker conducive for
 tracking and recognition.   For quadcopter applications, fiducials are
@@
 positions in the scene to be detected from the quadcopter's camera. Quadcopters,
-however, are subject to quick and unstable motions that causes notable motion
+however, are subject to quick and unstable motions that can cause significant motion
 blur that severely affects the detection rate of existing fiducial markers.
@@
 perpendicular to the motion blur direction will be unaffected by the blur and
-therefore still be recognized as a binary code.  We detail the design and
+therefore still be recognizable.  We detail the design and
 detection algorithm for our fiducial and show that our marker can significantly
-outperform existing fiducials on scenes captured with a quadcopter.
+outperform existing fiducial markers in scenes captured with a quadcopter.
 \keywords{Fiducials, Tracking, Detection using Blur}
@@
 \section{Introduction}
-Recently, use of Unmanned Aerial Vehicles(UAV) such as quadcopters is increased
-in various tracking activities e.g. aerial surveillance, search and rescue
-operations etc. Navigation of these vehicles is mainly based on the
-onboard inertial sensors. But sensor based measurments are prone to errors. So,
-visual cues captured through onboard camera can be used along with the sensor
-based measurments.  But, natural features may not be available always and
-quality cannot be guaranteed in every scene. So, results are not satisfactory in
-uncontrolled environment and hence use of such features is limited specifically
-when we need very high precision.
 
-Artificial markers are used when we need high precision. A fiducial marker or
-simply a fiducial is an synthetic object placed in the scene, which can provide
-additional information about the environment. Artificial fiducials are widely
-used in Augmented Reality(AR) \cite{Zhang:2002}\cite{Dorfmuller99}
-applications, vision based navigation of robots\cite{Davison:2007} etc.
+The recent availability of low-cost quadcopters has help to fuel significant efforts in
+research focused on Unmanned Aerial Vehicles.  Navigation and planning of
+these vehicles is typically performed using onboard inertial sensors and/or
+vision based modules that uses visual cues in the real world\cite{Davison:2007}. 
+However, to evaluate the effectiveness of navigation methods, artificial
+fiducial markers are commonly introduces into the environment to provide
+additional information that often serves for ground-truth
+measurements(e.g.\cite{Bosnak:2012}\cite{Lim09})
 
-Low cost quadcopters such as AR Drone are very unstable which
-causes non-uniform motion resulting lot of motion blur in captured images.
-Also, as image transfer is done through wireless media using User Datagram
-Protocol (UDP), there is possibility of missing intermediate frames . It
-results in lower frame rate (around 15 frames per second (FPS)) instead of
-normal rate of 30 FPS. This frequent dropping of frames may cause drastic
-change in position of object in successive frames. Thus, performance of
-traditional tracking methods is not satisfactory for tracking through
-quadcopters. Our aim is to design a fiducial which we will be able to track
-under significant amount of motion blur and is robust in terms of drastic
-change in its position in successive frames.
+In order to be effective, fiducial markers (or simply called, fiducials) need
+to be easily detected in the scene.  There are various existing commonly
+used fiducial markers 
+\cite{NaimarkF02}\cite{ARToolkit02}\cite{Fiala05}\cite{Pitag13}\cite{runetag11}.
+These typically take the form of binary codes arranged into rectangular grids (\cite{ARToolkit02}\cite{Fiala05})
+or other geometric features arranged in unique spatial patterns
+(\cite{NaimarkF02}\cite{Pitag13}\cite{runetag11}).
+Figure \ref{fig:teaser} shows an example of the popular ARTag\cite{Fiala05} as
+seen from a quad-copter.  One p roblem, however, is that low-cost quadcopters
+often exhibit very quick and erratic motion.  These fast physical movements
+results in motion blur in the quadcopters onboard camera.  Such motion blur has an adverse effect the
+reconition of fiducial  markers.  This can be seen in Figure \ref{fig:teaser}(b)
+where the ARTag cannot be recongized. This is not too surprising as most
+fidicuals are not explicitly designed to handle motion blur.  Compounding this
+problem is the common problem of dropped video frames from the quadcopters
+wireless communication module.   This means that no only is blurring
+introduced, but there may be large discountinues in the patterns position due
+to missing video frames that makes tracking challenging.
 
-We observed that blur in a single frame captured through quadcopter is linear.
-There is no blur in the direction perpendicular to the direction of motion. We
-tried to design a fiducial whose ``signature'' remains intact in any direction.
+To address this problem, propose a fiducial design that is robust to motion
+blur and drastic drastic change in its position in successive frames.  Our
+design is based on concentric circles as shown in Figure \ref{fig:fiducials}. 
+The design is based on the observation that motion blur from a quadcopter tends
+to be linear in nature.  As such, when our code is blurred, there is no blur in
+the direction perpendicular to the direction of motion.   This allows the
+signature of the fiducial to remain intact in any direction.  In addition, by
+using concentric rings, we can treat them as bits allowing us to encode us
+different fiducial identifers.  As far as we are aware, this is the first work
+to design a blur resistent marker.   Our experiments show that this design can
+significantly outperform existing codes in the face of motion blur.
+
+The remainder of this paper is organized as follows.   Section 2 gives an
+overview of related work, focused on fiducials as well the related problem of
+tracking.  Section X discusses the our design and detection algorithm, by first
+examining the performance of existing codes under blur. Section 3 shows several
+experiments using quadcopter imagery.  This is followed by a discussion and
+summary in Section 4 and 5 respectively.
 
@@
 algorithm, in normal and blurred scene}
+\label{fig:teaser}
 \end{figure}
@@
 \section{Related Work}
+
+[For related work, you need to give more context of how these are related to your work. 
+This is more of a list of papers and what they do, there relationship is not clear.]
+
 Our work is related to two areas: fiducial markers and
@@
   \centering
-  \includegraphics[width=\linewidth]{pifiducial.png}
+  \includegraphics[width=\linewidth]{pifiducial.jpg}
   Pi-Tag\cite{Pitag13}
@@
 
-The ARToolkit \cite{ARToolkit02} \cite{kato-artoolkit} is well known toolkit in
+The ARToolkit \cite{ARToolkit02}\cite{kato-artoolkit} is well known toolkit in
 Augmented Reality system, widely used to find pose of the object on which it is
@@
 tracking in large scale applications. In \cite{NaimarkF02}, Naimark et al.
-have developed ``Circular Data Matrix Fiducial System'', for wide area tracking.
+have developed ``Circular Data Matrix Fiducial System'', for wide area tracking. ....
 
-Zhang el. al.\cite{Zhang:2002} and Claus et al. \cite{ClausF04} have done
+Zhang et al.\cite{Zhang:2002} and Claus et al. \cite{ClausF04} have done
 quite comprehensive comparative study of various fiducial marker systems with
@@
 
+We begin by first motivating the need for a new blur resistent fiducial by examining
+the performance of prior fiducials under motion blur.  After this, we detail
+our design as well as the detection algorithm used to find our marker in an image.
+
+\subsection{Examining Prior Fiducials Under Motion Blur}
+
 Before we detail the design of our fiducial, we examine the performance of two
-popular fidicuals, ARTags and PiTags, in the face of motion blur.
+popular fiducials under motion blur that have different designs. Specifically,
+we examine ARTags\cite{Fiala05} and PiTags\cite{Pitag13}.
 
-We conducted a small experiment to test ARTag's resilience towards blur.
-We scaled down ARTag fiducial to size 150x150.  Then, we blurred ARTag
-at various orientations using different scales. Finally, we tried to detect
-ARTag in these blurred images using ALVAR library\cite{alvar}.
+We scaled down ARTag as well as PiTag fiducial to size 150x150.  Then, we
+blurred both fiducials at various orientations using different scales.
+Figure \ref{fig:artag_pitag} shows sample blurred AR Tag and Pi-Tag. Finally, we
+tried to detect ARTag using ALVAR library\cite{alvar} and Pi-Tag using\cite{ros_pitag}.
+
+\begin{figure}
+\centering
+\includegraphics[width=\linewidth]{artag_pitag.pdf}
+\caption{Blurred AR Tag and Pi--tag with various blur scales}
+\label{fig:artag_pitag}
+\end{figure}
+
+\begin{table}
+\centering
+\caption{Recognition rate of AR Tag and Pi-tag fiducial marker at various blur
+scales}
+\begin{tabularx}{0.75\textwidth}{|Y|Y|Y|}
+\cline{1-3}
+\multirow{2}{*}{Blur Scale} & \multicolumn{2}{c|}{Recognition Rate}
+\\\cline{2-3}
+ & AR Tag &	Pi-Tag \\ \cline{1-3}
+15 & 100 & 100 \\ \cline{1-3}
+30 & 0 & 100 \\  \cline{1-3}
+35 & 0 & 19 \\ \cline{1-3}
+50 & 0 & 0 \\ \cline{1-3}
+\end{tabularx}
+\label{tab:artag_pitag}
+\end{table}
+
+From Table \ref{tab:artag_pitag}, it can be clearly seen that performance of
+ARTag as well as Pi-Tag drastically degrade with increase in blur scale.
+
+\begin{comment}
 
@@
 
-\begin{figure}
-\centering
-  \includegraphics[width=.22\linewidth]{newconcentric_00.pdf}
-  \includegraphics[width=.22\linewidth]{newconcentric_01.pdf}
-  \includegraphics[width=.22\linewidth]{newconcentric_10.pdf}
-  \includegraphics[width=.22\linewidth]{newconcentric_11.pdf}
-  \caption{Two bit binary coded Fiducials (from left to right: Binary Code 00,
-  Binary Code 01, Binary Code 10, Binary Code 11)}
-  \label{fig:fiducials}
-\end{figure}
-
-Inspired from Circular Data Matrix\cite{NaimarkF02} we have designed a fiducial
-that may be thought of as a binary code.  It contains concentric white rings of
-equal widths on a black background with a blurred border. The outermost and
-innermost rings represent the start and end of the code and is embedded in the
-fiducial; these are not considered part of the code itself. The binary code is
-represented by the presence (or absence) of rings between ``marker'' rings.
-
-Depending on which ring is present or absent, the resulting binary code will
-change. The number of different patterns depends on the number of bits in the
-binary code. For example, if the binary code has three bits, there will be a
-maximum of three rings between``marker'' rings and we end up with eight
-different patterns. Fig. \ref{fig:fiducials} shows two bit binary coded
-fiducials.
-
-\section{Fiducial Detection Algorithm}
-
 We have performed blur simulation experiment on Pi-tag \cite{Pitag13} to find
@@
 
-From Fig. \ref{fig:pitag_blur}, it can be seen that, Pi-tag detection
+From Figure \ref{fig:pitag_blur}, it can be seen that, Pi-tag detection
 fails when blur scale is more than 15. The reason behind this is, Pi-tag
@@
 to detect circular patterns under blur.
+\end{comment}
+We have designed a fiducial that may be thought of as a binary code.  It
+contains concentric white rings of equal widths on a black background with a
+blurred border. The outermost and innermost rings represent the start and end
+of the code and is embedded in the fiducial; these are not considered part of
+the code itself. The binary code is represented by the presence (or absence) of
+rings between ``marker'' rings.
 
 \begin{figure}
-\includegraphics[width=\linewidth]{overall_flow.pdf}
-\caption{Overall Workflow}
+\centering
+  \includegraphics[width=.22\linewidth]{newconcentric_00.pdf}
+  \includegraphics[width=.22\linewidth]{newconcentric_01.pdf}
+  \includegraphics[width=.22\linewidth]{newconcentric_10.pdf}
+  \includegraphics[width=.22\linewidth]{newconcentric_11.pdf}
+  \caption{Two bit binary coded Fiducials (from left to right: Binary Code 00,
+  Binary Code 01, Binary Code 10, Binary Code 11)}
+  \label{fig:fiducials}
 \end{figure}
-Our fiducial detection strategy is different from \cite{NaimarkF02,Pitag13} and works
-under significant amount of blur.   In particular, we assume that scene motion 
-blur be modelled locally as a linear motion blur~\cite{}.  Under this assumption,
-scene content perpendicular to the blur direction is unaffected by the blur.  Because
-of our circular design, this means the perpendicular direction can be observed as a 
-unblurred linear pattern.  Figure \ref{fig:blur_direction} shows an example with
-various motion directions.
+
+Depending on which ring is present or absent, the resulting binary code will
+change. The number of different patterns depends on the number of bits in the
+binary code. For example, if the binary code has three bits, there will be a
+maximum of three rings between``marker'' rings and we end up with eight
+different patterns. Figure \ref{fig:fiducials} shows two bit binary coded
+fiducials.
+
+\subsection{Fiducial Detection Algorithm}
 
@@
 \end{figure}
+
+Our fiducial detection strategy is different from \cite{NaimarkF02,Pitag13} and works
+under significant amount of blur.   In particular, we assume that scene motion
+blur be modelled locally as a linear motion blur \cite{Moshe:2003,Moshe:2004}. 
+Under this assumption, scene content perpendicular to the blur direction is 
+unaffected by the blur.  Because of our circular design, this means the
+perpendicular direction can be observed as a unblurred linear pattern.  Figure
+\ref{fig:blur_direction} shows an example with various motion directions.
 
@@
 
+Figure \ref{fig:overall_flow} shows the process involved in fiducial detection
+process.
+
+\begin{figure}
+\includegraphics[width=\linewidth]{overall_flow.pdf}
+\caption{Overall Workflow}
+\label{fig:overall_flow}
+\end{figure}
+
 \textbf{Gabor Filter}: A 2D Gabor filter is a Gaussian kernel function modulated
@@
 part)}$.
-Then L2 norm of outputs along all orientations is calculated and finally, L2
+Then L2 norm of outputs along all orientations is calculated and finally L2
 normed image is binarized.
@@
   \caption{Training data for the fiducial pattern with binary code ``01''}
+  \label{fig:training_data}
 \end{figure}
@@
 principal component from every output is taken as training data for that
-fiducial pattern. Test pattern is matched against training data using 
-K-Nearest Neighbor Classifier (K=5) to output class label.
+fiducial pattern. Process of creation of training data for fiducial with
+code ``01'' is depicted in Figure \ref{fig:training_data}. Test pattern is matched
+against training data using K-Nearest Neighbor Classifier (K=5) to output class label.
 
@@
 \section{Experimental Validation}
+We have implemented our algorithm in C++ using OpenCV library. Our code was run
+on a PC with Intel Core i7 processor(@3.4GHz) and 4GB RAM.
 
@@
 quadcopter. Each image sequence contains frames containing different fiducial
-pattern. Sample output for each fiducial pattern is shown in Fig.
-\ref{fig:output0} -- Fig. \ref{fig:output3}.
+pattern. Sample output for each fiducial pattern is shown in Figure
+\ref{fig:output0} -- Figure \ref{fig:output3}. Our detection process takes
+around 0.3 seconds and can handle three to four frames per second.
 
@@
 in the same frame. Our algorithm successfully detected all fiducial patterns as
-well as correctly classified them as shown in Fig. \ref{fig:output_all}
+well as correctly classified them as shown in Figure \ref{fig:output_all}.
 \begin{figure}
@@
 using algorithm presented in earlier section. The comparison of recongition
-rate is shown in Fig. \label{fig:recognition_rate}.
+rate is shown in Figure \ref{fig:recognition_rate}.
 
@@
 We have used sample image sequence to test the performance of BLUT\cite{Wu:2011}
-and compare it with out result on the same image sequence. From Fig. \ref{fig:BLUT_output},
+and compare it with out result on the same image sequence. From Figure \ref{fig:BLUT_output},
 it can be inferred that BLUT is able to track the fiducial when the position of
@@
 that. But, our algorithm is able to track the fiducial irrespecive of the change
-in the position of the fiducial in the image as shown in Fig.
+in the position of the fiducial in the image as shown in Figure
 \ref{fig:our_output}.
@@
 \caption{Output of our algorithm on image sequence used in
-Fig. \ref{fig:BLUT_output}}
+Figure \ref{fig:BLUT_output}}
 \label{fig:our_output}
@@
 \section{Discussion}
-\begin{itemize}
-\item Processing Time
-\item False Positives and False Negatives
-\item Pose Estimation
-\end{itemize}
+
+\textbf{Processing Time} :-  Currently our processing time (0.3 seconds per
+frame) makes it difficult to do the fiducial detection in real-time. When we have
+done the code profiling, we found that Gabor filter takes most of the time (0.03
+-- 0.04 seconds perorientation). As we are applying Gabor filter along eight
+orientations, we should think of some optimized way to do filtering.
+Alternatively, some replacement for Gabor filter needs to be find out.
+
+\textbf{False Negatives} :- We found that sometime our detection algorithm is
+failed do recognize our fiducial with binary code ``0'' when there is large
+amount of blur. This is the reason behing low recognition rate of ``00''
+coded fiducial compared to that of our other fiducial patterns. When we
+investigated the problem, we found that, if there is too much blur, the
+innermost ring is not detected along the direction perpandicular to blur
+direction. This problem can be resolved by increasing radius of innermost ring.
+
+\textbf{Pose Estimation} :- Currently, we are not finding the pose from the
+fiducial marker. But, if we put multiple markers (atleast four) in the same
+scene, we may be able to find the pose. The current resolution of onboard camera
+will be main hurdle to clear before we can effectively use multiple markers in
+each scene.
+
+\textbf{Number of Fiducials} :- Currently, compared to AR Tag fiducial markers,
+we are able to generate less number of fiducials. Many applications in
+robotics (e.g. qudcopter navigation) may not require large number of fiducial
+markers as AR Tag. Most of the time, it is sufficient to have 4-6
+different fiducial patterns. Still, we may be able to generate more number of
+fiducials by using color background insted of black. E.g., if we just use Red,
+Green and Blue as background color, number of fiducials will be increased by
+factor of three.
+
 \section{Conclusion and Future Work}

### 2014-03-03 ECCV/paper.tex
Linked related work

@@
 Figure \ref{fig:teaser} shows an example of the popular ARTag\cite{Fiala05} as
-seen from a quad-copter.  One p roblem, however, is that low-cost quadcopters
+seen from a quad-copter.  One problem, however, is that low-cost quadcopters
 often exhibit very quick and erratic motion.  These fast physical movements
@@
 overview of related work, focused on fiducials as well the related problem of
-tracking.  Section X discusses the our design and detection algorithm, by first
-examining the performance of existing codes under blur. Section 3 shows several
+tracking.  Section 3 discusses the our design and detection algorithm, by first
+examining the performance of existing codes under blur. Section 4 shows several
 experiments using quadcopter imagery.  This is followed by a discussion and
-summary in Section 4 and 5 respectively.
+summary in Section 5 and 6 respectively.
 
@@
 
-[For related work, you need to give more context of how these are related to your work. 
-This is more of a list of papers and what they do, there relationship is not clear.]
-
 Our work is related to two areas: fiducial markers and
 object tracking. We will briefly discuss work done in both areas.
+
+\textbf{Fiducials} :- Some of fiducial designs are shown in Figure
+\ref{fig:previous_work}.
+
 \begin{figure}
@@
 
-The ARToolkit \cite{ARToolkit02}\cite{kato-artoolkit} is well known toolkit in
-Augmented Reality system, widely used to find pose of the object on which it is
-placed.  Fiala et al. \cite{Fiala05} developed a fiducial termed, ARTag, which is a
-bi-tonal system consisting of a square border and
-an interior region filled with a 6x6 grid of black or white cells. It proved to
-be more efficient than \cite{ARToolkit02} in terms of marker recognition rate
-as well as the number of different patterns which can be created.
+Intitially there were attempts to design a fiducial embeded with two dimensional
+barcode inside a rectangular grid. One of the examples of such fiducial is,
+ARToolkit\cite{ARToolkit02}, well known toolkit in Augmented Reality(AR) system. 
+Kato et al.\cite{kato-artoolkit} have deomstrated the use of ARToolkit to find
+the pose in cideo conferencing system. Many AR applications used ARToolkit
+due to its simplicity and efficiency.
+
+Fiala et al. \cite{Fiala05} developed a fiducial termed, ARTag, which is a
+bi-tonal system consisting of a square border and an interior region filled
+with a 6x6 grid of black or white cells. The improvement in ARTag compared
+ARToolkit was detection of coreners instead of detection of lines to find
+possible pattern. It proved to be more efficient than \cite{ARToolkit02} in
+terms of marker recognition rate as well as the number of different patterns
+which can be created. But, drawback of ARTag is, under significant amount of
+motion blur, corners can not be detected, resulting in non-recognition of tag.
+
+There were also attempts to use circular patterns instead of rectangular, as
+the projective transfomration of circles, i.e. conics, are invariant with
+resepctive to point of view of camera\cite{runetag11}. Also, such patterns are
+mostly distingushable from background and generally can not be missed.
 
@@
 for monocular pose estimation as well as object identification in space. Cho et al.
-\cite{Cho:2001}\cite{Cho97fastcolor} have used multi color rings in wide area
-tracking in large scale applications. In \cite{NaimarkF02}, Naimark et al.
-have developed ``Circular Data Matrix Fiducial System'', for wide area tracking. ....
+\cite{Cho:2001}\cite{Cho97fastcolor} have used multi color rings instead of
+black and white rings\cite{concentric} to increase possible number of fiducials.
+These multicolor rings are used in wide area tracking in large scale
+applications.
+
+Naimark et al. \cite{NaimarkF02} have combined concentric rings and 2D bar code
+in their fiducial named, Circular Data Matrix. It was beneficial in terms of
+easy detection of fiducial as well as more number of fiducial patterns.
+
+All of these fiducials are not recognizable under occlusion.
+Bergamasco et al. \cite{runetag11} have divided fiducial into number of
+circular dots, and arranged them in circular fashion, named as RUNE-Tag.
+RUNE-tags are reportedly detectable even if 50\% of fiducial area is occluded.
+Bergamasco et al. have devloped another fiducial, named as Pi-Tag
+\cite{Pitag13}, using cross-ratio concept. As cross-ratio is projective
+invariant, the detection of Pi-tag is easier than other tags. Also, compared
+to RUNE-tag, it uses remarkably less number of circular dots (12 dots instead of
+minimum of 43 dots), still reconisable under occlusion.
+
+But again problem with circular fiducials is, it is very difficult to detect
+ellipses accurately under significant motion blur. So, under blur, recognition
+rate of these fiducials is very low.
 
@@
 
-Bergamasco et al. \cite{runetag11} developed RUNE-Tag, fiducial marker
-system which works under large amount of occlusion. Bergamasco et al. also
-designed Pi-Tag \cite{Pitag13}, marker design based on projective
-invariants.
-
-The main hurdle in detection of current fiducials is, the detecton of features:
-lines in \cite{ARToolkit02}, corners in \cite{Fiala05} while ellipses in
-\cite{Cho:2001}, \cite{Cho97fastcolor}, \cite{runetag11} and \cite{Pitag13}.
-Such features are very difficult to detect accurately under significant motion
-blur. So, under blur, recognition rate of these fiducials is very low.
-
+\textbf{Tracking}:-
 Fiducial detection in video may be considered as tracking problem where tracked
@@
 imaging\cite{Yilmaz:2006}. Yilmaz et al.\cite{Yilmaz:2006} have done survey of
-various tracking methods. Most tracking methods
-( \cite{Ross:2008} \cite{Wu:2009} \cite{Perez02} \cite{Mei:2009} ) assume image
-sequence to be blur free. But in reality, motion blur is inherent part of most
-of the videos. Wu et al.\cite{Wu:2011} have developed BLUr-driven Tracker (BLUT)
-framework for tracking motion-blurred targets. BLUT is based on the observation
-that although motion blurs degrade the visual features of the target, they, at
-thde same time, provide useful cues about the movements to help tracking.
+various tracking methods.
+
+Most tracking methods( \cite{Ross:2008} \cite{Wu:2009} \cite{Perez02}
+\cite{Mei:2009} ) assume image sequence to be blur free. But in reality, motion
+blur is inherent part of most of the videos. Wu et al.\cite{Wu:2011} have
+developed BLUr-driven Tracker (BLUT) framework for tracking motion-blurred
+targets. BLUT is based on the observation that although motion blurs degrade
+the visual features of the target, they, at thde same time, provide useful cues
+about the movements to help tracking.
 
@@
 Later, we recorded the real data using AR Drone quadcopter. In our experimental
-setup, we have kept our fiducial alog with two AR Tags, to compare the
+setup, we have kept our fiducial along with two AR Tags, to compare the
 resilience of blur by each fiducial type. We have used ar\_track\_alvar, ROS
 Wrapper for ALVAR libray \cite{ros_alvar}, to detect AR Tags from the stream
-captured through quadcopter. The comparison of recognition rate shown in Table
-\ref{tab:recongition_accuracy}. Classification accuracy of all fiducials(ARTag
+captured through quadcopter. The comparison of recognition rate is shown in
+Table \ref{tab:recongition_accuracy}. Classification accuracy of all fiducials(ARTag
 as well as ours) is almost 100\%.
@@
 We have used sample image sequence to test the performance of BLUT\cite{Wu:2011}
-and compare it with out result on the same image sequence. From Figure \ref{fig:BLUT_output},
-it can be inferred that BLUT is able to track the fiducial when the position of
+and compare it with our result on the same image sequence. From Figure
+\ref{fig:BLUT_output}, it can be inferred that BLUT is able to track the fiducial when the position of
 fiducial doesnot change too much in successive frames. Also, it can be seen
@@
 done the code profiling, we found that Gabor filter takes most of the time (0.03
--- 0.04 seconds perorientation). As we are applying Gabor filter along eight
+-- 0.04 seconds per orientation). As we are applying Gabor filter along eight
 orientations, we should think of some optimized way to do filtering.
@@
 \textbf{False Negatives} :- We found that sometime our detection algorithm is
-failed do recognize our fiducial with binary code ``0'' when there is large
-amount of blur. This is the reason behing low recognition rate of ``00''
+failed do recognize our fiducial with binary code ``00'' when there is large
+amount of blur. This is the reason behing lower recognition rate of ``00''
 coded fiducial compared to that of our other fiducial patterns. When we
-investigated the problem, we found that, if there is too much blur, the
-innermost ring is not detected along the direction perpandicular to blur
-direction. This problem can be resolved by increasing radius of innermost ring.
+investigated the problem, we found that, if there is too much blur, in Gabor
+output, the innermost ring is unable to give any response along the direction
+perpandicular to blur direction. This problem can be resolved by increasing
+radius of innermost ring, reducing effect of blur on the innermost ring.
 

### 2014-03-03 ECCV/paper.tex
added conclusion, corrected typos.

@@
 additional information that often serves for ground-truth
-measurements(e.g.\cite{Bosnak:2012}\cite{Lim09})
+measurements(e.g.\cite{Bosnak:2012}\cite{Lim09}\cite{Klopschitz:2007})
 
@@
 results in motion blur in the quadcopters onboard camera.  Such motion blur has an adverse effect the
-reconition of fiducial  markers.  This can be seen in Figure \ref{fig:teaser}(b)
-where the ARTag cannot be recongized. This is not too surprising as most
-fidicuals are not explicitly designed to handle motion blur.  Compounding this
+recognition of fiducial  markers.  This can be seen in Figure
+\ref{fig:teaser}(b) where the ARTag cannot be recognized. This is not too surprising as most
+fiducials are not explicitly designed to handle motion blur.  Compounding this
 problem is the common problem of dropped video frames from the quadcopters
 wireless communication module.   This means that no only is blurring
-introduced, but there may be large discountinues in the patterns position due
+introduced, but there may be large discontinuities in the patterns position due
 to missing video frames that makes tracking challenging.
@@
 using concentric rings, we can treat them as bits allowing us to encode us
-different fiducial identifers.  As far as we are aware, this is the first work
-to design a blur resistent marker.   Our experiments show that this design can
+different fiducial identifiers.  As far as we are aware, this is the first work
+to design a blur resistant marker.   Our experiments show that this design can
 significantly outperform existing codes in the face of motion blur.
@@
 
-Intitially there were attempts to design a fiducial embeded with two dimensional
-barcode inside a rectangular grid. One of the examples of such fiducial is,
+Initially there were attempts to design a fiducial embedded with two
+dimensional barcode inside a rectangular grid. One of the examples of such fiducial is,
 ARToolkit\cite{ARToolkit02}, well known toolkit in Augmented Reality(AR) system. 
-Kato et al.\cite{kato-artoolkit} have deomstrated the use of ARToolkit to find
-the pose in cideo conferencing system. Many AR applications used ARToolkit
+Kato et al.\cite{kato-artoolkit} have demonstrated the use of ARToolkit to find
+the pose in video conferencing system. Many AR applications used ARToolkit
 due to its simplicity and efficiency.
@@
 bi-tonal system consisting of a square border and an interior region filled
-with a 6x6 grid of black or white cells. The improvement in ARTag compared
-ARToolkit was detection of coreners instead of detection of lines to find
+with a 6x6 grid of black or white cells. The improvement in ARTag compared to
+ARToolkit was detection of corners instead of detection of lines to find
 possible pattern. It proved to be more efficient than \cite{ARToolkit02} in
@@
 There were also attempts to use circular patterns instead of rectangular, as
-the projective transfomration of circles, i.e. conics, are invariant with
-resepctive to point of view of camera\cite{runetag11}. Also, such patterns are
-mostly distingushable from background and generally can not be missed.
+the projective transformation of circles, i.e., conics, are invariant with
+respective to point of view of camera\cite{runetag11}. Also, such patterns are
+mostly distinguishable from background and generally can not be missed.
 
@@
 for monocular pose estimation as well as object identification in space. Cho et al.
-\cite{Cho:2001}\cite{Cho97fastcolor} have used multi color rings instead of
+\cite{Cho:2001}\cite{Cho97fastcolor} have used multicolor rings instead of
 black and white rings\cite{concentric} to increase possible number of fiducials.
@@
 RUNE-tags are reportedly detectable even if 50\% of fiducial area is occluded.
-Bergamasco et al. have devloped another fiducial, named as Pi-Tag
+Bergamasco et al. have developed another fiducial, named as Pi-Tag
 \cite{Pitag13}, using cross-ratio concept. As cross-ratio is projective
@@
 to RUNE-tag, it uses remarkably less number of circular dots (12 dots instead of
-minimum of 43 dots), still reconisable under occlusion.
+minimum of 43 dots), still recognisable under occlusion.
 
@@
 targets. BLUT is based on the observation that although motion blurs degrade
-the visual features of the target, they, at thde same time, provide useful cues
+the visual features of the target, they at the same time, provide useful cues
 about the movements to help tracking.
@@
 and the position of tracked object does not change drastically in successive
-frames. But in our case, due to frequntly dropping of intermediate frame, this
+frames. But in our case, due to frequently dropping of intermediate frame, this
 criterion may not be satisfied.
@@
 
-We begin by first motivating the need for a new blur resistent fiducial by examining
+We begin by first motivating the need for a new blur resistant fiducial by examining
 the performance of prior fiducials under motion blur.  After this, we detail
@@
 scale is greater than 30, ARTag is not recognisable with horizontal blur
-orientation(blur angle near zero degrees) as well as vertial blur
+orientation(blur angle near zero degrees) as well as vertical blur
 orientation(blur angle near 90 degrees).
@@
 \section{Experimental Validation}
-We have implemented our algorithm in C++ using OpenCV library. Our code was run
-on a PC with Intel Core i7 processor(@3.4GHz) and 4GB RAM.
+We have implemented\footnote{Code as well as experimental data will be made
+online soon} our algorithm in C++ using OpenCV library.
+Our code was run on a PC with Intel Core i7 processor(@3.4GHz) and 4GB RAM.
 
@@
 orientations with different blur scales. Then, we tried to detect the patterns
-using algorithm presented in earlier section. The comparison of recongition
+using algorithm presented in earlier section. The comparison of recognition
 rate is shown in Figure \ref{fig:recognition_rate}.
@@
 resilience of blur by each fiducial type. We have used ar\_track\_alvar, ROS
-Wrapper for ALVAR libray \cite{ros_alvar}, to detect AR Tags from the stream
+Wrapper for ALVAR library \cite{ros_alvar}, to detect AR Tags from the stream
 captured through quadcopter. The comparison of recognition rate is shown in
@@
 \ref{fig:BLUT_output}, it can be inferred that BLUT is able to track the fiducial when the position of
-fiducial doesnot change too much in successive frames. Also, it can be seen
+fiducial does not change too much in successive frames. Also, it can be seen
 that, once BLUT looses the track of the fiducial, it is not able to recover from
-that. But, our algorithm is able to track the fiducial irrespecive of the change
-in the position of the fiducial in the image as shown in Figure
+that. But, our algorithm is able to track the fiducial irrespective of the
+change in the position of the fiducial in the image as shown in Figure
 \ref{fig:our_output}.
@@
 failed do recognize our fiducial with binary code ``00'' when there is large
-amount of blur. This is the reason behing lower recognition rate of ``00''
+amount of blur. This is the reason behind lower recognition rate of ``00''
 coded fiducial compared to that of our other fiducial patterns. When we
@@
 output, the innermost ring is unable to give any response along the direction
-perpandicular to blur direction. This problem can be resolved by increasing
+perpendicular to blur direction. This problem can be resolved by increasing
 radius of innermost ring, reducing effect of blur on the innermost ring.
@@
 \textbf{Pose Estimation} :- Currently, we are not finding the pose from the
-fiducial marker. But, if we put multiple markers (atleast four) in the same
+fiducial marker. But, if we put multiple markers (at least four) in the same
 scene, we may be able to find the pose. The current resolution of onboard camera
@@
 we are able to generate less number of fiducials. Many applications in
-robotics (e.g. qudcopter navigation) may not require large number of fiducial
+robotics (e.g. quadcopter navigation) may not require large number of fiducial
 markers as AR Tag. Most of the time, it is sufficient to have 4-6
 different fiducial patterns. Still, we may be able to generate more number of
-fiducials by using color background insted of black. E.g., if we just use Red,
+fiducials by using color background instead of black. E.g., if we just use Red,
 Green and Blue as background color, number of fiducials will be increased by
@@
 \section{Conclusion and Future Work}
+Quadcopters are subject to quick and unstable motions that can cause significant
+motion blur in the captured images. It severely affects the detection rate of
+existing fiducial markers. We proposed the design of a fiducial that is robust
+to motion blur. Our design of contrasting concentric rings is based on the the
+observation that the direction perpendicular to the motion blur direction will
+be unaffected by the blur and therefore still be recognizable. We have shown
+through experimental validation that our fiducial will work under significant
+amount of motion blur. When compared to popular fiducials, our fiducial can
+withstand around twice the amount of blur.  Though, currently we are not able to
+find the pose using single pattern, we may be able to overcome this
+shortcoming by using multiple markers in single scene. Also, through faster
+implementation of Gabor filter, the fiducial detection can be done in realtime.
 

### 2014-03-03 ECCV/paper.tex
Changed figures, tables ...

@@
 additional information that often serves for ground-truth
-measurements(e.g.\cite{Bosnak:2012}\cite{Lim09}\cite{Klopschitz:2007})
+measurements(e.g.\cite{Bosnak:2012,Lim09,Klopschitz:2007})
 
@@
 used fiducial markers 
-\cite{NaimarkF02}\cite{ARToolkit02}\cite{Fiala05}\cite{Pitag13}\cite{runetag11}.
-These typically take the form of binary codes arranged into rectangular grids (\cite{ARToolkit02}\cite{Fiala05})
+\cite{NaimarkF02,ARToolkit02,Fiala05,Pitag13,runetag11}.
+These typically take the form of binary codes arranged into rectangular grids (\cite{ARToolkit02,Fiala05})
 or other geometric features arranged in unique spatial patterns
-(\cite{NaimarkF02}\cite{Pitag13}\cite{runetag11}).
+(\cite{NaimarkF02,Pitag13,runetag11}).
 Figure \ref{fig:teaser} shows an example of the popular ARTag\cite{Fiala05} as
@@
 output of ALVAR\cite{alvar} (for detecting ARTag) versus output of our
-algorithm, in normal and blurred scene}
+algorithm, in normal and blurred scene. (b) clearly shows that ALVAR is not
+able to detect ARTag in blurred image while our algorithm can detect our
+fiducial in blurred image (d)}
 \label{fig:teaser}
@@
 Kato et al.\cite{kato-artoolkit} have demonstrated the use of ARToolkit to find
-the pose in video conferencing system. Many AR applications used ARToolkit
-due to its simplicity and efficiency.
+the pose in video based AR conferencing system. Many AR applications used
+ARToolkit due to its simplicity and efficiency.
 
@@
 for monocular pose estimation as well as object identification in space. Cho et al.
-\cite{Cho:2001}\cite{Cho97fastcolor} have used multicolor rings instead of
+\cite{Cho:2001,Cho97fastcolor} have used multicolor rings instead of
 black and white rings\cite{concentric} to increase possible number of fiducials.
@@
 
-Most tracking methods( \cite{Ross:2008} \cite{Wu:2009} \cite{Perez02}
+Most tracking methods( \cite{Ross:2008,Wu:2009,Perez02}
 \cite{Mei:2009} ) assume image sequence to be blur free. But in reality, motion
@@
 tried to detect ARTag using ALVAR library\cite{alvar} and Pi-Tag using\cite{ros_pitag}.
+Figure \ref{fig:artag_pitag} shows ARTag and Pi-tag blurred with various blur
+scales at different orientation. Table in the left side of Figure
+\ref{fig:artag_pitag} shows the recognition rate (in percent) of two fiducial
+markers at various blur scales. Table clearly indicates that both fiducial
+markers can not handle large amount of motion blur.
 
-\begin{figure}
+\begin{minipage}[h!]{\textwidth}
 \centering
+ \begin{minipage}{0.7\textwidth}
 \includegraphics[width=\linewidth]{artag_pitag.pdf}
-\caption{Blurred AR Tag and Pi--tag with various blur scales}
+%\captionof{figure}{Blurred AR Tag and Pi--tag with various blur scales}
+\end{minipage}
+\begin{minipage}{0.25\textwidth}
+%\captionof{table}{Recognition rate of AR Tag and Pi-tag fiducial marker atvarious blur scales}
+\begin{tabularx}{\textwidth}{|Y|Y|Y|}
+\cline{1-3}
+\tiny{Blur} & \multicolumn{2}{c|}{\tiny{Recognition Rate}} \\\cline{2-3}
+ \tiny{Scale}& \tiny{AR Tag} &	\tiny{Pi-Tag} \\ \cline{1-3}
+\tiny{15} & \tiny{100} & \tiny{100} \\ \cline{1-3}
+\tiny{30} & \tiny{0} & \tiny{100} \\  \cline{1-3}
+\tiny{35} & \tiny{0} & \tiny{19} \\ \cline{1-3}
+\tiny{50} & \tiny{0} & \tiny{0} \\ \cline{1-3}
+\end{tabularx}
+\end{minipage}
 \label{fig:artag_pitag}
-\end{figure}
-
-\begin{table}
-\centering
-\caption{Recognition rate of AR Tag and Pi-tag fiducial marker at various blur
-scales}
-\begin{tabularx}{0.75\textwidth}{|Y|Y|Y|}
-\cline{1-3}
-\multirow{2}{*}{Blur Scale} & \multicolumn{2}{c|}{Recognition Rate}
-\\\cline{2-3}
- & AR Tag &	Pi-Tag \\ \cline{1-3}
-15 & 100 & 100 \\ \cline{1-3}
-30 & 0 & 100 \\  \cline{1-3}
-35 & 0 & 19 \\ \cline{1-3}
-50 & 0 & 0 \\ \cline{1-3}
-\end{tabularx}
-\label{tab:artag_pitag}
-\end{table}
-
-From Table \ref{tab:artag_pitag}, it can be clearly seen that performance of
-ARTag as well as Pi-Tag drastically degrade with increase in blur scale.
+\captionof{figure}{Figure showing ARTag and Pi-tag blurred with various blur
+scales at different orientation. Table on the right shows the recognition rate
+(in percent) of both fiducial markers at various blur scales along all blur
+orientations. Table clearly indicates that both fiducial markers can not handle
+large motion blur.}
+\end{minipage}
 
@@
   \includegraphics[width=.22\linewidth]{newconcentric_11.pdf}
-  \caption{Two bit binary coded Fiducials (from left to right: Binary Code 00,
-  Binary Code 01, Binary Code 10, Binary Code 11)}
+  \caption{Two bit binary coded fiducials (from left to right: binary code 00,
+  binary code 01, binary code 10, binary code 11)}
   \label{fig:fiducials}
@@
 \includegraphics[width=\linewidth]{blur_direction.pdf}
-\caption{Relation of blur direction and unblurred linear pattern}
+\caption{Figure showing how change in blur direction changes the location of
+unblurred linear pattern.}
 \label{fig:blur_direction}
@@
 
+\begin{comment}
 Overall flow of fiducial detection algorithm can be summarised as follows:
@@
 \begin{itemize}
-  \item Apply Gabor Filter on input image
+  \item Apply Gabor filter on input image
   \item Find connected components in Gabor output
@@
 \end{itemize}
+\end{comment}
 
@@
 
-\textbf{Gabor Filter}: A 2D Gabor filter is a Gaussian kernel function modulated
-by a sinusoidal plane wave. It is used to find high gradient patches from the
+\noindent\textbf{Gabor filter}: A 2D Gabor filter is a Gaussian kernel function
+modulated by a sinusoidal plane wave. It is used to find high gradient patches from the
 image. In our case, it will detect blur invariant sections of the fiducials. We
@@
 
-\begin{figure}
+\noindent\textbf{Clustering}: Connected components are found from the Gabor
+output.
+These connected components are then clustered in hierarchical fashion, to find
+the group of closely positioned patches.
+
+\noindent\textbf{PCA}: Principal Component Analysis is done on the clustered
+Gabor output. Along first principal component, intensity profile in the original image
+is found. Number of transitions in the intensity profile will give us the
+number of rings.
+
+\noindent\textbf{Classification}: Each synthetic fiducial pattern is blurred
+along 36 orientations (0, 10, 20, \ldots , 350) and intensity profile along first
+principal component from every output is taken as training data for that
+fiducial pattern. Process of creation of training data for fiducial with
+code ``01'' is depicted in Figure \ref{fig:training_data}. Test pattern is matched
+against training data using K-Nearest Neighbor Classifier (K=5) to output class label.
+
+\begin{figure}[h!]
 \centering
@@
 \end{figure}
-
-\textbf{Clustering}: Connected components are found from the Gabor output.
-These connected components are then clustered in hierarchical fashion, to find
-the group of closely positioned patches.
-
-\textbf{PCA}: Principal Component Analysis is done on the clustered Gabor
-output. Along first principal component, intensity profile in the original image
-is found. Number of transitions in the intensity profile will give us the
-number of rings.
-
-\textbf{Classification}: Each synthetic fiducial pattern is blurred along 36
-orientations (0, 10, 20, \ldots , 350) and intensity profile along first
-principal component from every output is taken as training data for that
-fiducial pattern. Process of creation of training data for fiducial with
-code ``01'' is depicted in Figure \ref{fig:training_data}. Test pattern is matched
-against training data using K-Nearest Neighbor Classifier (K=5) to output class label.
 
@@
 \caption{Comparison of recognition rate of AR Tag and our fiducials on
-blur simulated data at various blur scales}
+blur simulated data at various blur scales. It can be clearly seen that except
+fiducial with binary code ``00'', our fiducial patterns are 
+recognised all times.}
 \label{fig:recognition_rate}
@@
 Wrapper for ALVAR library \cite{ros_alvar}, to detect AR Tags from the stream
-captured through quadcopter. The comparison of recognition rate is shown in
-Table \ref{tab:recongition_accuracy}. Classification accuracy of all fiducials(ARTag
+captured through quadcopter. In each test dataset, we used different two bit
+binary coded fiducial and recorded video of around two minute duration (i.e.,
+around 1000 frames) The comparison of recognition rate is shown in Table
+\ref{tab:recongition_accuracy}. Classification accuracy of all fiducials (ARTag
 as well as ours) is almost 100\%.
@@
 \begin{table}
-\caption{Comparison of Recognition Rate of AR Tag and our fiducials on real
-data captured through AR Drone}
+\caption{Comparison of recognition rate of AR Tag and our fiducials on real
+data captured through AR Drone. Each row shows analysis of a test
+dataset captured for our fiducial with different binary code embedded in it}
 \centering
-\begin{tabularx}{0.8\textwidth}{|Y|Y|Y|Y|Y|}
-\cline{1-5}
-\multirow{2}{*}{AR Tag} & \multicolumn{4}{ c |}{Our Fiducial} \\ \cline{2-5}
-& 00 & 01 & 10 & 11 \\  \cline{1-5}
-65.6\% & 86.5\% & 94.1\% & 92.74\% & 93.54\% \\ \cline{1-5}
+\begin{tabularx}{0.8\textwidth}{|Y|Y|Y|Y|}
+\cline{1-4}
+\multirow{2}{*}{Test Dataset ID} & \multirow{2}{*}{Binary Code}
+&\multicolumn{2}{c|}{Recognition Rate (\%)} \\ \cline{3-4} 
+& & Our Fiducial & AR Tag\\\cline{1-4} 
+1 & 00 & 86.5 &  65.6 \\ \cline{1-4} 
+2 & 01 & 94.1 &  61.9 \\ \cline{1-4} 
+3 & 10 & 92.74 & 62.4 \\ \cline{1-4}
+4 & 11 & 93.54 & 60.3 \\ \cline{1-4}
 \end{tabularx}
@@
 \subsubsection{Comparison with BLUT}
-We have used sample image sequence to test the performance of BLUT\cite{Wu:2011}
-and compare it with our result on the same image sequence. From Figure
-\ref{fig:BLUT_output}, it can be inferred that BLUT is able to track the fiducial when the position of
-fiducial does not change too much in successive frames. Also, it can be seen
-that, once BLUT looses the track of the fiducial, it is not able to recover from
-that. But, our algorithm is able to track the fiducial irrespective of the
-change in the position of the fiducial in the image as shown in Figure
-\ref{fig:our_output}.
+We have used sample image sequence (consisting of 20 frames) to test the
+performance of BLUT\cite{Wu:2011} and compare it with our result on the same
+image sequence. From Figure \ref{fig:BLUT_output}, it can be inferred that BLUT
+is able to track the fiducial when the position of fiducial does not change too
+much in successive frames. Also, it can be seen that, once BLUT looses the
+track of the fiducial, it is not able to recover from that. But, our algorithm
+is able to track the fiducial irrespective of the change in the position of the
+fiducial in the image as shown in Figure \ref{fig:our_output}.
 
@@
 \end{subfigure}
-\caption{Output of BLUT on sample image sequence}
+\caption{Output of BLUT on sample image sequence. It can be seen that from third
+frame, BLUT looses the track of our fiducial}
 \label{fig:BLUT_output}
@@
 \caption{Output of our algorithm on image sequence used in
-Figure \ref{fig:BLUT_output}}
+Figure \ref{fig:BLUT_output}. Our algorithm is able to detect our fiducial in
+all frames.}
 \label{fig:our_output}
@@
 
-\textbf{Processing Time} :-  Currently our processing time (0.3 seconds per
-frame) makes it difficult to do the fiducial detection in real-time. When we have
+\noindent\textbf{Processing Time} :-  Currently our processing time (0.3 seconds
+per frame) makes it difficult to do the fiducial detection in real-time. When we have
 done the code profiling, we found that Gabor filter takes most of the time (0.03
@@
 
-\textbf{False Negatives} :- We found that sometime our detection algorithm is
-failed do recognize our fiducial with binary code ``00'' when there is large
+\noindent\textbf{False Negatives} :- We found that sometime our detection
+algorithm is failed do recognize our fiducial with binary code ``00'' when there is large
 amount of blur. This is the reason behind lower recognition rate of ``00''
@@
 
-\textbf{Pose Estimation} :- Currently, we are not finding the pose from the
-fiducial marker. But, if we put multiple markers (at least four) in the same
+\noindent\textbf{Pose Estimation} :- Currently, we are not finding the pose from
+the fiducial marker. But, if we put multiple markers (at least four) in the same
 scene, we may be able to find the pose. The current resolution of onboard camera
@@
 
-\textbf{Number of Fiducials} :- Currently, compared to AR Tag fiducial markers,
-we are able to generate less number of fiducials. Many applications in
+\noindent\textbf{Number of Fiducials} :- Currently, compared to AR Tag fiducial
+markers, we are able to generate less number of fiducials. Many applications in
 robotics (e.g. quadcopter navigation) may not require large number of fiducial

### 2014-03-04 ECCV/paper.tex
Incorporated Michael's changes

@@
 for use with low-cost quadcopters.  Fiducial markers are commonly placed
-in environments to provide a reliable and unique marker conducive for
-tracking and recognition.   For quadcopter applications, fiducials are
+in environments to provide a uniquely identifiable object in the scene.
+For quadcopter applications, fiducials are
 typically used for evaluating planning algorithms by allowing ground truth
@@
 blur that severely affects the detection rate of existing fiducial markers.
-This motivated us to design a fiducial that is robust to motion blur. Our design
-uses a series of concentric circles with the observation is that the direction
-perpendicular to the motion blur direction will be unaffected by the blur and
-therefore still be recognizable.  We detail the design and
+This problem motivated us to design a fiducial that is robust to motion blur.
+Our proposed fiducial design uses concentric circles with the observation that the direction perpendicular to the motion blur direction will be unaffected by the blur.  As a result,
+the fiducial code along this direction is recognizable.  The circular design allows this to
+  work for all motion blur directions.  We detail the design and
 detection algorithm for our fiducial and show that our marker can significantly
 outperform existing fiducial markers in scenes captured with a quadcopter.
-\keywords{Fiducials, Tracking, Detection using Blur}
+\keywords{Fiducials, tracking, recognition under blur}
 \end{abstract}
@@
 The recent availability of low-cost quadcopters has help to fuel significant efforts in
-research focused on Unmanned Aerial Vehicles.  Navigation and planning of
+research focused on unmanned aerial vehicles.  Navigation and planning of
 these vehicles is typically performed using onboard inertial sensors and/or
-vision based modules that uses visual cues in the real world\cite{Davison:2007}. 
+vision based modules that uses visual cues in the real world~\cite{Davison:2007}.
 However, to evaluate the effectiveness of navigation methods, artificial
-fiducial markers are commonly introduces into the environment to provide
-additional information that often serves for ground-truth
-measurements(e.g.\cite{Bosnak:2012,Lim09,Klopschitz:2007})
+fiducial markers are commonly placed into the environment to provide
+additional information that serves for ground-truth
+positional measurements (e.g.\cite{Bosnak:2012,Lim09,Klopschitz:2007}).
 
-In order to be effective, fiducial markers (or simply called, fiducials) need
-to be easily detected in the scene.  There are various existing commonly
-used fiducial markers 
-\cite{NaimarkF02,ARToolkit02,Fiala05,Pitag13,runetag11}.
-These typically take the form of binary codes arranged into rectangular grids (\cite{ARToolkit02,Fiala05})
-or other geometric features arranged in unique spatial patterns
+In order to be effective, fiducial markers (or simply, fiducials) need
+to be easily detected in the scene.  A variety of fiducial markers
+have been proposed in the literature (e.g.~\cite{NaimarkF02,ARToolkit02,Fiala05,Pitag13,runetag11}).
+These take the form of binary codes arranged into rectangular grids (\cite{ARToolkit02,Fiala05})
+or other geometric features arranged in predefined spatial patterns
 (\cite{NaimarkF02,Pitag13,runetag11}).
-Figure \ref{fig:teaser} shows an example of the popular ARTag\cite{Fiala05} as
-seen from a quad-copter.  One problem, however, is that low-cost quadcopters
-often exhibit very quick and erratic motion.  These fast physical movements
-results in motion blur in the quadcopters onboard camera.  Such motion blur has an adverse effect the
-recognition of fiducial  markers.  This can be seen in Figure
-\ref{fig:teaser}(b) where the ARTag cannot be recognized. This is not too surprising as most
-fiducials are not explicitly designed to handle motion blur.  Compounding this
-problem is the common problem of dropped video frames from the quadcopters
-wireless communication module.   This means that no only is blurring
+Figure \ref{fig:teaser}-top shows an example of the popular ARTag\cite{Fiala05} as
+seen from a quadcopter.  A problem for existing fiducials is  that low-cost quadcopters
+oftenexhibit very quick and erratic physical movements that
+results in motion blur in the quadcopters onboard camera.  This motion blur has an adverse effect the  recognition of fiducial  markers.  This can be seen in Figure
+\ref{fig:teaser}(top) where the ARTag cannot be recognized due to motion blur. This is not too surprising as most  existing fiducials are not explicitly designed to handle motion blur.
+
+Compounding this problem is the additional issue of dropped video frames from the quadcopters
+wireless communication module.   This means that not only is blurring
 introduced, but there may be large discontinuities in the patterns position due
-to missing video frames that makes tracking challenging.
+to missing video frames.  As we will show in Section 4, this latter problem makes it challenging to apply tracking algorithms that can exploit temporal coherence for determining
+the fiducial positions.
 
-To address this problem, propose a fiducial design that is robust to motion
-blur and drastic drastic change in its position in successive frames.  Our
-design is based on concentric circles as shown in Figure \ref{fig:fiducials}. 
-The design is based on the observation that motion blur from a quadcopter tends
-to be linear in nature.  As such, when our code is blurred, there is no blur in
-the direction perpendicular to the direction of motion.   This allows the
-signature of the fiducial to remain intact in any direction.  In addition, by
-using concentric rings, we can treat them as bits allowing us to encode us
-different fiducial identifiers.  As far as we are aware, this is the first work
-to design a blur resistant marker.   Our experiments show that this design can
-significantly outperform existing codes in the face of motion blur.
+\noindent{\textbf Contribution}~~To address these problems, we propose a
+fiducial that is designed to be robust to motion blur.  Our design is based on
+concentric circles as shown in Figure \ref{fig:teaser}-b.  The design is based
+on the observation that motion blur from a quadcopter tends to be linear in
+nature.  As such, when our code is blurred, there is no blur in the direction
+perpendicular to the direction of motion.   This allows the signature of the
+fiducial to remain intact in any direction.  In addition, by using concentric
+rings, we can treat the presence or absence of a ring as a bit, allowing us to
+assign an code to the marker.  Our experiments show that this design can
+significantly outperform existing codes in the face of motion blur. As far as
+we are aware, this is the first work to propose a blur resistant marker.
 
@@
 \includegraphics[width=\linewidth]{teaser.pdf}
-\caption{Figure showing experimental setup and comparison of
-output of ALVAR\cite{alvar} (for detecting ARTag) versus output of our
-algorithm, in normal and blurred scene. (b) clearly shows that ALVAR is not
-able to detect ARTag in blurred image while our algorithm can detect our
-fiducial in blurred image (d)}
+\caption{This figure show experimental setup and comparison of
+output of ALVAR\cite{alvar} (for detecting ARTag) versus our blur resistant fiducial
+in a normal and blurred scene. The scene contains two ARTags and our code.
+(a) shows that the ARTag can be detected when the image has no blur. 
+(b) shows that ARTags are no longer detectible due to the blur.
+(c-d) show the same images in (a) and (b) where our code is being detected.}
 \label{fig:teaser}
@@
 
+[MSB: related works still needs a couple more passes, I've left it as it.
+as mentioned yesterday, we need to address the problems with the circular 
+pattern design, this needs to be done in the same paragraph, not later as done now. ]
+
 Our work is related to two areas: fiducial markers and
 object tracking. We will briefly discuss work done in both areas.
-
-\textbf{Fiducials} :- Some of fiducial designs are shown in Figure
-\ref{fig:previous_work}.
 
@@
  \end{subfigure}
- \caption{Various Fiducial Marker Designs}
+ \caption{This figure shows the design of several existing fiducial markers.  While
+ suitable for many environments that are not designed to be recognized under blur.}
  \label{fig:previous_work}
@@
 
-Initially there were attempts to design a fiducial embedded with two
-dimensional barcode inside a rectangular grid. One of the examples of such fiducial is,
-ARToolkit\cite{ARToolkit02}, well known toolkit in Augmented Reality(AR) system. 
-Kato et al.\cite{kato-artoolkit} have demonstrated the use of ARToolkit to find
-the pose in video based AR conferencing system. Many AR applications used
+\noindent{\textbf{Fiducials}}~Figure~\ref{fig:previous_work} shows several examples
+of existing fiducial markers.
+Many designs use a two dimensional barcode inside a rectangular grid.
+One of the examples of such fiducial is, ARToolkit\cite{ARToolkit02}, well known toolkit in Augmented Reality (AR) system.
+Kato et al.\cite{kato-artoolkit} have demonstrated the use of ARToolkit to find the pose in video based AR conferencing system.
+Many AR applications used
 ARToolkit due to its simplicity and efficiency.
@@
 respective to point of view of camera\cite{runetag11}. Also, such patterns are
-mostly distinguishable from background and generally can not be missed.
+more distinguishable from the background scene due to their unique design.
 
-Concentric rings are reportedly used first by Gatrell et al.\cite{concentric}
+The use of concentric rings was used  by Gatrell et al.\cite{concentric}
 for monocular pose estimation as well as object identification in space. Cho et al.
@@
 in their fiducial named, Circular Data Matrix. It was beneficial in terms of
-easy detection of fiducial as well as more number of fiducial patterns.
+easy detection of fiducial as well as being able to encode more unique IDs.
 
@@
 Bergamasco et al. have developed another fiducial, named as Pi-Tag
-\cite{Pitag13}, using cross-ratio concept. As cross-ratio is projective
+\cite{Pitag13}, using the cross-ratio concept. As cross-ratio is projective
 invariant, the detection of Pi-tag is easier than other tags. Also, compared
@@
 
-\textbf{Tracking}:-
-Fiducial detection in video may be considered as tracking problem where tracked
-object is fiducial itself. Visual tracking plays an important role in
-surveillance, robotics, human computer interaction, and medical
-imaging\cite{Yilmaz:2006}. Yilmaz et al.\cite{Yilmaz:2006} have done survey of
-various tracking methods.
+\noindent{\textbf{Tracking}}~~Fiducial detection between successive video 
+frames can be considered a tracking problem where the tracked object is fiducial itself.
+There is a very large body of research dedicated to tracking and interested
+readers are referred to~\cite{Yilmaz:2006} for a survey.
 
 Most tracking methods( \cite{Ross:2008,Wu:2009,Perez02}
-\cite{Mei:2009} ) assume image sequence to be blur free. But in reality, motion
-blur is inherent part of most of the videos. Wu et al.\cite{Wu:2011} have
+\cite{Mei:2009} ) assume the image sequence to be blur free. In reality, however,
+motion blur in video sequences is often unavoidable. Wu et al.\cite{Wu:2011} have
 developed BLUr-driven Tracker (BLUT) framework for tracking motion-blurred
@@
 
-BLUT framework successfully tracks blurred target when there is uniform motion
+The BLUT framework successfully tracks blurred target when there is uniform motion
 and the position of tracked object does not change drastically in successive
-frames. But in our case, due to frequently dropping of intermediate frame, this
-criterion may not be satisfied.
+frames. But as we will demonstrate in Section 4, the erratic motion from quadcopters as 
+well as the problem of dropped video frames is beyond the current ability of such trackers.
 
@@
 Before we detail the design of our fiducial, we examine the performance of two
-popular fiducials under motion blur that have different designs. Specifically,
-we examine ARTags\cite{Fiala05} and PiTags\cite{Pitag13}.
+popular fiducials under motion blur.  Specifically we examine ARTags\cite{Fiala05} and PiTags\cite{Pitag13} given their difference in geometry design.
 
-We scaled down ARTag as well as PiTag fiducial to size 150x150.  Then, we
-blurred both fiducials at various orientations using different scales.
-Figure \ref{fig:artag_pitag} shows sample blurred AR Tag and Pi-Tag. Finally, we
-tried to detect ARTag using ALVAR library\cite{alvar} and Pi-Tag using\cite{ros_pitag}.
-Figure \ref{fig:artag_pitag} shows ARTag and Pi-tag blurred with various blur
-scales at different orientation. Table in the left side of Figure
+To simulate the appearance of the maker as seen by a quadcopter, 
+we scaled down ARTag as well as PiTag fiducial to size 150x150. 
+ Both fiducials are then blurred at various orientations with different blurs scales
+(denoted in pixels).   The blur motion ranged from X to Y in magnitude, representing
+small to significant moton blur.   Figure \ref{fig:artag_pitag} shows the visual appearance
+of the blurred tags.   We then use try to detect the markers using the 
+ALVAR library\cite{alvar} and Pi-Tag library\cite{ros_pitag}.
+The table in the left side of Figure
 \ref{fig:artag_pitag} shows the recognition rate (in percent) of two fiducial
-markers at various blur scales. Table clearly indicates that both fiducial
-markers can not handle large amount of motion blur.
+markers at various blur scales under different orientation.
+As we can see, the PiTag performance quickly diminished under small amounts of blur, however, at 40 motion blur, ARTag is recognition rate drops to less than 20\%.
 
@@
 (in percent) of both fiducial markers at various blur scales along all blur
-orientations. Table clearly indicates that both fiducial markers can not handle
-large motion blur.}
+orientations.  Recognition rates for both tag is significantly reduces due to blur.
+For severe blur, detection is not possible.}
 \end{minipage}
+
+\subsection{Blur Resistent Fiducial}
 
@@
 \end{comment}
-We have designed a fiducial that may be thought of as a binary code.  It
-contains concentric white rings of equal widths on a black background with a
-blurred border. The outermost and innermost rings represent the start and end
-of the code and is embedded in the fiducial; these are not considered part of
-the code itself. The binary code is represented by the presence (or absence) of
-rings between ``marker'' rings.
+
+We have designed a fiducial that can be considered a binary code.  The design
+uses concentric white rings of equal widths on a black background with a
+blurred border\footnote{This design can be easily inverted to have a white background with white rings}. The outermost and innermost rings represent the start and end
+of the code and is embedded in the fiducial.  The binary code is represented by the presence (or absence) of rings between ``marker'' rings.
 
@@
 Our fiducial detection strategy is different from \cite{NaimarkF02,Pitag13} and works
-under significant amount of blur.   In particular, we assume that scene motion
-blur be modelled locally as a linear motion blur \cite{Moshe:2003,Moshe:2004}. 
-Under this assumption, scene content perpendicular to the blur direction is 
+under significant amounts of blur.   As previously mentioned, our approach works
+ under the assumption that the motion blur on the camera mount on the quadcoptuer
+ can be modelled as linear motion.  This assumption about the motion blur has been shown to be
+ reasonable in prior works targeting camera motion blur (e.g.~\cite{Moshe:2003,Moshe:2004}).
+Under this assumption, the scene content perpendicular to the blur direction is
 unaffected by the blur.  Because of our circular design, this means the
@@
 \ref{fig:blur_direction} shows an example with various motion directions.
+
+[MSB: You have to describe the algorithm here as discussed yesterday.  Please complete this
+part.]
+ We give a brief overview of our algorithm here and details to each step in the following. Figure \ref{fig:overall_flow} shows the process involved in fiducial detection
+process. Our detection algorithm has four steps.  First, we apply a Gabor filter on the camera frame, next . . .
 
@@
 \includegraphics[width=\linewidth]{overall_flow.pdf}
-\caption{Overall Workflow}
+\caption{Overall Workflow - [MSB: Details?  This is why I said this I didn't think this
+was the updated version of the paper. We discussed this yesterday, you need details in all of your captions.] }
 \label{fig:overall_flow}
@@
 \section{Experimental Validation}
-We have implemented\footnote{Code as well as experimental data will be made
-online soon} our algorithm in C++ using OpenCV library.
-Our code was run on a PC with Intel Core i7 processor(@3.4GHz) and 4GB RAM.
 
-Our system has been tested on the image sequences captured from AR Drone
+[MSB: As discussed yesterday, in the table reporting the results you need to give the 
+number of frames in tested video clip.  We may also need to comment on the
+number of dropped frames if this is possible to get. We mentioned this in the
+paper, but never mentioned this in the experimetal results.]
+
+We have implemented our algorithm in C++ using OpenCV library.
+Experiments were performed on a PC with Intel Core i7 processor(@3.4GHz) and 4GB RAM.
+Source code and data sets in this paper will be made publicly available.
+
+Our system has been tested several image sequences captured from AR Drone
 quadcopter. Each image sequence contains frames containing different fiducial
@@
 \subsubsection{Comparison with BLUT}
-We have used sample image sequence (consisting of 20 frames) to test the
-performance of BLUT\cite{Wu:2011} and compare it with our result on the same
+
+We have used sample image sequence (consisting of 20 frames [MSB: This is inviting trouble, I can guarentee you this will likely get your paper rejected.]) to test the performance of BLUT\cite{Wu:2011} and compare it with our result on the same
 image sequence. From Figure \ref{fig:BLUT_output}, it can be inferred that BLUT

### 2014-03-04 ECCV/paper.tex
Long captions, added figures for BLUT comparison and many more ...

@@
 This problem motivated us to design a fiducial that is robust to motion blur.
-Our proposed fiducial design uses concentric circles with the observation that the direction perpendicular to the motion blur direction will be unaffected by the blur.  As a result,
-the fiducial code along this direction is recognizable.  The circular design allows this to
-  work for all motion blur directions.  We detail the design and
-detection algorithm for our fiducial and show that our marker can significantly
-outperform existing fiducial markers in scenes captured with a quadcopter.
+Our proposed fiducial design uses concentric circles with the observation that
+the direction perpendicular to the motion blur direction will be unaffected by
+the blur.  As a result, the fiducial code along this direction is recognizable.
+The circular design allows this to work for all motion blur directions.  We
+detail the design and detection algorithm for our fiducial and show that our
+marker can significantly outperform existing fiducial markers in scenes captured with a quadcopter.
 \keywords{Fiducials, tracking, recognition under blur}
@@
 seen from a quadcopter.  A problem for existing fiducials is  that low-cost quadcopters
-oftenexhibit very quick and erratic physical movements that
-results in motion blur in the quadcopters onboard camera.  This motion blur has an adverse effect the  recognition of fiducial  markers.  This can be seen in Figure
-\ref{fig:teaser}(top) where the ARTag cannot be recognized due to motion blur. This is not too surprising as most  existing fiducials are not explicitly designed to handle motion blur.
+often exhibit very quick and erratic physical movements that
+results in motion blur in the quadcopters onboard camera.  This motion blur has
+an adverse effect the  recognition of fiducial  markers.  This can be seen in
+Figure \ref{fig:teaser}(top) where the ARTag cannot be recognized due to motion
+blur. This is not too surprising as most  existing fiducials are not explicitly
+designed to handle motion blur.
 
@@
 introduced, but there may be large discontinuities in the patterns position due
-to missing video frames.  As we will show in Section 4, this latter problem makes it challenging to apply tracking algorithms that can exploit temporal coherence for determining
-the fiducial positions.
+to missing video frames.  As we will show in Section 4, this latter problem
+makes it challenging to apply tracking algorithms that can exploit temporal
+coherence for determining the fiducial positions.
 
@@
 
-[MSB: related works still needs a couple more passes, I've left it as it.
-as mentioned yesterday, we need to address the problems with the circular 
-pattern design, this needs to be done in the same paragraph, not later as done now. ]
-
-Our work is related to two areas: fiducial markers and
-object tracking. We will briefly discuss work done in both areas.
+Our work is related to two areas: fiducial markers and object tracking. We will
+briefly discuss work done in both areas.
 
@@
 
-Most tracking methods( \cite{Ross:2008,Wu:2009,Perez02}
-\cite{Mei:2009} ) assume the image sequence to be blur free. In reality, however,
-motion blur in video sequences is often unavoidable. Wu et al.\cite{Wu:2011} have
-developed BLUr-driven Tracker (BLUT) framework for tracking motion-blurred
-targets. BLUT is based on the observation that although motion blurs degrade
-the visual features of the target, they at the same time, provide useful cues
-about the movements to help tracking.
+Most tracking methods( \cite{Ross:2008,Wu:2009,Perez02,Mei:2009} ) assume the
+image sequence to be blur free. In reality, however, motion blur in video
+sequences is often unavoidable. Wu et al.\cite{Wu:2011} have developed
+BLUr-driven Tracker (BLUT) framework for tracking motion-blurred targets. BLUT
+is based on the observation that although motion blurs degrade the visual
+features of the target, they at the same time, provide useful cues about the
+movements to help tracking.
 
@@
 Before we detail the design of our fiducial, we examine the performance of two
-popular fiducials under motion blur.  Specifically we examine ARTags\cite{Fiala05} and PiTags\cite{Pitag13} given their difference in geometry design.
+popular fiducials under motion blur.  Specifically we examine ARTags
+\cite{Fiala05} and PiTags\cite{Pitag13} given their difference in geometry design.
 
-To simulate the appearance of the maker as seen by a quadcopter, 
-we scaled down ARTag as well as PiTag fiducial to size 150x150. 
- Both fiducials are then blurred at various orientations with different blurs scales
-(denoted in pixels).   The blur motion ranged from X to Y in magnitude, representing
-small to significant moton blur.   Figure \ref{fig:artag_pitag} shows the visual appearance
-of the blurred tags.   We then use try to detect the markers using the 
-ALVAR library\cite{alvar} and Pi-Tag library\cite{ros_pitag}.
+To simulate the appearance of the maker as seen by a quadcopter,  we scaled down
+ARTag as well as PiTag fiducial to size 150x150. Both fiducials are then blurred
+at various orientations with different blurs scales (denoted in pixels).   The
+blur motion ranged from 15 to 50 in magnitude, representing small to significant
+motion blur. Figure \ref{fig:artag_pitag} shows the visual appearance of the
+blurred tags. We then use try to detect the markers using the ALVAR
+library\cite{alvar} and Pi-Tag library\cite{ros_pitag}.
 The table in the left side of Figure
 \ref{fig:artag_pitag} shows the recognition rate (in percent) of two fiducial
-markers at various blur scales under different orientation.
-As we can see, the PiTag performance quickly diminished under small amounts of blur, however, at 40 motion blur, ARTag is recognition rate drops to less than 20\%.
+markers at various blur scales under different orientation.   As we can see,
+the PiTag performance quickly diminished under small amounts of blur, however,
+at 35 motion blur, ARTag is recognition rate drops to less than 20\%.
 
-\begin{minipage}[h!]{\textwidth}
-\centering
- \begin{minipage}{0.7\textwidth}
-\includegraphics[width=\linewidth]{artag_pitag.pdf}
+\noindent\begin{minipage}[h!]{\textwidth}
+\noindent\begin{minipage}{0.6\textwidth}
+\includegraphics[width=\textwidth]{artag_pitag.pdf}
 %\captionof{figure}{Blurred AR Tag and Pi--tag with various blur scales}
 \end{minipage}
-\begin{minipage}{0.25\textwidth}
+\begin{minipage}{0.35\textwidth}
 %\captionof{table}{Recognition rate of AR Tag and Pi-tag fiducial marker atvarious blur scales}
@@
 \cline{1-3}
-\tiny{Blur} & \multicolumn{2}{c|}{\tiny{Recognition Rate}} \\\cline{2-3}
- \tiny{Scale}& \tiny{AR Tag} &	\tiny{Pi-Tag} \\ \cline{1-3}
-\tiny{15} & \tiny{100} & \tiny{100} \\ \cline{1-3}
-\tiny{30} & \tiny{0} & \tiny{100} \\  \cline{1-3}
-\tiny{35} & \tiny{0} & \tiny{19} \\ \cline{1-3}
-\tiny{50} & \tiny{0} & \tiny{0} \\ \cline{1-3}
+\small{Blur} & \multicolumn{2}{c|}{ \small{Recognition Rate}}
+\\\cline{2-3}
+\small{Scale}& \small{AR Tag} &	\small{Pi-Tag} \\ \cline{1-3}
+\small{15} & \small{100} & \small{100} \\ %\cline{1-3}
+\small{30} & \small{0} & \small{100} \\  %\cline{1-3}
+\small{35} & \small{0} & \small{19} \\ %\cline{1-3}
+\small{50} & \small{0} & \small{0} \\ \cline{1-3}
 \end{tabularx}
@@
 uses concentric white rings of equal widths on a black background with a
-blurred border\footnote{This design can be easily inverted to have a white background with white rings}. The outermost and innermost rings represent the start and end
-of the code and is embedded in the fiducial.  The binary code is represented by the presence (or absence) of rings between ``marker'' rings.
+blurred border\footnote{This design can be easily inverted to have a white
+background with white rings}. The outermost and innermost rings represent the
+start and end of the code and is embedded in the fiducial.  The binary code is
+represented by the presence (or absence) of rings between ``marker'' rings.
 
@@
 
-[MSB: You have to describe the algorithm here as discussed yesterday.  Please complete this
-part.]
- We give a brief overview of our algorithm here and details to each step in the following. Figure \ref{fig:overall_flow} shows the process involved in fiducial detection
-process. Our detection algorithm has four steps.  First, we apply a Gabor filter on the camera frame, next . . .
+We give a brief overview of our algorithm here and details to each step in the
+following. Figure \ref{fig:overall_flow} shows the process involved in fiducial
+detection process. Our detection algorithm has four steps. First, we apply a
+Gabor filter (Step 1) on the image captured through AR Drone. Next, we find the
+clusters of patches found in Gabor output using hierarchical clustering (Step
+2). Later, we perform Principal Component Analysis (PCA) on each cluster, to
+find the blur invariant direction (Step 3). The intensity profile along this
+direction is found in the original image. And finally, we match this intensity
+profile with training data using K-Nearest neighbor classifier (Step 4).
 
@@
 
-Figure \ref{fig:overall_flow} shows the process involved in fiducial detection
-process.
-
-\begin{figure}
+\begin{figure}[ht!]
 \includegraphics[width=\linewidth]{overall_flow.pdf}
-\caption{Overall Workflow - [MSB: Details?  This is why I said this I didn't think this
-was the updated version of the paper. We discussed this yesterday, you need details in all of your captions.] }
+\caption{The flow of our algorithm to detect and classify fiducial in the scene
+captured from AR Drone. Four step process includes Gabor Filter(Step 1),
+Hierarchical Clustering (Step 2), PCA (Step 3) and Classification using
+K-Nearest Neighbor (KNN) classifier (Step 4). Training data for KNN classifier is gathered
+offline.}
 \label{fig:overall_flow}
@@
 
+\noindent Details of each of the steps are as follows:\\
 \noindent\textbf{Gabor filter}: A 2D Gabor filter is a Gaussian kernel function
@@
   \includegraphics[width=\linewidth]{training_data.pdf}
-  \caption{Training data for the fiducial pattern with binary code ``01''}
+  \caption{Process to create training data for the fiducial pattern with binary
+  code ``01''. Synthetic pattern is blurred along various orientations. Gabor
+  filter is applied on the blurred pattern. Intensity profile is found along the
+  first principal component of the clustered Gabor output. Same process is used
+  to create training data for other fiducial patterns.}
   \label{fig:training_data}
@@
 
-[MSB: As discussed yesterday, in the table reporting the results you need to give the 
-number of frames in tested video clip.  We may also need to comment on the
-number of dropped frames if this is possible to get. We mentioned this in the
-paper, but never mentioned this in the experimetal results.]
-
 We have implemented our algorithm in C++ using OpenCV library.
@@
 
-\begin{figure}
+\begin{figure}[hb!]
 \begin{subfigure}{0.5\textwidth}
@@
   \end{subfigure}
-  \caption{Sample Outputs for two bit binary coded fiducials}
+  \caption{Sample outputs for two bit binary coded fiducials. Class label
+  attached to the detected fiducial is decimal equivalent of the binary code of
+  the detected fiducial.}
 \end{figure}
@@
 well as correctly classified them as shown in Figure \ref{fig:output_all}.
+
 \begin{figure}
@@
   \includegraphics[width=.8\linewidth]{output_all_2.jpg}
-  \caption{Sample output containing all two bit binary coded fiducial patterns}
+  \caption{Sample output containing all two bit binary coded fiducial patterns
+  in single frame.}
   \label{fig:output_all}
@@
 
-\begin{figure}
+\begin{figure}[h!]
 \centering
@@
 
-\begin{table}
+\begin{table}[h!]
 \caption{Comparison of recognition rate of AR Tag and our fiducials on real
 data captured through AR Drone. Each row shows analysis of a test
-dataset captured for our fiducial with different binary code embedded in it}
+dataset captured for our fiducial with different binary code embedded in it.
+Each dataset has around 1000 frames captured in around two minutes.}
 \centering
-\begin{tabularx}{0.8\textwidth}{|Y|Y|Y|Y|}
-\cline{1-4}
-\multirow{2}{*}{Test Dataset ID} & \multirow{2}{*}{Binary Code}
-&\multicolumn{2}{c|}{Recognition Rate (\%)} \\ \cline{3-4}
-& & Our Fiducial & AR Tag\\\cline{1-4}
-1 & 00 & 86.5 &  65.6 \\ \cline{1-4}
-2 & 01 & 94.1 &  61.9 \\ \cline{1-4}
-3 & 10 & 92.74 & 62.4 \\ \cline{1-4}
-4 & 11 & 93.54 & 60.3 \\ \cline{1-4}
+\begin{tabularx}{\textwidth}{|c|Y|Y|Y|Y|}
+\cline{1-5}
+\multirow{2}{*}{Test \#} & \multirow{2}{*}{Number of Frames}
+&\multirow{2}{*}{Binary Code} &\multicolumn{2}{c|}{Recognition Rate (\%)} \\
+\cline{4-5} & & & Our Fiducial & AR Tag\\\cline{1-5}
+1 & 1205 & 00 & 86.5 &  65.6 \\ \cline{1-5}
+2 & 1047 & 01 & 94.1 &  61.9 \\ \cline{1-5}
+3 & 1102 & 10 &  92.74 & 62.4 \\ \cline{1-5}
+4 & 1081 & 11 & 93.54 & 60.3 \\ \cline{1-5}
 \end{tabularx}
@@
 
-We have used sample image sequence (consisting of 20 frames [MSB: This is inviting trouble, I can guarentee you this will likely get your paper rejected.]) to test the performance of BLUT\cite{Wu:2011} and compare it with our result on the same
-image sequence. From Figure \ref{fig:BLUT_output}, it can be inferred that BLUT
-is able to track the fiducial when the position of fiducial does not change too
-much in successive frames. Also, it can be seen that, once BLUT looses the
-track of the fiducial, it is not able to recover from that. But, our algorithm
-is able to track the fiducial irrespective of the change in the position of the
-fiducial in the image as shown in Figure \ref{fig:our_output}.
+We have used four image sequences (consisting of around 1000 frames each) , each
+one containing our different fiducial pattern, to test the performance of
+BLUT\cite{Wu:2011} and compare it with our result on the same image sequence.
+From top rows of Figure \ref{fig:BLUT_compare_00}-\ref{fig:BLUT_compare_11}, it
+can be inferred that BLUT is able to track the fiducial when the position of
+fiducial does not change too much in successive frames. Also, it can be seen
+that, once BLUT looses the track of the fiducial, it is not able to recover
+from that. But, our algorithm is able to track the fiducial irrespective of the
+change in the position of the fiducial in the image as shown in bottom rows of Figure
+\ref{fig:BLUT_compare_00}-\ref{fig:BLUT_compare_11}.
+
+We have also found that, even if we reset the BLUT tracker after loosing track,
+it looses track again after around 100 frames i.e., approximately 6 seconds.
+When we checked the timestamp data from image header captured through AR Drone,
+we found that, there was difference of 0.14 seconds between two successive
+frames in the earlier case, which clearly suggests the dropping of frame. Also,
+there were around 50 instances in 1000 frames where timestamp difference between two
+successive frames was greater than 0.1 seconds. So, it is evident that
+due to dropping of frames combined with unstable motion of quadcopter, tracking
+through quadcopter using conventional tracking methods is not accurate.
 
@@
 \begin{subfigure}[b]{.19\textwidth}
-\includegraphics[width=\linewidth]{11.jpg}
+\includegraphics[width=\linewidth]{BLUT_output_00/2.jpg}
 \end{subfigure}
 \begin{subfigure}[b]{.19\textwidth}
-\includegraphics[width=\linewidth]{12.jpg}
+\includegraphics[width=\linewidth]{BLUT_output_00/3.jpg}
 \end{subfigure}
 \begin{subfigure}[b]{.19\textwidth}
-\includegraphics[width=\linewidth]{13.jpg}
+\includegraphics[width=\linewidth]{BLUT_output_00/4.jpg}
 \end{subfigure}
 \begin{subfigure}[b]{.19\textwidth}
-\includegraphics[width=\linewidth]{14.jpg}
+\includegraphics[width=\linewidth]{BLUT_output_00/5.jpg}
 \end{subfigure}
 \begin{subfigure}[b]{.19\textwidth}
-\includegraphics[width=\linewidth]{15.jpg}
+\includegraphics[width=\linewidth]{BLUT_output_00/6.jpg}
+\end{subfigure}\\
+\begin{subfigure}[b]{.19\textwidth}
+\includegraphics[width=\linewidth]{BLUT_input_00/output2.jpg}
 \end{subfigure}
-\caption{Output of BLUT on sample image sequence. It can be seen that from third
-frame, BLUT looses the track of our fiducial}
-\label{fig:BLUT_output}
+\begin{subfigure}[b]{.19\textwidth}
+\includegraphics[width=\linewidth]{BLUT_input_00/output3.jpg}
+\end{subfigure}
+\begin{subfigure}[b]{.19\textwidth}
+\includegraphics[width=\linewidth]{BLUT_input_00/output4.jpg}
+\end{subfigure}
+\begin{subfigure}[b]{.19\textwidth}
+\includegraphics[width=\linewidth]{BLUT_input_00/output5.jpg}
+\end{subfigure}
+\begin{subfigure}[b]{.19\textwidth}
+\includegraphics[width=\linewidth]{BLUT_input_00/output6.jpg}
+\end{subfigure}
+\caption{Top: Output of BLUT\cite{Wu:2011} on sample image sequence containing ``00''
+binary coded fiducial, Bottom: Output of our algorithm on the same image
+sequence. BLUT is able to track the fiducial till third frame, but from fourth
+frame, BLUT looses track of the fiducial. In first three frames, size of the
+fiducials is less but in fourth and fifth frame it is bigger, hinting sudden
+forward movement of quadcopter.}
+\label{fig:BLUT_compare_00}
 \end{figure}
@@
 \begin{subfigure}[b]{.19\textwidth}
-\includegraphics[width=\linewidth]{output11.jpg}
+\includegraphics[width=\linewidth]{BLUT_output_01/11.jpg}
 \end{subfigure}
 \begin{subfigure}[b]{.19\textwidth}
-\includegraphics[width=\linewidth]{output12.jpg}
+\includegraphics[width=\linewidth]{BLUT_output_01/12.jpg}
 \end{subfigure}
 \begin{subfigure}[b]{.19\textwidth}
-\includegraphics[width=\linewidth]{output13.jpg}
+\includegraphics[width=\linewidth]{BLUT_output_01/13.jpg}
 \end{subfigure}
 \begin{subfigure}[b]{.19\textwidth}
-\includegraphics[width=\linewidth]{output14.jpg}
+\includegraphics[width=\linewidth]{BLUT_output_01/14.jpg}
 \end{subfigure}
 \begin{subfigure}[b]{.19\textwidth}
-\includegraphics[width=\linewidth]{output15.jpg}
+\includegraphics[width=\linewidth]{BLUT_output_01/15.jpg}
+\end{subfigure}\\
+\begin{subfigure}[b]{.19\textwidth}
+\includegraphics[width=\linewidth]{BLUT_input_01/output11.jpg}
 \end{subfigure}
-\caption{Output of our algorithm on image sequence used in
-Figure \ref{fig:BLUT_output}. Our algorithm is able to detect our fiducial in
-all frames.}
-\label{fig:our_output}
+\begin{subfigure}[b]{.19\textwidth}
+\includegraphics[width=\linewidth]{BLUT_input_01/output12.jpg}
+\end{subfigure}
+\begin{subfigure}[b]{.19\textwidth}
+\includegraphics[width=\linewidth]{BLUT_input_01/output13.jpg}
+\end{subfigure}
+\begin{subfigure}[b]{.19\textwidth}
+\includegraphics[width=\linewidth]{BLUT_input_01/output14.jpg}
+\end{subfigure}
+\begin{subfigure}[b]{.19\textwidth}
+\includegraphics[width=\linewidth]{BLUT_input_01/output15.jpg}
+\end{subfigure}
+\caption{Top: Output of BLUT\cite{Wu:2011} on sample image sequence containing
+``01'' binary coded fiducial, Bottom: Output of our algorithm on the same image
+sequence. BLUT looses the track from third frame.}
+\label{fig:BLUT_compare_01}
+\end{figure}
+
+\begin{figure}
+\begin{subfigure}[b]{.19\textwidth}
+\includegraphics[width=\linewidth]{BLUT_output_10/1.jpg}
+\end{subfigure}
+\begin{subfigure}[b]{.19\textwidth}
+\includegraphics[width=\linewidth]{BLUT_output_10/2.jpg}
+\end{subfigure}
+\begin{subfigure}[b]{.19\textwidth}
+\includegraphics[width=\linewidth]{BLUT_output_10/3.jpg}
+\end{subfigure}
+\begin{subfigure}[b]{.19\textwidth}
+\includegraphics[width=\linewidth]{BLUT_output_10/4.jpg}
+\end{subfigure}
+\begin{subfigure}[b]{.19\textwidth}
+\includegraphics[width=\linewidth]{BLUT_output_10/5.jpg}
+\end{subfigure}\\
+\begin{subfigure}[b]{.19\textwidth}
+\includegraphics[width=\linewidth]{BLUT_input_10/output1.jpg}
+\end{subfigure}
+\begin{subfigure}[b]{.19\textwidth}
+\includegraphics[width=\linewidth]{BLUT_input_10/output2.jpg}
+\end{subfigure}
+\begin{subfigure}[b]{.19\textwidth}
+\includegraphics[width=\linewidth]{BLUT_input_10/output3.jpg}
+\end{subfigure}
+\begin{subfigure}[b]{.19\textwidth}
+\includegraphics[width=\linewidth]{BLUT_input_10/output4.jpg}
+\end{subfigure}
+\begin{subfigure}[b]{.19\textwidth}
+\includegraphics[width=\linewidth]{BLUT_input_10/output5.jpg}
+\end{subfigure}
+\caption{Top: Output of BLUT\cite{Wu:2011} on sample image sequence containing
+``10'' binary coded fiducial, Bottom: Output of our algorithm on the same image
+sequence. From second frame itself, BLUT looses the track.}
+\label{fig:BLUT_compare_10}
+\end{figure}
+
+\begin{figure}
+\begin{subfigure}[b]{.19\textwidth}
+\includegraphics[width=\linewidth]{BLUT_output_11/2.jpg}
+\end{subfigure}
+\begin{subfigure}[b]{.19\textwidth}
+\includegraphics[width=\linewidth]{BLUT_output_11/3.jpg}
+\end{subfigure}
+\begin{subfigure}[b]{.19\textwidth}
+\includegraphics[width=\linewidth]{BLUT_output_11/4.jpg}
+\end{subfigure}
+\begin{subfigure}[b]{.19\textwidth}
+\includegraphics[width=\linewidth]{BLUT_output_11/5.jpg}
+\end{subfigure}
+\begin{subfigure}[b]{.19\textwidth}
+\includegraphics[width=\linewidth]{BLUT_output_11/6.jpg}
+\end{subfigure}\\
+\begin{subfigure}[b]{.19\textwidth}
+\includegraphics[width=\linewidth]{BLUT_input_11/output2.jpg}
+\end{subfigure}
+\begin{subfigure}[b]{.19\textwidth}
+\includegraphics[width=\linewidth]{BLUT_input_11/output3.jpg}
+\end{subfigure}
+\begin{subfigure}[b]{.19\textwidth}
+\includegraphics[width=\linewidth]{BLUT_input_11/output4.jpg}
+\end{subfigure}
+\begin{subfigure}[b]{.19\textwidth}
+\includegraphics[width=\linewidth]{BLUT_input_11/output5.jpg}
+\end{subfigure}
+\begin{subfigure}[b]{.19\textwidth}
+\includegraphics[width=\linewidth]{BLUT_input_11/output6.jpg}
+\end{subfigure}
+\caption{Top: Output of BLUT\cite{Wu:2011} on sample image sequence containing
+``11'' binary coded fiducial, Bottom: Output of our algorithm on the same image
+sequence. BlUT lost the track from third frame. There is sudden reversal of
+direction of quadcopter from third frame. In first two frames quadcopter was
+going up, but suddenly it moved down in third frame.}
+\label{fig:BLUT_compare_11}
 \end{figure}

### 2014-03-06 DetectFiducial/src/main.cpp
Normalized intensity along 1st principal component.

@@ -17,7 +17,7 @@
 
 
 //#define TRAIN_MODE
-//define DEBUG
+//#define DEBUG
 //#define DEBUG2
 //#define DEBUG3
 
@@ -100,7 +100,7 @@ int main(int argc, char* argv[])
 	doCluster(connectedComponents, clusters);
 	int numClusters = clusters.rows;
 #ifdef DEBUG
-	Mat cloned_input = input.clone();
+	//Mat cloned_input = input.clone();
 #endif
 	for(int i=0; i<numClusters; i++)
 	{
@@ -387,9 +387,9 @@ bool detectCode(const Mat &pts, int left, int top, int right, int bottom, const 
 			Point last_pt = downward_pts.back();
 			if (index ==1)
 				line(cloned_input, first_pt, last_pt, Scalar(0,255,0), 3);
-
 		}
-*/
+		*/
+
 		reverse(upward_pts.begin(), upward_pts.end());
 		line_pts[index] = upward_pts;
 		line_pts[index].insert(line_pts[index].end(), downward_pts.begin(), downward_pts.end());
@@ -408,13 +408,14 @@ bool detectCode(const Mat &pts, int left, int top, int right, int bottom, const 
 	imwrite("pca.jpg", cloned_input);
 	*/
 #ifdef DEBUG
-	Mat cloned_input = input.clone();
+	//Mat cloned_input = input.clone();
 #endif
 	vector<int> ring_starts[3];
 	vector<int> ring_widths[3];
 	for(int i=0; i<3; i++){
 		int totalPoints = numPtsPerLine[i];
 		Mat profile(totalPoints, 1, CV_8U, intensities[i]);
+		normalize(profile, profile, 0, 255, NORM_MINMAX, CV_8UC1);
 		//Mat smoothProfile;
 		//boxFilter(profile, smoothProfile, CV_32FC1, Size(5,1));
 		Mat thresh_profile;

### 2014-03-06 ECCV/paper.tex
Added new results, incorporated Michael's changes in PPTs.

@@
 additional information that serves for ground-truth
-positional measurements (e.g.\cite{Bosnak:2012,Lim09,Klopschitz:2007}).
+positional measurements (e.g.,\cite{Bosnak:2012,Lim09,Klopschitz:2007}).
 
@@
 to be easily detected in the scene.  A variety of fiducial markers
-have been proposed in the literature (e.g.~\cite{NaimarkF02,ARToolkit02,Fiala05,Pitag13,runetag11}).
+have been proposed in the literature
+(e.g.,~\cite{NaimarkF02,ARToolkit02,Fiala05,Pitag13,runetag11}).
 These take the form of binary codes arranged into rectangular grids (\cite{ARToolkit02,Fiala05})
@@
 often exhibit very quick and erratic physical movements that
-results in motion blur in the quadcopters onboard camera.  This motion blur has
-an adverse effect the  recognition of fiducial  markers.  This can be seen in
+results in motion blur in the quadcopter's onboard camera.  This motion blur has
+an adverse effect on the  recognition of fiducial  markers.  This can be seen in
 Figure \ref{fig:teaser}(top) where the ARTag cannot be recognized due to motion
@@
 
-Compounding this problem is the additional issue of dropped video frames from the quadcopters
-wireless communication module.   This means that not only is blurring
+Compounding this problem is the additional issue of dropped video frames from
+the quadcopter's wireless communication module.   This means that not only is blurring
 introduced, but there may be large discontinuities in the patterns position due
-to missing video frames.  As we will show in Section 4, this latter problem
+to missing video frames.  As we will show in Section 4, this later problem
 makes it challenging to apply tracking algorithms that can exploit temporal
@@
 
-\noindent{\textbf Contribution}~~To address these problems, we propose a
+\noindent\textbf{Contribution:}~~To address these problems, we propose a
 fiducial that is designed to be robust to motion blur.  Our design is based on
@@
 The remainder of this paper is organized as follows.   Section 2 gives an
-overview of related work, focused on fiducials as well the related problem of
+overview of related work, focused on fiducials as well as the related problem of
 tracking.  Section 3 discusses the our design and detection algorithm, by first
@@
 \includegraphics[width=\linewidth]{teaser.pdf}
-\caption{This figure show experimental setup and comparison of
+\caption{This figure shows experimental setup and comparison of
 output of ALVAR\cite{alvar} (for detecting ARTag) versus our blur resistant fiducial
@@
 (a) shows that the ARTag can be detected when the image has no blur. 
-(b) shows that ARTags are no longer detectible due to the blur.
+(b) shows that ARTags are no longer detectable due to the blur.
 (c-d) show the same images in (a) and (b) where our code is being detected.}
@@
 
-\noindent{\textbf{Fiducials}}~Figure~\ref{fig:previous_work} shows several examples
-of existing fiducial markers.
-Many designs use a two dimensional barcode inside a rectangular grid.
-One of the examples of such fiducial is, ARToolkit\cite{ARToolkit02}, well known toolkit in Augmented Reality (AR) system.
-Kato et al.\cite{kato-artoolkit} have demonstrated the use of ARToolkit to find the pose in video based AR conferencing system.
-Many AR applications used
-ARToolkit due to its simplicity and efficiency.
+\noindent{\textbf{Fiducials:}}~Figure~\ref{fig:previous_work} shows several 
+examples of existing fiducial markers.  Many designs use a two dimensional
+barcode inside a rectangular grid. One of the examples of such fiducial is,
+ARToolkit\cite{ARToolkit02}, well known toolkit in Augmented Reality (AR)
+system. Kato et al.\cite{kato-artoolkit} have demonstrated the use of ARToolkit
+to find the pose in video based AR conferencing system. Many AR applications
+used ARToolkit due to its simplicity and efficiency.
 
@@
 
-\noindent{\textbf{Tracking}}~~Fiducial detection between successive video 
+\noindent{\textbf{Tracking:}}~~Fiducial detection between successive video 
 frames can be considered a tracking problem where the tracked object is fiducial itself.
@@
 motion blur. Figure \ref{fig:artag_pitag} shows the visual appearance of the
-blurred tags. We then use try to detect the markers using the ALVAR
+blurred tags. We then try to detect the markers using the ALVAR
 library\cite{alvar} and Pi-Tag library\cite{ros_pitag}.
@@
 (in percent) of both fiducial markers at various blur scales along all blur
-orientations.  Recognition rates for both tag is significantly reduces due to blur.
+orientations.  Recognition rates for both tag is significantly reduced due to
+blur.
 For severe blur, detection is not possible.}
@@
 
-\subsection{Blur Resistent Fiducial}
+\subsection{Blur Resistant Fiducial}
 
@@
 
-We have designed a fiducial that can be considered a binary code.  The design
+We have designed a fiducial that can be considered as a binary code.  The design
 uses concentric white rings of equal widths on a black background with a
@@
 under significant amounts of blur.   As previously mentioned, our approach works
- under the assumption that the motion blur on the camera mount on the quadcoptuer
+ under the assumption that the motion blur on the camera mount on the quadcopter
  can be modelled as linear motion.  This assumption about the motion blur has been shown to be
@@
 \begin{figure}[hb!]
-\begin{subfigure}{0.5\textwidth}
+\begin{subfigure}{\textwidth}
 \centering
-  \includegraphics[width=\linewidth]{output_00.jpg}
+  \includegraphics[width=0.48\linewidth]{output_00.jpg}
+  \includegraphics[width=0.48\linewidth]{new_results/output_00.jpg}
   \caption{Binary code ``00''}
@@
 \end{subfigure}
-\begin{subfigure}{0.5\textwidth}
+\begin{subfigure}{\textwidth}
 \centering
-  \includegraphics[width=\linewidth]{output_01.jpg}
+  \includegraphics[width=0.48\linewidth]{output_01.jpg}
+  \includegraphics[width=0.48\linewidth]{new_results/output_01.jpg}
   \caption{Binary code ``01''}
@@
 \end{subfigure}
-\begin{subfigure}{0.5\textwidth}
+\begin{subfigure}{\textwidth}
 \centering
-  \includegraphics[width=\linewidth]{output_10.jpg}
+  \includegraphics[width=0.48\linewidth]{output_10.jpg}
+  \includegraphics[width=0.48\linewidth]{new_results/output_10.jpg}
   \caption{Binary code ``10''}
@@
 \end{subfigure}
-\begin{subfigure}{0.5\textwidth}
+\begin{subfigure}{\textwidth}
 \centering
-  \includegraphics[width=\linewidth]{output_11.jpg}
+  \includegraphics[width=0.48\linewidth]{output_11.jpg}
+  \includegraphics[width=0.48\linewidth]{new_results/output_11.jpg}
   \caption{Binary code ``11''}
@@
   \end{subfigure}
-  \caption{Sample outputs for two bit binary coded fiducials. Class label
-  attached to the detected fiducial is decimal equivalent of the binary code of
-  the detected fiducial.}
+  \caption{Sample outputs for two bit binary coded fiducials on different
+  datasets. Class label attached to the detected fiducial is decimal equivalent
+  of the binary code embedded in the detected fiducial.}
 \end{figure}
@@
 \centering
-  \includegraphics[width=.8\linewidth]{output_all_2.jpg}
-  \caption{Sample output containing all two bit binary coded fiducial patterns
-  in single frame.}
+  \includegraphics[width=.45\linewidth]{output_all_2.jpg}
+  \includegraphics[width=.45\linewidth]{new_results/output_test_all1.jpg}
+  \caption{Sample outputs containing all two bit binary coded fiducial patterns
+  in single frame}
   \label{fig:output_all}
@@
 compare our results with Blur driven tracker(BLUT)\cite{Wu:2011}.
-\subsubsection{Comparison with ARTag}
+\subsubsection{Comparison with ARTag:}
 First, we have repeated blur simulation experiment on our fiducials too, i.e.,
@@
 
-\subsubsection{Comparison with BLUT}
+\subsubsection{Comparison with BLUT:}
 
@@
 ``11'' binary coded fiducial, Bottom: Output of our algorithm on the same image
-sequence. BlUT lost the track from third frame. There is sudden reversal of
+sequence. BLUT lost the track from third frame. There is sudden reversal of
 direction of quadcopter from third frame. In first two frames quadcopter was
@@
 
-\noindent\textbf{Processing Time} :-  Currently our processing time (0.3 seconds
+\noindent\textbf{Processing Time:}~~Currently our processing time (0.3 seconds
 per frame) makes it difficult to do the fiducial detection in real-time. When we have
@@
 
-\noindent\textbf{False Negatives} :- We found that sometime our detection
-algorithm is failed do recognize our fiducial with binary code ``00'' when there is large
-amount of blur. This is the reason behind lower recognition rate of ``00''
+\noindent\textbf{False Negatives:}~~We found that sometimes our detection
+algorithm fails to recognize our fiducial with binary code ``00'' when there is
+large amount of blur. This is the reason behind lower recognition rate of ``00''
 coded fiducial compared to that of our other fiducial patterns. When we
@@
 
-\noindent\textbf{Pose Estimation} :- Currently, we are not finding the pose from
+\noindent\textbf{Pose Estimation:}~~Currently, we are not finding the pose from
 the fiducial marker. But, if we put multiple markers (at least four) in the same
@@
 
-\noindent\textbf{Number of Fiducials} :- Currently, compared to AR Tag fiducial
+\noindent\textbf{Number of Fiducials:}~~Currently, compared to AR Tag fiducial
 markers, we are able to generate less number of fiducials. Many applications in

### 2014-03-06 DetectFiducial/src/main.cpp
Output center point.

@@ -30,6 +30,7 @@ void doCluster(const Mat&, Mat&);
 void getPoints(const Mat &binOutput, int left, int top, int right, int bottom, Mat &outPts);
 bool detectCode(const Mat &pts, int left, int top, int right, int bottom, const Mat &input, vector<float>& intensity_profile, int& num_rings );
 void createTrainingData(const string &orig_dirname, Mat & trainingData, Mat & response);
+Point center;
 
 int findDiffMinMax(vector<int> ring_widths[], int dim, int first, int second){
 	vector<int> first_ring_width = ring_widths[first];
@@ -198,11 +199,13 @@ int main(int argc, char* argv[])
 			Point pt_text_end = pt2 + Point(82,0);
 			rectangle(output,pt_text_start, pt_text_end, Scalar(0,255,255),-1);
 			putText(output, str, pt2, FONT_HERSHEY_DUPLEX, 0.75, Scalar(0,0,255));
+			circle(output, center, 1, Scalar(0,0,255), -1, 8, 0);
 			break;
 		}
 	}
 	//imshow("output", output);
 	waitKey();
+	cout<<"Center:"<<center<<"\n";
 	imwrite("output.jpg", output);
 	if(!found){
 		cout<<"Code not detected\n";
@@ -381,14 +384,18 @@ bool detectCode(const Mat &pts, int left, int top, int right, int bottom, const 
 				}
 			}
 		}
-/*
+
 		if(upward_pts.size() > 0 && downward_pts.size() > 0){
 			Point first_pt = upward_pts.back();
 			Point last_pt = downward_pts.back();
-			if (index ==1)
-				line(cloned_input, first_pt, last_pt, Scalar(0,255,0), 3);
+			if (index ==1){
+				center = first_pt + last_pt;
+				center.x = center.x/2;
+				center.y = center.y/2;
+				//line(cloned_input, first_pt, last_pt, Scalar(0,255,0), 3);
+			}
 		}
-		*/
+
 
 		reverse(upward_pts.begin(), upward_pts.end());
 		line_pts[index] = upward_pts;

### 2014-03-06 ECCV/paper.tex
Incorporated Michael's changes, suggestions and many more...

@@
 For quadcopter applications, fiducials are
-typically used for evaluating planning algorithms by allowing ground truth
+often used for evaluating planning algorithms by allowing ground truth
 positions in the scene to be detected from the quadcopter's camera. Quadcopters,
@@
 the direction perpendicular to the motion blur direction will be unaffected by
-the blur.  As a result, the fiducial code along this direction is recognizable.
+the blur.  This allows the fiducial code along the blur direction to be recognized.
 The circular design allows this to work for all motion blur directions.  We
 detail the design and detection algorithm for our fiducial and show that our
-marker can significantly outperform existing fiducial markers in scenes captured with a quadcopter.
+marker can significantly outperform existing fiducial markers in scenes
+captured with a quadcopter.
 \keywords{Fiducials, tracking, recognition under blur}
@@
 these vehicles is typically performed using onboard inertial sensors and/or
-vision based modules that uses visual cues in the real world~\cite{Davison:2007}.
-However, to evaluate the effectiveness of navigation methods, artificial
-fiducial markers are commonly placed into the environment to provide
-additional information that serves for ground-truth
+vision based modules that uses visual cues in the real world~(e.g.
+\cite{Davison:2007,Engel12,Engel13}). However, to evaluate the effectiveness of
+navigation methods, fiducial markers are commonly placed into the environment
+to provide additional information that serves for ground-truth
 positional measurements (e.g.,\cite{Bosnak:2012,Lim09,Klopschitz:2007}).
@@
 These take the form of binary codes arranged into rectangular grids (\cite{ARToolkit02,Fiala05})
-or other geometric features arranged in predefined spatial patterns
+or other geometric primitives arranged in predefined spatial patterns
 (\cite{NaimarkF02,Pitag13,runetag11}).
-Figure \ref{fig:teaser}-top shows an example of the popular ARTag\cite{Fiala05} as
+Figure \ref{fig:teaser}-(a) show the popular ARTag\cite{Fiala05} as
 seen from a quadcopter.  A problem for existing fiducials is that low-cost quadcopters
@@
 an adverse effect on the  recognition of fiducial  markers.  This can be seen in
-Figure \ref{fig:teaser}(top) where the ARTag cannot be recognized due to motion
+Figure \ref{fig:teaser}-(b) where the ARTag cannot be recognized due to motion
 blur. This is not too surprising as most  existing fiducials are not explicitly
@@
 fiducial that is designed to be robust to motion blur.  Our design is based on
-concentric circles as shown in Figure \ref{fig:teaser}-b.  The design is based
+concentric circles as shown in Figure \ref{fig:teaser}-(c,d).  The design is based
 on the observation that motion blur from a quadcopter tends to be linear in
@@
 rings, we can treat the presence or absence of a ring as a bit, allowing us to
-assign an code to the marker.  Our experiments show that this design can
+assign a code to the marker.  Our experiments show that this design can
 significantly outperform existing codes in the face of motion blur. As far as
@@
 The remainder of this paper is organized as follows.   Section 2 gives an
-overview of related work, focused on fiducials as well as the related problem of
-tracking.  Section 3 discusses the our design and detection algorithm, by first
-examining the performance of existing codes under blur. Section 4 shows several
+overview of related work related to fiducials as well as the related problem of
+tracking.  Section 3 discusses the our design and detection algorithm as well as 
+examining the performance of existing codes under motion blur. Section 4 shows several
 experiments using quadcopter imagery.  This is followed by a discussion and
@@
 
-Our work is related to two areas: fiducial markers and object tracking. We will
+Our work is related to two areas: fiducial markers and object tracking. We
 briefly discuss work done in both areas.
@@
  \end{subfigure}
- \begin{subfigure}[b]{0.19\textwidth}
+ \begin{subfigure}[b]{0.14\textwidth}
  \centering
@@
  \end{subfigure}
- \begin{subfigure}[b]{0.19\textwidth}
+ \begin{subfigure}[b]{0.14\textwidth}
   \centering
@@
  \caption{This figure shows the design of several existing fiducial markers.  While
- suitable for many environments that are not designed to be recognized under blur.}
+ each codes have their own pros and cons of various environments, none are designed to be recognized under motion blur.}
  \label{fig:previous_work}
@@
 examples of existing fiducial markers.  Many designs use a two dimensional
-barcode inside a rectangular grid. One of the examples of such fiducial is,
-ARToolkit\cite{ARToolkit02}, well known toolkit in Augmented Reality (AR)
-system. Kato et al.\cite{kato-artoolkit} have demonstrated the use of ARToolkit
-to find the pose in video based AR conferencing system. Many AR applications
-used ARToolkit due to its simplicity and efficiency.
+barcode inside a rectangular grid. One examples of such a fiducial is from the 
+ARToolkit~\cite{ARToolkit02}, a well known toolkit used in many augmented reality (AR) applications. Kato et al.\cite{kato-artoolkit} demonstrated the use of ARToolkit
+to find the pose in video based AR conferencing system.
 
-Fiala et al. \cite{Fiala05} developed a fiducial termed, ARTag, which is a
-bi-tonal system consisting of a square border and an interior region filled
-with a 6x6 grid of black or white cells. The improvement in ARTag compared to
+Fiala et al. \cite{Fiala05} proposed a fiducial termed, ARTag, which is a
+bi-tonal system consisting of a square border and an interior 6$\times$6 grid of black or white cells. The improvement in ARTag compared to
 ARToolkit was detection of corners instead of detection of lines to find
-possible pattern. It proved to be more efficient than \cite{ARToolkit02} in
+possible pattern. This proved to be more efficient than \cite{ARToolkit02} in
 terms of marker recognition rate as well as the number of different patterns
-which can be created. But, drawback of ARTag is, under significant amount of
-motion blur, corners can not be detected, resulting in non-recognition of tag.
+which can be created.   The reliance on both line and corner detection hampers recognition under motion blur.
 
-There were also attempts to use circular patterns instead of rectangular, as
-the projective transformation of circles, i.e., conics, are invariant with
-respective to point of view of camera\cite{runetag11}. Also, such patterns are
-more distinguishable from the background scene due to their unique design.
-
+There were also attempts to use circular patterns instead of rectangular. 
 The use of concentric rings was used  by Gatrell et al.\cite{concentric}
@@
 These multicolor rings are used in wide area tracking in large scale
-applications.
+applications.  While based on a concentric rings, these particular approaches require 
+the full ring to be recognized which is not possible when the pattern undergoes directional
+motion blur.
 
-Naimark et al. \cite{NaimarkF02} have combined concentric rings and 2D bar code
-in their fiducial named, Circular Data Matrix. It was beneficial in terms of
-easy detection of fiducial as well as being able to encode more unique IDs.
+Naimark et al.~\cite{NaimarkF02} proposed a circular bar code
+called the, Circular Data Matrix that is beneficial in terms of
+easy detection and ability to have a large number
+of uniquely identifiable codes.  Addressing the issue of occlusion, 
+Bergamasco et al. \cite{runetag11} proposed the RUNE-tag fiducial divided into number of
+circular dots arranged them in circular fashion.
+RUNE-tags can be detected even when up to 50\% of fiducial area is occluded.
+Bergamasco et al.~\cite{Pitag13} proposed the Pi-Tag fiducial also composed 
+of circular structures but arranged in a rectangle to exploit projective invariant cross-ration.
+This provided similar occlusion resistance as RUNE-tag but with even less
+circular dots. All of these techniques however relies on generic features
+(e.g., circle detection) that break down under motion blur.
 
-All of these fiducials are not recognizable under occlusion.
-Bergamasco et al. \cite{runetag11} have divided fiducial into number of
-circular dots, and arranged them in circular fashion, named as RUNE-Tag.
-RUNE-tags are reportedly detectable even if 50\% of fiducial area is occluded.
-Bergamasco et al. have developed another fiducial, named as Pi-Tag
-\cite{Pitag13}, using the cross-ratio concept. As cross-ratio is projective
-invariant, the detection of Pi-tag is easier than other tags. Also, compared
-to RUNE-tag, it uses remarkably less number of circular dots (12 dots instead of
-minimum of 43 dots), still recognisable under occlusion.
-
-But again problem with circular fiducials is, it is very difficult to detect
-ellipses accurately under significant motion blur. So, under blur, recognition
-rate of these fiducials is very low.
-
-Zhang et al.\cite{Zhang:2002} and Claus et al. \cite{ClausF04} have done
-quite comprehensive comparative study of various fiducial marker systems with
-respect to processing time, recognition rate and accuracy with
-respect to viewing angle and distance.
+%Zhang et al.\cite{Zhang:2002} and Claus et al. \cite{ClausF04} have done
+%quite comprehensive comparative study of various fiducial marker systems with
+%respect to processing time, recognition rate and accuracy with
+%respect to viewing angle and distance.
 
@@
 
-Most tracking methods( \cite{Ross:2008,Wu:2009,Perez02,Mei:2009} ) assume the
+Most tracking methods(~\cite{Ross:2008,Wu:2009,Perez02,Mei:2009} ) assume the
 image sequence to be blur free. In reality, however, motion blur in video
-sequences is often unavoidable. Wu et al.\cite{Wu:2011} have developed
-BLUr-driven Tracker (BLUT) framework for tracking motion-blurred targets. BLUT
+sequences is often unavoidable. To this end, Wu et al.\cite{Wu:2011} proposed the
+Blur-driven Tracker (BLUT) framework for tracking motion-blurred targets. BLUT
 is based on the observation that although motion blurs degrade the visual
@@
 
-\section{Design of Fiducial}
+\section{Design of Blur Resistant Fiducial}
 
@@
 
-\subsection{Examining Prior Fiducials Under Motion Blur}
+\subsection{Examining Prior Fiducials Under Motion Blur}\label{sec:blurtest}
 
@@
 To simulate the appearance of the maker as seen by a quadcopter,  we scaled down
-ARTag as well as PiTag fiducial to size 150x150. Both fiducials are then blurred
-at various orientations with different blurs scales (denoted in pixels).   The
-blur motion ranged from 15 to 50 in magnitude, representing small to significant
-motion blur. Figure \ref{fig:artag_pitag} shows the visual appearance of the
-blurred tags. We then try to detect the markers using the ALVAR
-library\cite{alvar} and Pi-Tag library\cite{ros_pitag}.
-The table in the left side of Figure
-\ref{fig:artag_pitag} shows the recognition rate (in percent) of two fiducial
-markers at various blur scales under different orientation.   As we can see,
-the PiTag performance quickly diminished under small amounts of blur, however,
-at 35 motion blur, ARTag is recognition rate drops to less than 20\%.
+the ARTag and PiTag fiducials to be size 150$\times$150 pixels. Both fiducials are then blurred
+using linear motion blur at various orientations with different blurs scales.  
+The blur motion ranged from 15 to 50 in magnitude (denoted in pixels),
+representing small to significant motion blur. Figure \ref{fig:artag_pitag}
+shows the visual appearance of the blurred tags.  We then try to detect the
+markers using the ALVAR library~\cite{alvar} and Pi-Tag
+library~\cite{ros_pitag}. The table in the left side of
+Figure~\ref{fig:artag_pitag} shows the recognition rate (in percentage) of two
+fiducial markers at various blur scales over all the different orientation.  
+As we can see, the PiTag performance quickly diminished under small amounts of
+blur, however, at 35 motion blur, ARTag is recognition rate drops to less than 20\%.
 
@@
 orientations.  Recognition rates for both tag is significantly reduced due to
-blur.
-For severe blur, detection is not possible.}
+blur. For severe blur, detection is not possible.}
 \end{minipage}
@@
 
-\begin{comment}
-
-\begin{minipage}{\textwidth}
-  \begin{minipage}[b]{0.49\textwidth}
-\captionof{table}{Recognition rate of AR Tag at various blur scales}
-\centering
- \begin{tabularx}{0.75\textwidth}{|Y|Y|}
-\cline{1-2}
-Blur Scale & Recognition Rate(\%) \\ \cline{1-2}
-30 & 100\\ \cline{1-2}
-35 & 19 \\ \cline{1-2}
-40 & 9 \\ \cline{1-2}
-45 & 5 \\ \cline{1-2}
-50 & 0 \\ \cline{1-2}
-\end{tabularx}
-\label{tab:ARTag_blur}
- \end{minipage}	
- \begin{minipage}[b]{0.49\textwidth} 	
-\captionof{table}{Blur angle range}
-\centering
-\begin{tabularx}{0.75\textwidth}{|Y|Y|}
-\cline{1-2}
-Blur Scale & Blur Angle Range \\ \cline{1-2}
-30 & 0 -- 90\\ \cline{1-2}
-35 & 32 -- 58 \\ \cline{1-2}
-40 & 41 -- 48 \\ \cline{1-2}
-45 & 41 -- 48 \\ \cline{1-2}
-50 & 44 -- 46 \\ \cline{1-2}
-\end{tabularx}
-\label{tab:artag_blurangle}
- \end{minipage}
-\end{minipage}
-
-From Table \ref{tab:ARTag_blur}, it can be clearly seen that performance of
-ARTag drastically degrade with increase in blur scale.
-
-We have also analysed the recognition rate along different blur orientations
-(from 0 to 90 degrees) at different blur scales. We found that per blur scale,
-at certain blur orientations, recognition of ARTag fails. Table shows the range
-of blur angles for which we are able to recognise the ARTag at different blur
-scales. From Table \ref{tab:artag_blurangle}, it can be seen that, when blur
-scale is greater than 30, ARTag is not recognisable with horizontal blur
-orientation(blur angle near zero degrees) as well as vertical blur
-orientation(blur angle near 90 degrees).
-
-We have performed blur simulation experiment on Pi-tag \cite{Pitag13} to find
-how blur effects circular patterns. We tried to detect blurred Pi-tag using
-\cite{ros_pitag}.
-
-\begin{figure}
-\begin{subfigure}[b]{0.3\textwidth}
-  \centering
-  \includegraphics[width=\linewidth]{detect_noblur.jpg}
-  No Blur
- \end{subfigure}
- \begin{subfigure}[b]{0.3\textwidth}
-  \centering
-  \includegraphics[width=\linewidth]{detect_blur15.jpg}
-  Blur Scale = 15
- \end{subfigure}
- \begin{subfigure}[b]{0.3\textwidth}
-  \centering
-  \includegraphics[width=\linewidth]{nodetect_blur20.jpg}
-  Blur Scale = 20
- \end{subfigure}
- \caption{Effect of blur on detection of Pi-Tag}
- \label{fig:pitag_blur}
-\end{figure}
-
-From Figure \ref{fig:pitag_blur}, it can be seen that, Pi-tag detection
-fails when blur scale is more than 15. The reason behind this is, Pi-tag
-detection is based on Ellipse detection which will fail in the presence of
-significant amount of blur. So, ellipse detection may not be the efficient way
-to detect circular patterns under blur.
-\end{comment}
-
-We have designed a fiducial that can be considered as a binary code.  The design
-uses concentric white rings of equal widths on a black background with a
-blurred border\footnote{This design can be easily inverted to have a white
-background with white rings}. The outermost and innermost rings represent the
-start and end of the code and is embedded in the fiducial.  The binary code is
-represented by the presence (or absence) of rings between ``marker'' rings.
+We have designed binary coded fiducial that uses concentric white rings of
+equal widths on a black background with a blurred border\footnote{This design
+can be easily inverted to have a white background with white rings}. The
+outermost and innermost rings represent the start and end of the code and is
+embedded in the fiducial.  The binary code is represented by the presence (or
+absence) of rings between ``marker'' rings.
 
@@
 \centering
-  \includegraphics[width=.22\linewidth]{newconcentric_00.pdf}
-  \includegraphics[width=.22\linewidth]{newconcentric_01.pdf}
-  \includegraphics[width=.22\linewidth]{newconcentric_10.pdf}
-  \includegraphics[width=.22\linewidth]{newconcentric_11.pdf}
+  \includegraphics[width=.18\linewidth]{newconcentric_00.pdf}
+  \includegraphics[width=.18\linewidth]{newconcentric_01.pdf}
+  \includegraphics[width=.18\linewidth]{newconcentric_10.pdf}
+  \includegraphics[width=.18\linewidth]{newconcentric_11.pdf}
   \caption{Two bit binary coded fiducials (from left to right: binary code 00,
-  binary code 01, binary code 10, binary code 11)}
+  binary code 01, binary code 10, binary code 11.)}
   \label{fig:fiducials}
@@
 binary code. For example, if the binary code has three bits, there will be a
-maximum of three rings between``marker'' rings and we end up with eight
-different patterns. Figure \ref{fig:fiducials} shows two bit binary coded
+maximum of three rings between marker-rings and we end up with eight
+different patterns. Figure \ref{fig:fiducials} shows a two bit binary coded
 fiducials.
@@
 under significant amounts of blur.   As previously mentioned, our approach works
- under the assumption that the motion blur on the camera mount on the quadcopter
- can be modelled as linear motion.  This assumption about the motion blur has been shown to be
+under the observation that the motion blur for the quadcopter's camera
+can be well modelled as linear motion.  This  linear motion blur assumption has been shown to be
 reasonable in prior works targeting camera motion blur (e.g.~\cite{Moshe:2003,Moshe:2004}).
 Under this assumption, the scene content perpendicular to the blur direction is
-unaffected by the blur.  Because of our circular design, this means the
-perpendicular direction can be observed as a unblurred linear pattern.  Figure
-\ref{fig:blur_direction} shows an example with various motion directions.
+unaffected by the blur.  Because of our circular design, the
+direction perpendicular to the linear motion will appear as an unblurred linear
+pattern.  Figure \ref{fig:blur_direction} shows examples of this using a
+pattern  with various motion directions.
 
-We give a brief overview of our algorithm here and details to each step in the
-following. Figure \ref{fig:overall_flow} shows the process involved in fiducial
-detection process. Our detection algorithm has four steps. First, we apply a
-Gabor filter (Step 1) on the image captured through AR Drone. Next, we find the
-clusters of patches found in Gabor output using hierarchical clustering (Step
-2). Later, we perform Principal Component Analysis (PCA) on each cluster, to
-find the blur invariant direction (Step 3). The intensity profile along this
-direction is found in the original image. And finally, we match this intensity
-profile with training data using K-Nearest neighbor classifier (Step 4).
-
-\begin{comment}
-Overall flow of fiducial detection algorithm can be summarised as follows:
-
-\begin{itemize}
-  \item Apply Gabor filter on input image
-  \item Find connected components in Gabor output
-  \item Cluster the connected components into bounding boxes
-  \item Detect code in the bounding box
-  \begin{itemize}
-    \item Run PCA on Gabor output in bounding box
-    \item Find intensity profile along first principal component passing through
-    centroid
-    \item Classify the detected code by training examples
-    standards.
-  \end{itemize}
-\end{itemize}
-\end{comment}
+Figure \ref{fig:overall_flow} shows the process involved in fiducial
+detection process. We give a brief overview of our algorithm here and details
+to each step in the following.  Our detection algorithm has four steps. Step 1,
+we apply a Gabor filter on the image captured through AR Drone to isolate the
+potential locations of the pattern.  Step 2, we find the clusters of patches
+found in Gabor output using spatial clustering.  Step 3, performs Principal
+Component Analysis (PCA) on each cluster to find the dominate direction
+unaffected by blur.  Step 4, based on the direction we extract the intensity
+profile of the pattern and classify the code using a K-Nearest neighbor
+classifier based on training data.
 
@@
 \includegraphics[width=\linewidth]{overall_flow.pdf}
-\caption{The flow of our algorithm to detect and classify fiducial in the scene
-captured from AR Drone. Four step process includes Gabor Filter(Step 1),
-Hierarchical Clustering (Step 2), PCA (Step 3) and Classification using
-K-Nearest Neighbor (KNN) classifier (Step 4). Training data for KNN classifier is gathered
-offline.}
+\caption{An overview of our algorithm to detect and classify fiducial. 
+The four step process includes (Step 1) Gabor filtering,
+(Step 2) component clustering, (Step 3) PCA to determine the dominate direction, 
+and (Step 4) KNN classification using training-data captured for each pattern.}
 \label{fig:overall_flow}
@@
 \noindent\textbf{Gabor filter}: A 2D Gabor filter is a Gaussian kernel function
-modulated by a sinusoidal plane wave. It is used to find high gradient patches from the
-image. In our case, it will detect blur invariant sections of the fiducials. We
-have applied Gabor filter for eight different orientations ($\theta = 0, 45,
-90, 135, 180, 225, 270, 315$). We have used following parameters for
-creating each Gabor kernel: $\lambda = 8$, $\gamma = 0.5$, $\sigma =
-0.56\lambda$, $\psi = 0 \text{(for real part)}, \pi/2 \text{(for imaginary
-part)}$.
+modulated by a sinusoidal plane wave~\cite{Kruizinga:2002}. It is used to find
+high gradient patches from the image. In our case, it is used to detect blur
+invariant sections of the fiducials. We have applied Gabor filter for eight
+different orientations ($\theta = 0, 45, 90, \ldots ,225, 270, 315$).  The
+following parameters where used for creating each Gabor kernel: $\lambda$ (wavelength) $= 8$, $\gamma$
+(aspect ratio) $= 0.5$, $\sigma$ (spread) $= 0.56\lambda$, $\psi$
+(phase angle) $= 0$ (for real part), $\pi/2$ (for imaginary part).
 Then L2 norm of outputs along all orientations is calculated and finally L2
-normed image is binarized.
+normalized image is thresholded with threshold set to $0.4$ (on scale of zero to
+one).
 
-\noindent\textbf{Clustering}: Connected components are found from the Gabor
-output.
-These connected components are then clustered in hierarchical fashion, to find
-the group of closely positioned patches.
+\noindent\textbf{Clustering}: The binarized Gabor filter response are
+treated as a set of connected components in the image.   This clustering
+stage is to find components that are located in a close spatial region.  We do
+this by using hierarchical fashion clustering~\cite{ALGLIB}. We used unweighted
+average linkage with distance threshold set to 150 for merging clusters in
+hierarchical fashion.
 
-\noindent\textbf{PCA}: Principal Component Analysis is done on the clustered
-Gabor output. Along first principal component, intensity profile in the original image
-is found. Number of transitions in the intensity profile will give us the
-number of rings.
+\noindent\textbf{PCA}: For each clustered set of components, we apply 
+PCA to determine the dominate direction.  This is done by examining the
+orientation of the first principal component.  We then extract an intensity
+profile patch in the input image along this direction as it extends through the
+bounding box of the cluster. The signature of this profile will be used to
+identify the code.
 
-\noindent\textbf{Classification}: Each synthetic fiducial pattern is blurred
-along 36 orientations (0, 10, 20, \ldots , 350) and intensity profile along first
-principal component from every output is taken as training data for that
-fiducial pattern. Process of creation of training data for fiducial with
-code ``01'' is depicted in Figure \ref{fig:training_data}. Test pattern is matched
-against training data using K-Nearest Neighbor Classifier (K=5) to output class label.
+\noindent\textbf{Classification}: As mentioned above, a small image patch containing
+the intensity profile of the fiducial is used to identify the code.   We found
+that a training-based method using KNN gave better results than trying to directly determine
+the number of transitions in the image patch.  To build the training-data, a
+synthetic fiducial pattern is blurred along 36 orientations (0, 10, 20, \ldots
+, 350) and its intensity profile along the first principal component from every
+output is taken as training data for that fiducial pattern. Figure
+\ref{fig:training_data} shows the process of creating this training data for
+``01'' fiducial with.  For an input image patch, we normalize its intensity
+range and then compare it against the training-data. The class label from the
+closest top $K=5$ images in the training-data is used to label the patch.
 
@@
   \caption{Process to create training data for the fiducial pattern with binary
-  code ``01''. Synthetic pattern is blurred along various orientations. Gabor
+  code ``01''. The synthetic pattern is blurred along various orientations. Gabor
   filter is applied on the blurred pattern. Intensity profile is found along the
@@
 
-To increase classification accuracy, training data for patterns having same
+To increase the classification accuracy, training data for patterns having same
 number of rings is grouped together; e.g., in two bit binary coded fiducial,
 training data for pattern ``01'' and ``10'' will be grouped together, In three
-bit binary coded fiducial, training data for pattern “001”, “010” and “100” will
-form one group while training data for pattern “110”, “011” and “101” will be
-in other group, etc. Now, Depending on the number of detected rings in test
-pattern, it is matched against corresponding group of training data, again
+bit binary coded fiducial, training data for pattern ``001'', ``010'' and
+``100'' will form one group while training data for pattern ``110'', ``011'' and
+``101'' will be in other group, etc. Now, depending on the number of detected
+rings in test pattern, it is matched against corresponding group of training data, again
 using  K-Nearest Neighbor Classifier. In this way, if we detect either zero
@@
 Experiments were performed on a PC with Intel Core i7 processor(@3.4GHz) and 4GB RAM.
-Source code and data sets in this paper will be made publicly available.
+Source code and data sets in this paper will be made publicly available.  Video clips
+have also been provided in the supplemental materials.
 
-Our system has been tested several image sequences captured from AR Drone
-quadcopter. Each image sequence contains frames containing different fiducial
-pattern. Sample output for each fiducial pattern is shown in Figure
+Our system has been tested on several image sequences captured from an AR Drone
+quadcopter.  The Drone was flown indoors looking at patterns attached to various walls.
+Each image sequence contains frames containing different fiducial
+patterns. Sample output for each fiducial pattern is shown in Figure
 \ref{fig:output0} -- Figure \ref{fig:output3}. Our detection process takes
-around 0.3 seconds and can handle three to four frames per second.
+around 0.3 seconds which translates to around three to four frames per second.
 
-\begin{figure}[hb!]
+Our system has also been tested on images containing multiple fiducial patterns
+in the same frame. Our algorithm successfully detected all fiducial patterns as
+well as correctly classified them as shown in Figure \ref{fig:output_all}.
+
+\begin{figure}
+\centering
+  \includegraphics[width=.45\linewidth]{output_all_2.jpg}
+  \includegraphics[width=.45\linewidth]{new_results/output_test_all1.jpg}
+  \caption{Sample outputs containing all two bit binary coded fiducial patterns
+  in single frame}
+  \label{fig:output_all}
+\end{figure}
+
+\subsection{Comparisons}
+
+We compare our results with the commonly used ARTag. We also compare 
+our results with Blur-driven tracker (BLUT)\cite{Wu:2011}.
+\subsubsection{Comparison with ARTag}
+First, we have repeated blur simulation experiment on our fiducials as reported
+in Section~\ref{sec:blurtest}.  Specifically, we build our blur resistant
+patterns size 150x150 and blurred them along various orientations with different
+blur scales. Then, we tried to detect our fiducial using a 2-bit patterns using
+algorithm presented in earlier section.
+
+\begin{figure}
+\includegraphics[width=\linewidth]{blur_maximum.pdf}
+\caption{Result of our fiducial detection algorithm on blur simulated data}
+\label{fig:blur_maximum}
+\end{figure}
+
+The comparison of recognition rate is shown in Figure
+\ref{fig:recognition_rate}. In this experiment, we use even more blur, up to 65
+pixels.  The graph shows in Figure \ref{fig:recognition_rate} that our
+recognition to 100\% for all codes except the ``00'' which has is undetectable
+after 50 pixels blur (which is still significantly better than ARTag).  Reasons
+for the ``00'' tags lower performance is discussed in Section~\ref{sec:discussion}.
+
+We have also checked the difference between the actual center of the fiducial
+and center found by our algorithm, on blur simulated data along different blur
+orientations. From Table \ref{tab:blur_angle_center}, it can be clearly seen
+that the difference between the actual center and center found by algorithm is
+less than three percent of the diameter of fiducial.
+
+\noindent\begin{minipage}{\linewidth}
+\noindent\begin{minipage}{0.67\linewidth}
+\includegraphics[width=\linewidth]{recognition_rate.png}
+\captionof{figure}{Comparison of recognition rate of AR Tag and our fiducials on
+blur simulated data at various blur scales. It can be clearly seen that except
+fiducial with binary code ``00'', our fiducial patterns are
+recognised all times.}
+\label{fig:recognition_rate}
+\end{minipage}
+\noindent\begin{minipage}{0.32\linewidth}
+\begin{tabularx}{\textwidth}{|c|Y|Y|}
+\cline{1-3}
+\small{Blur} & \small{Actual} & \small{Found} \\
+\small{Angle} & \small{center} & \small{center} \\
+\cline{1-3}
+0 & (55,75) & (54,75) \\
+22 & (56,67) & (55,64) \\
+45 & (61,61) & (59,62) \\
+67 & (67,56) & (63,56) \\
+90 & (75,55) & (75,53) \\  \cline{1-3}
+\end{tabularx}
+\captionof{table}{Table showing the actual center of our fiducial and center
+found by our algorithm, when blurred along various blur angles (Blur Scale =
+40).}
+\label{tab:blur_angle_center}
+\end{minipage}
+\end{minipage}
+
+We also compared results on the recorded feed using AR Drone quadcopter. In our
+experimental setup, we have placed two AR Tags in the scene along with our fiducial  to
+compare the resilience of blur by each fiducial type. We have used
+ar\_track\_alvar, ROS Wrapper for ALVAR library \cite{ros_alvar}, to detect AR
+Tags from the stream captured through quadcopter. In each test dataset, we used
+different two bit binary coded fiducial and recorded video of around two minute
+duration (i.e., around 1000 frames).   The quadcopter was flown in a routine
+manner about the room with its camera facing the wall (see supplemental
+videos). The comparison of recognition rate is shown in Table
+\ref{tab:recongition_accuracy}. Classification accuracy of all fiducials (ARTag
+as well as ours) ranges from 86.5\% to 94.1\%, while the AR Tag is 60.3\% to 65.6\%.
+\begin{figure}
 \begin{subfigure}{\textwidth}
@@
 
-Our system has also been tested on images containing multiple fiducial patterns
-in the same frame. Our algorithm successfully detected all fiducial patterns as
-well as correctly classified them as shown in Figure \ref{fig:output_all}.
-
-\begin{figure}
-\centering
-  \includegraphics[width=.45\linewidth]{output_all_2.jpg}
-  \includegraphics[width=.45\linewidth]{new_results/output_test_all1.jpg}
-  \caption{Sample outputs containing all two bit binary coded fiducial patterns
-  in single frame}
-  \label{fig:output_all}
-\end{figure}
-
-\subsection{Comparison}
-We will compare our results with standard fiducials such as ARTag. Also, we will
-compare our results with Blur driven tracker(BLUT)\cite{Wu:2011}.
-\subsubsection{Comparison with ARTag:}
-First, we have repeated blur simulation experiment on our fiducials too, i.e.,
-we have downsized our fiducial to size 150x150 and blurred it along various
-orientations with different blur scales. Then, we tried to detect the patterns
-using algorithm presented in earlier section. The comparison of recognition
-rate is shown in Figure \ref{fig:recognition_rate}.
-
-\begin{figure}[h!]
-\centering
-\includegraphics[width=\linewidth]{recognition_rate.png}
-\caption{Comparison of recognition rate of AR Tag and our fiducials on
-blur simulated data at various blur scales. It can be clearly seen that except
-fiducial with binary code ``00'', our fiducial patterns are
-recognised all times.}
-\label{fig:recognition_rate}
-\end{figure}
-
-Later, we recorded the real data using AR Drone quadcopter. In our experimental
-setup, we have kept our fiducial along with two AR Tags, to compare the
-resilience of blur by each fiducial type. We have used ar\_track\_alvar, ROS
-Wrapper for ALVAR library \cite{ros_alvar}, to detect AR Tags from the stream
-captured through quadcopter. In each test dataset, we used different two bit
-binary coded fiducial and recorded video of around two minute duration (i.e.,
-around 1000 frames) The comparison of recognition rate is shown in Table
-\ref{tab:recongition_accuracy}. Classification accuracy of all fiducials (ARTag
-as well as ours) is almost 100\%.
-
 \begin{table}[h!]
@@
 
-We have used four image sequences (consisting of around 1000 frames each) , each
-one containing our different fiducial pattern, to test the performance of
+We also compare out approach with tracking designed for blurred input scenes. 
+We have used four image sequences (consisting of around 1000 frames each), each
+one containing a different blur resistent fiducial pattern to test the performance of
 BLUT\cite{Wu:2011} and compare it with our result on the same image sequence.
-From top rows of Figure \ref{fig:BLUT_compare_00}-\ref{fig:BLUT_compare_11}, it
-can be inferred that BLUT is able to track the fiducial when the position of
+From top rows of Figure \ref{fig:BLUT_compare_00}-\ref{fig:BLUT_compare_11}. From
+the images we can see that BLUT is able to track the fiducial when the position of
 fiducial does not change too much in successive frames. Also, it can be seen
-that, once BLUT looses the track of the fiducial, it is not able to recover
-from that. But, our algorithm is able to track the fiducial irrespective of the
-change in the position of the fiducial in the image as shown in bottom rows of Figure
+that, once BLUT looses the track of the fiducial, it is not able to recover. 
+Since our approach detects the code at each frame, large changes in the patterns
+position is not an issue.   Our detection results are also shown in Figure
 \ref{fig:BLUT_compare_00}-\ref{fig:BLUT_compare_11}.
@@
 We have also found that, even if we reset the BLUT tracker after loosing track,
-it looses track again after around 100 frames i.e., approximately 6 seconds.
-When we checked the timestamp data from image header captured through AR Drone,
-we found that, there was difference of 0.14 seconds between two successive
-frames in the earlier case, which clearly suggests the dropping of frame. Also,
-there were around 50 instances in 1000 frames where timestamp difference between two
-successive frames was greater than 0.1 seconds. So, it is evident that
-due to dropping of frames combined with unstable motion of quadcopter, tracking
-through quadcopter using conventional tracking methods is not accurate.
+it will loose track again after around 100 frames i.e., approximately within 6
+seconds. When we checked the timestamp data from image header captured through
+AR Drone, we found that, there was difference of 0.14 seconds between two
+successive frames in the earlier case, which clearly suggests the dropping of
+frame (e.g., normal 30fps should be 0.33 seconds). Also,  there were around 50
+instances in 1000 frames where timestamp difference between two successive
+frames was greater than 0.1 seconds. As such, it appears one of the main
+culprits causing the BLUT tracker to fail is the dropping of frames combined
+with unstable motion of quadcopter resulting in large discrepancies in the
+patterns position between successive frames.
 
@@
 \caption{Top: Output of BLUT\cite{Wu:2011} on sample image sequence containing ``00''
-binary coded fiducial, Bottom: Output of our algorithm on the same image
+binary coded fiducial. Bottom: Output of our algorithm on the same image
 sequence. BLUT is able to track the fiducial till third frame, but from fourth
@@
 
-\section{Discussion}
+\section{Discussion}\label{sec:discussion}
+
+We have demonstrated the effectiveness of our blur invariant fiducial both
+synthetically and on real video clips captured from a quadcopter.   Our approach obtains
+approximately 86-95\% recognition rate on fiducals in real scenes compared to existing codes
+that are around 64\%.  We discuss some limitations of our approach in the following.
 
 \noindent\textbf{Processing Time:}~~Currently our processing time (0.3 seconds
-per frame) makes it difficult to do the fiducial detection in real-time. When we have
-done the code profiling, we found that Gabor filter takes most of the time (0.03
+per frame) makes it difficult to do the fiducial detection in real-time.  As such, we currently
+envision this will be used in an offline manner for performing analysis of flight paths.
+Code profiling revealed that the Gabor filtering takes most of the time (0.03
 -- 0.04 seconds per orientation). As we are applying Gabor filter along eight
@@
 algorithm fails to recognize our fiducial with binary code ``00'' when there is
-large amount of blur. This is the reason behind lower recognition rate of ``00''
-coded fiducial compared to that of our other fiducial patterns. When we
-investigated the problem, we found that, if there is too much blur, in Gabor
-output, the innermost ring is unable to give any response along the direction
-perpendicular to blur direction. This problem can be resolved by increasing
-radius of innermost ring, reducing effect of blur on the innermost ring.
+large amount of blur.  When we
+investigated the problem, we found that if there is too much blur the Gabor
+output the innermost ring response it too low and not detected properly.  
+This problem can be resolved by increasing radius of innermost ring to 
+reduce the effect of blur on the innermost ring.
 
-\noindent\textbf{Pose Estimation:}~~Currently, we are not finding the pose from
-the fiducial marker. But, if we put multiple markers (at least four) in the same
-scene, we may be able to find the pose. The current resolution of onboard camera
-will be main hurdle to clear before we can effectively use multiple markers in
-each scene.
+\noindent\textbf{Pose Estimation:}~~We note that other markers are able to give
+full pose estimation after detection.  However, we are only able to reliably detect
+the center point and therefore cannot estimate pose.  Of course, if four
+markers were used in a known order pose could be estimated. The current
+resolution of onboard camera will be main hurdle to clear before we can
+effectively use multiple markers in each scene.
 
@@
 
-\section{Conclusion and Future Work}
+\section{Conclusion}
+
 Quadcopters are subject to quick and unstable motions that can cause significant
@@
 through experimental validation that our fiducial will work under significant
-amount of motion blur. When compared to popular fiducials, our fiducial can
-withstand around twice the amount of blur.  Though, currently we are not able to
-find the pose using single pattern, we may be able to overcome this
-shortcoming by using multiple markers in single scene. Also, through faster
-implementation of Gabor filter, the fiducial detection can be done in realtime.
+amount of motion blur and can significantly out perform existing fiducial
+markers under this scenario.
 

### 2014-03-07 ECCV/paper.tex
Added new figures (with center), proof reading.

@@
 \setlength{\floatsep}{7pt plus 2pt minus 2pt}
-\setlength{\textfloatsep}{7pt plus 2pt minus 2pt}
+\setlength{\textfloatsep}{5pt plus 2pt minus 2pt}
 \setlength{\intextsep}{7pt plus 2pt minus 2pt}
@@
 
-The recent availability of low-cost quadcopters has help to fuel significant efforts in
-research focused on unmanned aerial vehicles.  Navigation and planning of
+The recent availability of low-cost quadcopters has helped to fuel significant
+efforts in research focused on unmanned aerial vehicles.  Navigation and planning of
 these vehicles is typically performed using onboard inertial sensors and/or
-vision based modules that uses visual cues in the real world~(e.g.
+vision based modules that uses visual cues in the real world~(e.g., 
 \cite{Davison:2007,Engel12,Engel13}). However, to evaluate the effectiveness of
@@
 (\cite{NaimarkF02,Pitag13,runetag11}).
-Figure \ref{fig:teaser}-(a) show the popular ARTag\cite{Fiala05} as
+Figure \ref{fig:teaser}-(a) shows the popular ARTag\cite{Fiala05} as
 seen from a quadcopter.  A problem for existing fiducials is that low-cost quadcopters
@@
 the quadcopter's wireless communication module.   This means that not only is blurring
-introduced, but there may be large discontinuities in the patterns position due
+introduced, but there may be large discontinuities in the pattern's position due
 to missing video frames.  As we will show in Section 4, this later problem
@@
 \begin{figure}
+\centering
  \begin{subfigure}[b]{0.19\textwidth}
   \centering
-  \includegraphics[width=\linewidth]{intersense.jpg}
-  Intersense\cite{NaimarkF02}
- \end{subfigure}
+  \includegraphics[width=0.8\linewidth]{intersense.jpg}
+  Circular Data Matrix\cite{NaimarkF02}
+ \end{subfigure}\quad
  \begin{subfigure}[b]{0.14\textwidth}
@@
   ARToolkit\cite{ARToolkit02}
- \end{subfigure}
+ \end{subfigure}\quad
  \begin{subfigure}[b]{0.14\textwidth}
@@
   \includegraphics[width=\linewidth]{ARtag.jpg}
-  ARTag\cite{Fiala05}
- \end{subfigure}
+  AR Tag\quad\cite{Fiala05}
+ \end{subfigure}\quad
  \begin{subfigure}[b]{0.14\textwidth}
@@
   \includegraphics[width=\linewidth]{pifiducial.jpg}
-  Pi-Tag\cite{Pitag13}
- \end{subfigure}
+  Pi-Tag\quad\cite{Pitag13}
+ \end{subfigure}\quad
  \begin{subfigure}[b]{0.14\textwidth}
@@
  \caption{This figure shows the design of several existing fiducial markers.  While
- each codes have their own pros and cons of various environments, none are designed to be recognized under motion blur.}
+ each code has their own pros and cons of various environments, none are
+ designed to be recognized under motion blur.}
  \label{fig:previous_work}
@@
 examples of existing fiducial markers.  Many designs use a two dimensional
-barcode inside a rectangular grid. One examples of such a fiducial is from the 
+barcode inside a rectangular grid. One example of such a fiducial is from the 
 ARToolkit~\cite{ARToolkit02}, a well known toolkit used in many augmented reality (AR) applications. Kato et al.\cite{kato-artoolkit} demonstrated the use of ARToolkit
@@
 There were also attempts to use circular patterns instead of rectangular. 
-The use of concentric rings was used  by Gatrell et al.\cite{concentric}
+The use of concentric rings was done  by Gatrell et al.\cite{concentric}
 for monocular pose estimation as well as object identification in space. Cho et al.
@@
 Naimark et al.~\cite{NaimarkF02} proposed a circular bar code
-called the, Circular Data Matrix that is beneficial in terms of
+called, the Circular Data Matrix that is beneficial in terms of
 easy detection and ability to have a large number
@@
 Bergamasco et al. \cite{runetag11} proposed the RUNE-tag fiducial divided into number of
-circular dots arranged them in circular fashion.
+circular dots arranged in circular fashion.
 RUNE-tags can be detected even when up to 50\% of fiducial area is occluded.
-Bergamasco et al.~\cite{Pitag13} proposed the Pi-Tag fiducial also composed 
-of circular structures but arranged in a rectangle to exploit projective invariant cross-ration.
+Bergamasco et al.~\cite{Pitag13} proposed the Pi-Tag fiducial, also composed 
+of circular structures but arranged in a rectangle to exploit projective invariant cross-ratio.
 This provided similar occlusion resistance as RUNE-tag but with even less
-circular dots. All of these techniques however relies on generic features
+circular dots. All of these techniques however rely on generic features
 (e.g., circle detection) that break down under motion blur.
@@
 \cite{Fiala05} and PiTags\cite{Pitag13} given their difference in geometry design.
+We didn't find source code as well as samples for RUNE-tag\cite{runetag11}
+online. Also, for Circular data matrix\cite{NaimarkF02}, the software should be
+used with their proprietary hardware. So, we couldn't examine these fiducials.
 
@@
 Figure~\ref{fig:artag_pitag} shows the recognition rate (in percentage) of two
-fiducial markers at various blur scales over all the different orientation.  
+fiducial markers at various blur scales over all the different orientations.  
 As we can see, the PiTag performance quickly diminished under small amounts of
-blur, however, at 35 motion blur, ARTag is recognition rate drops to less than 20\%.
+blur, however, at 35 motion blur, ARTag's recognition rate drops to less than
+20\%.
 
@@
 \captionof{figure}{Figure showing ARTag and Pi-tag blurred with various blur
-scales at different orientation. Table on the right shows the recognition rate
+scales at different orientations. Table on the right shows the recognition rate
 (in percent) of both fiducial markers at various blur scales along all blur
@@
 Figure \ref{fig:overall_flow} shows the process involved in fiducial
-detection process. We give a brief overview of our algorithm here and details
+detection. We give a brief overview of our algorithm here and details
 to each step in the following.  Our detection algorithm has four steps. Step 1,
@@
 found in Gabor output using spatial clustering.  Step 3, performs Principal
-Component Analysis (PCA) on each cluster to find the dominate direction
+Component Analysis (PCA) on each cluster to find the dominant direction
 unaffected by blur.  Step 4, based on the direction we extract the intensity
@@
 different orientations ($\theta = 0, 45, 90, \ldots ,225, 270, 315$).  The
-following parameters where used for creating each Gabor kernel: $\lambda$ (wavelength) $= 8$, $\gamma$
+following parameters were used for creating each Gabor kernel: $\lambda$ (wavelength) $= 8$, $\gamma$
 (aspect ratio) $= 0.5$, $\sigma$ (spread) $= 0.56\lambda$, $\psi$
@@
 the intensity profile of the fiducial is used to identify the code.   We found
-that a training-based method using KNN gave better results than trying to directly determine
-the number of transitions in the image patch.  To build the training-data, a
-synthetic fiducial pattern is blurred along 36 orientations (0, 10, 20, \ldots
-, 350) and its intensity profile along the first principal component from every
-output is taken as training data for that fiducial pattern. Figure
-\ref{fig:training_data} shows the process of creating this training data for
-``01'' fiducial with.  For an input image patch, we normalize its intensity
-range and then compare it against the training-data. The class label from the
-closest top $K=5$ images in the training-data is used to label the patch.
+that a training-based method using KNN gave better results than trying to
+find binary code directly by determining the presence (or absence) of ring
+ at particular positions in the image patch. To build
+ the training-data, a synthetic fiducial pattern is blurred along 36 orientations (0, 10, 20, \ldots , 350) with blur scale set to 40, and its intensity profile along the first principal component from every output is
+taken as training data for that fiducial pattern. Figure
+\ref{fig:training_data} shows the process of creating training data for
+fiducial with binary code ``01'' embedded in it.  For an input image patch, we
+normalize its intensity range and then compare it against the training-data.
+The class label from the closest top $K=5$ images in the training-data is used
+to label the patch.
 
@@
 
-To increase the classification accuracy, training data for patterns having same
-number of rings is grouped together; e.g., in two bit binary coded fiducial,
-training data for pattern ``01'' and ``10'' will be grouped together, In three
-bit binary coded fiducial, training data for pattern ``001'', ``010'' and
-``100'' will form one group while training data for pattern ``110'', ``011'' and
-``101'' will be in other group, etc. Now, depending on the number of detected
-rings in test pattern, it is matched against corresponding group of training data, again
-using  K-Nearest Neighbor Classifier. In this way, if we detect either zero
-rings or maximum possible rings in the test pattern, there will be no need to do
-further classification.
+We are able to find the number of rings in the fiducial by finding transitions
+in the intensity profile. To increase the classification accuracy, training data
+for patterns having same number of rings is grouped together; e.g., in two bit
+binary coded fiducial, training data for pattern ``01'' and ``10'' will be
+grouped together, In three bit binary coded fiducial, training data for pattern
+``001'', ``010'' and ``100'' will form one group while training data for
+pattern ``110'', ``011'' and ``101'' will be in other group, etc. Now,
+depending on the number of detected rings in test pattern, it is matched
+against corresponding group of training data, again using  K-Nearest Neighbor
+Classifier. In this way, if we detect either zero rings or maximum possible
+rings in the test pattern, there will be no need to do further classification.
 
@@
 Our system has been tested on several image sequences captured from an AR Drone
-quadcopter.  The Drone was flown indoors looking at patterns attached to various walls.
-Each image sequence contains frames containing different fiducial
+quadcopter.  The Drone was flown indoors looking at patterns attached to
+various walls. Each image sequence contains frames containing different fiducial
 patterns. Sample output for each fiducial pattern is shown in Figure
@@
 
-\begin{figure}
+\begin{figure}[ht!]
 \centering
@@
 
-\begin{figure}
-\includegraphics[width=\linewidth]{blur_maximum.pdf}
-\caption{Result of our fiducial detection algorithm on blur simulated data}
-\label{fig:blur_maximum}
-\end{figure}
-
 The comparison of recognition rate is shown in Figure
@@
 pixels.  The graph shows in Figure \ref{fig:recognition_rate} that our
-recognition to 100\% for all codes except the ``00'' which has is undetectable
+recognition is 100\% for all codes except the ``00'' which is undetectable
 after 50 pixels blur (which is still significantly better than ARTag).  Reasons
@@
 less than three percent of the diameter of fiducial.
+
+\begin{figure}
+\includegraphics[width=\linewidth]{blur_maximum.pdf}
+\caption{Result of our fiducial detection algorithm on blur simulated data.
+Detection result is shown on each of our fiducial pattern, blurred at the
+maximum scale it can handle.}
+\label{fig:blur_maximum}
+\end{figure}
 
@@
 duration (i.e., around 1000 frames).   The quadcopter was flown in a routine
-manner about the room with its camera facing the wall (see supplemental
+manner in the room with its camera facing the wall (see supplemental
 videos). The comparison of recognition rate is shown in Table
-\ref{tab:recongition_accuracy}. Classification accuracy of all fiducials (ARTag
-as well as ours) ranges from 86.5\% to 94.1\%, while the AR Tag is 60.3\% to 65.6\%.
-\begin{figure}
+\ref{tab:recongition_accuracy}. Recognition rate of our fiducials ranges from
+86.5\% to 94.1\%, while the AR Tag is 60.3\% to 65.6\%. Classification
+accuracy of all fiducials (ARTag as well as ours) was approximately 100\%.
+
+\begin{figure}[hb!]
 \begin{subfigure}{\textwidth}
@@
 We have used four image sequences (consisting of around 1000 frames each), each
-one containing a different blur resistent fiducial pattern to test the performance of
+one containing a different blur resistant fiducial pattern to test the performance of
 BLUT\cite{Wu:2011} and compare it with our result on the same image sequence.
-From top rows of Figure \ref{fig:BLUT_compare_00}-\ref{fig:BLUT_compare_11}. From
-the images we can see that BLUT is able to track the fiducial when the position of
-fiducial does not change too much in successive frames. Also, it can be seen
-that, once BLUT looses the track of the fiducial, it is not able to recover. 
+From the images in top rows of Figure
+\ref{fig:BLUT_compare_00}-\ref{fig:BLUT_compare_11}, we can see that BLUT is able to track the fiducial when the position of fiducial does not change too much in successive frames.
+Also, it can be seen that, once BLUT looses the track of the fiducial, it is not able to recover.
 Since our approach detects the code at each frame, large changes in the patterns
@@
 large amount of blur.  When we
-investigated the problem, we found that if there is too much blur the Gabor
-output the innermost ring response it too low and not detected properly.  
+investigated the problem, we found that if there is too much blur, the innermost
+ring's response in the Gabor output is too low and not detected properly.  
 This problem can be resolved by increasing radius of innermost ring to 
@@
 the center point and therefore cannot estimate pose.  Of course, if four
-markers were used in a known order pose could be estimated. The current
+markers were used in a known order, pose could be estimated. The current
 resolution of onboard camera will be main hurdle to clear before we can
@@
 existing fiducial markers. We proposed the design of a fiducial that is robust
-to motion blur. Our design of contrasting concentric rings is based on the the
+to motion blur. Our design of contrasting concentric rings is based on the 
 observation that the direction perpendicular to the motion blur direction will
@@
 through experimental validation that our fiducial will work under significant
-amount of motion blur and can significantly out perform existing fiducial
+amount of motion blur and can significantly outperform existing fiducial
 markers under this scenario.

### 2014-03-07 ECCV/paper.tex
Final Version

@@
 in environments to provide a uniquely identifiable object in the scene.
-For quadcopter applications, fiducials are
-often used for evaluating planning algorithms by allowing ground truth
-positions in the scene to be detected from the quadcopter's camera. Quadcopters,
-however, are subject to quick and unstable motions that can cause significant motion
-blur that severely affects the detection rate of existing fiducial markers.
-This problem motivated us to design a fiducial that is robust to motion blur.
-Our proposed fiducial design uses concentric circles with the observation that
-the direction perpendicular to the motion blur direction will be unaffected by
-the blur.  This allows the fiducial code along the blur direction to be recognized.
+For quadcopter applications, fiducials are often used for evaluating planning
+algorithms by allowing ground truth positions in the scene to be detected from
+the quadcopter's camera. Quadcopters, however, are subject to quick and
+unstable motions that can cause significant motion blur that severely affects
+the detection rate of existing fiducial markers. This problem motivated us to
+design a fiducial that is robust to motion blur. Our proposed fiducial design
+uses concentric circles with the observation that the direction perpendicular
+to the motion blur direction will be relatively unaffected by the blur. This
+allows the fiducial code along the blur direction to be recognized.
 The circular design allows this to work for all motion blur directions. We
@@
 
-The recent availability of low-cost quadcopters has helped to fuel significant
+The recent availability of low-cost quadcopters have helped to fuel significant
 efforts in research focused on unmanned aerial vehicles. Navigation and planning of
@@
 vision based modules that uses visual cues in the real world~(e.g.,
-\cite{Davison:2007,Engel12,Engel13}). However, to evaluate the effectiveness of
-navigation methods, fiducial markers are commonly placed into the environment
-to provide additional information that serves for ground-truth
-positional measurements (e.g.,\cite{Bosnak:2012,Lim09,Klopschitz:2007}).
+\cite{Davison:2007,Engel12,Engel13}).
+However, to evaluate the effectiveness of navigation methods, fiducial markers are commonly placed into the environment to provide additional information that serves for ground-truth
+positional measurements (e.g., \cite{Bosnak:2012,Lim09,Klopschitz:2007}).
 
@@
 (\cite{NaimarkF02,Pitag13,runetag11}).
-Figure \ref{fig:teaser}-(a) shows the popular ARTag\cite{Fiala05} as
+Figure \ref{fig:teaser}-(a) shows the popular ARTag \cite{Fiala05} as
 seen from a quadcopter. A problem for existing fiducials is that low-cost quadcopters
 often exhibit very quick and erratic physical movements that
-results in motion blur in the quadcopter's onboard camera.  This motion blur has
+result in motion blur in the quadcopter's onboard camera. This motion blur has
 an adverse effect on the recognition of fiducial markers. This can be seen in
 Figure \ref{fig:teaser}-(b) where the ARTag cannot be recognized due to motion
-blur. This is not too surprising as most  existing fiducials are not explicitly
+blur. This is not too surprising as most existing fiducials are not
 designed to handle motion blur.
@@
 Compounding this problem is the additional issue of dropped video frames from
-the quadcopter's wireless communication module.   This means that not only is blurring
-introduced, but there may be large discontinuities in the pattern's position due
-to missing video frames.  As we will show in Section 4, this later problem
+the quadcopter's wireless communication module. This means that not only is
+blur a problem, but there may be large discontinuities in the pattern's
+position due to missing video frames. As we will show in Section 4, this later problem
 makes it challenging to apply tracking algorithms that can exploit temporal
-coherence for determining the fiducial positions.
+coherence for determining the fiducial's position.
 
-\noindent\textbf{Contribution:}~~To address these problems, we propose a
-fiducial that is designed to be robust to motion blur.  Our design is based on
+\noindent\textbf{Contribution}~~To address these problems, we propose a
+fiducial that is designed to be resistant to motion blur. Our design is based on
 concentric circles as shown in Figure \ref{fig:teaser}-(c,d). The design is based
@@
 assign a code to the marker. Our experiments show that this design can
-significantly outperform existing codes in the face of motion blur. As far as
-we are aware, this is the first work to propose a blur resistant marker.
+significantly outperform existing codes in the presence of motion blur. As far
+as we are aware, this is the first work to propose a blur resistant marker.
 
@@
 overview of related work related to fiducials as well as the related problem of
-tracking.  Section 3 discusses the our design and detection algorithm as well as 
-examining the performance of existing codes under motion blur. Section 4 shows several
+tracking. Section 3 discusses our design and detection algorithm as well as
+the performance of existing codes under motion blur. Section 4 shows several
 experiments using quadcopter imagery. This is followed by a discussion and
@@
 \includegraphics[width=\linewidth]{teaser.pdf}
-\caption{This figure shows experimental setup and comparison of
-output of ALVAR\cite{alvar} (for detecting ARTag) versus our blur resistant fiducial
-in a normal and blurred scene. The scene contains two ARTags and our code.
+\caption{This figure shows the experimental setup and comparison of
+output of ALVAR~\cite{alvar} (for detecting ARTag) versus our blur resistant
+fiducial in a normal and blurred video frame. The scene contains two ARTags and our code.
 (a) shows that the ARTag can be detected when the image has no blur.
@@
   \includegraphics[width=0.8\linewidth]{intersense.jpg}
-  Circular Data Matrix\cite{NaimarkF02}
+  Circular Data Matrix~\cite{NaimarkF02}
  \end{subfigure}\quad
@@
   \includegraphics[width=\linewidth]{pattKanji.pdf}
-  ARToolkit\cite{ARToolkit02}
+  ARToolkit~\cite{ARToolkit02}
  \end{subfigure}\quad
@@
   \includegraphics[width=\linewidth]{ARtag.jpg}
-  AR Tag\quad\cite{Fiala05}
+  ARTag\quad~\cite{Fiala05}
  \end{subfigure}\quad
@@
   \includegraphics[width=\linewidth]{pifiducial.jpg}
-  Pi-Tag\quad\cite{Pitag13}
+  PiTag\quad~\cite{Pitag13}
  \end{subfigure}\quad
@@
  \caption{This figure shows the design of several existing fiducial markers.  While
- each code has their own pros and cons of various environments, none are
+ each code has their own pros and cons for various environments, none are
  designed to be recognized under motion blur.}
@@
 
-\noindent{\textbf{Fiducials:}}~Figure~\ref{fig:previous_work} shows several
+\noindent{\textbf{Fiducials}}~Figure~\ref{fig:previous_work} shows several
 examples of existing fiducial markers.  Many designs use a two dimensional
 barcode inside a rectangular grid. One example of such a fiducial is from the
-ARToolkit~\cite{ARToolkit02}, a well known toolkit used in many augmented reality (AR) applications. Kato et al.\cite{kato-artoolkit} demonstrated the use of ARToolkit
-to find the pose in video based AR conferencing system.
+ARToolkit~\cite{ARToolkit02}, a well known toolkit used in many augmented
+reality (AR) applications. Kato and Billinghurst~\cite{kato-artoolkit}
+demonstrated the use of ARToolkit to find the pose in video based AR
+conferencing system.
 
-Fiala et al. \cite{Fiala05} proposed a fiducial termed, ARTag, which is a
-bi-tonal system consisting of a square border and an interior 6$\times$6 grid of black or white cells. The improvement in ARTag compared to
-ARToolkit was detection of corners instead of detection of lines to find
-possible pattern. This proved to be more efficient than \cite{ARToolkit02} in
-terms of marker recognition rate as well as the number of different patterns
-which can be created.   The reliance on both line and corner detection hampers recognition under motion blur.
+Fiala~\cite{Fiala05} proposed a fiducial termed, ARTag, which is a
+bi-tonal system consisting of a square border and an interior 6$\times$6 grid
+of black or white cells. The improvement in ARTag compared to ARToolkit was
+detection of corners instead of detection of lines to find possible pattern.
+This proved to be more efficient than \cite{ARToolkit02} in terms of
+recognition rate as well as the number of different patterns which can be
+created.   The reliance on both line and corner detection hampers recognition
+under motion blur.
 
 There were also attempts to use circular patterns instead of rectangular.
-The use of concentric rings was done  by Gatrell et al.\cite{concentric}
-for monocular pose estimation as well as object identification in space. Cho et al.
-\cite{Cho:2001,Cho97fastcolor} have used multicolor rings instead of
-black and white rings\cite{concentric} to increase possible number of fiducials.
+Gatrell et al.~\cite{concentric} used concentric circles
+for monocular pose estimation as well as object identification. Cho et al.
+\cite{Cho:2001,Cho97fastcolor} have used multicolor rings instead of black and white rings~\cite{concentric} to increase possible number of fiducials.
 These multicolor rings are used in wide area tracking in large scale
-applications.  While based on a concentric rings, these particular approaches require 
+applications.  While based on a concentric rings, these approaches require
 the full ring to be recognized which is not possible when the pattern undergoes directional
@@
 
-Naimark et al.~\cite{NaimarkF02} proposed a circular bar code
-called, the Circular Data Matrix that is beneficial in terms of
+Naimark and Foxlin~\cite{NaimarkF02} proposed a circular bar code
+called the Circular Data Matrix that is beneficial in terms of
 easy detection and ability to have a large number
-of uniquely identifiable codes.  Addressing the issue of occlusion, 
-Bergamasco et al. \cite{runetag11} proposed the RUNE-tag fiducial divided into number of
-circular dots arranged in circular fashion.
-RUNE-tags can be detected even when up to 50\% of fiducial area is occluded.
-Bergamasco et al.~\cite{Pitag13} proposed the Pi-Tag fiducial, also composed 
-of circular structures but arranged in a rectangle to exploit projective invariant cross-ratio.
+of uniquely identifiable codes.  To address the issue of occlusion,
+Bergamasco et al.~\cite{runetag11} proposed the RUNE-tag fiducial by dividing
+into number of circular dots arranged in circular fashion. RUNE-tags can be
+detected even when up to 50\% of fiducial area is occluded. Bergamasco et
+al.~\cite{Pitag13} proposed the PiTag fiducial, also composed of circular
+structures but arranged in a rectangle to exploit projective invariant cross-ratio.
 This provided similar occlusion resistance as RUNE-tag but with even less
 circular dots. All of these techniques however rely on generic features
-(e.g., circle detection) that break down under motion blur.
+detection (e.g., circle detection) that break down under motion blur.
 
@@
 
-\noindent{\textbf{Tracking:}}~~Fiducial detection between successive video
-frames can be considered a tracking problem where the tracked object is fiducial itself.
-There is a very large body of research dedicated to tracking and interested
-readers are referred to~\cite{Yilmaz:2006} for a survey.
+\noindent{\textbf{Tracking}}~~Fiducial detection between successive video
+frames can be considered as a tracking problem where the tracked object is
+fiducial itself.  There is a very large body of research dedicated to tracking and interested
+readers are referred to~\cite{Yilmaz:2006} for a good survey.
 
-Most tracking methods(~\cite{Ross:2008,Wu:2009,Perez02,Mei:2009} ) assume the
-image sequence to be blur free. In reality, however, motion blur in video
-sequences is often unavoidable. To this end, Wu et al.\cite{Wu:2011} proposed the
-Blur-driven Tracker (BLUT) framework for tracking motion-blurred targets. BLUT
+Most tracking methods (e.g.,~\cite{Ross:2008,Wu:2009,Perez02,Mei:2009}) assume
+the image sequence to be blur free. In reality, however, the presence of motion blur in 
+a video sequence is often unavoidable. To this end, Wu et al.~\cite{Wu:2011}
+proposed the Blur-driven Tracker (BLUT) framework for tracking motion-blurred targets. BLUT
 is based on the observation that although motion blurs degrade the visual
@@
 popular fiducials under motion blur.  Specifically we examine ARTags
-\cite{Fiala05} and PiTags\cite{Pitag13} given their difference in geometry design.
-We didn't find source code as well as samples for RUNE-tag\cite{runetag11}
-online. Also, for Circular data matrix\cite{NaimarkF02}, the software should be
-used with their proprietary hardware. So, we couldn't examine these fiducials.
+~\cite{Fiala05} and PiTags~\cite{Pitag13} given their difference in geometry
+design and the availability of API to develop applications to recognize the tags.
+RUNE-tag~\cite{runetag11} currently does not provide access to the an
+implementation to generate or recognize the tag.  The circular data
+matrix~\cite{NaimarkF02} is available as a commercial product, however it
+requires proprietary hardware to recognize the fiducial.
 
-To simulate the appearance of the maker as seen by a quadcopter,  we scaled down
-the ARTag and PiTag fiducials to be size 150$\times$150 pixels. Both fiducials are then blurred
-using linear motion blur at various orientations with different blurs scales.  
-The blur motion ranged from 15 to 50 in magnitude (denoted in pixels),
-representing small to significant motion blur. Figure \ref{fig:artag_pitag}
-shows the visual appearance of the blurred tags.  We then try to detect the
-markers using the ALVAR library~\cite{alvar} and Pi-Tag
-library~\cite{ros_pitag}. The table in the left side of
+To evaluate the ARTag and PiTag under blur, we simulate the appearance of the
+marker as seen by a quadcopter by scaling the tags to 150$\times$150 pixels.
+Both fiducials are then blurred using linear motion blur at various
+orientations with different blur scales. The blur motion ranged from 15 to 50
+in magnitude (denoted in pixels), representing small to significant motion
+blur. Figure \ref{fig:artag_pitag} shows the visual appearance of the blurred
+tags. We then try to detect the markers using the ALVAR library~\cite{alvar} and
+PiTag library~\cite{ros_pitag}. The table in the right side of
 Figure~\ref{fig:artag_pitag} shows the recognition rate (in percentage) of two
 fiducial markers at various blur scales over all the different orientations.
-As we can see, the PiTag performance quickly diminished under small amounts of
-blur, however, at 35 motion blur, ARTag's recognition rate drops to less than
+As we can see, the PiTag performance quickly diminishes under small amounts of
+blur, while at 35 motion blur, the ARTag's recognition rate drops to less than
 20\%.
@@
 \\\cline{2-3}
-\small{Scale}& \small{AR Tag} &	\small{Pi-Tag} \\ \cline{1-3}
+\small{Scale}& \small{PiTag} &	\small{ARTag} \\ \cline{1-3}
 \small{15} & \small{100} & \small{100} \\ %\cline{1-3}
@@
 \end{minipage}
-\label{fig:artag_pitag}
-\captionof{figure}{Figure showing ARTag and Pi-tag blurred with various blur
+\captionof{figure}{Figure showing PiTag and ARTag blurred with various blur
 scales at different orientations. Table on the right shows the recognition rate
 (in percent) of both fiducial markers at various blur scales along all blur
-orientations.  Recognition rates for both tag is significantly reduced due to
+orientations.  Recognition rates for both tags are significantly reduced due to
 blur. For severe blur, detection is not possible.}
+\label{fig:artag_pitag}
 \end{minipage}
@@
 
-We have designed binary coded fiducial that uses concentric white rings of
+We have designed a binary coded fiducial that uses concentric white rings of
 equal widths on a black background with a blurred border\footnote{This design
-can be easily inverted to have a white background with white rings}. The
+can be inverted to have a white background with white rings.}. The
 outermost and innermost rings represent the start and end of the code and is
@@
 \centering
-\includegraphics[width=\linewidth]{blur_direction.pdf}
+\includegraphics[width=0.8\linewidth]{blur_direction.pdf}
 \caption{Figure showing how change in blur direction changes the location of
@@
 under the observation that the motion blur for the quadcopter's camera
-can be well modelled as linear motion.  This  linear motion blur assumption has been shown to be
-reasonable in prior works targeting camera motion blur (e.g.~\cite{Moshe:2003,Moshe:2004}).
-Under this assumption, the scene content perpendicular to the blur direction is
-unaffected by the blur.  Because of our circular design, the
-direction perpendicular to the linear motion will appear as an unblurred linear
-pattern.  Figure \ref{fig:blur_direction} shows examples of this using a
-pattern  with various motion directions.
+can be well modelled as linear motion.  This  linear motion blur assumption has
+been shown to be reasonable in prior works targeting camera motion blur
+(e.g.~\cite{Moshe:2003,Moshe:2004}). Under this assumption, the scene content
+perpendicular to the blur direction is unaffected by the blur.  Because of our
+circular design, the direction perpendicular to the linear motion will still be
+recognizable as a linear pattern.  Figure \ref{fig:blur_direction} shows
+examples of this using a pattern under various motion directions.
 
 Figure \ref{fig:overall_flow} shows the process involved in fiducial
-detection. We give a brief overview of our algorithm here and details
-to each step in the following.  Our detection algorithm has four steps. Step 1,
-we apply a Gabor filter on the image captured through AR Drone to isolate the
+detection. We give a brief overview of our algorithm here with each step described 
+in detail afterwards.  Our detection algorithm has four steps. Step 1,
+we apply a Gabor filter on the image to isolate the
 potential locations of the pattern.  Step 2, we find the clusters of patches
-found in Gabor output using spatial clustering.  Step 3, performs Principal
+found in the Gabor output by clustering.  Step 3, performs Principal
 Component Analysis (PCA) on each cluster to find the dominant direction
 unaffected by blur.  Step 4, based on the direction we extract the intensity
-profile of the pattern and classify the code using a K-Nearest neighbor
+profile of the pattern and classify the code using a K-Nearest Neighbor
 classifier based on training data.
@@
 The four step process includes (Step 1) Gabor filtering,
-(Step 2) component clustering, (Step 3) PCA to determine the dominate direction, 
-and (Step 4) KNN classification using training-data captured for each pattern.}
+(Step 2) component clustering, (Step 3) PCA to determine the dominant direction,
+and (Step 4) K-NN classification using training-data captured for each pattern.}
 \label{fig:overall_flow}
@@
 modulated by a sinusoidal plane wave~\cite{Kruizinga:2002}. It is used to find
-high gradient patches from the image. In our case, it is used to detect blur
-invariant sections of the fiducials. We have applied Gabor filter for eight
+high gradient patches from the image. In our case, it is used to detect portions
+of the circular fiducials that were not affected by the blur. 
+We applied the Gabor filter in eight
 different orientations ($\theta = 0, 45, 90, \ldots ,225, 270, 315$).  The
@@
 (phase angle) $= 0$ (for real part), $\pi/2$ (for imaginary part).
-Then L2 norm of outputs along all orientations is calculated and finally L2
-normalized image is thresholded with threshold set to $0.4$ (on scale of zero to
-one).
+Then $\ell^2$-norm of outputs along all orientations is calculated and finally
+$\ell^2$-normalized image is thresholded with threshold set to $0.4$ (on scale of zero to
+one).  For further details to the Gabor filter, see~\cite{Kruizinga:2002}.
+%% MBS - is the Kruizinga filter resonable to cite?
 
-\noindent\textbf{Clustering}: The binarized Gabor filter response are
-treated as a set of connected components in the image.   This clustering
-stage is to find components that are located in a close spatial region.  We do
-this by using hierarchical fashion clustering~\cite{ALGLIB}. We used unweighted
-average linkage with distance threshold set to 150 for merging clusters in
-hierarchical fashion.
+\noindent\textbf{Clustering}: The binarized Gabor filter responses are
+treated as a set of connected components in the image.   Clustering
+is used to find components that are located in a close spatial region.  We do
+this via hierarchical clustering~\cite{ALGLIB} using unweighted
+average linkage with a distance threshold set to 150.
 
 \noindent\textbf{PCA}: For each clustered set of components, we apply
-PCA to determine the dominate direction.  This is done by examining the
+PCA to determine the dominant direction.  This is done by examining the
 orientation of the first principal component.  We then extract an intensity
@@
 
+After finding the intensity profile, we examine it by
+projecting the pixel intensities onto the PCA direction and record the
+number and width of transitions.  If the number of transitions or the
+width of the transitions is not consistent with what is allowable by
+our code, we reject the clustered region as a potential fiducial.
+Clustered components that have allowable transitions counts and transitions with
+uniform widths are further considered for classification to determine
+the binary code.
+
 \noindent\textbf{Classification}: As mentioned above, a small image patch containing
 the intensity profile of the fiducial is used to identify the code.   We found
-that a training-based method using KNN gave better results than trying to
+that a training-based method using K-NN gave better results than trying to
 find binary code directly by determining the presence (or absence) of ring
- at particular positions in the image patch. To build
- the training-data, a synthetic fiducial pattern is blurred along 36 orientations (0, 10, 20, \ldots , 350) with blur scale set to 40, and its intensity profile along the first principal component from every output is
-taken as training data for that fiducial pattern. Figure
-\ref{fig:training_data} shows the process of creating training data for
-fiducial with binary code ``01'' embedded in it.  For an input image patch, we
-normalize its intensity range and then compare it against the training-data.
-The class label from the closest top $K=5$ images in the training-data is used
-to label the patch.
+at particular positions in the image patch. To build the training-data, a
+synthetic fiducial pattern is blurred along 36 orientations (0, 10, 20, \ldots
+, 350) with blur scale set to 40, and its intensity profile along the first
+principal component from every output is taken as training data for that
+fiducial pattern. Figure \ref{fig:training_data} shows the process of creating
+training data for fiducial with binary code ``01'' embedded in it.  For an
+input image patch, we normalize its intensity range and then compare it against
+the training-data. The class label from the closest top $K=5$ images in the
+training-data is used to label the patch.
 
@@
 \centering
-  \includegraphics[width=\linewidth]{training_data.pdf}
+  \includegraphics[width=0.8\linewidth]{training_data.pdf}
   \caption{Process to create training data for the fiducial pattern with binary
@@
 
-We are able to find the number of rings in the fiducial by finding transitions
-in the intensity profile. To increase the classification accuracy, training data
-for patterns having same number of rings is grouped together; e.g., in two bit
+We are able to find the number of rings in the fiducial by finding
+number of transitions in the intensity profile. To increase the classification
+accuracy, training data for patterns having same number of rings are grouped together; e.g., in two bit
 binary coded fiducial, training data for pattern ``01'' and ``10'' will be
-grouped together, In three bit binary coded fiducial, training data for pattern
-``001'', ``010'' and ``100'' will form one group while training data for
-pattern ``110'', ``011'' and ``101'' will be in other group, etc. Now,
-depending on the number of detected rings in test pattern, it is matched
-against corresponding group of training data, again using  K-Nearest Neighbor
-Classifier. In this way, if we detect either zero rings or maximum possible
-rings in the test pattern, there will be no need to do further classification.
+grouped together. In three bit binary coded fiducial, training data for pattern
+``001'', ``010'' and ``100'' will form one group, while training data for
+pattern ``110'', ``011'' and ``101'' will be in other group, and so on. 
+Depending on the number of detected rings in test pattern, it is matched
+against corresponding group in the training data, again using  the K-NN. 
+If we detect either zero rings or maximum possible
+rings in the test pattern, there will be no need to do further classification, we
+can classify the pattern as class 0 or the maximum class containing all 1s.
 
@@
 
-We have implemented our algorithm in C++ using OpenCV library.
+We have implemented our algorithm in C++ using the OpenCV library.
 Experiments were performed on a PC with Intel Core i7 processor(@3.4GHz) and 4GB RAM.
-Source code and data sets in this paper will be made publicly available.  Video clips
-have also been provided in the supplemental materials.
+Source code to generate and recognize the code, as well as the data sets used in
+this paper will be made publicly available.  Video clips
+of collected data are provided in the supplementary material.
 
 Our system has been tested on several image sequences captured from an AR Drone
-quadcopter.  The Drone was flown indoors looking at patterns attached to
-various walls. Each image sequence contains frames containing different fiducial
+quadcopter.  The drone was flown indoors looking at patterns attached to
+various walls. Each image sequence contains frames of different fiducial
 patterns. Sample output for each fiducial pattern is shown in Figure
-\ref{fig:output0} -- Figure \ref{fig:output3}. Our detection process takes
-around 0.3 seconds which translates to around three to four frames per second.
+\ref{fig:out_outputs}-(a) -- Figure \ref{fig:out_outputs}-(d). Our detection
+process takes around 0.3 seconds which translates to slightly over three frames per second.
 
 Our system has also been tested on images containing multiple fiducial patterns
-in the same frame. Our algorithm successfully detected all fiducial patterns as
+in the same frame. Our algorithm can successfully detected all fiducial patterns as
 well as correctly classified them as shown in Figure \ref{fig:output_all}.
@@
 \subsubsection{Comparison with ARTag}
-First, we have repeated blur simulation experiment on our fiducials as reported
+First, we have repeated the blur simulation experiment on our fiducials as reported
 in Section~\ref{sec:blurtest}.  Specifically, we build our blur resistant
-patterns size 150x150 and blurred them along various orientations with different
-blur scales. Then, we tried to detect our fiducial using a 2-bit patterns using
-algorithm presented in earlier section.
+patterns at 150$\times$150 pixel resolution and blurred them along various
+orientations with different blur scales. Then, we tried to detect our fiducial using a 2-bit
+patterns using algorithm presented in earlier section.
 
 The comparison of recognition rate is shown in Figure
-\ref{fig:recognition_rate}. In this experiment, we use even more blur, up to 65
-pixels.  The graph shows in Figure \ref{fig:recognition_rate} that our
-recognition is 100\% for all codes except the ``00'' which is undetectable
-after 50 pixels blur (which is still significantly better than ARTag).  Reasons
-for the ``00'' tags lower performance is discussed in Section~\ref{sec:discussion}.
+\ref{fig:simulated_blur}-(a). In this experiment, we use even more blur, up to 65
+pixels. Figure \ref{fig:blur_maximum} shows the patterns under maximum blur they
+can sustain are still be recognized. The graph in Figure
+\ref{fig:simulated_blur}-(a) shows that our recognition is 100\% for all codes
+except the ``00'' which is undetectable after 50 pixels blur (which is still
+significantly better than ARTag).  Reasons for the ``00'' tags lower
+performance is discussed in Section~\ref{sec:discussion}.
 
-We have also checked the difference between the actual center of the fiducial
-and center found by our algorithm, on blur simulated data along different blur
-orientations. From Table \ref{tab:blur_angle_center}, it can be clearly seen
-that the difference between the actual center and center found by algorithm is
-less than three percent of the diameter of fiducial.
+We also performed analysis to detect how accurately the center of the blur pattern 
+can be localized under blur.  To do this, we have simulated data along different blur
+orientations for all patterns over eight different blur scales (30 to 65 with
+step size of 5). Values for the localization of the pattern ``00'' after blur
+with 50 pixels is omitted since the pattern cannot be detected. From the Table in Figure
+~\ref{fig:simulated_blur}-(b), it can be clearly seen that the mean error in
+locating center by our algorithm is within approximate 3 pixels, or 3\% of the
+diameter of fiducial.
 
@@
 
-\noindent\begin{minipage}{\linewidth}
-\noindent\begin{minipage}{0.67\linewidth}
-\includegraphics[width=\linewidth]{recognition_rate.png}
-\captionof{figure}{Comparison of recognition rate of AR Tag and our fiducials on
-blur simulated data at various blur scales. It can be clearly seen that except
-fiducial with binary code ``00'', our fiducial patterns are
-recognised all times.}
+\noindent\begin{figure}
+\begin{tabular}{c|c}
+\begin{subfigure}[b]{0.65\linewidth}
+\includegraphics[width=\linewidth]{recognition_rate.pdf}
+\caption{Comparison of recognition rate of fiducials}
 \label{fig:recognition_rate}
-\end{minipage}
-\noindent\begin{minipage}{0.32\linewidth}
-\begin{tabularx}{\textwidth}{|c|Y|Y|}
-\cline{1-3}
-\small{Blur} & \small{Actual} & \small{Found} \\
-\small{Angle} & \small{center} & \small{center} \\
-\cline{1-3}
-0 & (55,75) & (54,75) \\
-22 & (56,67) & (55,64) \\
-45 & (61,61) & (59,62) \\
-67 & (67,56) & (63,56) \\
-90 & (75,55) & (75,53) \\  \cline{1-3}
+\end{subfigure}
+&
+\begin{subfigure}[b]{0.33\linewidth}
+\begin{tabularx}{\textwidth}{|c|Y|}
+\cline{1-2}
+\footnotesize{Blur} & \footnotesize{Mean($\pm$std) error}  \\
+\footnotesize{angle} & \footnotesize{(in pixels)}  \\
+\cline{1-2}
+\footnotesize{0} & \footnotesize{1.33 $\pm$ 0.40}  \\
+\footnotesize{22} & \footnotesize{2.42 $\pm$ 1.05} \\
+\footnotesize{45} & \footnotesize{1.46 $\pm$ 0.65}  \\
+\footnotesize{67} & \footnotesize{2.39 $\pm$ 1.28}  \\
+\footnotesize{90} & \footnotesize{1.83 $\pm$ 0.25}  \\ 
+\cline{1-2}
 \end{tabularx}
-\captionof{table}{Table showing the actual center of our fiducial and center
-found by our algorithm, when blurred along various blur angles (Blur Scale =
-40).}
+\caption{Center localization error}
 \label{tab:blur_angle_center}
-\end{minipage}
-\end{minipage}
+\end{subfigure}
+\end{tabular}
+\caption{(a): Comparison of recognition rate of the ARTag and our fiducials on
+blur simulated data at various blur scales. It can be seen that except for the
+fiducial with binary code ``00'', our fiducial patterns are recognized all times.
+(b): Table showing the mean error and standard deviation of the localized fiducial center
+versus the ground truth.  Error is computed for various blur angles over
+different blur scales.}
+\label{fig:simulated_blur}
+\end{figure}
 
 We also compared results on the recorded feed using AR Drone quadcopter. In our
-experimental setup, we have placed two AR Tags in the scene along with our fiducial  to
+experimental setup, we have placed two ARTags in the scene along with our fiducial  to
 compare the resilience of blur by each fiducial type. We have used
-ar\_track\_alvar, ROS Wrapper for ALVAR library \cite{ros_alvar}, to detect AR
-Tags from the stream captured through quadcopter. In each test dataset, we used
-different two bit binary coded fiducial and recorded video of around two minute
-duration (i.e., around 1000 frames).   The quadcopter was flown in a routine
-manner in the room with its camera facing the wall (see supplemental
-videos). The comparison of recognition rate is shown in Table
+ar\_track\_alvar, ROS Wrapper for the ALVAR library~\cite{ros_alvar}, to detect the ARTags from the stream captured with the quadcopter camera. In each test dataset, we
+have used different two bit binary coded fiducial and recorded video of around
+two minute duration (i.e., around 1000 frames).   The quadcopter was flown in a routine
+manner in the room with its camera facing the wall (see supplementary
+videos). The comparison of the recognition rate is shown in Table
 \ref{tab:recongition_accuracy}. Recognition rate of our fiducials ranges from
-86.5\% to 94.1\%, while the AR Tag is 60.3\% to 65.6\%. Classification
-accuracy of all fiducials (ARTag as well as ours) was approximately 100\%.
+86.5\% to 94.1\%, while the ARTag is 60.3\% to 65.6\%. Classification
+accuracy of all fiducials (ARTag as well as ours) was approximately 100\%, i.e.,
+when tags were detected they were the correct fiducials and not other objects in the scene.
 
@@
 \centering
-  \includegraphics[width=0.48\linewidth]{output_00.jpg}
-  \includegraphics[width=0.48\linewidth]{new_results/output_00.jpg}
+  \includegraphics[width=0.4\linewidth]{output_00.jpg}
+  \includegraphics[width=0.4\linewidth]{new_results/output_00.jpg}
   \caption{Binary code ``00''}
@@
 \centering
-  \includegraphics[width=0.48\linewidth]{output_01.jpg}
-  \includegraphics[width=0.48\linewidth]{new_results/output_01.jpg}
+  \includegraphics[width=0.4\linewidth]{output_01.jpg}
+  \includegraphics[width=0.4\linewidth]{new_results/output_01.jpg}
   \caption{Binary code ``01''}
@@
 \centering
-  \includegraphics[width=0.48\linewidth]{output_10.jpg}
-  \includegraphics[width=0.48\linewidth]{new_results/output_10.jpg}
+  \includegraphics[width=0.4\linewidth]{output_10.jpg}
+  \includegraphics[width=0.4\linewidth]{new_results/output_10.jpg}
   \caption{Binary code ``10''}
@@
 \centering
-  \includegraphics[width=0.48\linewidth]{output_11.jpg}
-  \includegraphics[width=0.48\linewidth]{new_results/output_11.jpg}
+  \includegraphics[width=0.4\linewidth]{output_11.jpg}
+  \includegraphics[width=0.4\linewidth]{new_results/output_11.jpg}
   \caption{Binary code ``11''}
@@
   of the binary code embedded in the detected fiducial.}
+  \label{fig:out_outputs}
 \end{figure}
@@
 \begin{table}[h!]
-\caption{Comparison of recognition rate of AR Tag and our fiducials on real
+\caption{Comparison of recognition rate of ARTag and our fiducials on real
 data captured through AR Drone. Each row shows analysis of a test
 dataset captured for our fiducial with different binary code embedded in it.
-Each dataset has around 1000 frames captured in around two minutes.}
+Each dataset has around 1000 frames captured representing roughly two minutes of video each.}
 \centering
@@
 &\multirow{2}{*}{Binary Code} &\multicolumn{2}{c|}{Recognition Rate (\%)} \\
-\cline{4-5} & & & Our Fiducial & AR Tag\\\cline{1-5}
-1 & 1205 & 00 & 86.5 &  65.6 \\ \cline{1-5}
-2 & 1047 & 01 & 94.1 &  61.9 \\ \cline{1-5}
-3 & 1102 & 10 &  92.74 & 62.4 \\ \cline{1-5}
-4 & 1081 & 11 & 93.54 & 60.3 \\ \cline{1-5}
+\cline{4-5} & & & ARTag & Our Fiducial \\\cline{1-5}
+1 & 1205 & 00 &  65.6 & 86.5  \\ \cline{1-5}
+2 & 1047 & 01 &  61.9 & 94.1  \\ \cline{1-5}
+3 & 1102 & 10 &  62.4 & 92.74 \\ \cline{1-5}
+4 & 1081 & 11 &  60.3 & 93.54  \\ \cline{1-5}
 \end{tabularx}
@@
 
-\subsubsection{Comparison with BLUT:}
+\subsubsection{Comparison with BLUT}
 
-We also compare out approach with tracking designed for blurred input scenes. 
+We also compare our approach with tracking designed for blurred input scenes.
 We have used four image sequences (consisting of around 1000 frames each), each
 one containing a different blur resistant fiducial pattern to test the performance of
-BLUT\cite{Wu:2011} and compare it with our result on the same image sequence.
-From the images in top rows of Figure
-\ref{fig:BLUT_compare_00}-\ref{fig:BLUT_compare_11}, we can see that BLUT is able to track the fiducial when the position of fiducial does not change too much in successive frames.
-Also, it can be seen that, once BLUT looses the track of the fiducial, it is not able to recover.
-Since our approach detects the code at each frame, large changes in the patterns
-position is not an issue.   Our detection results are also shown in Figure
+BLUT \cite{Wu:2011} and compare it with our result on the same image sequence.
+From the images in the top rows of Figure
+\ref{fig:BLUT_compare_00}-\ref{fig:BLUT_compare_11}, we can see that BLUT is
+able to track the fiducial when the position of fiducial does not change too
+much in successive frames. Also, it can be seen that once BLUT looses 
+track of the fiducial, it is not able to recover. Since our approach detects the
+code in each frame, large changes in the patterns position is not an issue.
+Our detection results are also shown in Figure
 \ref{fig:BLUT_compare_00}-\ref{fig:BLUT_compare_11}.
 
-We have also found that, even if we reset the BLUT tracker after loosing track,
-it will loose track again after around 100 frames i.e., approximately within 6
-seconds. When we checked the timestamp data from image header captured through
-AR Drone, we found that, there was difference of 0.14 seconds between two
-successive frames in the earlier case, which clearly suggests the dropping of
-frame (e.g., normal 30fps should be 0.33 seconds). Also,  there were around 50
-instances in 1000 frames where timestamp difference between two successive
+We have also found that even if we reset the BLUT tracker after loosing track,
+it will loose track again after around 100 frames, that is approximately within
+6 seconds. When we checked the timestamp data from image header captured through
+the AR Drone, we found that, there was a difference of 0.14 seconds between two
+successive frames in the earlier case, which clearly indicates the dropping of
+video frame (e.g., normal 30fps should be 0.033 seconds). Also, there were around 50
+instances in 1000 frames where the timestamp difference between two successive
 frames was greater than 0.1 seconds. As such, it appears one of the main
@@
 \end{subfigure}
-\caption{Top: Output of BLUT\cite{Wu:2011} on sample image sequence containing ``00''
+\caption{Top: Output of BLUT~\cite{Wu:2011} on sample image sequence containing ``00''
 binary coded fiducial. Bottom: Output of our algorithm on the same image
-sequence. BLUT is able to track the fiducial till third frame, but from fourth
-frame, BLUT looses track of the fiducial. In first three frames, size of the
-fiducials is less but in fourth and fifth frame it is bigger, hinting sudden
+sequence. BLUT is able to track the fiducial till the third frame, but from fourth
+frame BLUT looses track of the fiducial. In first three frames, the size of the
+fiducials is less but in fourth and fifth frame it is bigger, hinting at a sudden
 forward movement of quadcopter.}
@@
 \end{subfigure}
-\caption{Top: Output of BLUT\cite{Wu:2011} on sample image sequence containing
-``01'' binary coded fiducial, Bottom: Output of our algorithm on the same image
-sequence. BLUT looses the track from third frame.}
+\caption{Top: Output of BLUT~\cite{Wu:2011} on sample image sequence containing
+``01'' binary coded fiducial. Bottom: Output of our algorithm on the same image
+sequence. BLUT looses the track from the third frame.}
 \label{fig:BLUT_compare_01}
@@
 \end{subfigure}
-\caption{Top: Output of BLUT\cite{Wu:2011} on sample image sequence containing
-``10'' binary coded fiducial, Bottom: Output of our algorithm on the same image
-sequence. From second frame itself, BLUT looses the track.}
+\caption{Top: Output of BLUT~\cite{Wu:2011} on sample image sequence containing
+``10'' binary coded fiducial. Bottom: Output of our algorithm on the same image
+sequence. From the second frame, BLUT looses track.}
 \label{fig:BLUT_compare_10}
@@
 \end{subfigure}
-\caption{Top: Output of BLUT\cite{Wu:2011} on sample image sequence containing
-``11'' binary coded fiducial, Bottom: Output of our algorithm on the same image
+\caption{Top: Output of BLUT~\cite{Wu:2011} on sample image sequence containing
+``11'' binary coded fiducial. Bottom: Output of our algorithm on the same image
 sequence. BLUT lost the track from third frame. There is sudden reversal of
-direction of quadcopter from third frame. In first two frames quadcopter was
-going up, but suddenly it moved down in third frame.}
+direction from the quadcopter in the third frame. In first two frames, the quadcopter was
+going up, but suddenly moved down.}
 \label{fig:BLUT_compare_11}
@@
 
-\noindent\textbf{Processing Time:}~~Currently our processing time (0.3 seconds
-per frame) makes it difficult to do the fiducial detection in real-time.  As such, we currently
-envision this will be used in an offline manner for performing analysis of flight paths.
-Code profiling revealed that the Gabor filtering takes most of the time (0.03
--- 0.04 seconds per orientation). As we are applying Gabor filter along eight
-orientations, we should think of some optimized way to do filtering.
-Alternatively, some replacement for Gabor filter needs to be find out.
+\noindent\textbf{Processing Time}~~Currently, our processing time (0.3 seconds
+per frame) does not provide real-time performance.  As such, we currently
+envision this will be used in an offline manner for performing analysis of
+flight paths. Code profiling revealed that the Gabor filtering along the eight
+directions takes most of the time (0.03 -- 0.04 seconds per orientation).  Either an
+improved Gabor filter scheme is required or an alternative strategy for
+detection is required.
 
-\noindent\textbf{False Negatives:}~~We found that sometimes our detection
+\noindent\textbf{False Negatives}~~We found that sometimes our detection
 algorithm fails to recognize our fiducial with binary code ``00'' when there is
-large amount of blur.  When we
-investigated the problem, we found that if there is too much blur, the innermost
+large amount of blur.  The is because when there is too much blur, the innermost
 ring's response in the Gabor output is too low and not detected properly.
-This problem can be resolved by increasing radius of innermost ring to 
+This problem can be resolved by increasing the radius of innermost ring to
 reduce the effect of blur on the innermost ring.
 
-\noindent\textbf{Pose Estimation:}~~We note that other markers are able to give
+\noindent\textbf{Pose Estimation}~~We note that other markers are able to give
 full pose estimation after detection.  However, we are only able to reliably detect
@@
 
-\noindent\textbf{Number of Fiducials:}~~Currently, compared to AR Tag fiducial
+\noindent\textbf{Number of Fiducials}~~Currently, compared to ARTag fiducial
 markers, we are able to generate less number of fiducials. Many applications in
 robotics (e.g. quadcopter navigation) may not require large number of fiducial
-markers as AR Tag. Most of the time, it is sufficient to have 4-6
-different fiducial patterns. Still, we may be able to generate more number of
-fiducials by using color background instead of black. E.g., if we just use Red,
-Green and Blue as background color, number of fiducials will be increased by
-factor of three.
+markers as available by ARTag.  Most of the time, it is sufficient to have 4-6
+different fiducial patterns. Still, we may be able to generate a larger number of
+fiducials by using color backgrounds. This is an area interest for further
+investigation.
 
@@
 Quadcopters are subject to quick and unstable motions that can cause significant
-motion blur in the captured images. It severely affects the detection rate of
-existing fiducial markers. We proposed the design of a fiducial that is robust
-to motion blur. Our design of contrasting concentric rings is based on the 
+motion blur in the captured images. This severely affects the detection rate of
+existing fiducial markers. We proposed the design of a fiducial that is
+resistant to motion blur. Our design of contrasting concentric rings is based on the
 observation that the direction perpendicular to the motion blur direction will
 be unaffected by the blur and therefore still be recognizable. We have shown
-through experimental validation that our fiducial will work under significant
-amount of motion blur and can significantly outperform existing fiducial
+through experimental validation that our fiducial will work under large
+amounts of motion blur and can significantly outperform existing fiducial
 markers under this scenario.

### 2014-03-07 ECCV/paper.tex
Super Final version (Most probably)

@@
 vision based modules that uses visual cues in the real world~(e.g.,
-\cite{Davison:2007,Engel12,Engel13}).
-However, to evaluate the effectiveness of navigation methods, fiducial markers are commonly placed into the environment to provide additional information that serves for ground-truth
-positional measurements (e.g., \cite{Bosnak:2012,Lim09,Klopschitz:2007}).
+\cite{Davison:2007,Engel12,Engel13}). However, to evaluate the effectiveness of
+navigation methods, fiducial markers are commonly placed into the environment
+to provide additional information that serves for ground-truth positional
+measurements (e.g., \cite{Bosnak:2012,Lim09,Klopschitz:2007}).
 
@@
 \noindent Details of each of the steps are as follows:\\
-\noindent\textbf{Gabor filter}: A 2D Gabor filter is a Gaussian kernel function
+\noindent\textbf{Gabor filter}~~A 2D Gabor filter is a Gaussian kernel function
 modulated by a sinusoidal plane wave~\cite{Kruizinga:2002}. It is used to find
@@
 
-\noindent\textbf{Clustering}: The binarized Gabor filter responses are
+\noindent\textbf{Clustering}~~The binarized Gabor filter responses are
 treated as a set of connected components in the image.   Clustering
@@
 
-\noindent\textbf{PCA}: For each clustered set of components, we apply
+\noindent\textbf{PCA}~~For each clustered set of components, we apply
 PCA to determine the dominant direction.  This is done by examining the
@@
 
-\noindent\textbf{Classification}: As mentioned above, a small image patch containing
-the intensity profile of the fiducial is used to identify the code.   We found
+\noindent\textbf{Classification}~~As mentioned above, a small image patch
+containing the intensity profile of the fiducial is used to identify the code.   We found
 that a training-based method using K-NN gave better results than trying to
@@
 compare the resilience of blur by each fiducial type. We have used
-ar\_track\_alvar, ROS Wrapper for the ALVAR library~\cite{ros_alvar}, to detect the ARTags from the stream captured with the quadcopter camera. In each test dataset, we
-have used different two bit binary coded fiducial and recorded video of around
-two minute duration (i.e., around 1000 frames).   The quadcopter was flown in a routine
-manner in the room with its camera facing the wall (see supplementary
-videos). The comparison of the recognition rate is shown in Table
-\ref{tab:recongition_accuracy}. Recognition rate of our fiducials ranges from
-86.5\% to 94.1\%, while the ARTag is 60.3\% to 65.6\%. Classification
-accuracy of all fiducials (ARTag as well as ours) was approximately 100\%, i.e.,
-when tags were detected they were the correct fiducials and not other objects in the scene.
+ar\_track\_alvar, ROS Wrapper for the ALVAR library~\cite{ros_alvar}, to detect
+the ARTags from the stream captured with the quadcopter camera. In each test
+dataset, we have used different two bit binary coded fiducial and recorded
+video of around two minute duration (i.e., around 1000 frames).   The
+quadcopter was flown in a routine manner in the room with its camera facing the
+wall (see supplementary videos). The comparison of the recognition rate is
+shown in Table \ref{tab:recongition_accuracy}. Recognition rate of our
+fiducials ranges from 86.5\% to 94.1\%, while the ARTag is 60.3\% to 65.6\%.
+Classification accuracy of all fiducials (ARTag as well as ours) was
+approximately 100\%, i.e., when tags were detected they were the correct
+fiducials and not other objects in the scene.
 

### 2014-05-26 WACV/egpaper_final.tex
Initial Commit

\documentclass[10pt,twocolumn,letterpaper]{article}

\usepackage{wacv}
\usepackage{times}
\usepackage{epsfig}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}

% Include other packages here, before hyperref.

% If you comment hyperref and then uncomment it, you should delete
% egpaper.aux before re-running latex.  (Or just hit 'q' on the first latex
% run, let it finish, and you should be clear).
%\usepackage[pagebackref=true,breaklinks=true,letterpaper=true,colorlinks,bookmarks=false]{hyperref}

\wacvfinalcopy % *** Uncomment this line for the final submission

\def\wacvPaperID{****} % *** Enter the wacv Paper ID here
\def\httilde{\mbox{\tt\raisebox{-.5ex}{\symbol{126}}}}

% Pages are numbered in submission mode, and unnumbered in camera-ready
%\ifwacvfinal\pagestyle{empty}\fi
\setcounter{page}{4321}
\begin{document}

%%%%%%%%% TITLE
\title{\LaTeX\ Author Guidelines for WACV Proceedings}

\author{First Author\\
Institution1\\
Institution1 address\\
{\tt\small firstauthor@i1.org}
% For a paper whose authors are all at the same institution,
% omit the following lines up until the closing ``}''.
% Additional authors and addresses can be added with ``\and'',
% just like the second author.
% To save space, use either the email address or home page, not both
\and
Second Author\\
Institution2\\
First line of institution2 address\\
{\tt\small secondauthor@i2.org}
}

\maketitle
%\thispagestyle{empty}

%%%%%%%%% ABSTRACT
\begin{abstract}
   The ABSTRACT is to be in fully-justified italicized text, at the top
   of the left-hand column, below the author and affiliation
   information. Use the word ``Abstract'' as the title, in 12-point
   Times, boldface type, centered relative to the column, initially
   capitalized. The abstract is to be in 10-point, single-spaced type.
   Leave two blank lines after the Abstract, then begin the main text.
   Look at previous WACV abstracts to get a feel for style and length.
\end{abstract}

%%%%%%%%% BODY TEXT
\section{Introduction}

Please follow the steps outlined below when submitting your manuscript to
the IEEE Computer Society Press.  This style guide now has several
important modifications (for example, you are no longer warned against the
use of sticky tape to attach your artwork to the paper), so all authors
should read this new version.

%-------------------------------------------------------------------------
\subsection{Language}

All manuscripts must be in English.

\subsection{Dual submission}

By submitting a manuscript to WACV, the authors assert that it has not been
previously published in substantially similar form. Furthermore, no paper
which contains significant overlap with the contributions of this paper
either has been or will be submitted during the WACV 2014 review period to
{\bf either a journal} or any conference (including WACV 2014) or any
workshop.
 {\bf Papers violating this condition will be rejected.}

If there are papers that may appear to the reviewers
to violate this condition, then it is your responsibility to: (1)~cite
these papers (preserving anonymity as described in Section 1.6 below),
(2)~argue in the body of your paper why your WACV paper is non-trivially
different from these concurrent submissions, and (3)~include anonymized
versions of those papers in the supplemental material.

\subsection{Paper length}
WACV papers may be between 6 pages and 8 pages, with a \$100 per page added
fee.  Overlength papers will simply not be reviewed.  This includes papers
where the margins and formatting are deemed to have been significantly
altered from those laid down by this style guide.  Note that this
\LaTeX\ guide already sets figure captions and references in a smaller font.
The reason such papers will not be reviewed is that there is no provision for
supervised revisions of manuscripts.  The reviewing process cannot determine
the suitability of the paper for presentation in eight pages if it is
reviewed in eleven.  If you submit 8 for review expect to pay the added page
charges for them.

%-------------------------------------------------------------------------
\subsection{The ruler}
The \LaTeX\ style defines a printed ruler which should be present in the
version submitted for review.  The ruler is provided in order that
reviewers may comment on particular lines in the paper without
circumlocution.  If you are preparing a document using a non-\LaTeX\
document preparation system, please arrange for an equivalent ruler to
appear on the final output pages.  The presence or absence of the ruler
should not change the appearance of any other content on the page.  The
camera ready copy should not contain a ruler. (\LaTeX\ users may uncomment
the \verb'\wacvfinalcopy' command in the document preamble.)  Reviewers:
note that the ruler measurements do not align well with lines in the paper
--- this turns out to be very difficult to do well when the paper contains
many figures and equations, and, when done, looks ugly.  Just use fractional
references (e.g.\ this line is $095.5$), although in most cases one would
expect that the approximate location will be adequate.

\subsection{Mathematics}

Please number all of your sections and displayed equations.  It is
important for readers to be able to refer to any particular equation.  Just
because you didn't refer to it in the text doesn't mean some future reader
might not need to refer to it.  It is cumbersome to have to use
circumlocutions like ``the equation second from the top of page 3 column
1''.  (Note that the ruler will not be present in the final copy, so is not
an alternative to equation numbers).  All authors will benefit from reading
Mermin's description of how to write mathematics.%: \url{http://www.wacv.org/doc/mermin.pdf}.

\subsection{Blind review}

Many authors misunderstand the concept of anonymizing for blind
review.  Blind review does not mean that one must remove
citations to one's own work---in fact it is often impossible to
review a paper unless the previous citations are known and
available.

Blind review means that you do not use the words ``my'' or ``our''
when citing previous work.  That is all.  (But see below for
techreports)

Saying ``this builds on the work of Lucy Smith [1]'' does not say
that you are Lucy Smith, it says that you are building on her
work.  If you are Smith and Jones, do not say ``as we show in
[7]'', say ``as Smith and Jones show in [7]'' and at the end of the
paper, include reference 7 as you would any other cited work.

An example of a bad paper just asking to be rejected:
\begin{quote}
\begin{center}
    An analysis of the frobnicatable foo filter.
\end{center}

   In this paper we present a performance analysis of our
   previous paper [1], and show it to be inferior to all
   previously known methods.  Why the previous paper was
   accepted without this analysis is beyond me.

   [1] Removed for blind review
\end{quote}

An example of an acceptable paper:

\begin{quote}
\begin{center}
     An analysis of the frobnicatable foo filter.
\end{center}

   In this paper we present a performance analysis of the
   paper of Smith \etal [1], and show it to be inferior to
   all previously known methods.  Why the previous paper
   was accepted without this analysis is beyond me.

   [1] Smith, L and Jones, C. ``The frobnicatable foo
   filter, a fundamental contribution to human knowledge''.
   Nature 381(12), 1-213.
\end{quote}

If you are making a submission to another conference at the same time,
which covers similar or overlapping material, you may need to refer to that
submission in order to explain the differences, just as you would if you
had previously published related work.  In such cases, include the
anonymized parallel submission~\cite{Authors06} as additional material and
cite it as
\begin{quote}
[1] Authors. ``The frobnicatable foo filter'', F\&G 2011 Submission ID 324,
Supplied as additional material {\tt fg324.pdf}.
\end{quote}

Finally, you may feel you need to tell the reader that more details can be
found elsewhere, and refer them to a technical report.  For conference
submissions, the paper must stand on its own, and not {\em require} the
reviewer to go to a techreport for further details.  Thus, you may say in
the body of the paper ``further details may be found
in~\cite{Authors06b}''.  Then submit the techreport as additional material.
Again, you may not assume the reviewers will read this material.

Sometimes your paper is about a problem which you tested using a tool which
is widely known to be restricted to a single institution.  For example,
let's say it's 1969, you have solved a key problem on the Apollo lander,
and you believe that the WACV 70 audience would like to hear about your
solution.  The work is a development of your celebrated 1968 paper entitled
``Zero-g frobnication: How being the only people in the world with access to
the Apollo lander source code makes us a wow at parties'', by Zeus \etal.

You can handle this paper like any other.  Don't write ``We show how to
improve our previous work [Anonymous, 1968].  This time we tested the
algorithm on a lunar lander [name of lander removed for blind review]''.
That would be silly, and would immediately identify the authors. Instead
write the following:
\begin{quotation}
\noindent
   We describe a system for zero-g frobnication.  This
   system is new because it handles the following cases:
   A, B.  Previous systems [Zeus et al. 1968] didn't
   handle case B properly.  Ours handles it by including
   a foo term in the bar integral.

   ...

   The proposed system was integrated with the Apollo
   lunar lander, and went all the way to the moon, don't
   you know.  It displayed the following behaviours
   which show how well we solved cases A and B: ...
\end{quotation}
As you can see, the above text follows standard scientific convention,
reads better than the first version, and does not explicitly name you as
the authors.  A reviewer might think it likely that the new paper was
written by Zeus \etal, but cannot make any decision based on that guess.
He or she would have to be sure that no other authors could have been
contracted to solve problem B.

FAQ: Are acknowledgements OK?  No.  Leave them for the final copy.

\begin{figure}[t]
\begin{center}
\fbox{\rule{0pt}{2in} \rule{0.9\linewidth}{0pt}}
   %\includegraphics[width=0.8\linewidth]{egfigure.eps}
\end{center}
   \caption{Example of caption.  It is set in Roman so that mathematics
   (always set in Roman: $B \sin A = A \sin B$) may be included without an
   ugly clash.}
\label{fig:long}
\label{fig:onecol}
\end{figure}

\subsection{Miscellaneous}

\noindent
Compare the following:\\
\begin{tabular}{ll}
 \verb'$conf_a$' &  $conf_a$ \\
 \verb'$\mathit{conf}_a$' & $\mathit{conf}_a$
\end{tabular}\\
See The \TeX book, p165.

The space after \eg, meaning ``for example'', should not be a
sentence-ending space. So \eg is correct, {\em e.g.} is not.  The provided
\verb'\eg' macro takes care of this.

When citing a multi-author paper, you may save space by using ``et alia'',
shortened to ``\etal'' (not ``{\em et.\ al.}'' as ``{\em et}'' is a complete word.)
However, use it only when there are three or more authors.  Thus, the
following is correct: ``
   Frobnication has been trendy lately.
   It was introduced by Alpher~\cite{Alpher02}, and subsequently developed by
   Alpher and Fotheringham-Smythe~\cite{Alpher03}, and Alpher \etal~\cite{Alpher04}.''

This is incorrect: ``... subsequently developed by Alpher \etal~\cite{Alpher03} ...''
because reference~\cite{Alpher03} has just two authors.  If you use the
\verb'\etal' macro provided, then you need not worry about double periods
when used at the end of a sentence as in Alpher \etal.

For this citation style, keep multiple citations in numerical (not
chronological) order, so prefer \cite{Alpher03,Alpher02,Authors06} to
\cite{Alpher02,Alpher03,Authors06}.

\begin{figure*}
\begin{center}
\fbox{\rule{0pt}{2in} \rule{.9\linewidth}{0pt}}
\end{center}
   \caption{Example of a short caption, which should be centered.}
\label{fig:short}
\end{figure*}

%------------------------------------------------------------------------
\section{Formatting your paper}

All text must be in a two-column format. The total allowable width of the
text area is $6\frac78$ inches (17.5 cm) wide by $8\frac78$ inches (22.54
cm) high. Columns are to be $3\frac14$ inches (8.25 cm) wide, with a
$\frac{5}{16}$ inch (0.8 cm) space between them. The main title (on the
first page) should begin 1.0 inch (2.54 cm) from the top edge of the
page. The second and following pages should begin 1.0 inch (2.54 cm) from
the top edge. On all pages, the bottom margin should be 1-1/8 inches (2.86
cm) from the bottom edge of the page for $8.5 \times 11$-inch paper; for A4
paper, approximately 1-5/8 inches (4.13 cm) from the bottom edge of the
page.

%-------------------------------------------------------------------------
\subsection{Margins and page numbering}

All printed material, including text, illustrations, and charts, must be kept
within a print area 6-7/8 inches (17.5 cm) wide by 8-7/8 inches (22.54 cm)
high.  Page numbers should be in footer with page numbers, centered and .75
inches from the bottom of the page and make it start at the correct page
number rather than the 4321 in the example.  To do this fine the line (around
line 23)
\begin{verbatim}
%\ifwacvfinal\pagestyle{empty}\fi
\setcounter{page}{4321}
\end{verbatim}
where the number 4321 is your assigned starting page.

Make sure the first page is numbered by commenting out the first page being
empty on line 46
\begin{verbatim}
%\thispagestyle{empty}
\end{verbatim}

%-------------------------------------------------------------------------
\subsection{Type-style and fonts}

Wherever Times is specified, Times Roman may also be used. If neither is
available on your word processor, please use the font closest in
appearance to Times to which you have access.

MAIN TITLE. Center the title 1-3/8 inches (3.49 cm) from the top edge of
the first page. The title should be in Times 14-point, boldface type.
Capitalize the first letter of nouns, pronouns, verbs, adjectives, and
adverbs; do not capitalize articles, coordinate conjunctions, or
prepositions (unless the title begins with such a word). Leave two blank
lines after the title.

AUTHOR NAME(s) and AFFILIATION(s) are to be centered beneath the title
and printed in Times 12-point, non-boldface type. This information is to
be followed by two blank lines.

The ABSTRACT and MAIN TEXT are to be in a two-column format.

MAIN TEXT. Type main text in 10-point Times, single-spaced. Do NOT use
double-spacing. All paragraphs should be indented 1 pica (approx. 1/6
inch or 0.422 cm). Make sure your text is fully justified---that is,
flush left and flush right. Please do not place any additional blank
lines between paragraphs.

Figure and table captions should be 9-point Roman type as in
Figures~\ref{fig:onecol} and~\ref{fig:short}.  Short captions should be centred.

\noindent Callouts should be 9-point Helvetica, non-boldface type.
Initially capitalize only the first word of section titles and first-,
second-, and third-order headings.

FIRST-ORDER HEADINGS. (For example, {\large \bf 1. Introduction})
should be Times 12-point boldface, initially capitalized, flush left,
with one blank line before.

SECOND-ORDER HEADINGS. (For example, { \bf 1.1. Database elements})
should be Times 11-point boldface, initially capitalized, flush left,
with one blank line before, and one after. If you require a third-order
heading (we discourage it), use 10-point Times, boldface, initially
capitalized, flush left, preceded by one blank line, followed by a period
and your text on the same line.

%-------------------------------------------------------------------------
\subsection{Footnotes}

Please use footnotes\footnote {This is what a footnote looks like.  It
often distracts the reader from the main flow of the argument.} sparingly.
Indeed, try to avoid footnotes altogether and include necessary peripheral
observations in
the text (within parentheses, if you prefer, as in this sentence).  If you
wish to use a footnote, place it at the bottom of the column on the page on
which it is referenced. Use Times 8-point type, single-spaced.

%-------------------------------------------------------------------------
\subsection{References}

List and number all bibliographical references in 9-point Times,
single-spaced, at the end of your paper. When referenced in the text,
enclose the citation number in square brackets, for
example~\cite{Authors06}.  Where appropriate, include the name(s) of
editors of referenced books.

\begin{table}
\begin{center}
\begin{tabular}{|l|c|}
\hline
Method & Frobnability \\
\hline\hline
Theirs & Frumpy \\
Yours & Frobbly \\
Ours & Makes one's heart Frob\\
\hline
\end{tabular}
\end{center}
\caption{Results.   Ours is better.}
\end{table}

%-------------------------------------------------------------------------
\subsection{Illustrations, graphs, and photographs}

All graphics should be centered.  Please ensure that any point you wish to
make is resolvable in a printed copy of the paper.  Resize fonts in figures
to match the font in the body text, and choose line widths which render
effectively in print.  Many readers (and reviewers), even of an electronic
copy, will choose to print your paper in order to read it.  You cannot
insist that they do otherwise, and therefore must not assume that they can
zoom in to see tiny details on a graphic.

When placing figures in \LaTeX, it's almost always best to use
\verb+\includegraphics+, and to specify the  figure width as a multiple of
the line width as in the example below
{\small\begin{verbatim}
   \usepackage[dvips]{graphicx} ...
   \includegraphics[width=0.8\linewidth]
                   {myfile.eps}
\end{verbatim}
}

%-------------------------------------------------------------------------
\subsection{Color}

Color is valuable, and will be visible to readers of the electronic copy.
However ensure that, when printed on a monochrome printer, no important
information is lost by the conversion to grayscale.

%------------------------------------------------------------------------
\section{Final copy}

You must include your signed IEEE copyright release form when you submit
your finished paper. We MUST have this form before your paper can be
published in the proceedings.

{\small
\bibliographystyle{ieee}
\bibliography{egbib}
}

\end{document}

### 2014-05-26 WACV/egpaper_for_review.tex
Initial Commit

--- 2014-05-26 WACV/egpaper_final.tex
@@
 % run, let it finish, and you should be clear).
-%\usepackage[pagebackref=true,breaklinks=true,letterpaper=true,colorlinks,bookmarks=false]{hyperref}
+\usepackage[pagebackref=true,breaklinks=true,letterpaper=true,colorlinks,bookmarks=false]{hyperref}
 
-\wacvfinalcopy % *** Uncomment this line for the final submission
+%\wacvfinalcopy % *** Uncomment this line for the final submission
 
@@
 % Pages are numbered in submission mode, and unnumbered in camera-ready
-%\ifwacvfinal\pagestyle{empty}\fi
-\setcounter{page}{4321}
+\ifwacvfinal\pagestyle{empty}\fi
 \begin{document}
@@
 First line of institution2 address\\
-{\tt\small secondauthor@i2.org}
+{\small\url{http://www.author.org/~second}}
 }
@@
 \maketitle
-%\thispagestyle{empty}
+% \thispagestyle{empty}
 
@@
 {\bf either a journal} or any conference (including WACV 2014) or any
-workshop.
- {\bf Papers violating this condition will be rejected.}
+workshop.  {\bf Papers violating this condition will be rejected.}
 
@@
 many figures and equations, and, when done, looks ugly.  Just use fractional
-references (e.g.\ this line is $095.5$), although in most cases one would
+references (e.g.\ this line is $097.15$), although in most cases one would
 expect that the approximate location will be adequate.
@@
 an alternative to equation numbers).  All authors will benefit from reading
-Mermin's description of how to write mathematics.%: \url{http://www.wacv.org/doc/mermin.pdf}.
+Mermin's description of how to write mathematics.
 
@@
 
-All printed material, including text, illustrations, and charts, must be kept
-within a print area 6-7/8 inches (17.5 cm) wide by 8-7/8 inches (22.54 cm)
-high.  Page numbers should be in footer with page numbers, centered and .75
-inches from the bottom of the page and make it start at the correct page
-number rather than the 4321 in the example.  To do this fine the line (around
-line 23)
-\begin{verbatim}
-%\ifwacvfinal\pagestyle{empty}\fi
-\setcounter{page}{4321}
-\end{verbatim}
-where the number 4321 is your assigned starting page.
-
-Make sure the first page is numbered by commenting out the first page being
-empty on line 46
-\begin{verbatim}
-%\thispagestyle{empty}
-\end{verbatim}
+All printed material, including text, illustrations, and charts, must be
+kept within a print area 6-7/8 inches (17.5 cm) wide by 8-7/8 inches
+(22.54 cm) high.
 
@@
 should be Times 12-point boldface, initially capitalized, flush left,
-with one blank line before.
+with one blank line before, and one blank line after.
 
@@
 
+Please direct any questions to the production editor in charge of these
+proceedings at the IEEE Computer Society Press: Phone (714) 821-8380, or
+Fax (714) 761-1784.
+
 {\small

### 2014-05-26 WACV/paper.tex
Initial Commit

--- 2014-03-07 ECCV/paper.tex
@@
-% last updated in April 2002 by Antje Endemann
-% Based on CVPR 07 and LNCS, with modifications by DAF, AZ and elle, 2008 and AA, 2010, and CC, 2011
+\documentclass[10pt,twocolumn,letterpaper]{article}
 
-\documentclass[runningheads]{llncs}
+\usepackage{wacv}
+\usepackage{times}
+\usepackage{epsfig}
+\usepackage{amsmath}
+\usepackage{amssymb}
 \usepackage{graphicx}
@@
 \captionsetup{compatibility=false}
-\usepackage{amsmath,amssymb} % define this before the line numbering.
-\usepackage{ruler}
 \usepackage{color}
@@
 \usepackage{comment}
-\usepackage[width=122mm,left=12mm,paperwidth=146mm,height=193mm,top=12mm,paperheight=217mm]{geometry}
 \usepackage{multirow}
@@
 \newcolumntype{Y}{>{\centering\arraybackslash}X}
-\captionsetup[table]{belowskip=12pt,aboveskip=4pt}
-\setlength{\floatsep}{7pt plus 2pt minus 2pt}
-\setlength{\textfloatsep}{5pt plus 2pt minus 2pt}
-\setlength{\intextsep}{7pt plus 2pt minus 2pt}
+% Include other packages here, before hyperref.
 
+% If you comment hyperref and then uncomment it, you should delete
+% egpaper.aux before re-running latex.  (Or just hit 'q' on the first latex
+% run, let it finish, and you should be clear).
+\usepackage[pagebackref=true,breaklinks=true,letterpaper=true,colorlinks,bookmarks=false]{hyperref}
+
+%\wacvfinalcopy % *** Uncomment this line for the final submission
+
+\def\wacvPaperID{****} % *** Enter the wacv Paper ID here
+\def\httilde{\mbox{\tt\raisebox{-.5ex}{\symbol{126}}}}
+
+% Pages are numbered in submission mode, and unnumbered in camera-ready
+\ifwacvfinal\pagestyle{empty}\fi
 \begin{document}
-% \renewcommand\thelinenumber{\color[rgb]{0.2,0.5,0.8}\normalfont\sffamily\scriptsize\arabic{linenumber}\color[rgb]{0,0,0}}
-% \renewcommand\makeLineNumber {\hss\thelinenumber\ \hspace{6mm} \rlap{\hskip\textwidth\ \hspace{6.5mm}\thelinenumber}}
-% \linenumbers \
-
-\pagestyle{headings}
-\mainmatter
-\def\ECCV14SubNumber{150}  % Insert your submission number here
-
-\title{A Motion Blur Resilient Fiducial Marker For Quadcopter Imaging} % Replace
-% with your title
-
-\titlerunning{ECCV-14 submission ID \ECCV14SubNumber}
-
-\authorrunning{ECCV-14 submission ID \ECCV14SubNumber}
-
-\author{Anonymous ECCV submission}
-\institute{Paper ID \ECCV14SubNumber}
-
+\title{A Motion Blur Resilient Fiducial Marker For Quadcopter Imaging}
 \maketitle
@@
 captured with a quadcopter.
-\keywords{Fiducials, tracking, recognition under blur}
 \end{abstract}
@@
 
-\bibliographystyle{splncs}
+{\small
+\bibliographystyle{ieee}
 \bibliography{egbib}
-
+}
 \end{document}

### 2014-05-29 WACV/paper.tex
Two column changes
1. Removed bullets in discussion 2. Added figures for setup

@@
 \centering
- \begin{subfigure}[b]{0.19\textwidth}
+ \begin{subfigure}[b]{0.19\linewidth}
   \centering
@@
  \end{subfigure}\quad
- \begin{subfigure}[b]{0.14\textwidth}
+ \begin{subfigure}[b]{0.14\linewidth}
  \centering
@@
  \end{subfigure}\quad
- \begin{subfigure}[b]{0.14\textwidth}
+ \begin{subfigure}[b]{0.14\linewidth}
   \centering
@@
 
-\noindent\begin{minipage}[h!]{\textwidth}
-\noindent\begin{minipage}{0.6\textwidth}
-\includegraphics[width=\textwidth]{artag_pitag.pdf}
+\noindent\begin{figure}
+\includegraphics[width=\linewidth]{artag_pitag.pdf}
 %\captionof{figure}{Blurred AR Tag and Pi--tag with various blur scales}
-\end{minipage}
-\begin{minipage}{0.35\textwidth}
 %\captionof{table}{Recognition rate of AR Tag and Pi-tag fiducial marker atvarious blur scales}
-\begin{tabularx}{\textwidth}{|Y|Y|Y|}
+\begin{tabularx}{\linewidth}{|Y|Y|Y|}
 \cline{1-3}
@@
 \end{tabularx}
-\end{minipage}
 \captionof{figure}{Figure showing PiTag and ARTag blurred with various blur
@@
 \label{fig:artag_pitag}
-\end{minipage}
+\end{figure}
 
@@
 Source code to generate and recognize the code, as well as the data sets used in
-this paper will be made publicly available.  Video clips
-of collected data are provided in the supplementary material.
+this paper will be made publicly available.  
+%Video clips of collected data are provided in the supplementary material.
 
@@
 patterns. Sample output for each fiducial pattern is shown in Figure
-\ref{fig:out_outputs}-(a) -- Figure \ref{fig:out_outputs}-(d). Our detection
-process takes around 0.3 seconds which translates to slightly over three frames per second.
+\ref{fig:out_outputs}. Our detection process takes around 0.3 seconds which
+translates to slightly over three frames per second.
 
@@
 well as correctly classified them as shown in Figure \ref{fig:output_all}.
+
+\begin{figure}[hb!]
+\centering
+  \includegraphics[width=0.4\linewidth]{output_00.jpg}
+  \includegraphics[width=0.4\linewidth]{output_01.jpg}
+  \includegraphics[width=0.4\linewidth]{output_10.jpg}
+  \includegraphics[width=0.4\linewidth]{output_11.jpg}
+  \caption{Sample outputs for two bit binary coded fiducials on different
+  datasets. Class label attached to the detected fiducial is decimal equivalent
+  of the binary code embedded in the detected fiducial.}
+  \label{fig:out_outputs}
+\end{figure}
 
@@
 
-\noindent\begin{figure}
+\noindent\begin{figure*}
 \begin{tabular}{c|c}
@@
 \label{fig:simulated_blur}
-\end{figure}
+\end{figure*}
 
@@
 
-\begin{figure}[hb!]
-\begin{subfigure}{\textwidth}
-\centering
-  \includegraphics[width=0.4\linewidth]{output_00.jpg}
-  \includegraphics[width=0.4\linewidth]{new_results/output_00.jpg}
-  \caption{Binary code ``00''}
-  \label{fig:output0}
-\end{subfigure}
-\begin{subfigure}{\textwidth}
-\centering
-  \includegraphics[width=0.4\linewidth]{output_01.jpg}
-  \includegraphics[width=0.4\linewidth]{new_results/output_01.jpg}
-  \caption{Binary code ``01''}
-  \label{fig:output1}
-\end{subfigure}
-\begin{subfigure}{\textwidth}
-\centering
-  \includegraphics[width=0.4\linewidth]{output_10.jpg}
-  \includegraphics[width=0.4\linewidth]{new_results/output_10.jpg}
-  \caption{Binary code ``10''}
-  \label{fig:output2}
-\end{subfigure}
-\begin{subfigure}{\textwidth}
-\centering
-  \includegraphics[width=0.4\linewidth]{output_11.jpg}
-  \includegraphics[width=0.4\linewidth]{new_results/output_11.jpg}
-  \caption{Binary code ``11''}
-  \label{fig:output3}
-  \end{subfigure}
-  \caption{Sample outputs for two bit binary coded fiducials on different
-  datasets. Class label attached to the detected fiducial is decimal equivalent
-  of the binary code embedded in the detected fiducial.}
-  \label{fig:out_outputs}
-\end{figure}
-
-\begin{table}[h!]
+\begin{table}[t!]
 \caption{Comparison of recognition rate of ARTag and our fiducials on real
@@
 \centering
-\begin{tabularx}{\textwidth}{|c|Y|Y|Y|Y|}
+\begin{tabularx}{\linewidth}{|c|Y|Y|Y|Y|}
 \cline{1-5}
-\multirow{2}{*}{Test \#} & \multirow{2}{*}{Number of Frames}
-&\multirow{2}{*}{Binary Code} &\multicolumn{2}{c|}{Recognition Rate (\%)} \\
+\multirow{2}{*}{Test \#} & {Number of frames}
+&{Binary Code} &\multicolumn{2}{c|}{Recognition Rate (\%)} \\
 \cline{4-5} & & & ARTag & Our Fiducial \\\cline{1-5}
@@
 
+In another setup we arranged our fiducials on four sides of a box and revolved
+quadcopter around it. Later, we repeated the process by replacing our fiducial
+by AR Tags. Some intermediate frames are shown in Figure \ref{fig:setup}.
+
+\begin{figure*}
+\begin{subfigure}[b]{.19\textwidth}
+\includegraphics[width=\linewidth]{setup_our/output_6/output_514.jpg}
+\end{subfigure}
+\begin{subfigure}[b]{.19\textwidth}
+\includegraphics[width=\linewidth]{setup_our/output_6/output_556.jpg}
+\end{subfigure}
+\begin{subfigure}[b]{.19\textwidth}
+\includegraphics[width=\linewidth]{setup_our/output_2/output_35.jpg}
+\end{subfigure}
+\begin{subfigure}[b]{.19\textwidth}
+\includegraphics[width=\linewidth]{setup_our/output_2/output_330.jpg}
+\end{subfigure}
+\begin{subfigure}[b]{.19\textwidth}
+\includegraphics[width=\linewidth]{setup_our/output_6/output_943.jpg}
+\end{subfigure}
+\caption{Figure showing intermediate frames captured by quadcopter while
+revolving around our setup}
+\label{fig:setup}
+\end{figure*}
 \subsubsection{Comparison with BLUT}
@@
 
-\begin{figure}
+\begin{figure*}
 \begin{subfigure}[b]{.19\textwidth}
@@
 \label{fig:BLUT_compare_00}
-\end{figure}
+\end{figure*}
 
-\begin{figure}
+\begin{figure*}
 \begin{subfigure}[b]{.19\textwidth}
@@
 \label{fig:BLUT_compare_01}
-\end{figure}
+\end{figure*}
 
-\begin{figure}
+\begin{figure*}
 \begin{subfigure}[b]{.19\textwidth}
@@
 \label{fig:BLUT_compare_10}
-\end{figure}
+\end{figure*}
 
-\begin{figure}
+\begin{figure*}
 \begin{subfigure}[b]{.19\textwidth}
@@
 \label{fig:BLUT_compare_11}
-\end{figure}
+\end{figure*}
 
@@
 approximately 86-95\% recognition rate on fiducals in real scenes compared to existing codes
-that are around 64\%.  We discuss some limitations of our approach in the following.
-
-\noindent\textbf{Processing Time}~~Currently, our processing time (0.3 seconds
-per frame) does not provide real-time performance.  As such, we currently
-envision this will be used in an offline manner for performing analysis of
-flight paths. Code profiling revealed that the Gabor filtering along the eight
+that are around 64\%.  We discuss some limitations of our approach in the
+section.
+%\noindent\textbf{Processing Time}~~
+Currently, our processing time (0.3 seconds per frame) does not provide
+real-time performance.  As such, we currently envision this will be used in an
+offline manner for performing analysis of flight paths. Code profiling revealed that the Gabor filtering along the eight
 directions takes most of the time (0.03 -- 0.04 seconds per orientation).  Either an
@@
 detection is required.
-
-\noindent\textbf{False Negatives}~~We found that sometimes our detection
+%\noindent\textbf{False Negatives}~~
+We found that sometimes our detection
 algorithm fails to recognize our fiducial with binary code ``00'' when there is
@@
 reduce the effect of blur on the innermost ring. 
-
-\noindent\textbf{Pose Estimation}~~We note that other markers are able to give
+%\noindent\textbf{Pose Estimation}~~
+We note that other markers are able to give
 full pose estimation after detection.  However, we are only able to reliably detect
@@
 effectively use multiple markers in each scene.
-
-\noindent\textbf{Number of Fiducials}~~Currently, compared to ARTag fiducial
-markers, we are able to generate less number of fiducials. Many applications in
-robotics (e.g. quadcopter navigation) may not require large number of fiducial
-markers as available by ARTag.  Most of the time, it is sufficient to have 4-6
-different fiducial patterns. Still, we may be able to generate a larger number of
-fiducials by using color backgrounds. This is an area interest for further
-investigation.
+%\noindent\textbf{Number of Fiducials}~~
+Currently, compared to ARTag fiducial markers, we are able to generate less
+number of fiducials. Many applications in robotics (e.g. quadcopter navigation)
+may not require large number of fiducial markers as available by ARTag.  Most
+of the time, it is sufficient to have 4-6 different fiducial patterns. Still,
+we may be able to generate a larger number of fiducials by using color
+backgrounds. This is an area interest for further investigation.
 

### 2014-05-30 WACV/paper.tex
1. Added Comparison on new setup 2. Commented some result on BLUT

@@
 
-\def\wacvPaperID{****} % *** Enter the wacv Paper ID here
+\def\wacvPaperID{1} % *** Enter the wacv Paper ID here
 \def\httilde{\mbox{\tt\raisebox{-.5ex}{\symbol{126}}}}
@@
 \centering
- \begin{subfigure}[b]{0.19\linewidth}
+ \begin{subfigure}[b]{0.23\linewidth}
   \centering
@@
  \end{subfigure}\quad
- \begin{subfigure}[b]{0.14\linewidth}
+ \begin{subfigure}[b]{0.12\linewidth}
   \centering
@@
 \includegraphics[width=\linewidth]{artag_pitag.pdf}
-%\captionof{figure}{Blurred AR Tag and Pi--tag with various blur scales}
-%\captionof{table}{Recognition rate of AR Tag and Pi-tag fiducial marker atvarious blur scales}
+%\captionof{figure}{Blurred ARTag and Pi--tag with various blur scales}
+%\captionof{table}{Recognition rate of ARTag and Pi-tag fiducial marker atvarious blur scales}
 \begin{tabularx}{\linewidth}{|Y|Y|Y|}
@@
 
+\begin{comment}
 We are able to find the number of rings in the fiducial by finding
@@
 can classify the pattern as class 0 or the maximum class containing all 1s.
+\end{comment}
 
@@
 quadcopter around it. Later, we repeated the process by replacing our fiducial
-by AR Tags. Some intermediate frames are shown in Figure \ref{fig:setup}.
+by ARTags. Some intermediate frames are shown in Figure \ref{fig:setup}.
 
 \begin{figure*}
+\begin{subfigure}[b]{.19\textwidth}
+\includegraphics[width=\linewidth]{setup_artag/output_79.jpg}
+\end{subfigure}
+\begin{subfigure}[b]{.19\textwidth}
+\includegraphics[width=\linewidth]{setup_artag/output_150.jpg}
+\end{subfigure}
+\begin{subfigure}[b]{.19\textwidth}
+\includegraphics[width=\linewidth]{setup_artag/output_194.jpg}
+\end{subfigure}
+\begin{subfigure}[b]{.19\textwidth}
+\includegraphics[width=\linewidth]{setup_artag/output_339.jpg}
+\end{subfigure}
+\begin{subfigure}[b]{.19\textwidth}
+\includegraphics[width=\linewidth]{setup_artag/output_480.jpg}
+\end{subfigure}\\
 \begin{subfigure}[b]{.19\textwidth}
@@
 \begin{subfigure}[b]{.19\textwidth}
-\includegraphics[width=\linewidth]{setup_our/output_6/output_556.jpg}
+\includegraphics[width=\linewidth]{setup_our/output_2/output_64.jpg}
 \end{subfigure}
@@
 \includegraphics[width=\linewidth]{setup_our/output_6/output_943.jpg}
+\end{subfigure}\\
+\begin{subfigure}[b]{\textwidth}
+\includegraphics[width=\linewidth]{compare_detection.jpg}
 \end{subfigure}
-\caption{Figure showing intermediate frames captured by quadcopter while
-revolving around our setup}
+\caption{Figure showing comparison of detection of ARTag versus our fiducial
+when quadcopter is revolving around our setup.
+Top row shows ARTags are not getting detected while middle row shows in
+similar condition our tags are getting detected. Overall detection rate of our
+tags is 90\% while that of ARTags is around 60\%. In bottom, comparison of
+detection of two type of tags over time is shown. We can see that ARTag is
+``chopped off'' frequently while our tag is detected continuously.}
 \label{fig:setup}
 \end{figure*}
+
 \subsubsection{Comparison with BLUT}
@@
 From the images in the top rows of Figure
-\ref{fig:BLUT_compare_00}-\ref{fig:BLUT_compare_11}, we can see that BLUT is
+\ref{fig:BLUT_compare_00} and \ref{fig:BLUT_compare_01}, we can see that BLUT is
 able to track the fiducial when the position of fiducial does not change too
@@
 code in each frame, large changes in the patterns position is not an issue.
-Our detection results are also shown in Figure
-\ref{fig:BLUT_compare_00}-\ref{fig:BLUT_compare_11}.
+Some of our detection results are also shown in Figure
+\ref{fig:BLUT_compare_00} and \ref{fig:BLUT_compare_01}. (Results on other two
+tags are shown in supplementary material.)
 
@@
 
+\begin{comment}
 \begin{figure*}
@@
 \end{figure*}
+\end{comment}
 
@@
 real-time performance.  As such, we currently envision this will be used in an
-offline manner for performing analysis of flight paths. Code profiling revealed that the Gabor filtering along the eight
-directions takes most of the time (0.03 -- 0.04 seconds per orientation).  Either an
-improved Gabor filter scheme is required or an alternative strategy for
-detection is required.
+offline manner for performing analysis of flight paths. Code profiling revealed
+that the Gabor filtering along the eight directions takes most of the time
+(0.03 -- 0.04 seconds per orientation).  Either an improved Gabor filter scheme
+is required or an alternative strategy for detection is required.
 %\noindent\textbf{False Negatives}~~
@@
 we may be able to generate a larger number of fiducials by using color
-backgrounds. This is an area interest for further investigation.
+backgrounds. This is an area of interest for further investigation.
 

### 2014-06-03 WACV/paper.tex
Enlarged overall_flow.jpg, compressed tables

@@
 \newcolumntype{Y}{>{\centering\arraybackslash}X}
+\setlength{\floatsep}{7pt plus 2pt minus 2pt}
+\setlength{\textfloatsep}{5pt plus 2pt minus 2pt}
+\setlength{\intextsep}{5pt plus 2pt minus 2pt}
 % Include other packages here, before hyperref.
@@
 on the observation that motion blur from a quadcopter tends to be linear in
-nature. As such, when our code is blurred, there is no blur in the direction
+nature. As such, when our fiducial is blurred, there is no blur in the direction
 perpendicular to the direction of motion.  This allows the signature of the
@@
 \caption{This figure shows the experimental setup and comparison of
-output of ALVAR~\cite{alvar} (for detecting ARTag) versus our blur resistant
+the output of ALVAR~\cite{alvar} (for detecting ARTag) versus our blur resistant
 fiducial in a normal and blurred video frame. The scene contains two ARTags and our code.
@@
 reality (AR) applications. Kato and Billinghurst~\cite{kato-artoolkit}
-demonstrated the use of ARToolkit to find the pose in video based AR
-conferencing system.
+first demonstrated the use of ARToolkit in various augmented-reality-based applications.
 
@@
 bi-tonal system consisting of a square border and an interior 6$\times$6 grid
-of black or white cells. The improvement in ARTag compared to ARToolkit was
+of black or white cells. The improvement of the ARTag compared to the ARToolkit was
 detection of corners instead of detection of lines to find possible pattern.
@@
 recognition rate as well as the number of different patterns which can be
-created.   The reliance on both line and corner detection hampers recognition
+created.   The reliance on both line and corner detection, however, hampers recognition
 under motion blur.
@@
 frames can be considered as a tracking problem where the tracked object is
-fiducial itself.  There is a very large body of research dedicated to tracking and interested
-readers are referred to~\cite{Yilmaz:2006} for a good survey.
+the fiducial.  There is a very large body of research dedicated to tracking and interested readers are referred to~\cite{Yilmaz:2006} for a good survey.
 
@@
 proposed the Blur-driven Tracker (BLUT) framework for tracking motion-blurred targets. BLUT
-is based on the observation that although motion blurs degrade the visual
-features of the target, they at the same time, provide useful cues about the
+is based on the observation that although motion blur degrades the visual
+features of the target, it may also provide useful cues about the
 movements to help tracking.
 
-The BLUT framework successfully tracks blurred target when there is uniform motion
-and the position of tracked object does not change drastically in successive
-frames. But as we will demonstrate in Section 4, the erratic motion from quadcopters as
-well as the problem of dropped video frames is beyond the current ability of such trackers.
+The BLUT framework successfully tracks a blurred target when there is uniform motion
+and the position of the tracked object does not change drastically in successive
+frames. However, as we will demonstrate in Section 4, the erratic motion from the quadcopters as well as the problem of dropped video frames is too problematic to be successively tracked.
 
@@
 
-Before we detail the design of our fiducial, we examine the performance of two
+Here we examine the the performance of two
 popular fiducials under motion blur.  Specifically we examine ARTags
-~\cite{Fiala05} and PiTags~\cite{Pitag13} given their difference in geometry
+~\cite{Fiala05} and PiTags~\cite{Pitag13} given their difference in geometric
 design and the availability of API to develop applications to recognize the tags.
 RUNE-tag~\cite{runetag11} currently does not provide access to the an
-implementation to generate or recognize the tag.  The circular data
+implementation to generate or recognize its tags.  The circular data
 matrix~\cite{NaimarkF02} is available as a commercial product, however it
@@
 \centering
-  \includegraphics[width=.18\linewidth]{newconcentric_00.pdf}
-  \includegraphics[width=.18\linewidth]{newconcentric_01.pdf}
-  \includegraphics[width=.18\linewidth]{newconcentric_10.pdf}
-  \includegraphics[width=.18\linewidth]{newconcentric_11.pdf}
+  \includegraphics[width=.24\linewidth]{newconcentric_00.pdf}
+  \includegraphics[width=.24\linewidth]{newconcentric_01.pdf}
+  \includegraphics[width=.24\linewidth]{newconcentric_10.pdf}
+  \includegraphics[width=.24\linewidth]{newconcentric_11.pdf}
   \caption{Two bit binary coded fiducials (from left to right: binary code 00,
@@
 maximum of three rings between marker-rings and we end up with eight
-different patterns.  Figure \ref{fig:fiducials} shows a two bit binary coded
+different patterns.  Figure \ref{fig:fiducials} shows two bit binary coded
 fiducials.
@@
 \centering
-\includegraphics[width=0.8\linewidth]{blur_direction.pdf}
+\includegraphics[width=\linewidth]{blur_direction.pdf}
 \caption{Figure showing how change in blur direction changes the location of
@@
 
-\begin{figure}[ht!]
-\includegraphics[width=\linewidth]{overall_flow.pdf}
+\begin{figure*}[ht!]
+\centering
+\includegraphics[width=0.8\linewidth]{overall_flow.pdf}
 \caption{An overview of our algorithm to detect and classify fiducial.
@@
 \label{fig:overall_flow}
-\end{figure}
+\end{figure*}
 
@@
 projecting the pixel intensities onto the PCA direction and record the
-number and width of transitions.  If the number of transitions or the
-width of the transitions is not consistent with what is allowable by
+number and width of the white-to-black transitions.  If the number of transitions or the
+width of the transitions are not consistent with what is allowable by
 our code, we reject the clustered region as a potential fiducial.
@@
 \centering
-  \includegraphics[width=0.8\linewidth]{training_data.pdf}
+  \includegraphics[width=0.95\linewidth]{training_data.pdf}
   \caption{Process to create training data for the fiducial pattern with binary
@@
 \noindent\begin{figure*}
+\centering
 \begin{tabular}{c|c}
-\begin{subfigure}[b]{0.65\linewidth}
+\begin{subfigure}[b]{0.45\linewidth}
+\centering
 \includegraphics[width=\linewidth]{recognition_rate.pdf}
@@
 &
-\begin{subfigure}[b]{0.33\linewidth}
+\begin{subfigure}[b]{0.25\linewidth}
+\centering
 \begin{tabularx}{\textwidth}{|c|Y|}
@@
 \cline{1-5}
-\multirow{2}{*}{Test \#} & {Number of frames}
-&{Binary Code} &\multicolumn{2}{c|}{Recognition Rate (\%)} \\
-\cline{4-5} & & & ARTag & Our Fiducial \\\cline{1-5}
+\multirow{2}{*}{Test \#} & {Number}
+&{Binary} &\multicolumn{2}{c|}{Recognition Rate (\%)} \\
+\cline{4-5} & {of frames}& {Code}& ARTag & Our Fiducial \\\cline{1-5}
 1 & 1205 & 00 &  65.6 & 86.5  \\ \cline{1-5}
@@
 In another setup we arranged our fiducials on four sides of a box and revolved
-quadcopter around it. Later, we repeated the process by replacing our fiducial
-by ARTags. Some intermediate frames are shown in Figure \ref{fig:setup}.
+the quadcopter around the box. Later, we repeated the process by replacing our fiducial
+by ARTags. Figure \ref{fig:setup} some frames from this sequence as well as the performance of both fiducials. The overall detection rate of our tags is 90\% while that of ARTags is only around 60\%.
 
@@
 Some of our detection results are also shown in Figure
-\ref{fig:BLUT_compare_00} and \ref{fig:BLUT_compare_01}. (Results on other two
-tags are shown in supplementary material.)
+\ref{fig:BLUT_compare_00} and \ref{fig:BLUT_compare_01}.
 
@@
 %\noindent\textbf{Processing Time}~~
-Currently, our processing time (0.3 seconds per frame) does not provide
-real-time performance.  As such, we currently envision this will be used in an
+Our  current processing time (0.3 seconds per frame) does not provide
+real-time performance.  As such, we envision this will be used in an
 offline manner for performing analysis of flight paths. Code profiling revealed

### 2014-06-09 WACV/paper.tex
Actually deleted files from Git

@@
 \begin{abstract}
-This paper describes the design and evaluation of a binary fiducial marker
-for use with low-cost quadcopters.  Fiducial markers are commonly placed
-in environments to provide a uniquely identifiable object in the scene.
-For quadcopter applications, fiducials are often used for evaluating planning
-algorithms by allowing ground truth positions in the scene to be detected from
-the quadcopter's camera. Quadcopters, however, are subject to quick and
-unstable motions that can cause significant motion blur that severely affects
-the detection rate of existing fiducial markers. This problem motivated us to
-design a fiducial that is robust to motion blur. Our proposed fiducial design
-uses concentric circles with the observation that the direction perpendicular
-to the motion blur direction will be relatively unaffected by the blur. This
-allows the fiducial code along the blur direction to be recognized.
-The circular design allows this to work for all motion blur directions. We
-detail the design and detection algorithm for our fiducial and show that our
-marker can significantly outperform existing fiducial markers in scenes
-captured with a quadcopter.
+
+  Fiducial markers are commonly placed in environments to provide a
+  uniquely identifiable object in the scene.  In quadcopter
+  applications, these fiducials are often used to evaluate planning
+  algorithms given that ground truth positions can be
+  detected from the quadcopter's camera.
+
+  Low cost quadcopters, however, are subject to quick and unstable
+  motions that can cause significant motion blur that severely affects
+  the detection rate of existing fiducial markers. This problem
+  motivated us to design a fiducial that is robust to motion blur. Our
+  proposed design uses concentric circles with the observation that
+  the direction perpendicular to the motion blur direction will be
+  relatively unaffected by the blur. As a result, an appropriate
+  fiducial code orthogonal to the blur direction can be
+  recognized. Since the direction of motion blur is unknown, the
+  circular design is good for all motion blur directions. We describe
+  the design of binary fiducial markers, and also a detection
+  algorithm.  We show that our marker can significantly outperform
+  existing fiducial markers in scenes captured with a quadcopter.
+
 \end{abstract}
@@
 
-The recent availability of low-cost quadcopters have helped to fuel significant
-efforts in research focused on unmanned aerial vehicles. Navigation and planning of
-these vehicles is typically performed using onboard inertial sensors and/or
-vision based modules that uses visual cues in the real world~(e.g.,
-\cite{Davison:2007,Engel12,Engel13}). However, to evaluate the effectiveness of
-navigation methods, fiducial markers are commonly placed into the environment
-to provide additional information that serves for ground-truth positional
-measurements (e.g., \cite{Bosnak:2012,Lim09,Klopschitz:2007}).
+The recent availability of low-cost quadcopters has helped  fuel
+significant efforts in research focused on unmanned aerial
+vehicles. Navigation and planning
+of these vehicles is typically~\cite{Davison:2007,Engel12,Engel13}
+performed using onboard inertial sensors and/or vision based modules
+that uses visual cues in the real world. However, to evaluate the
+effectiveness of navigation methods, one or more fiducial markers are commonly
+placed~\cite{Bosnak:2012,Lim09,Klopschitz:2007}
+ in the environment to provide additional information that
+serves for ground-truth positional measurements.
 
 In order to be effective, fiducial markers (or simply, fiducials) need
-to be easily detected in the scene. A variety of fiducial markers
-have been proposed in the literature
-(e.g.,~\cite{NaimarkF02,ARToolkit02,Fiala05,Pitag13,runetag11}).
-These take the form of binary codes arranged into rectangular grids (\cite{ARToolkit02,Fiala05})
-or other geometric primitives arranged in predefined spatial patterns
-(\cite{NaimarkF02,Pitag13,runetag11}).
-Figure \ref{fig:teaser}-(a) shows the popular ARTag \cite{Fiala05} as
-seen from a quadcopter. A problem for existing fiducials is that low-cost quadcopters
-often exhibit very quick and erratic physical movements that
-result in motion blur in the quadcopter's onboard camera. This motion blur has
-an adverse effect on the recognition of fiducial markers. This can be seen in
-Figure \ref{fig:teaser}-(b) where the ARTag cannot be recognized due to motion
-blur. This is not too surprising as most existing fiducials are not
-designed to handle motion blur.
+to be easily detected in the scene. A variety of fiducial markers have
+been proposed~\cite{NaimarkF02,ARToolkit02,Fiala05,Pitag13,runetag11}
+in the literature.  These take the form of binary codes arranged into
+rectangular grids~\cite{ARToolkit02,Fiala05} or other geometric
+primitives arranged in predefined spatial
+patterns~\cite{NaimarkF02,Pitag13,runetag11}.  Figure \ref{fig:teaser}
+shows the popular ARTag \cite{Fiala05} fiducial as possibly seen from
+a quadcopter. A problem for existing fiducials is that low-cost
+quadcopters often exhibit very quick and erratic physical movements
+that result in motion blur in the quadcopter's onboard camera. This
+motion blur has an adverse effect on the recognition of fiducial
+markers. This can be seen in Figure \ref{fig:teaser}--(b) where the
+ARTag fiducial cannot be recognized due to motion blur. This is not
+too surprising as most existing fiducials are not designed to handle
+motion blur.
 
-Compounding this problem is the additional issue of dropped video frames from
-the quadcopter's wireless communication module. This means that not only is
-blur a problem, but there may be large discontinuities in the pattern's
-position due to missing video frames. As we will show in Section 4, this later problem
-makes it challenging to apply tracking algorithms that can exploit temporal
+Compounding this problem is the additional issue of dropped video
+frames from the quadcopter's wireless communication module. This means
+that not only is blur a problem, but there may be large
+discontinuities in the pattern's position due to missing video
+frames. As we will show in Section~4, this later problem makes it
+challenging to apply tracking algorithms that can exploit temporal
 coherence for determining the fiducial's position.
 
-\noindent\textbf{Contribution}~~To address these problems, we propose a
-fiducial that is designed to be resistant to motion blur. Our design is based on
-concentric circles as shown in Figure \ref{fig:teaser}-(c,d). The design is based
-on the observation that motion blur from a quadcopter tends to be linear in
-nature. As such, when our fiducial is blurred, there is no blur in the direction
-perpendicular to the direction of motion.  This allows the signature of the
-fiducial to remain intact in any direction. In addition, by using concentric
-rings, we can treat the presence or absence of a ring as a bit, allowing us to
-assign a code to the marker. Our experiments show that this design can
-significantly outperform existing codes in the presence of motion blur. As far
-as we are aware, this is the first work to propose a blur resistant marker.
+\noindent\textbf{Contributions:}~~To address these problems, we propose a
+fiducial that is designed to be resistant to motion blur. Our design
+is based on circles as shown in Figure~\ref{fig:teaser}--(c,d). The
+design is based on the observation that motion blur from a quadcopter
+tends to be linear in nature. As such, when our fiducial is blurred,
+there is no blur in the direction perpendicular to the direction of
+motion.  This allows the signature of the fiducial to remain intact in
+any direction.
 
-The remainder of this paper is organized as follows.  Section 2 gives an
-overview of related work related to fiducials as well as the related problem of
-tracking. Section 3 discusses our design and detection algorithm as well as
-the performance of existing codes under motion blur. Section 4 shows several
-experiments using quadcopter imagery. This is followed by a discussion and
-summary in Section 5 and 6 respectively.
+When multiple fiducials are present, using concentric rings, we can
+treat the presence or absence of a ring as a bit, allowing us to
+assign a code to the marker. Our experiments show that these designs can
+significantly outperform existing codes in the presence of motion
+blur. As far as we are aware, this is the first work to propose a blur
+resistant marker especially in quadcopter settings.
 
-\begin{figure}
-\includegraphics[width=\linewidth]{teaser.pdf}
-\caption{This figure shows the experimental setup and comparison of
-the output of ALVAR~\cite{alvar} (for detecting ARTag) versus our blur resistant
-fiducial in a normal and blurred video frame. The scene contains two ARTags and our code.
-(a) shows that the ARTag can be detected when the image has no blur.
-(b) shows that ARTags are no longer detectable due to the blur.
-(c-d) show the same images in (a) and (b) where our code is being detected.}
-\label{fig:teaser}
+The remainder of this paper is organized as follows.  Section~2 gives
+an overview of related work in fiducials, as well as the related
+problem of tracking. Section~3 motivates our fiducial design by
+analysing the performance of existing codes under motion blur, and
+describes our detection algorithm. Section~4 shows several
+experiments using quadcopter imagery. This is followed by a discussion
+and a summary in Section~5 and Section~6 respectively.
+
+\begin{figure}[t!]
+  \includegraphics[width=\linewidth]{images/teaser}
+  \caption{Experimental setup and comparison of fiducial-based
+    algorithms. A green border signifies success. 
+    \textbf{(Left)} A drone encounters three different fiducials. 
+    \textbf{(Right, Top)} Output of ALVAR~\cite{alvar} under favorable and blurred
+    circumstances. No green border is seen in (b) signifying failure.
+    \textbf{(Right, Bottom)} Output of the fiducial proposed in this paper. Green
+    border is seen in both (c) and (d).
+    \label{fig:teaser}}
   \end{figure}
@@
 
-\begin{figure}
+\textbf{Fiducials:}~Figure~\ref{fig:previous_work} shows a few
+examples of existing fiducial markers.  Many designs use a two
+dimensional barcode inside a rectangular grid. One example of such a
+fiducial is from the ARToolkit~\cite{ARToolkit02}, a well known
+toolkit used in many augmented reality (AR) applications. Kato and
+Billinghurst~\cite{kato-artoolkit} first demonstrated the use of
+ARToolkit in various augmented-reality-based applications.
+
+\begin{figure}[b!]
 \centering
@@
   \centering
-  \includegraphics[width=0.8\linewidth]{intersense.jpg}
+  \includegraphics[width=0.8\linewidth]{images/intersense.jpg}
   Circular Data Matrix~\cite{NaimarkF02}
@@
  \centering
-  \includegraphics[width=\linewidth]{pattKanji.pdf}
+  \includegraphics[width=\linewidth]{images/pattKanji.pdf}
   ARToolkit~\cite{ARToolkit02}
@@
   \centering
-  \includegraphics[width=\linewidth]{ARtag.jpg}
+  \includegraphics[width=\linewidth]{images/ARtag.jpg}
   ARTag\quad~\cite{Fiala05}
@@
   \centering
-  \includegraphics[width=\linewidth]{pifiducial.jpg}
+  \includegraphics[width=\linewidth]{images/pifiducial.jpg}
   PiTag\quad~\cite{Pitag13}
@@
   \centering
-  \includegraphics[width=\linewidth]{our_fiducial}
+  \includegraphics[width=\linewidth]{images/our_fiducial}
   Our Fiducial
  \end{subfigure}
- \caption{This figure shows the design of several existing fiducial markers.  While
- each code has their own pros and cons for various environments, none are
- designed to be recognized under motion blur.}
+ \caption{Prior fiducial markers and our proposal.  While
+ each code has its pros and cons depending on the environment, no
+ prior code is expressly designed to be recognized under motion blur.}
  \label{fig:previous_work}
@@
 
-\noindent{\textbf{Fiducials}}~Figure~\ref{fig:previous_work} shows several
-examples of existing fiducial markers.  Many designs use a two dimensional
-barcode inside a rectangular grid. One example of such a fiducial is from the
-ARToolkit~\cite{ARToolkit02}, a well known toolkit used in many augmented
-reality (AR) applications. Kato and Billinghurst~\cite{kato-artoolkit}
-first demonstrated the use of ARToolkit in various augmented-reality-based applications.
+Fiala~\cite{Fiala05} proposed a fiducial termed, ARTag, which is a
+bi-tonal system consisting of a square border and an interior
+6$\times$6 grid of black or white cells. The improvement of the ARTag
+compared to the ARToolkit lies in the detection of corners instead of
+detection of lines to find possible patterns.  This proved to be more
+efficient than \cite{ARToolkit02} in terms of recognition rate as well
+as the number of different patterns which can be created.  {\it The
+reliance on both line and corner detection, however, hampers
+recognition under motion blur.}
 
-Fiala~\cite{Fiala05} proposed a fiducial termed, ARTag, which is a
-bi-tonal system consisting of a square border and an interior 6$\times$6 grid
-of black or white cells. The improvement of the ARTag compared to the ARToolkit was
-detection of corners instead of detection of lines to find possible pattern.
-This proved to be more efficient than \cite{ARToolkit02} in terms of
-recognition rate as well as the number of different patterns which can be
-created.   The reliance on both line and corner detection, however, hampers recognition
-under motion blur.
-
-There were also attempts to use circular patterns instead of rectangular.
-Gatrell et al.~\cite{concentric} used concentric circles
-for monocular pose estimation as well as object identification. Cho et al.
-\cite{Cho:2001,Cho97fastcolor} have used multicolor rings instead of black and white rings~\cite{concentric} to increase possible number of fiducials.
-These multicolor rings are used in wide area tracking in large scale
-applications.  While based on a concentric rings, these approaches require
-the full ring to be recognized which is not possible when the pattern undergoes directional
-motion blur.
+There were also attempts to use circular patterns instead of
+rectangular.  Gatrell et al.~\cite{concentric} used concentric circles
+for monocular pose estimation as well as object identification. Cho et
+al.~\cite{Cho:2001,Cho97fastcolor} have used multicolor rings instead
+of black and white rings~\cite{concentric} to increase possible number
+of fiducials.  These multicolor rings are used in wide area tracking
+in large scale applications.  {\it Although based on  concentric rings, these
+approaches require the complete ring to be recognized; this is
+impractical when the pattern undergoes directional motion blur.}
 
 Naimark and Foxlin~\cite{NaimarkF02} proposed a circular bar code
-called the Circular Data Matrix that is beneficial in terms of
-easy detection and ability to have a large number
-of uniquely identifiable codes.  To address the issue of occlusion,
-Bergamasco et al.~\cite{runetag11} proposed the RUNE-tag fiducial by dividing
-into number of circular dots arranged in circular fashion. RUNE-tags can be
-detected even when up to 50\% of fiducial area is occluded. Bergamasco et
-al.~\cite{Pitag13} proposed the PiTag fiducial, also composed of circular
-structures but arranged in a rectangle to exploit projective invariant cross-ratio.
-This provided similar occlusion resistance as RUNE-tag but with even less
-circular dots. All of these techniques however rely on generic features
-detection (e.g., circle detection) that break down under motion blur.
+called the Circular Data Matrix that is beneficial in terms of easy
+detection and ability to have a large number of uniquely identifiable
+codes.  To address the issue of occlusion, Bergamasco et
+al.~\cite{runetag11} proposed the RUNE-tag fiducial by creating a
+number of circular dots arranged in circular fashion. RUNE-tags can be
+detected even when 50\% of the fiducial area is occluded. Bergamasco
+et al.~\cite{Pitag13} proposed the PiTag fiducial, also composed of
+circular structures but arranged in a rectangle, to exploit projective
+invariant cross-ratio.  This provided similar occlusion resistance as
+RUNE-tag but with even less circular dots. {\it All of these techniques,
+however, rely on generic feature detection (e.g., circle detection)
+and such algorithms break down under motion blur.}
 
@@
 
-\noindent{\textbf{Tracking}}~~Fiducial detection between successive video
-frames can be considered as a tracking problem where the tracked object is
-the fiducial.  There is a very large body of research dedicated to tracking and interested readers are referred to~\cite{Yilmaz:2006} for a good survey.
+{\textbf{Tracking}}~~Fiducial detection between successive video
+frames can be considered as a tracking problem where the tracked
+object is the fiducial.  There is a very large body of research
+dedicated to tracking and interested readers are referred
+to~\cite{Yilmaz:2006} for a good survey.
 
-Most tracking methods (e.g.,~\cite{Ross:2008,Wu:2009,Perez02,Mei:2009}) assume
-the image sequence to be blur free. In reality, however, the presence of motion blur in
-a video sequence is often unavoidable. To this end, Wu et al.~\cite{Wu:2011}
-proposed the Blur-driven Tracker (BLUT) framework for tracking motion-blurred targets. BLUT
-is based on the observation that although motion blur degrades the visual
-features of the target, it may also provide useful cues about the
-movements to help tracking.
+Most tracking methods~\cite{Ross:2008,Wu:2009,Perez02,Mei:2009} assume
+the image sequence to be blur free. In reality, however, the presence
+of motion blur in a video sequence is often unavoidable. To this end,
+Wu et al.~\cite{Wu:2011} proposed the Blur-driven Tracker (BLUT)
+framework for tracking motion-blurred targets. BLUT is based on the
+observation that although motion blur degrades the visual features of
+the target, it may also provide useful cues about the movements to
+help tracking.
 
-The BLUT framework successfully tracks a blurred target when there is uniform motion
-and the position of the tracked object does not change drastically in successive
-frames. However, as we will demonstrate in Section 4, the erratic motion from the quadcopters as well as the problem of dropped video frames is too problematic to be successively tracked.
+The BLUT framework successfully tracks a blurred target when there is
+uniform motion, and the position of the tracked object does not change
+drastically in successive frames. However, as we will demonstrate in
+Section~ 4, {\it the erratic motion from the quadcopters, as well as the
+problem of dropped video frames makes the task too problematic for
+BLUT to successfully track.}
+%to be successively tracked.
 
@@
 
-We begin by first motivating the need for a new blur resistant fiducial by examining
-the performance of prior fiducials under motion blur.  After this, we detail
-our design as well as the detection algorithm used to find our marker in an image.
+We begin by first motivating the need for a new blur resistant
+fiducial by examining the performance of prior fiducials under motion
+blur.  After this, we detail our design as well as the detection
+algorithm used to find the fiducial in an image, or a video sequence.
 
-\subsection{Examining Prior Fiducials Under Motion Blur}\label{sec:blurtest}
+\subsection{Prior Fiducials Under Motion Blur}\label{sec:blurtest}
 
-Here we examine the the performance of two
-popular fiducials under motion blur.  Specifically we examine ARTags
-~\cite{Fiala05} and PiTags~\cite{Pitag13} given their difference in geometric
-design and the availability of API to develop applications to recognize the tags.
-RUNE-tag~\cite{runetag11} currently does not provide access to the an
+Here we examine the the performance of two popular fiducials under
+motion blur.  Specifically we examine ARTags ~\cite{Fiala05} and
+PiTags~\cite{Pitag13} given their differences in geometric design and
+the availability of an API to develop applications to recognize the tags.
+\footnote{RUNE-tag~\cite{runetag11} currently does not provide access to  an
 implementation to generate or recognize its tags.  The circular data
-matrix~\cite{NaimarkF02} is available as a commercial product, however it
-requires proprietary hardware to recognize the fiducial.
+matrix~\cite{NaimarkF02} is available as a commercial product, however
+it requires proprietary hardware.}
 
-To evaluate the ARTag and PiTag under blur, we simulate the appearance of the
-marker as seen by a quadcopter by scaling the tags to 150$\times$150 pixels.
+%To evaluate the ARTag and PiTag under blur, 
+For controlled study, we simulate the appearance of the ARTag and PiTag
+markers by scaling the tags to 150$\times$150 pixels.
 Both fiducials are then blurred using linear motion blur at various
 orientations with different  blur scales. The blur motion ranged from 15 to 50
-in magnitude (denoted in pixels), representing small to significant motion
-blur. Figure \ref{fig:artag_pitag} shows the visual appearance of the blurred
+in magnitude (measured in pixels), representing small to significant motion
+blur. Figure~\ref{fig:artag_pitag} shows the visual appearance of the blurred
 tags. We then try to detect the markers using the ALVAR library~\cite{alvar} and
-PiTag library~\cite{ros_pitag}. The table in the right side of
-Figure~\ref{fig:artag_pitag} shows the recognition rate (in percentage) of two
-fiducial markers at various blur scales over all the different orientations.
+PiTag library~\cite{ros_pitag}. The table in %the right side of
+Figure~\ref{fig:artag_pitag} shows the recognition rate (in
+percentage) of the two
+fiducial markers at various blur scales over all  orientations.
 As we can see, the PiTag performance quickly diminishes under small amounts of
-blur, while at 35 motion blur, the ARTag's recognition rate drops to less than
+blur, while at 35 units, the ARTag's recognition rate drops to less than
 20\%.
 
-\noindent\begin{figure}
-\includegraphics[width=\linewidth]{artag_pitag.pdf}
+\begin{figure}[t!]
+\includegraphics[width=\linewidth]{images/artag_pitag.pdf}
 %\captionof{figure}{Blurred ARTag and Pi--tag with various blur scales}
 %\captionof{table}{Recognition rate of ARTag and Pi-tag fiducial marker atvarious blur scales}
+
 \begin{tabularx}{\linewidth}{|Y|Y|Y|}
@@
 \end{tabularx}
-\captionof{figure}{Figure showing PiTag and ARTag blurred with various blur
-scales at different orientations. Table on the right shows the recognition rate
-(in percent) of both fiducial markers at various blur scales along all blur
-orientations.  Recognition rates for both tags are significantly reduced due to
-blur. For severe blur, detection is not possible.}
+\captionof{figure}{\textbf{Top:} The PiTag and ARTag fiducials blurred
+  with various blur scales at different orientations. \textbf{Bottom
+    Table:} Recognition rate (in percent). We see that the recognition
+  rates for both the tags are significantly reduced. For severe blur,
+  detection fails.}
 \label{fig:artag_pitag}
@@
 
-We have designed a binary coded fiducial that uses concentric white rings of
-equal widths on a black background with a blurred border\footnote{This design
-can be inverted to have a white background with white rings.}. The
-outermost and innermost rings represent the start and end of the code and is
-embedded in the fiducial.  The binary code is represented by the presence (or
-absence) of rings between ``marker'' rings.
+We propose a binary coded fiducial that uses concentric white rings of
+equal widths on a black background with a blurred
+border\footnote{Obviously, this design can be inverted to have a white
+  background with black rings.}. The outermost and innermost rings
+represent the start and end of the code and is embedded in the
+fiducial.  The binary code is represented by the presence (or absence)
+of rings between ``marker'' rings.
 
@@
 \centering
-  \includegraphics[width=.24\linewidth]{newconcentric_00.pdf}
-  \includegraphics[width=.24\linewidth]{newconcentric_01.pdf}
-  \includegraphics[width=.24\linewidth]{newconcentric_10.pdf}
-  \includegraphics[width=.24\linewidth]{newconcentric_11.pdf}
-  \caption{Two bit binary coded fiducials (from left to right: binary code 00,
-  binary code 01, binary code 10, binary code 11.)}
+  \includegraphics[width=.24\linewidth]{images/newconcentric_00.pdf}
+  \includegraphics[width=.24\linewidth]{images/newconcentric_01.pdf}
+  \includegraphics[width=.24\linewidth]{images/newconcentric_10.pdf}
+  \includegraphics[width=.24\linewidth]{images/newconcentric_11.pdf}
+  \caption{Two bit, binary  fiducials, representing, from left to
+    right 00, 01, 10, and 11.}
   \label{fig:fiducials}
@@
 
-Depending on which ring is present or absent, the resulting binary code will
-change. The number of different patterns depends on the number of bits in the
-binary code. For example, if the binary code has three bits, there will be a
-maximum of three rings between marker-rings and we end up with eight
-different patterns.  Figure \ref{fig:fiducials} shows two bit binary coded
-fiducials.
+Depending on which ring is present or absent, the resulting binary
+code will change. The number of different patterns depends on the
+number of bits in the binary code. For example, if the binary code has
+three bits, there will be a maximum of three rings between marker
+rings and we end up with eight different patterns.
+Figure~\ref{fig:fiducials} shows two bit binary fiducials.
 
-\subsection{Fiducial Detection Algorithm}
+Our fiducial detection strategy is different from
+\cite{NaimarkF02,Pitag13} and works under significant amounts of blur.
+As previously mentioned, our approach works under the observation that
+the motion blur for the quadcopter's camera can be well modeled as
+linear motion.  This linear motion blur assumption has been shown to
+be reasonable in prior works~\cite{Moshe:2003,Moshe:2004}
+targeting camera motion blur. Under this assumption, the scene
+content perpendicular to the blur direction is unaffected by the blur.
+Because of our circular design, the direction perpendicular to the
+linear motion will still be recognizable as a linear pattern.
+Figure~\ref{fig:blur_direction} shows examples of this using a pattern
+under 
+various motion directions.
 
-\begin{figure}
+\begin{figure}[h!]
 \centering
-\includegraphics[width=\linewidth]{blur_direction.pdf}
-\caption{Figure showing how change in blur direction changes the location of
-unblurred linear pattern.}
+\includegraphics[width=\linewidth]{images/blur_direction}
+\caption{Change in blur direction changes the location and orientation
+  of an unblurred linear pattern.}
 \label{fig:blur_direction}
@@
 
-Our fiducial detection strategy is different from \cite{NaimarkF02,Pitag13} and works
-under significant amounts of blur.   As previously mentioned, our approach works
-under the observation that the motion blur for the quadcopter's camera
-can be well modelled as linear motion.  This  linear motion blur assumption has
-been shown to be reasonable in prior works targeting camera motion blur
-(e.g.~\cite{Moshe:2003,Moshe:2004}). Under this assumption, the scene content
-perpendicular to the blur direction is unaffected by the blur.  Because of our
-circular design, the direction perpendicular to the linear motion will still be
-recognizable as a linear pattern.  Figure \ref{fig:blur_direction} shows
-examples of this using a pattern under various motion directions.
+\subsection{Detection Algorithm}
 
-Figure \ref{fig:overall_flow} shows the process involved in fiducial
-detection. We give a brief overview of our algorithm here with each step described
-in detail afterwards.  Our detection algorithm has four steps. Step 1,
-we apply a Gabor filter on the image to isolate the
-potential locations of the pattern.  Step 2, we find the clusters of patches
-found in the Gabor output by clustering.  Step 3, performs Principal
-Component Analysis (PCA) on each cluster to find the dominant direction
-unaffected by blur.  Step 4, based on the direction we extract the intensity
-profile of the pattern and classify the code using a K-Nearest Neighbor
-classifier based on training data.
+Figure~\ref{fig:overall_flow} shows the process involved in fiducial
+detection. We give a brief overview of our algorithm here with each
+step described in detail afterwards.  Our detection algorithm has four
+steps. In Step~1, we apply a Gabor filter on the image to isolate the
+potential locations of the pattern.  In Step~2, we find clusters of
+patches in the Gabor output.  In Step~3, we perform Principal
+Component Analysis (PCA) on each cluster to find the dominant
+direction unaffected by blur.  Finally in Step~4, based on the
+direction detected, we extract the intensity profile of the pattern
+and classify the fiducial.
 
@@
   \centering
-\includegraphics[width=0.8\linewidth]{overall_flow.pdf}
-\caption{An overview of our algorithm to detect and classify fiducial.
-The four step process includes (Step 1) Gabor filtering,
-(Step 2) component clustering, (Step 3) PCA to determine the dominant direction,
-and (Step 4) K-NN classification using training-data captured for each pattern.}
+  \includegraphics[width=0.8\linewidth]{images/overall_flow.pdf}
+  \caption{An overview of our algorithm.
+    The four step process includes (Step 1) Filtering,
+    (Step 2) Component clustering, (Step 3) Dominant direction determination
+    and (Step 4) Classification using prior training data.}
   \label{fig:overall_flow}
@@
 
-\noindent Details of each of the steps are as follows:\\
-\noindent\textbf{Gabor filter}~~A 2D Gabor filter is a Gaussian kernel function
+%\noindent Details of each of the steps are as follows:\\
+\textbf{Gabor filter}~~A 2D Gabor filter is a Gaussian kernel function
 modulated by a sinusoidal plane wave~\cite{Kruizinga:2002}. It is used to find
-high gradient patches from the image. In our case, it is used to detect portions
+high gradient patches. In our case, it is used to detect portions
 of the circular fiducials that were not affected by the blur.
 We applied the Gabor filter in eight
-different orientations ($\theta = 0, 45, 90, \ldots ,225, 270, 315$).  The
+different orientations ($\theta = 0, 45, 90, \ldots, 225, 270, 315$).  The
 following parameters were used for creating each Gabor kernel: $\lambda$ (wavelength) $= 8$, $\gamma$
@@
 
-\noindent\textbf{Clustering}~~The binarized Gabor filter responses are
+\textbf{Clustering}~~The binarized Gabor filter responses are
 treated as a set of connected components in the image.   Clustering
@@
 
-\noindent\textbf{PCA}~~For each clustered set of components, we apply
-PCA to determine the dominant direction.  This is done by examining the
-orientation of the first principal component.  We then extract an intensity
-profile patch in the input image along this direction as it extends through the
-bounding box of the cluster. The signature of this profile will be used to
-identify the code.
+\textbf{PCA}~~For each clustered set of components, we apply
+PCA to determine the dominant direction.  This is done by examining
+the orientation of the first principal component.  We then extract an
+intensity profile patch in the input image along this direction as it
+extends through the bounding box of the cluster. The signature of this
+profile will be used to identify the code.
 
-After finding the intensity profile, we examine it by
-projecting the pixel intensities onto the PCA direction and record the
-number and width of the white-to-black transitions.  If the number of transitions or the
-width of the transitions are not consistent with what is allowable by
-our code, we reject the clustered region as a potential fiducial.
-Clustered components that have allowable transitions counts and transitions with
-uniform widths are further considered for classification to determine
-the binary code.
+After finding the intensity profile, we project the pixel intensities,
+and record the number and width of the white-to-black transitions.  If
+the number of transitions, or the width of the transitions is not
+consistent with what is allowable by our code, we reject the clustered
+region as a potential fiducial.  Clustered components that have
+allowable transitions counts and transitions with uniform widths are
+further considered for classification to determine the binary code.
 
-\noindent\textbf{Classification}~~As mentioned above, a small image patch
-containing the intensity profile of the fiducial is used to identify the code.   We found
-that a training-based method using K-NN gave better results than trying to
-find binary code directly by determining the presence (or absence) of ring
-at particular positions in the image patch. To build the training-data, a
-synthetic fiducial pattern is blurred along 36 orientations (0, 10, 20, \ldots
-, 350) with blur scale set to 40, and its intensity profile along the first
-principal component from every output is taken as training data for that
-fiducial pattern. Figure \ref{fig:training_data} shows the process of creating
-training data for fiducial with binary code ``01'' embedded in it.  For an
-input image patch, we normalize its intensity range and then compare it against
-the training-data. The class label from the closest top $K=5$ images in the
-training-data is used to label the patch.
+\textbf{Classification}~~As mentioned above, a small image patch
+containing the intensity profile of the fiducial is used to identify
+which of the many fiducials might be present and is represented by a
+code.  We found that a training-based method using the k nearest
+neighbor (k-NN) technique gave better results than trying to find
+binary code directly by determining the presence (or absence) of ring
+at particular positions in the image patch. This required
+training-data which was easy to generate. A synthetic fiducial pattern
+is blurred along 36 orientations (0, 10, 20, \ldots , 350) with blur
+scale set to 40, and the intensity profile along the first principal
+component from every output is taken as training data for that
+fiducial pattern. Figure~\ref{fig:training_data} shows the process of
+creating training data for fiducial with binary code ``01'' embedded
+in it.  For a query image patch, we normalize the intensity range, and
+then compare this information against the training data. The class
+label from the closest top $K=5$ images in the training data is used
+to label the patch.
 
@@
 \centering
-  \includegraphics[width=0.95\linewidth]{training_data.pdf}
-  \caption{Process to create training data for the fiducial pattern with binary
-  code ``01''. The synthetic pattern is blurred along various orientations. Gabor
-  filter is applied on the blurred pattern. Intensity profile is found along the
-  first principal component of the clustered Gabor output. Same process is used
-  to create training data for other fiducial patterns.}
+  \includegraphics[width=0.95\linewidth]{images/training_data.pdf}
+  \caption{Creating training data for the fiducial pattern with binary
+  code ``01'': The synthetic pattern is blurred along various
+  orientations and the intensity profile monitored and stored. The
+  same process is used to create training data for all other fiducials.}
   \label{fig:training_data}
@@
 We have implemented our algorithm in C++ using the OpenCV library.
-Experiments were performed on a PC with Intel Core i7 processor(@3.4GHz) and 4GB RAM.
-Source code to generate and recognize the code, as well as the data sets used in
-this paper will be made publicly available.
-%Video clips of collected data are provided in the supplementary material.
+Experiments were performed on a laptop with Intel Core i7
+processor(@3.4GHz) and 4GB RAM.  Source code to generate and recognize
+the code, as well as the data sets used in this paper will be made
+publicly available.
+%Video clips of collected data are provided in the supplementary
+%material.
+% Meghshyam: Is it a desktop PC or a laptop?
 
-Our system has been tested on several image sequences captured from an AR Drone
-quadcopter.  The drone was flown indoors looking at patterns attached to
-various walls. Each image sequence contains frames of different fiducial
-patterns. Sample output for each fiducial pattern is shown in Figure
-\ref{fig:out_outputs}. Our detection process takes around 0.3 seconds which
-translates to slightly over three frames per second.
+Our system has been tested on several image sequences captured from an
+AR Drone quadcopter.  The drone was flown indoors looking at patterns
+attached to various walls. Each image sequence contains frames of
+different fiducials. Some sample outputs for each fiducial pattern
+is shown in Figure~\ref{fig:out_outputs}. Our detection process takes
+around 0.3 seconds which translates to slightly over three frames per
+second.
 
-Our system has also been tested on images containing multiple fiducial patterns
-in the same frame. Our algorithm can successfully detected all fiducial patterns as
-well as correctly classified them as shown in Figure \ref{fig:output_all}.
+\begin{figure}[h!]
+\centering
+  \includegraphics[width=0.4\linewidth]{images/output_00.jpg}
+  \includegraphics[width=0.4\linewidth]{images/output_01.jpg}
 
-\begin{figure}[hb!]
-\centering
-  \includegraphics[width=0.4\linewidth]{output_00.jpg}
-  \includegraphics[width=0.4\linewidth]{output_01.jpg}
-  \includegraphics[width=0.4\linewidth]{output_10.jpg}
-  \includegraphics[width=0.4\linewidth]{output_11.jpg}
-  \caption{Sample outputs for two bit binary coded fiducials on different
-  datasets. Class label attached to the detected fiducial is decimal equivalent
-  of the binary code embedded in the detected fiducial.}
+  \includegraphics[width=0.4\linewidth]{images/output_10.jpg}
+  \includegraphics[width=0.4\linewidth]{images/output_11.jpg}
+  \caption{Sample outputs. The class label shown is the decimal equivalent
+  of the binary coded fiducial.}
   \label{fig:out_outputs}
@@
 
+Our system has also been tested on images containing multiple fiducial
+patterns in the same frame. Our algorithm can successfully detected
+all fiducial patterns as well as correctly classified them as shown in
+Figure \ref{fig:output_all}.
+
 \begin{figure}[ht!]
 \centering
-  \includegraphics[width=.45\linewidth]{output_all_2.jpg}
-  \includegraphics[width=.45\linewidth]{new_results/output_test_all1.jpg}
-  \caption{Sample outputs containing all two bit binary coded fiducial patterns
-  in single frame}
+  \includegraphics[width=.45\linewidth]{images/output_all_2.jpg}
+  \includegraphics[width=.45\linewidth]{images/new_results/output_test_all1.jpg}
+  \caption{Multiple fiducials in the same frame can be efficiently
+    detected. }
   \label{fig:output_all}
@@
 
-\subsection{Comparisons}
+%\subsection{Comparisons}
 
@@
 our results with Blur-driven tracker (BLUT)\cite{Wu:2011}.
-\subsubsection{Comparison with ARTag}
-First, we have repeated the blur simulation experiment on our fiducials as reported
-in Section~\ref{sec:blurtest}.  Specifically, we build our blur resistant
-patterns at 150$\times$150 pixel resolution and blurred them along various
-orientations with different blur scales. Then, we tried to detect our fiducial using a 2-bit
-patterns using algorithm presented in earlier section.
 
-The comparison of recognition rate is shown in Figure
-\ref{fig:simulated_blur}-(a). In this experiment, we use even more blur, up to 65
-pixels. Figure \ref{fig:blur_maximum} shows the patterns under maximum blur they
-can sustain are still be recognized. The graph in Figure
-\ref{fig:simulated_blur}-(a) shows that our recognition is 100\% for all codes
-except the ``00'' which is undetectable after 50 pixels blur (which is still
-significantly better than ARTag).  Reasons for the ``00'' tags lower
-performance is discussed in Section~\ref{sec:discussion}.
+\subsection{Comparison with ARTag}
+First, we repeat the same blur simulation experiment
+(Section~\ref{sec:blurtest}) on the proposed fiducial. Specifically,
+we build our blur resistant patterns at 150$\times$150 pixel
+resolution and blurred them along various orientations with different
+blur scales. 
+%Then, we tried to detect our fiducial using a 2-bit
+%patterns using algorithm presented in earlier section.
 
-We also performed analysis to detect how accurately the center of the blur pattern
-can be localized under blur.  To do this, we have simulated data along different blur
-orientations for all patterns over eight different blur scales (30 to 65 with
-step size of 5). Values for the localization of the pattern ``00'' after blur
-with 50 pixels is omitted since the pattern cannot be detected. From the Table in Figure
-~\ref{fig:simulated_blur}-(b), it can be clearly seen that the mean error in
-locating center by our algorithm is within approximate 3 pixels, or 3\% of the
-diameter of fiducial.
-
-\begin{figure}
-\includegraphics[width=\linewidth]{blur_maximum.pdf}
-\caption{Result of our fiducial detection algorithm on blur simulated data.
-Detection result is shown on each of our fiducial pattern, blurred at the
-maximum scale it can handle.}
+\begin{figure}[t!]
+  \includegraphics[width=\linewidth]{images/blur_maximum.pdf}
+  \caption{On synthetic experiments, we increase the blur much beyond
+    the best possible results (see Figure~\ref{fig:artag_pitag}) for
+    prior methods. Even upto 65 units, the algorithm is successful.}
   \label{fig:blur_maximum}
@@
 
-\noindent\begin{figure*}
+Qualitatively we see in Figure~\ref{fig:blur_maximum} that despite
+even more blur than earlier described (50 units or more) detection is
+still feasible and practical.  Quantitatively, the comparison of
+recognition rate is shown in Figure~\ref{fig:recognition_rate}.
+Even under more severe blur, of 65 pixels, the algorithm is
+successful.  Our recognition is 100\% for all codes except the ``00''
+which is undetectable after 50 pixels blur (which is still
+significantly better than ARTag).  Reasons for the lower performance
+when``00'' tags are present is discussed in
+Section~\ref{sec:discussion}.
+
+\begin{figure}[h!]
+\centering
+\includegraphics[width=\linewidth]{images/recognition_rate.pdf}  
+\caption{Comparison of recognition rate of fiducials.  The proposed
+  fiducial handsomely outperforms prior methods.}
+\label{fig:recognition_rate}
+\end{figure}
+
+We also performed analysis to detect how accurately the center of the
+blur pattern can be localized under blur.  To do this, we have
+simulated data along different blur orientations for all patterns over
+eight different blur scales (30 to 65 with step size of 5). Values for
+the localization of the pattern ``00'' after blur with 50 pixels is
+omitted since the pattern cannot be detected. From
+Table~\ref{tab:blur_angle_center}, it can be clearly seen that the 
+mean error in locating center by our algorithm is within approximate 3
+pixels, or 3\% of the diameter of fiducial.
+
+\begin{table}[h!]
+  \centering
+  \begin{tabularx}{\linewidth}{|c|Y|}
+    \cline{1-2}
+    \footnotesize{Blur} & \footnotesize{Mean($\pm$std) error}  \\
+    \footnotesize{angle} & \footnotesize{(in pixels)}  \\
+    \cline{1-2}
+    \footnotesize{0} & \footnotesize{1.33 $\pm$ 0.40}  \\
+    \footnotesize{22} & \footnotesize{2.42 $\pm$ 1.05} \\
+    \footnotesize{45} & \footnotesize{1.46 $\pm$ 0.65}  \\
+    \footnotesize{67} & \footnotesize{2.39 $\pm$ 1.28}  \\
+    \footnotesize{90} & \footnotesize{1.83 $\pm$ 0.25}  \\
+    \cline{1-2}
+  \end{tabularx}
+    \caption{Center localization error.
+      Error is computed for various blur angles over various scales.}
+    \label{tab:blur_angle_center}
+\end{table}
+
+\begin{comment}
+\begin{figure*}
 \centering
@@
 \centering
-\includegraphics[width=\linewidth]{recognition_rate.pdf}
+\includegraphics[width=\linewidth]{images/recognition_rate.pdf}
 \caption{Comparison of recognition rate of fiducials}
@@
 \end{figure*}
+\end{comment}
 
-We also compared results on the recorded feed using AR Drone quadcopter. In our
-experimental setup, we have placed two ARTags in the scene along with our fiducial  to
-compare the resilience of blur by each fiducial type. We have used
-ar\_track\_alvar, ROS Wrapper for the ALVAR library~\cite{ros_alvar}, to detect
-the ARTags from the stream captured with the quadcopter camera. In each test
-dataset, we have used different two bit binary coded fiducial and recorded
-video of around two minute duration (i.e., around 1000 frames).   The
-quadcopter was flown in a routine manner in the room with its camera facing the
-wall (see supplementary videos). The comparison of the recognition rate is
-shown in Table \ref{tab:recongition_accuracy}. Recognition rate of our
-fiducials ranges from 86.5\% to 94.1\%, while the ARTag is 60.3\% to 65.6\%.
-Classification accuracy of all fiducials (ARTag as well as ours) was
-approximately 100\%, i.e., when tags were detected they were the correct
-fiducials and not other objects in the scene.
+\subsection{Real Data}
+
+We also compared results on the recorded feed using the AR Drone
+quadcopter. In our experimental setup, we have placed two ARTags in
+the scene along with our fiducial to compare the resilience of blur by
+each fiducial type. We have used ar\_track\_alvar, ROS Wrapper for the
+ALVAR library~\cite{ros_alvar}, to detect the ARTags from the stream
+captured with the quadcopter camera. In each test dataset, we have
+used different two bit binary coded fiducial and recorded video of
+around two minute duration (i.e., around 1000 frames).  The quadcopter
+was flown in a routine manner in the room with its camera facing the
+wall (see supplementary videos). The comparison of the recognition
+rate is shown in Table~\ref{tab:recognition_accuracy}. Recognition
+rate of our fiducials ranges from 86.5\% to 94.1\%, while the ARTag is
+60.3\% to 65.6\%.  Classification accuracy of all fiducials (ARTag as
+well as ours) was approximately 100\%, i.e., when tags were detected
+they were the correct fiducials and not other objects in the scene.
 
 \begin{table}[t!]
-\caption{Comparison of recognition rate of ARTag and our fiducials on real
-data captured through AR Drone. Each row shows analysis of a test
-dataset captured for our fiducial with different binary code embedded in it.
-Each dataset has around 1000 frames captured representing roughly two minutes of video each.}
   \centering
@@
   \end{tabularx}
-\label{tab:recongition_accuracy}
+  \caption{  \label{tab:recognition_accuracy}
+Recognition rate of ARTag and propsosed fiducials on real
+    data captured through AR Drone. Each row shows analysis of a test
+    dataset captured for our fiducial with different binary codes embedded in it.
+    Each dataset has around 1000 frames captured representing roughly two
+    minutes of video.} 
 \end{table}
 
-In another setup we arranged our fiducials on four sides of a box and revolved
-the quadcopter around the box. Later, we repeated the process by replacing our fiducial
-by ARTags. Figure \ref{fig:setup} some frames from this sequence as well as the performance of both fiducials. The overall detection rate of our tags is 90\% while that of ARTags is only around 60\%.
+In another setup we arranged our fiducials on four sides of a box and
+revolved the quadcopter around the box. Later, we repeated the process
+by replacing our fiducial by ARTags. Figure~\ref{fig:setup} some
+frames from this sequence as well as the performance of both
+fiducials. The overall detection rate of our tags is 90\% while that
+of ARTags is only around 60\%.
 
@@
 \begin{subfigure}[b]{.19\textwidth}
-\includegraphics[width=\linewidth]{setup_artag/output_79.jpg}
+\includegraphics[width=\linewidth]{images/setup_artag/output_79.jpg}
 \end{subfigure}
 \begin{subfigure}[b]{.19\textwidth}
-\includegraphics[width=\linewidth]{setup_artag/output_150.jpg}
+\includegraphics[width=\linewidth]{images/setup_artag/output_150.jpg}
 \end{subfigure}
 \begin{subfigure}[b]{.19\textwidth}
-\includegraphics[width=\linewidth]{setup_artag/output_194.jpg}
+\includegraphics[width=\linewidth]{images/setup_artag/output_194.jpg}
 \end{subfigure}
 \begin{subfigure}[b]{.19\textwidth}
-\includegraphics[width=\linewidth]{setup_artag/output_339.jpg}
+\includegraphics[width=\linewidth]{images/setup_artag/output_339.jpg}
 \end{subfigure}
 \begin{subfigure}[b]{.19\textwidth}
-\includegraphics[width=\linewidth]{setup_artag/output_480.jpg}
+\includegraphics[width=\linewidth]{images/setup_artag/output_480.jpg}
 \end{subfigure}\\
 \begin{subfigure}[b]{.19\textwidth}
-\includegraphics[width=\linewidth]{setup_our/output_6/output_514.jpg}
+\includegraphics[width=\linewidth]{images/setup_our/output_6/output_514.jpg}
 \end{subfigure}
 \begin{subfigure}[b]{.19\textwidth}
-\includegraphics[width=\linewidth]{setup_our/output_2/output_64.jpg}
+\includegraphics[width=\linewidth]{images/setup_our/output_2/output_64.jpg}
 \end{subfigure}
 \begin{subfigure}[b]{.19\textwidth}
-\includegraphics[width=\linewidth]{setup_our/output_2/output_35.jpg}
+\includegraphics[width=\linewidth]{images/setup_our/output_2/output_35.jpg}
 \end{subfigure}
 \begin{subfigure}[b]{.19\textwidth}
-\includegraphics[width=\linewidth]{setup_our/output_2/output_330.jpg}
+\includegraphics[width=\linewidth]{images/setup_our/output_2/output_330.jpg}
 \end{subfigure}
 \begin{subfigure}[b]{.19\textwidth}
-\includegraphics[width=\linewidth]{setup_our/output_6/output_943.jpg}
+\includegraphics[width=\linewidth]{images/setup_our/output_6/output_943.jpg}
 \end{subfigure}\\
 \begin{subfigure}[b]{\textwidth}
-\includegraphics[width=\linewidth]{compare_detection.jpg}
+\includegraphics[width=\linewidth]{images/compare_detection.jpg}
 \end{subfigure}
-\caption{Figure showing comparison of detection of ARTag versus our fiducial
-when quadcopter is revolving around our setup.
-Top row shows ARTags are not getting detected while middle row shows in
-similar condition our tags are getting detected. Overall detection rate of our
-tags is 90\% while that of ARTags is around 60\%. In bottom, comparison of
-detection of two type of tags over time is shown. We can see that ARTag is
-``chopped off'' frequently while our tag is detected continuously.}
+\caption{Comparison of ARTag and our fiducial when quadcopter is
+  revolving around our setup. 
+\textbf{Top} ARTags are not detected, shown by an absence of green rectangles. \textbf{Middle} In
+similar conditions, proposed fiducials are successfully
+detected. Overall detection rate of proposed
+fiducials is 90\% while that of ARTags is around 60\%. 
+\textbf{Bottom Rows} Time view of detection. ARTag is ``choppy'' with
+frequent losses, while the proposed fiducial (extreme bottom) is
+``up'' almost all the 
+time.}
 \label{fig:setup}
@@
 
-We also compare our approach with tracking designed for blurred input scenes.
-We have used four image sequences (consisting of around 1000 frames each), each
-one containing a different blur resistant fiducial pattern to test the performance of
-BLUT \cite{Wu:2011} and compare it with our result on the same image sequence.
-From the images in the top rows of Figure
-\ref{fig:BLUT_compare_00} and \ref{fig:BLUT_compare_01}, we can see that BLUT is
-able to track the fiducial when the position of fiducial does not change too
-much in successive frames. Also, it can be seen that once BLUT looses
-track of the fiducial, it is not able to recover. Since our approach detects the
-code in each frame, large changes in the patterns position is not an issue.
-Some of our detection results are also shown in Figure
-\ref{fig:BLUT_compare_00} and \ref{fig:BLUT_compare_01}.
+We also compare our approach with tracking designed for blurred input
+scenes.  We have used four image sequences (consisting of around 1000
+frames each). Each sequence contains different fiducials so that we
+are able to contrast the performance of BLUT~\cite{Wu:2011} with the
+proposed method.  From the images in the top rows of
+Figure~\ref{fig:BLUT_compare_00} and Figure~\ref{fig:BLUT_compare_01},
+we can see that BLUT is able to track the fiducial when the position
+of fiducial does not change too much in successive frames. Also, it
+can be seen that once BLUT loses track of the fiducial, it is not
+able to recover. Since our approach detects the code in each frame,
+large changes in the patterns position is not an issue.  Some of our
+detection results are also shown in Figure~\ref{fig:BLUT_compare_00}
+and Figure~\ref{fig:BLUT_compare_01}.
 
-We have also found that even if we reset the BLUT tracker after loosing track,
-it will loose track again after around 100 frames, that is approximately within
-6 seconds. When we checked the timestamp data from image header captured through
-the AR Drone, we found that, there was a difference of 0.14 seconds between two
-successive frames in the earlier case, which clearly indicates the dropping of
-video frame (e.g., normal 30fps should be 0.033 seconds). Also, there were around 50
-instances in 1000 frames where the timestamp difference between two successive
-frames was greater than 0.1 seconds. As such, it appears one of the main
-culprits causing the BLUT tracker to fail is the dropping of frames combined
-with unstable motion of quadcopter resulting in large discrepancies in the
-patterns position between successive frames.
+We have also found that even if we reset the BLUT tracker after it
+loses track, the tracker will once again malfunction after around 100
+frames (approximately within 6 seconds). When we checked the timestamp
+data from image header captured through the AR Drone, we found that,
+there was a difference of 0.14 seconds between two successive frames
+indicating the dropping of video frame (normal 30fps should have a gap
+of 0.033 seconds). Also, there were around 50 instances in 1000 frames
+where the timestamp difference between two successive frames was
+greater than 0.1 seconds. As such, it appears one of the main culprits
+causing the BLUT tracker to fail is the dropping of frames combined
+with the unstable motion of quadcopter, resulting in large discrepancies in
+the  position of the fiducial between successive frames.
 
@@
 \begin{subfigure}[b]{.19\textwidth}
-\includegraphics[width=\linewidth]{BLUT_output_00/2.jpg}
+\includegraphics[width=\linewidth]{images/BLUT_output_00/2.jpg}
 \end{subfigure}
 \begin{subfigure}[b]{.19\textwidth}
-\includegraphics[width=\linewidth]{BLUT_output_00/3.jpg}
+\includegraphics[width=\linewidth]{images/BLUT_output_00/3.jpg}
 \end{subfigure}
 \begin{subfigure}[b]{.19\textwidth}
-\includegraphics[width=\linewidth]{BLUT_output_00/4.jpg}
+\includegraphics[width=\linewidth]{images/BLUT_output_00/4.jpg}
 \end{subfigure}
 \begin{subfigure}[b]{.19\textwidth}
-\includegraphics[width=\linewidth]{BLUT_output_00/5.jpg}
+\includegraphics[width=\linewidth]{images/BLUT_output_00/5.jpg}
 \end{subfigure}
 \begin{subfigure}[b]{.19\textwidth}
-\includegraphics[width=\linewidth]{BLUT_output_00/6.jpg}
+\includegraphics[width=\linewidth]{images/BLUT_output_00/6.jpg}
 \end{subfigure}\\
 \begin{subfigure}[b]{.19\textwidth}
-\includegraphics[width=\linewidth]{BLUT_input_00/output2.jpg}
+\includegraphics[width=\linewidth]{images/BLUT_input_00/output2.jpg}
 \end{subfigure}
 \begin{subfigure}[b]{.19\textwidth}
-\includegraphics[width=\linewidth]{BLUT_input_00/output3.jpg}
+\includegraphics[width=\linewidth]{images/BLUT_input_00/output3.jpg}
 \end{subfigure}
 \begin{subfigure}[b]{.19\textwidth}
-\includegraphics[width=\linewidth]{BLUT_input_00/output4.jpg}
+\includegraphics[width=\linewidth]{images/BLUT_input_00/output4.jpg}
 \end{subfigure}
 \begin{subfigure}[b]{.19\textwidth}
-\includegraphics[width=\linewidth]{BLUT_input_00/output5.jpg}
+\includegraphics[width=\linewidth]{images/BLUT_input_00/output5.jpg}
 \end{subfigure}
 \begin{subfigure}[b]{.19\textwidth}
-\includegraphics[width=\linewidth]{BLUT_input_00/output6.jpg}
+\includegraphics[width=\linewidth]{images/BLUT_input_00/output6.jpg}
 \end{subfigure}
-\caption{Top: Output of BLUT~\cite{Wu:2011} on sample image sequence containing ``00''
-binary coded fiducial. Bottom: Output of our algorithm on the same image
-sequence. BLUT is able to track the fiducial till the third frame, but from fourth
-frame BLUT looses track of the fiducial. In first three frames, the size of the
-fiducials is less but in fourth and fifth frame it is bigger, hinting at a sudden
-forward movement of quadcopter.}
+\caption{\textbf{Top:} Output of BLUT~\cite{Wu:2011}. \textbf{Bottom:}
+  Output of our algorithm on the same image 
+  sequence. BLUT is able to track the fiducial till the third frame,
+  but from the fourth frame onwards, BLUT loses track. In the first
+  three frames, the size of the  bounding box is low, but in the fourth
+  and fifth frame it is large, indicating a sudden forward movement
+  of the quadcopter.} 
 \label{fig:BLUT_compare_00}
@@
 \begin{subfigure}[b]{.19\textwidth}
-\includegraphics[width=\linewidth]{BLUT_output_01/11.jpg}
+\includegraphics[width=\linewidth]{images/BLUT_output_01/11.jpg}
 \end{subfigure}
 \begin{subfigure}[b]{.19\textwidth}
-\includegraphics[width=\linewidth]{BLUT_output_01/12.jpg}
+\includegraphics[width=\linewidth]{images/BLUT_output_01/12.jpg}
 \end{subfigure}
 \begin{subfigure}[b]{.19\textwidth}
-\includegraphics[width=\linewidth]{BLUT_output_01/13.jpg}
+\includegraphics[width=\linewidth]{images/BLUT_output_01/13.jpg}
 \end{subfigure}
 \begin{subfigure}[b]{.19\textwidth}
-\includegraphics[width=\linewidth]{BLUT_output_01/14.jpg}
+\includegraphics[width=\linewidth]{images/BLUT_output_01/14.jpg}
 \end{subfigure}
 \begin{subfigure}[b]{.19\textwidth}
-\includegraphics[width=\linewidth]{BLUT_output_01/15.jpg}
+\includegraphics[width=\linewidth]{images/BLUT_output_01/15.jpg}
 \end{subfigure}\\
 \begin{subfigure}[b]{.19\textwidth}
-\includegraphics[width=\linewidth]{BLUT_input_01/output11.jpg}
+\includegraphics[width=\linewidth]{images/BLUT_input_01/output11.jpg}
 \end{subfigure}
 \begin{subfigure}[b]{.19\textwidth}
-\includegraphics[width=\linewidth]{BLUT_input_01/output12.jpg}
+\includegraphics[width=\linewidth]{images/BLUT_input_01/output12.jpg}
 \end{subfigure}
 \begin{subfigure}[b]{.19\textwidth}
-\includegraphics[width=\linewidth]{BLUT_input_01/output13.jpg}
+\includegraphics[width=\linewidth]{images/BLUT_input_01/output13.jpg}
 \end{subfigure}
 \begin{subfigure}[b]{.19\textwidth}
-\includegraphics[width=\linewidth]{BLUT_input_01/output14.jpg}
+\includegraphics[width=\linewidth]{images/BLUT_input_01/output14.jpg}
 \end{subfigure}
 \begin{subfigure}[b]{.19\textwidth}
-\includegraphics[width=\linewidth]{BLUT_input_01/output15.jpg}
+\includegraphics[width=\linewidth]{images/BLUT_input_01/output15.jpg}
 \end{subfigure}
-\caption{Top: Output of BLUT~\cite{Wu:2011} on sample image sequence containing
-``01'' binary coded fiducial. Bottom: Output of our algorithm on the same image
-sequence. BLUT looses the track from the third frame.}
+\caption{{\bf Top:} Output of BLUT~\cite{Wu:2011} on a sequence containing
+the ``01'' binary coded fiducial. {\bf Bottom:} Output of our
+algorithm on the same image 
+sequence. BLUT loses  track from the third frame onwards.}
 \label{fig:BLUT_compare_01}
@@
 \begin{subfigure}[b]{.19\textwidth}
-\includegraphics[width=\linewidth]{BLUT_output_10/1.jpg}
+\includegraphics[width=\linewidth]{images/BLUT_output_10/1.jpg}
 \end{subfigure}
 \begin{subfigure}[b]{.19\textwidth}
-\includegraphics[width=\linewidth]{BLUT_output_10/2.jpg}
+\includegraphics[width=\linewidth]{images/BLUT_output_10/2.jpg}
 \end{subfigure}
 \begin{subfigure}[b]{.19\textwidth}
-\includegraphics[width=\linewidth]{BLUT_output_10/3.jpg}
+\includegraphics[width=\linewidth]{images/BLUT_output_10/3.jpg}
 \end{subfigure}
 \begin{subfigure}[b]{.19\textwidth}
-\includegraphics[width=\linewidth]{BLUT_output_10/4.jpg}
+\includegraphics[width=\linewidth]{images/BLUT_output_10/4.jpg}
 \end{subfigure}
 \begin{subfigure}[b]{.19\textwidth}
-\includegraphics[width=\linewidth]{BLUT_output_10/5.jpg}
+\includegraphics[width=\linewidth]{images/BLUT_output_10/5.jpg}
 \end{subfigure}\\
 \begin{subfigure}[b]{.19\textwidth}
-\includegraphics[width=\linewidth]{BLUT_input_10/output1.jpg}
+\includegraphics[width=\linewidth]{images/BLUT_input_10/output1.jpg}
 \end{subfigure}
 \begin{subfigure}[b]{.19\textwidth}
-\includegraphics[width=\linewidth]{BLUT_input_10/output2.jpg}
+\includegraphics[width=\linewidth]{images/BLUT_input_10/output2.jpg}
 \end{subfigure}
 \begin{subfigure}[b]{.19\textwidth}
-\includegraphics[width=\linewidth]{BLUT_input_10/output3.jpg}
+\includegraphics[width=\linewidth]{images/BLUT_input_10/output3.jpg}
 \end{subfigure}
 \begin{subfigure}[b]{.19\textwidth}
-\includegraphics[width=\linewidth]{BLUT_input_10/output4.jpg}
+\includegraphics[width=\linewidth]{images/BLUT_input_10/output4.jpg}
 \end{subfigure}
 \begin{subfigure}[b]{.19\textwidth}
-\includegraphics[width=\linewidth]{BLUT_input_10/output5.jpg}
+\includegraphics[width=\linewidth]{images/BLUT_input_10/output5.jpg}
 \end{subfigure}
@@
 \begin{subfigure}[b]{.19\textwidth}
-\includegraphics[width=\linewidth]{BLUT_output_11/2.jpg}
+\includegraphics[width=\linewidth]{images/BLUT_output_11/2.jpg}
 \end{subfigure}
 \begin{subfigure}[b]{.19\textwidth}
-\includegraphics[width=\linewidth]{BLUT_output_11/3.jpg}
+\includegraphics[width=\linewidth]{images/BLUT_output_11/3.jpg}
 \end{subfigure}
 \begin{subfigure}[b]{.19\textwidth}
-\includegraphics[width=\linewidth]{BLUT_output_11/4.jpg}
+\includegraphics[width=\linewidth]{images/BLUT_output_11/4.jpg}
 \end{subfigure}
 \begin{subfigure}[b]{.19\textwidth}
-\includegraphics[width=\linewidth]{BLUT_output_11/5.jpg}
+\includegraphics[width=\linewidth]{images/BLUT_output_11/5.jpg}
 \end{subfigure}
 \begin{subfigure}[b]{.19\textwidth}
-\includegraphics[width=\linewidth]{BLUT_output_11/6.jpg}
+\includegraphics[width=\linewidth]{images/BLUT_output_11/6.jpg}
 \end{subfigure}\\
 \begin{subfigure}[b]{.19\textwidth}
-\includegraphics[width=\linewidth]{BLUT_input_11/output2.jpg}
+\includegraphics[width=\linewidth]{images/BLUT_input_11/output2.jpg}
 \end{subfigure}
 \begin{subfigure}[b]{.19\textwidth}
-\includegraphics[width=\linewidth]{BLUT_input_11/output3.jpg}
+\includegraphics[width=\linewidth]{images/BLUT_input_11/output3.jpg}
 \end{subfigure}
 \begin{subfigure}[b]{.19\textwidth}
-\includegraphics[width=\linewidth]{BLUT_input_11/output4.jpg}
+\includegraphics[width=\linewidth]{images/BLUT_input_11/output4.jpg}
 \end{subfigure}
 \begin{subfigure}[b]{.19\textwidth}
-\includegraphics[width=\linewidth]{BLUT_input_11/output5.jpg}
+\includegraphics[width=\linewidth]{images/BLUT_input_11/output5.jpg}
 \end{subfigure}
 \begin{subfigure}[b]{.19\textwidth}
-\includegraphics[width=\linewidth]{BLUT_input_11/output6.jpg}
+\includegraphics[width=\linewidth]{images/BLUT_input_11/output6.jpg}
 \end{subfigure}
@@
 
-\section{Discussion}\label{sec:discussion}
+\section{Discussion and Limitations}\label{sec:discussion}
 
-We have demonstrated the effectiveness of our blur invariant fiducial both
-synthetically and on real video clips captured from a quadcopter.   Our approach obtains
-approximately 86-95\% recognition rate on fiducals in real scenes compared to existing codes
-that are around 64\%.  We discuss some limitations of our approach in the
-section.
+We have demonstrated the effectiveness of our blur invariant fiducial
+both on synthetic data, and on real video clips captured from a quadcopter.
+Our approach obtains a recognition rate of 86\%--95\% 
+in real scenes compared to existing methods that average around
+64\%.  We discuss some limitations of our approach in this section.
 %\noindent\textbf{Processing Time}~~
+
 Our  current processing time (0.3 seconds per frame) does not provide
-real-time performance.  As such, we envision this will be used in an
+real-time performance.  As such, we envision the method will be used in an
 offline manner for performing analysis of flight paths. Code profiling revealed
@@
 %\noindent\textbf{False Negatives}~~
-We found that sometimes our detection
-algorithm fails to recognize our fiducial with binary code ``00'' when there is
-large amount of blur.  The is because when there is too much blur, the innermost
-ring's response in the Gabor output is too low and not detected properly.
-This problem can be resolved by increasing the radius of innermost ring to
-reduce the effect of blur on the innermost ring.
+
+We found that sometimes our detection algorithm fails to recognize the
+``00'' fiducial, when there is severe blur.  The is because when there
+is too much blur, the innermost ring's response in the Gabor output is
+too low and not detected properly.  This problem can be resolved by
+increasing the radius of innermost ring to reduce the effect of blur
+on the innermost ring.
 %\noindent\textbf{Pose Estimation}~~
-We note that other markers are able to give
-full pose estimation after detection.  However, we are only able to reliably detect
-the center point and therefore cannot estimate pose.  Of course, if four
-markers were used in a known order, pose could be estimated. The current
-resolution of onboard camera will be main hurdle to clear before we can
-effectively use multiple markers in each scene.
+
+We note that other markers are able to give full pose estimation after
+detection.  However, we are only able to reliably detect the center
+point and therefore cannot estimate pose.  Of course, if four markers
+were used in a known order, pose could be estimated. The current
+resolution of onboard camera is a significant  hurdle to clear before we
+can effectively use multiple markers in each scene.
 %\noindent\textbf{Number of Fiducials}~~
-Currently, compared to ARTag fiducial markers, we are able to generate less
-number of fiducials. Many applications in robotics (e.g. quadcopter navigation)
-may not require large number of fiducial markers as available by ARTag.  Most
-of the time, it is sufficient to have 4-6 different fiducial patterns. Still,
-we may be able to generate a larger number of fiducials by using color
-backgrounds. This is an area of interest for further investigation.
+
+In terms of numbers of fiducials, we are able to generate less markers
+than ARTag. Many applications in robotics (e.g. quadcopter navigation)
+may not require simultaneous use of a large number of fiducials.  Most
+of the time, it is sufficient to have 4-6 different
+fiducials. Nevertheless, we may be able to generate a larger number of
+fiducials by using color backgrounds. This is an area of interest for
+further investigation.
 
@@
 
-Quadcopters are subject to quick and unstable motions that can cause significant
-motion blur in the captured images. This severely affects the detection rate of
-existing fiducial markers. We proposed the design of a fiducial that is
-resistant to motion blur. Our design of contrasting concentric rings is based on the
-observation that the direction perpendicular to the motion blur direction will
-be unaffected by the blur and therefore still be recognizable. We have shown
-through experimental validation that our fiducial will work under large
-amounts of motion blur and can significantly outperform existing fiducial
-markers under this scenario.
+Quadcopters are subject to quick and unstable motions that can cause
+significant motion blur in the captured images. This severely affects
+the detection rate of existing fiducial markers. We proposed the
+design of a fiducial that is resistant to motion blur. Our design of
+contrasting concentric rings is based on the observation that the
+direction perpendicular to the motion blur direction will be
+unaffected by the blur and therefore still be recognizable. We have
+shown through experimental validation that our fiducial will work
+under large amounts of motion blur and can significantly outperform
+existing fiducial markers under this scenario.
 

### 2014-06-09 WACV/paper.tex
Done changes suggested by Prof. Sharat.

@@
 \begin{document}
-\title{A Motion Blur Resilient Fiducial Marker For Quadcopter Imaging}
+\title{A Motion Blur Resilient Fiducial For Quadcopter Imaging}
 \maketitle
@@
 
-  Fiducial markers are commonly placed in environments to provide a
+  fiducials are commonly placed in environments to provide a
   uniquely identifiable object in the scene.  In quadcopter
@@
   motions that can cause significant motion blur that severely affects
-  the detection rate of existing fiducial markers. This problem
+  the detection rate of existing fiducials. This problem
   motivated us to design a fiducial that is robust to motion blur. Our
@@
   circular design is good for all motion blur directions. We describe
-  the design of binary fiducial markers, and also a detection
+  the design of binary fiducials, and also a detection
   algorithm.  We show that our marker can significantly outperform
-  existing fiducial markers in scenes captured with a quadcopter.
+  existing fiducials in scenes captured with a quadcopter.
 
@@
 that uses visual cues in the real world. However, to evaluate the
-effectiveness of navigation methods, one or more fiducial markers are commonly
+effectiveness of navigation methods, one or more fiducials are commonly
 placed~\cite{Bosnak:2012,Lim09,Klopschitz:2007}
@@
 
-In order to be effective, fiducial markers (or simply, fiducials) need
-to be easily detected in the scene. A variety of fiducial markers have
+In order to be effective, fiducials (or simply, fiducials) need
+to be easily detected in the scene. A variety of fiducials have
 been proposed~\cite{NaimarkF02,ARToolkit02,Fiala05,Pitag13,runetag11}
@@
 problem of tracking. Section~3 motivates our fiducial design by
-analysing the performance of existing codes under motion blur, and
+analyzing the performance of existing codes under motion blur, and
 describes our detection algorithm. Section~4 shows several
@@
 
-Our work is related to two areas: fiducial markers and object tracking. We
+Our work is related to two areas: fiducials and object tracking. We
 briefly discuss work done in both areas.
@@
 \textbf{Fiducials:}~Figure~\ref{fig:previous_work} shows a few
-examples of existing fiducial markers.  Many designs use a two
+examples of existing fiducials.  Many designs use a two
 dimensional barcode inside a rectangular grid. One example of such a
@@
  \end{subfigure}
- \caption{Prior fiducial markers and our proposal.  While
+ \caption{Prior fiducials and our proposal.  While
  each code has its pros and cons depending on the environment, no
@@
 %Zhang et al.\cite{Zhang:2002} and Claus et al. \cite{ClausF04} have done
-%quite comprehensive comparative study of various fiducial marker systems with
+%quite comprehensive comparative study of various fiducial systems with
 %respect to processing time, recognition rate and accuracy with
@@
 percentage) of the two
-fiducial markers at various blur scales over all  orientations.
+fiducials at various blur scales over all  orientations.
 As we can see, the PiTag performance quickly diminishes under small amounts of
@@
 %\captionof{figure}{Blurred ARTag and Pi--tag with various blur scales}
-%\captionof{table}{Recognition rate of ARTag and Pi-tag fiducial marker atvarious blur scales}
+%\captionof{table}{Recognition rate of ARTag and Pi-tag fiducial at various blur scales}
 
@@
 one).  For further details to the Gabor filter, see~\cite{Kruizinga:2002}.
-%% MBS - is the Kruizinga filter resonable to cite?
+%% MBS - is the Kruizinga filter reasonable to cite?
 
@@
 at particular positions in the image patch. This required
-training-data which was easy to generate. A synthetic fiducial pattern
+training-data which was easy to generate. A synthetic fiducial
 is blurred along 36 orientations (0, 10, 20, \ldots , 350) with blur
@@
 component from every output is taken as training data for that
-fiducial pattern. Figure~\ref{fig:training_data} shows the process of
+fiducial. Figure~\ref{fig:training_data} shows the process of
 creating training data for fiducial with binary code ``01'' embedded
@@
   \includegraphics[width=0.95\linewidth]{images/training_data.pdf}
-  \caption{Creating training data for the fiducial pattern with binary
+  \caption{Creating training data for the fiducial with binary
   code ``01'': The synthetic pattern is blurred along various
@@
 attached to various walls. Each image sequence contains frames of
-different fiducials. Some sample outputs for each fiducial pattern
+different fiducials. Some sample outputs for each fiducial
 is shown in Figure~\ref{fig:out_outputs}. Our detection process takes
@@
 patterns in the same frame. Our algorithm can successfully detected
-all fiducial patterns as well as correctly classified them as shown in
+all fiducials as well as correctly classified them as shown in
 Figure \ref{fig:output_all}.
@@
   \centering
-  \begin{tabularx}{\linewidth}{|c|Y|}
+  \begin{tabularx}{0.6\linewidth}{|Y|Y|}
     \cline{1-2}
@@
 blur simulated data at various blur scales. It can be seen that except for the
-fiducial with binary code ``00'', our fiducial patterns are recognized all times.
+fiducial with binary code ``00'', our fiducials are recognized all times.
 (b): Table showing the mean error and standard deviation of the localized fiducial center
@@
   \caption{  \label{tab:recognition_accuracy}
-Recognition rate of ARTag and propsosed fiducials on real
+Recognition rate of ARTag and proposed fiducials on real
     data captured through AR Drone. Each row shows analysis of a test
@@
 of fiducial does not change too much in successive frames. Also, it
-can be seen that once BLUT loses track of the fiducial, it is not
+can be seen that once BLUT looses track of the fiducial, it is not
 able to recover. Since our approach detects the code in each frame,
@@
   sequence. BLUT is able to track the fiducial till the third frame,
-  but from the fourth frame onwards, BLUT loses track. In the first
+  but from the fourth frame onwards, BLUT looses track. In the first
   three frames, the size of the  bounding box is low, but in the fourth
@@
 algorithm on the same image 
-sequence. BLUT loses  track from the third frame onwards.}
+sequence. BLUT looses  track from the third frame onwards.}
 \label{fig:BLUT_compare_01}
@@
 In terms of numbers of fiducials, we are able to generate less markers
-than ARTag. Many applications in robotics (e.g. quadcopter navigation)
+than ARTag. Many applications in robotics (e.g., quadcopter navigation)
 may not require simultaneous use of a large number of fiducials.  Most
@@
 significant motion blur in the captured images. This severely affects
-the detection rate of existing fiducial markers. We proposed the
+the detection rate of existing fiducials. We proposed the
 design of a fiducial that is resistant to motion blur. Our design of
@@
 under large amounts of motion blur and can significantly outperform
-existing fiducial markers under this scenario.
+existing fiducials under this scenario.
 

### 2014-06-09 WACV/paper.tex
Proof read, made footnote in one page.
Looses to loses

@@
 \setlength{\intextsep}{5pt plus 2pt minus 2pt}
+\interfootnotelinepenalty=10000
 % Include other packages here, before hyperref.
@@
 
-  fiducials are commonly placed in environments to provide a
+Fiducials are commonly placed in environments to provide a
 uniquely identifiable object in the scene.  In quadcopter
@@
 the availability of an API to develop applications to recognize the tags.
-\footnote{RUNE-tag~\cite{runetag11} currently does not provide access to  an
-implementation to generate or recognize its tags.  The circular data
-matrix~\cite{NaimarkF02} is available as a commercial product, however
-it requires proprietary hardware.}
+\footnote{RUNE-tag~\cite{runetag11} currently does not
+provide access to an implementation to generate or recognize its tags. 
+The circular data matrix~\cite{NaimarkF02} is available as a
+commercial product, however it requires proprietary hardware.}
 
@@
 Figure~\ref{fig:artag_pitag} shows the recognition rate (in
-percentage) of the two
-fiducials at various blur scales over all  orientations.
+percentage) of the two fiducials at various blur scales over all  orientations.
 As we can see, the PiTag performance quickly diminishes under small amounts of
@@
 of fiducial does not change too much in successive frames. Also, it
-can be seen that once BLUT looses track of the fiducial, it is not
+can be seen that once BLUT loses track of the fiducial, it is not
 able to recover. Since our approach detects the code in each frame,
@@
   sequence. BLUT is able to track the fiducial till the third frame,
-  but from the fourth frame onwards, BLUT looses track. In the first
+  but from the fourth frame onwards, BLUT loses track. In the first
   three frames, the size of the  bounding box is low, but in the fourth
@@
 algorithm on the same image 
-sequence. BLUT looses  track from the third frame onwards.}
+sequence. BLUT loses  track from the third frame onwards.}
 \label{fig:BLUT_compare_01}
@@
 ``10'' binary coded fiducial. Bottom: Output of our algorithm on the same image
-sequence. From the second frame, BLUT looses track.}
+sequence. From the second frame, BLUT loses track.}
 \label{fig:BLUT_compare_10}

### 2014-06-13 WACV/paper.tex
Proof reading changes

@@
 
-In order to be effective, fiducials (or simply, fiducials) need
+In order to be effective, fiducial markers (or simply, fiducials) need
 to be easily detected in the scene. A variety of fiducials have
@@
 quadcopters often exhibit very quick and erratic physical movements
-that result in motion blur in the quadcopter's onboard camera. This
-motion blur has an adverse effect on the recognition of fiducial
+that result in motion blur in the captured images from the quadcopter's onboard
+camera. This motion blur has an adverse effect on the recognition of fiducial
 markers. This can be seen in Figure \ref{fig:teaser}--(b) where the
@@
 
-{\textbf{Tracking}}~~Fiducial detection between successive video
+{\textbf{Tracking:}}~~Fiducial detection between successive video
 frames can be considered as a tracking problem where the tracked
@@
 
-Here we examine the the performance of two popular fiducials under
+Here we examine the performance of two popular fiducials under
 motion blur.  Specifically we examine ARTags ~\cite{Fiala05} and
@@
 %\noindent Details of each of the steps are as follows:\\
-\textbf{Gabor filter}~~A 2D Gabor filter is a Gaussian kernel function
+\textbf{Gabor filter:}~~A 2D Gabor filter is a Gaussian kernel function
 modulated by a sinusoidal plane wave~\cite{Kruizinga:2002}. It is used to find
@@
 
-\textbf{Clustering}~~The binarized Gabor filter responses are
+\textbf{Clustering:}~~The binarized Gabor filter responses are
 treated as a set of connected components in the image.   Clustering
@@
 
-\textbf{PCA}~~For each clustered set of components, we apply
+\textbf{PCA:}~~For each clustered set of components, we apply
 PCA to determine the dominant direction.  This is done by examining
@@
 
-\textbf{Classification}~~As mentioned above, a small image patch
+\textbf{Classification:}~~As mentioned above, a small image patch
 containing the intensity profile of the fiducial is used to identify
@@
 Our system has also been tested on images containing multiple fiducial
-patterns in the same frame. Our algorithm can successfully detected
+patterns in the same frame. Our algorithm successfully detected
 all fiducials as well as correctly classified them as shown in
@@
 
-Qualitatively we see in Figure~\ref{fig:blur_maximum} that despite
+Qualitatively we see in Figure~\ref{fig:blur_maximum} that despite of
 even more blur than earlier described (50 units or more) detection is
@@
 revolved the quadcopter around the box. Later, we repeated the process
-by replacing our fiducial by ARTags. Figure~\ref{fig:setup} some
+by replacing our fiducial by ARTags. Figure~\ref{fig:setup} shows some
 frames from this sequence as well as the performance of both
@@
 able to recover. Since our approach detects the code in each frame,
-large changes in the patterns position is not an issue.  Some of our
+large changes in the pattern's position is not an issue.  Some of our
 detection results are also shown in Figure~\ref{fig:BLUT_compare_00}
@@
 We found that sometimes our detection algorithm fails to recognize the
-``00'' fiducial, when there is severe blur.  The is because when there
+``00'' fiducial, when there is severe blur.  This is because when there
 is too much blur, the innermost ring's response in the Gabor output is
@@
 fiducials by using color backgrounds. This is an area of interest for
-further investigation.
+further research.
 

### 2014-06-15 WACV/paper.tex
Proof-reading changes

@@
 quadcopters often exhibit very quick and erratic physical movements
-that result in motion blur in the captured images from the quadcopter's onboard
+that result in motion blur evidenced in the images captured from the quadcopter's onboard
 camera. This motion blur has an adverse effect on the recognition of fiducial
@@
 
-Qualitatively we see in Figure~\ref{fig:blur_maximum} that despite of
-even more blur than earlier described (50 units or more) detection is
+Qualitatively, we see in Figure~\ref{fig:blur_maximum} that despite of
+even more blur than earlier described (50 units or more), detection is
 still feasible and practical.  Quantitatively, the comparison of
@@
 significantly better than ARTag).  Reasons for the lower performance
-when``00'' tags are present is discussed in
+when``00'' tags are present, is discussed in
 Section~\ref{sec:discussion}.
@@
 was flown in a routine manner in the room with its camera facing the
-wall (see supplementary videos). The comparison of the recognition
+wall. The comparison of the recognition
 rate is shown in Table~\ref{tab:recognition_accuracy}. Recognition
@@
 In another setup we arranged our fiducials on four sides of a box and
-revolved the quadcopter around the box. Later, we repeated the process
-by replacing our fiducial by ARTags. Figure~\ref{fig:setup} shows some
+revolved the quadcopter around the box (see the supplementary video). Later, we
+repeated the process by replacing our fiducial by ARTags. Figure~\ref{fig:setup} shows some
 frames from this sequence as well as the performance of both

### 2014-11-07 DetectFiducial/src/ConnectedComponents.cpp
Removed unnecessary code

@@ -1,389 +1,16 @@
-///////////////////////////////////////////////////////////////////////////////////////
-//
-//  IMPORTANT: READ BEFORE DOWNLOADING, COPYING, INSTALLING OR USING.
+/*
+ * ConnectedComponents.cpp
+ *
+ *  Created on: Jan 28, 2014
+ *      Author: meghshyam
+ */
 
-//
-//  By downloading, copying, installing or using the software you agree to this license.
-//  If you do not agree to this license, do not download, install,
-//  copy or use the software.
-//
-//
-//                        Intel License Agreement
-//                For Open Source Computer Vision Library
-//
-// Copyright (C) 2000, Intel Corporation, all rights reserved.
-// Third party copyrights are property of their respective owners.
-//
-// Redistribution and use in source and binary forms, with or without modification,
-// are permitted provided that the following conditions are met:
-//
-//   * Redistribution's of source code must retain the above copyright notice,
-//     this list of conditions and the following disclaimer.
-//
-//   * Redistribution's in binary form must reproduce the above copyright notice,
-//     this list of conditions and the following disclaimer in the documentation
-//     and/or other materials provided with the distribution.
-//
-//   * The name of Intel Corporation may not be used to endorse or promote products
-//     derived from this software without specific prior written permission.
-//
-// This software is provided by the copyright holders and contributors "as is" and
-// any express or implied warranties, including, but not limited to, the implied
-// warranties of merchantability and fitness for a particular purpose are disclaimed.
-// In no event shall the Intel Corporation or contributors be liable for any direct,
-// indirect, incidental, special, exemplary, or consequential damages
-// (including, but not limited to, procurement of substitute goods or services;
[…]

### 2014-11-10 WACV/paper.tex
WACV Final Copy
Added links to project web page and You Tube video.

@@
 
-%\wacvfinalcopy % *** Uncomment this line for the final submission
+\wacvfinalcopy % *** Uncomment this line for the final submission
 
@@
 \title{A Motion Blur Resilient Fiducial For Quadcopter Imaging}
+
+\author{Meghshyam G. Prasad\\
+Dept. of Computer Science, IIT Bombay\\
+{\tt\small meghshyam@cse.iitb.ac.in}
+\and
+Sharat Chandran\\
+Dept. of Computer Science, IIT Bombay\\
+{\tt\small sharat@cse.iitb.ac.in}
+\and
+Michael S. Brown\\
+School of Computing, NUS\\
+{\tt\small brown@comp.nus.edu.sg}
+}
 \maketitle
@@
 Experiments were performed on a laptop with Intel Core i7
-processor(@3.4GHz) and 4GB RAM.  Source code to generate and recognize
-the code, as well as the data sets used in this paper will be made
-publicly available.
+processor(@3.4GHz) and 4GB RAM. (Please check author's webpage
+\url{http://www.comp.nus.edu.sg/~mgprasad/fiducial/} for details of source code
+and all datasets)
 %Video clips of collected data are provided in the supplementary
@@
   \includegraphics[width=0.4\linewidth]{images/output_11.jpg}
-  \caption{Sample outputs. The class label shown is the decimal equivalent
-  of the binary coded fiducial.}
+  \caption{Output of our fiducial detection algorithm on sample images. The
+  class label shown is the decimal equivalent of the binary coded fiducial.}
   \label{fig:out_outputs}
@@
 In another setup we arranged our fiducials on four sides of a box and
-revolved the quadcopter around the box (see the supplementary video). Later, we
-repeated the process by replacing our fiducial by ARTags. Figure~\ref{fig:setup} shows some
+revolved the quadcopter around the box (See video uploaded at \cite{video}).
+Later, we repeated the process by replacing our fiducial by ARTags. Figure~\ref{fig:setup} shows some
 frames from this sequence as well as the performance of both

### 2014-12-02 DetectFiducial/src/main.cpp
Changed some parameters to suit multiple tag detection

@@ -131,6 +131,7 @@ int main(int argc, char* argv[])
 	CvKNearest knn(trainingData, response, Mat(), false, K);
 
 	Mat output = input.clone();
+	bool found_one = false;
 	for(int i=0; i<numClusters; i++)
 	{
 		float * row = (float *)&clusters.at<float>(i,0);
@@ -161,6 +162,7 @@ int main(int argc, char* argv[])
 		string str = "Class:";
 		if(found)
 		{
+			found_one=true;
 			rectangle(output, pt1, pt2, Scalar(0,255,0), 3);
 			if(num_rings ==1 ){
 				Mat sample(1, 100, DataType<float>::type);
@@ -180,18 +182,18 @@ int main(int argc, char* argv[])
 				Mat dist(K, 1, DataType<float>::type);
 				knn.find_nearest (sample, K, results, responses, dist);
 				int class_id = results.at<float>(0);
-				cout<<"Class:"<<class_id<<"\n";
+				cout<<"Class:"<<class_id;
 				classid[0] = class_id+48;
 				classid[1] = '\0';
 				str.append(classid);
 			}
 			else{
 				if(num_rings == 0){
-					cout<<"Class:"<<0<<"\n";
+					cout<<"Class:0";
 					str.append("0");
 				}
 				else if(num_rings == 2){
-					cout<<"Class:"<<3<<"\n";
+					cout<<"Class:3";
 					str.append("3");
 				}
 			}
@@ -200,18 +202,19 @@ int main(int argc, char* argv[])
 			rectangle(output,pt_text_start, pt_text_end, Scalar(0,255,255),-1);
 			putText(output, str, pt2, FONT_HERSHEY_DUPLEX, 0.75, Scalar(0,0,255));
 			circle(output, center, 1, Scalar(0,0,255), -1, 8, 0);
-			break;
+			//break;
 		}
 	}
 	//imshow("output", output);
 	waitKey();
-	cout<<"Center:"<<center<<"\n";
+	//cout<<"Center:"<<center<<"\n";
 	imwrite("output.jpg", output);
-	if(!found){
+	if(!found_one){
 		cout<<"Code not detected\n";
 	}else{
 		//cout<<"Code detected\n";
 		//Classify the detected code
+		cout<<"\n";
 	}
 #else
 	int x1 = 0;
@@ -457,7 +460,7 @@ bool detectCode(const Mat &pts, int left, int top, int right, int bottom, const 
[…]

### 2014-12-02 WACV/paper.tex
Merging Prof. Sharat's changes

@@
 
-\author{Meghshyam G. Prasad\\
-Dept. of Computer Science, IIT Bombay\\
-{\tt\small meghshyam@cse.iitb.ac.in}
-\and
-Sharat Chandran\\
-Dept. of Computer Science, IIT Bombay\\
-{\tt\small sharat@cse.iitb.ac.in}
+\author{Meghshyam G. Prasad  \&  Sharat Chandran\\
+Dept. of Computer Science and Engineering, IIT Bombay\\
+{\tt\small \{meghshyam,sharat\}@cse.iitb.ac.in}
+% \and
+% Sharat Chandran\\
+% Dept. of Computer Science, IIT Bombay\\
+% {\tt\small sharat@cse.iitb.ac.in}
 \and
@@
 In another setup we arranged our fiducials on four sides of a box and
-revolved the quadcopter around the box (See video uploaded at \cite{video}).
+revolved the quadcopter around the box (See  \cite{video}).
 Later, we repeated the process by replacing our fiducial by ARTags. Figure~\ref{fig:setup} shows some
